### 2018-03-15 DiagrammeR/slide.Rmd
update

---
title: "報告"
subtitle: "副標題"
author: Yongfu Liao
date: March 13, 2018
output:
  ioslides_presentation:
    fig_height: 3
    css: ../presentation_style.css
    incremental: false
    logo: tux.svg
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment="")
library(DiagrammeR)
```

## 中文

- **粗體**
- <div class="red2">蘋方?</div>

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

A Graph
```{r fig_retina=1}
grViz('
digraph { //directed graph
    "總攻" -> "受";
    "強攻" -> "受";
    "健氣攻" -> "受";
     }'
)
```

## Slide with Plot {.smaller}

```{r echo=TRUE}
grViz('
digraph { //directed graph
    "總攻" -> "受";
    "強攻" -> "受";
    "健氣攻" -> "受";
     }'
)
```

### 2018-03-15 DiagrammeR/graphviz_syntax.R

@@ -1,0 +1,15 @@
+grViz('
+digraph { //directed graph
+    "總攻" -> "受";
+    "強攻" -> "受";
+    "健氣攻" -> "受";
+     }'
+)
+
+grViz('
+graph { //non-directed graph
+    "總 攻" -- "受";
+    "強 攻" -- "受";
+    "健氣攻" -- "受";
+     }'
+)

### 2018-03-17 DiagrammeR/slide.Rmd
update

@@
 ```{r fig_retina=1}
-grViz('
-digraph { //directed graph
-    "總攻" -> "受";
-    "強攻" -> "受";
-    "健氣攻" -> "受";
-     }'
-)
+grViz("
+graph { //non-directed graph
+    graph [layout = neato]  //layout = dot|neato|twopi|circo|fdp
+
+    node [shape = circle,
+          style = filled,
+          color = orange]
+
+    node [fillcolor = red]
+    a [label = '受']
+
+    node [fillcolor = orange1]  //orange1-4
+    b [label = '總攻']
+    c [label = '強攻']
+    d [label = '健氣攻']
+
+    edge [color = grey]
+    {b c d} -- a
+    }")
 ```

### 2018-03-17 DiagrammeR/graphviz_syntax.R

@@ -1,15 +1,28 @@
-grViz('
-digraph { //directed graph
-    "總攻" -> "受";
-    "強攻" -> "受";
-    "健氣攻" -> "受";
-     }'
-)
+library(DiagrammeR)
 
-grViz('
-graph { //non-directed graph
-    "總 攻" -- "受";
-    "強 攻" -- "受";
-    "健氣攻" -- "受";
-     }'
-)
+var <- 1:3
+
+grViz("
+digraph { //non-directed graph
+      graph [layout = neato]  //layout = dot|neato|twopi|circo|fdp
+      
+      node [shape = circle,
+      style = filled,
+      color = orange]
+      
+      node [fillcolor = red]
+      a [label = '受']
+      
+      node [fillcolor = orange1]  //orange1-4
+      b [label = '@@1-1']
+      c [label = '@@1-2']
+      d [label = '@@1-3']
+      
+      edge [color = grey, arrowhead = none, arrowtail = none]
+      {b c d} -> a
+      }
+      
+      # Comments for Ref: vector of length=3
+      [1]: paste('Number: ', var, sep='')   
+
+      ")

### 2018-03-17 DiagrammeR/slide.Rmd
update

@@
     fig_height: 3
-    css: ../presentation_style.css
+    css: ../style_sheets/presentation_style.css
     incremental: false

### 2018-03-19 DiagrammeR/rmd_features.rmd
update

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    css: ../style_sheets/style.css
    df_print: kable
    code_folding: show
---
<!--more-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## yaml Setup {.tabset}

### Citation

Include the code in yaml header.

```{yaml}
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl
link-citations: yes
```

### HTML Output Options

Include the code in yaml header.
```{yaml}
output:
  html_document:
    df_print: kable
    code_folding: hide
    fig_width: 7
    fig_height: 6
```

## Dynamic Variables

Include **R Code Chunks' Variables** in the body of text.

```{r}
alpha <- 1:3
text <- c("a", "b")
```

1. The numeric variable $\alpha =$ `r alpha[1]`.
    ```{yaml}
    # The numeric variable $\alpha =$ `r alpha[1]`.
    ```

2. The string variable $text =$ `r text[1]`.
    ```{yaml}
    # The string variable $text =$ `r text[1]`.
    ```

## $\LaTeX$ Rendering {.tabset}

### kable
```{r}
library(knitr)
library(dplyr)
iris_data <- head(iris) %>% select(Sepal.Length, Sepal.Width)

colnames(iris_data) <- c("$\\alpha$", "$\\frac{a}{b}$")
kable(iris_data, format = "markdown", align = "c")
```

### Plotting Expression
```{r}
library(latex2exp)
library(ggplot2)
iris_data2 <- iris[c(1:3, 50:53, 100 :103),] %>% select(Sepal.Length, Sepal.Width, Species)

iris_data2 %>% ggplot() +
    geom_point(mapping = aes(x=Sepal.Length, y=Sepal.Width, color=Species))+
    labs(x=TeX("Length($\\frac{kg}{cm^2}$)"),
         y=TeX("\\frac{a}{b}"))
```

## Citations 
To include **Citations**[^1], [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.

The text cited [@RN9].

@RN15 主張...

### Include `.bib` file in Reference {.tabset}

#### Specific References
Include specific references, which are **not cited** in the body of text.
```{pandoc}
---
nocite: |
  @item1, @item2
...
```

#### All References
Include **All references** in the body of text.
```{pandoc}
---
nocite: |
  @*
...
```

## Emphasis {.tabset}

### Full Example
```{html}
<div class="success">
| This is pragraph 1. [**Red text**]{.red}, line 1. The text[^2] is abcd 中文
| This is [line two]{style="color:rgba(255, 0, 0, 1)"}.

Paragraph 2 starts here.
</div>
```

<div class="success">
| This is [**Red text**]{.red}, line 1. The text[^2] is abcd 中文
| This is [line two]{style="color:rgba(255, 0, 0, 1)"}.

Paragraph.
</div>

### Colored divs
There are 4 choices of class: 
1. success
2. info
3. warning
4. error
```{html}
<div class="success">
    some text in the colored region
</div>
```

[^1]: This is footnote 1.

[^2]: This is footnote 2.

    long footnotes.

<!-- syntax of pandoc: reference will be added here --> 
# References

### 2018-03-19 DiagrammeR/slide.Rmd
update

@@
 - **粗體**
-- <div class="red2">蘋方?</div>
+- [紅色2]{.red2}
+- [**color=red**]{style="color:#8A2BE2"}
 
+<div class="error">
 When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+</div>
 
@@
 - Bullet 3
+
+<div class="notes">
+This is my *note*.
+
+- It can contain markdown
+- like this list
+
+</div>
 
@@
 grViz('
+### <b>
 digraph { //directed graph
+### </b>
     "總攻" -> "受";
@@
 ```
+
+## Dataframe Printing
+```{r}
+knitr::kable(head(iris), align = "c", format = "markdown")
+```

### 2018-03-19 DiagrammeR/rmd_features.rmd
update

@@
     code_folding: show
+    toc: true
+    toc_depth: 4
+    toc_float: true
 ---
@@
 	message = FALSE,
-	warning = FALSE
+	warning = FALSE,
+	dev='svg'
 )
@@
 ### Plotting Expression
-```{r}
+```{r fig.height=3}
 library(latex2exp)
@@
 ## Citations 
-To include **Citations**[^1], [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.
+To include **Citations**, [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.
 
@@
 <div class="success">
-| This is pragraph 1. [**Red text**]{.red}, line 1. The text[^2] is abcd 中文
-| This is [line two]{style="color:rgba(255, 0, 0, 1)"}.
+| This is pragraph one. [**Red text**]{.red}, line 1. Text text text text.
+| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
 
-Paragraph 2 starts here.
+Paragraph two starts here.
 </div>
@@
 <div class="success">
-| This is [**Red text**]{.red}, line 1. The text[^2] is abcd 中文
-| This is [line two]{style="color:rgba(255, 0, 0, 1)"}.
+| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
+| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
 
-Paragraph.
+Paragraph two starts here.
 </div>
@@
 ### Colored divs
-There are 4 choices of class: 
+There are 4 choices of classes, defined in my stylesheet[^css]:
+
 1. success
-2. info
+2. warning
 3. warning
 4. error
+
 ```{html}
-<div class="success">
+<div class="error">
 some text in the colored region
@@
 
-[^1]: This is footnote 1.
+<div class="error">
+some text in the colored region
+</div>
 
-[^2]: This is footnote 2.
+### New Line
+```{markdown}
+| Text of line 1
+| Text of line 2
 
-    long footnotes.
+New paragraph
+```
 
-<!-- syntax of pandoc: reference will be added here --> 
-# References
+<div class="warning">
+| Text of line 1
+| Text of line 2
+
+New paragraph
+</div>
+
+### Attach Attributes
+By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.
+
+#### `class`
+```{markdown}
+[**Red Bold text**]{.red}
+```
+<div class="warning">
+[**Red Bold text**]{.red}
+</div>
+
+Note[^red].
+
+#### Other Attributes
+```{markdown}
+Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
+```
+<div class="warning">
+Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
+</div>
+
+## Footnotes with Paragraphs
+Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
+
+Look at a long footnote[^longnote]
+```{markdown}
+[^longnote]: Here's one with multiple blocks.
+
+    Subsequent paragraphs are indented to show that they
+belong to the previous footnote.
+
+    In this way, multi-paragraph footnotes work like multi-paragraph list items.
+```
+
+## Shaped Images {.tabset}
+
+### Rounded Edge
+```{html}
+<div class="rounded">
+![](../icons/jekyll_dark.ico){width=auto height="30%"}
+</div>
+```
+<div class="rounded">
+![](../icons/jekyll_dark.ico){width=auto height="30%"}
+</div>
+
+### Circle Image
+```{html}
+<div class="circle">
+![](../icons/jekyll_dark.ico){width=auto height="30%"}
+</div>
+```
+<div class="circle">
+![](../icons/jekyll_dark.ico){width=auto height="30%"}
+</div>
+
+<!-- footnotes -->
+[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.
+
+[^longnote]: Here's one with multiple blocks.
+
+    Subsequent paragraphs are indented to show that they
+belong to the previous footnote.
+
+    In this way, multi-paragraph footnotes work like multi-paragraph list items.
+
+[^red]: `.red` is also a self-defined class in my stylesheet.
+<!-- footnotes -->
+
+<!-- syntax for Reference section --> 
+## References

### 2018-03-20 DiagrammeR/slide.Rmd
update

@@
     css: ../style_sheets/presentation_style.css
-    incremental: false
+    incremental: true
+    transition: 0.4
     logo: tux.svg
@@
 
-## 中文
+Part 1
+==================
+
+## 中文 {.build}
 
@@
 </div>
+
+Part 2
+==================
 

### 2018-03-20 DiagrammeR/rmd_features.rmd
update

@@
 ## yaml Setup {.tabset}
+Include the code in yaml header.
 
@@
 
-Include the code in yaml header.
 ```{yaml}
@@
   html_document:
+    css: ../style_sheets/style.css
     df_print: kable
@@
     fig_height: 6
+    toc: true
+    toc_depth: 4
+    toc_float: true
 ```
@@
 library(dplyr)
-iris_data <- head(iris) %>% select(Sepal.Length, Sepal.Width)
+iris_data <- head(iris) %>%
+    select(Sepal.Length, Sepal.Width)
 
@@
 library(ggplot2)
-iris_data2 <- iris[c(1:3, 50:53, 100 :103),] %>% select(Sepal.Length, Sepal.Width, Species)
+iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
+    select(Sepal.Length, Sepal.Width, Species)
 
 iris_data2 %>% ggplot() +
-    geom_point(mapping = aes(x=Sepal.Length, y=Sepal.Width, color=Species))+
-    labs(x=TeX("Length($\\frac{kg}{cm^2}$)"),
-         y=TeX("\\frac{a}{b}"))
+    geom_point(aes(x = Sepal.Length, 
+                   y = Sepal.Width, 
+                   color = Species)) +
+    labs(x = TeX("Length($\\frac{kg}{cm^2}$)"),
+         y = TeX("\\frac{a}{b}"))
 ```
@@
 
-Look at a long footnote[^longnote]
 ```{markdown}
@@
 ```
+- Output[^longnote].
 

### 2018-03-22 1062_class/eco_model/HW/W2/HW2.rmd
update

---
title: "Ecological Modeling HW2"
author: Yongfu Liao
date: March 22, 2018
output: html_document
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

```c
#include <stdio.h>

int main (void) {
    int age;

    printf("How old are you?\n");
    scanf("%d", &age);
    printf("You are %d years old.\n", age);

    return 0;
}
```

## Question 2

```c
#include <stdio.h>

int main (void) {
    int age;
    double height;

    printf("Please enter your age and height(cm).\n");
    scanf("%d", &age);
    scanf("%lf", &height);

    printf("Your age is %d and your height is %.1f cm.\n", age, height);

    return 0;
}
```

### 2018-03-22 DiagrammeR/rmd_features.rmd
update

@@
 
-#### Specific References
-Include specific references, which are **not cited** in the body of text.
+#### Specific Refs
+Include specific references that were **not cited** in the body of text.
 ```{pandoc}
@@
 
-#### All References
+#### All Refs
 Include **All references** in the body of text.

### 2018-03-22 1062_class/eco_model/HW/W1/Q1.c

@@ -1,0 +1,9 @@
+#include <stdio.h>
+
+int main (void) {
+	printf("How are you? \n"); 
+	printf("Not bad\n");
+	
+	return 0;
+}
+

### 2018-03-22 1062_class/eco_model/HW/W1/Q2.c

@@ -1,0 +1,8 @@
+#include <stdio.h>
+
+int main (void) {
+	printf("%.1f\t%.1f\t%.1f\n", 1.2, 3.4, 0.5);
+	printf("%.1f\t%.1f\t%d\n", 3.5, 6.0, -10);
+
+	return 0;
+}

### 2018-03-22 1062_class/eco_model/HW/W2/source1.c

@@ -1,0 +1,11 @@
+#include <stdio.h>
+
+int main (void) {
+    int age;
+
+    printf("How old are you?\n");
+    scanf("%d", &age);
+    printf("You are %d years old.\n", age);
+
+    return 0;
+}

### 2018-03-22 1062_class/eco_model/HW/W2/source2.c

@@ -1,0 +1,14 @@
+#include <stdio.h>
+
+int main (void) {
+    int age;
+    double height;
+
+    printf("Please enter your age and height(cm).\n");
+    scanf("%d", &age);
+    scanf("%lf", &height);
+
+    printf("Your age is %d and your height is %.1f cm.\n", age, height);
+
+    return 0;
+}

### 2018-03-22 1062_class/eco_model/forLoop&RandomNumber.c

@@ -1,0 +1,36 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>    // Gauss operator
+#include <time.h>
+
+// Functions
+double floor(double x); // Gauss operator
+double r2() {
+	return (double)rand() / (double)RAND_MAX ;
+}
+
+
+int main (void)
+{
+	// Initialize parameters
+	int i,T=20;  // add gen
+	double random, t= 0.0,gen=0.0;
+	
+	// Creating log file
+	FILE *out;
+	out= fopen("test.txt","w");
+	
+	srand(time(NULL));
+	
+	for (i=1;i<=T;i++){//create for loop
+		if(gen-floor(t)<=0) {
+			gen=gen+1.0;
+		}
+		else {
+			gen=gen;
+		}
+		random=r2();
+		fprintf(out, "%lf\t%lf\t%lf\n", t, gen, random);
+		t=t+0.1;
+	}
+}

### 2018-03-24 1062_class/Multivariate_Analysis/multi_Rnotes.Rmd
update

---
title: "Multivariate Analysis R Notes"
author: Yongfu, Liao
date: March 24, 2018
output:
    html_document:
        css: /Users/user/local_depend/style_sheets/style.css
        code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	dev = 'svg',
	fig.height = 3, 
	comment = ""
)
library(dplyr)
library(latex2exp)
library(ggplot2)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
```

Bivariate Normal Contour Map
-----------------------------------

### `ellipse` function
```r
ellipse(x, scale, centre, level, npoints = 1000)
```
- `x`: a single number, correlation of the two variables.

- `scale`: vector, **standard deviation** of the two variables.

- `centre`: vector, center of the ellipse, i.e. the mean vector of the bivariate normal distribution.

- `level`: a single number, the contour probability.

- `npoints`: number of points used to draw the contour.

`ellipse` returns a **matrix** with dimension (`npoints` $\times$ 2), which can be used to plot contour.

### Data Generation
The `for` loop below is used to generate a data frame with 3 columns(variables):
    - Column 1: First variable of bivariate normal function ($x_1$)
    - Column 2: Second variable of bivariate normal function ($x_2$)
    - Column 3: The contour that $x_1$ & $x_2$ on the same row belongs to.
```{r}
library(ellipse)

All_contours <- c(NA, NA, NA) 
    ## Set empty start for appending ##

for (i in 1:5) {
    level <- 0.1*i 
        ## Set Contour prob., prob. of obs within contour ##
    ell_data <-ellipse(-0.8, c(sqrt(2), 1), centre = c(1, 3), level = level, npoints = 800+(i-1)^3)
        ## npoints: bigger contours with more points ##
    class <- rep(paste(level*100, "% Contour", sep=""), nrow(ell_data))
        ## Assign contour class ##
    ell_data <- as.data.frame(ell_data)
        ## Change to data.frame BEFORE cbind, ##
        ## or coersion happens ##
    ell_data <- cbind(ell_data, class)

    All_contours <- rbind(All_contours, ell_data)
}

All_contours <- All_contours[-1,]
    ## Remove the empty start ##
```

### Plotting
```{r}
ggplot(data = All_contours) +
    geom_point(aes(x = x, y = y, color = class),
               size = 0.1) +
    scale_colour_grey(start = 0.7, end = 0.3) +
        ## Use gray scales instead of colored default ##
    labs(color = "Contours", 
         title = "Contour Plot",
         x = TeX("$x_1$"), y = TeX("$x_2$")
    )
```

Multivariate Normal Functions
----------------------------------

### Generate density f(x)

```{r echo=TRUE}
library(mvtnorm)

mu <- c(1, 3) # mean vector
Sigma <- matrix(c(2, -0.8*sqrt(2), -0.8*sqrt(2), 1),
                nrow = 2) # covariance matrix

dmvnorm(x = c(2, 5), mean = mu, sigma = Sigma)
```

- `x`: Vector x in f(x), all variables of the multivariate normal distribution.
- `mean`: Mean vector(center of ellipse) of the multivariate normal distribution.
- `sigma`: Covariance matrix of the multivariate normal distribution.

`dmvnorm` returns f(x), the range of the multivariate normal function. For example, `dmvnorm(x = c(2, 5), mean = mu, sigma = Sigma)` returns the value f($x_1=2$, $x_2=5$) of the multivariate normal distribution specified by mean vector, `mu`, and covariance matrix, `Sigma`.

#### Example: Densities of a Contour 
```{r echo=TRUE}
data <- All_contours %>% 
    filter(class == "50% Contour")

dmvnorm(x = data[1, 1:2], mean = mu, sigma = Sigma)[[1]]
dmvnorm(x = data[4, 1:2], mean = mu, sigma = Sigma)[[1]]
```

The retured values are the same(very close), since they are on the same contour. See the section [above]{#data-generation} for more details.

### Covariance Matrix

Generater covariance and correlation Matricies:
```{r echo=TRUE}
cov(iris[,1:4]) ## Cov Matrix of variable 1~4

```

```{r echo=TRUE}
cor(iris[,1:4]) ## Cor Matrix of variable 1~4
```

### 2018-03-24 1062_class/eco_model/HW/W2/HW2.rmd
update

@@
 ```
+Download [source1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W2/source1.c){target="_blank"}
 
@@
 ```
+Download [source2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W2/source2.c){target="_blank"}

### 2018-03-24 DiagrammeR/rmd_features.rmd
update

@@
     df_print: kable
-    code_folding: show
     toc: true
@@
 ---
-<!--more-->
 
@@
 ## $\LaTeX$ Rendering {.tabset}
+
+### Passing Matrix Object
+
+#### Setup
+
+Add `results='asis'` to r code chunk option.
+```{r results='asis'}
+library(mat2tex)
+mt <- c(1,2)
+"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
+```
+
+#### Include Matrix in Text
+
+![](mat2tex.png){width=60% height=auto}
+
+renders as:
+
+<div class="success">
+This is the variable `mt`,
+```{r results='asis', echo=FALSE}
+library(mat2tex)
+mt <- matrix(1:4, 2,2)
+"$A =" %_% xm(mt,0) %_%"^{-1}$"
+```
+, which is a matrix.
+</div>
+
+Check [here](http://markheckmann.github.io/mat2tex/){target=_blank""} for more information.
 

### 2018-03-25 1062_class/Multivariate_Analysis/multi_Rnotes.Rmd
update

@@
 ```{r echo=TRUE}
-cov(iris[,1:4]) ## Cov Matrix of variable 1~4
-
+library(mat2tex)
+cov.mt <- cov(iris[,1:4]) ## Cov Matrix of variable 1~4
+cor.mt <- cor(iris[,1:4]) ## Cor Matrix of variable 1~4
 ```
 
-```{r echo=TRUE}
-cor(iris[,1:4]) ## Cor Matrix of variable 1~4
+Covariance matrix 
+```{r echo=FALSE, results='asis'}
+"$=" %_% xm(cov.mt,2) %_%"$"
 ```
+
+Correlation matrix 
+```{r echo=FALSE, results='asis'}
+"$=" %_% xm(cor.mt,2) %_%"$"
+```

### 2018-03-25 Instructions/Rmarkdown_features/rmd_features.rmd
update

--- 2018-03-24 DiagrammeR/rmd_features.rmd
@@
 date: March 18, 2018
-bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa-no-doi-no-issue.csl
+bibliography: /Users/user/local_depend/citation/neanderthals.bib
+csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
 link-citations: yes
@@
   html_document:
-    css: ../style_sheets/style.css
+    css: /Users/user/local_depend/style_sheets/style.css
     df_print: kable
@@
 
-## yaml Setup {.tabset}
+yaml Setup {.tabset}
+-----------------------------
 Include the code in yaml header.
@@
 
-## Dynamic Variables
+Dynamic Variables
+-----------------------------
 
@@
 
-## $\LaTeX$ Rendering {.tabset}
-
+$\LaTeX$ Rendering {.tabset}
+-----------------------------
 ### Passing Matrix Object
@@
 
-![](mat2tex.png){width=60% height=auto}
+![](mat2tex.png){width=85% height=auto .rounded}
 
@@
 
-## Citations 
+Citations 
+-----------------------------
+
 To include **Citations**, [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.
@@
 
-## Emphasis {.tabset}
+Emphasis {.tabset}
+-----------------------------
 
@@
 
-## Footnotes with Paragraphs
+Footnotes with Paragraphs
+-----------------------------
 Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
@@
 
-## Shaped Images {.tabset}
+Shaped Images {.tabset}
+-----------------------------
 
@@
 ```{html}
-<div class="rounded">
-![](../icons/jekyll_dark.ico){width=auto height="30%"}
-</div>
+![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
 ```
-<div class="rounded">
-![](../icons/jekyll_dark.ico){width=auto height="30%"}
-</div>
+![](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
 
@@
 ```{html}
-<div class="circle">
-![](../icons/jekyll_dark.ico){width=auto height="30%"}
-</div>
+![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
 ```
-<div class="circle">
-![](../icons/jekyll_dark.ico){width=auto height="30%"}
-</div>
+![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
 
-<!-- footnotes -->
+<!-- footnotes ---------------------------- -->
 [^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.
@@
 [^red]: `.red` is also a self-defined class in my stylesheet.
-<!-- footnotes -->
+<!-- footnotes -------------------------- -->
 
 <!-- syntax for Reference section -->
-## References
+
+Figures
+-----------------------------
+
+### Captions
+Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
+```{r fig.cap='An Caption of the Plot'}
+library(ggplot2)
+ggplot(iris)+
+    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
+```
+
+References
+-----------------------------

### 2018-03-29 1062_class/eco_model/HW/W3/HW3.rmd
update

---
title: "Ecological Modeling HW3"
author: Yongfu Liao
date: March 29, 2018
output: html_document
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

```c
#include<stdio.h>

int main (void) {
    int bot_len, height;
    double area;

    printf("Please input the bottom length of a triangle (integer).\n");
    scanf("%d", &bot_len);

    printf("Please input the height of the triangle (integer).\n");
    scanf("%d", &height);

    area = (double) bot_len * (double) height / 2.0;
    printf("The area of the traingle is %.2lf.\n", area);

    return 0;
}

```
Download [Q1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W3/Q1.c){target="_blank"}

## Question 2

```c
#include<stdio.h>

int main (void) {
    double height, weight, BMI;
    double height_meter, std_weight;

    printf("Please input your height (cm) and weight (kg).\n");
    scanf("%lf", &height);
    scanf("%lf", &weight);

    height_meter = height / 100.0;

    BMI = (weight) / (height_meter * height_meter);
    std_weight = 24.0 * (height_meter * height_meter);

    printf("Your BMI is %.2lf.\n", BMI);
    printf("The standard BMI is assumed to be 24.0.\n");
    printf("The difference with a standard weight is %.2lf kg. \n", weight - std_weight);

    return 0;
}
```
Download [Q2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W3/Q2.c){target="_blank"}

### 2018-03-29 1062_class/eco_model/HW/W3/Q1.c

@@ -1,0 +1,17 @@
+#include<stdio.h>
+
+int main (void) {
+    int bot_len, height;
+    double area;
+    
+    printf("Please input the bottom length of a triangle (integer).\n");
+    scanf("%d", &bot_len);
+    
+    printf("Please input the height of the triangle (integer).\n");
+    scanf("%d", &height);
+    
+    area = (double) bot_len * (double) height / 2.0;
+    printf("The area of the traingle is %.2lf.\n", area);
+    
+    return 0;
+}

### 2018-03-29 1062_class/eco_model/HW/W3/Q2.c

@@ -1,0 +1,21 @@
+#include<stdio.h>
+
+int main (void) {
+    double height, weight, BMI;
+    double height_meter, std_weight;
+    
+    printf("Please input your height (cm) and weight (kg).\n");
+    scanf("%lf", &height);
+    scanf("%lf", &weight);
+    
+    height_meter = height / 100.0;
+    
+    BMI = (weight) / (height_meter * height_meter);
+    std_weight = 24.0 * (height_meter * height_meter);
+    
+    printf("Your BMI is %.2lf.\n", BMI);
+    printf("The standard BMI is assumed to be 24.0.\n");
+    printf("The difference with a standard weight is %.2lf kg. \n", weight - std_weight);
+    
+    return 0;
+}

### 2018-03-29 1062_class/eco_model/practice.c

@@ -1,0 +1,16 @@
+#include<stdio.h>
+
+int main (void) {
+    int d1 = 3;
+    int d2 = 4;
+    int d2_d1;
+    double div1, div2;
+    
+    div1 = d1/d2;
+    div2 = (double) d1/(double) d2;
+    d2_d1 = d1/d2;
+    
+    printf("div1 = %lf & div2 = %lf & d2/d1 = %d\n", div1, div2, d2_d1);
+    
+    return 0;
+}

### 2018-03-29 1062_class/eco_model/HW/C3/HW2.rmd
update

--- 2018-03-22 1062_class/eco_model/HW/W2/HW2.rmd
@@
 
+> How old are you? (output)
+>
+> 23 ⏎ (input)
+>
+> You are 23 years old. (output)
+
 ```c
@@
 ```
+Download [source1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C3/source1.c){target="_blank"}
 
 ## Question 2
+
+> Please input your age and height (cm). (output)
+>
+> 23 ⏎ (input)
+> 
+> 172.3 ⏎ (input)
+>
+> Your age is 23 and your height is 172.3 cm. (output)
 
@@
 
-    printf("Your age is %d and your height is %.1f cm.\n", age, height);
+    printf("Your age is %d and your height is %.1lf cm.\n", age, height);
 
@@
 ```
+Download [source2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C3/source2.c){target="_blank"}

### 2018-03-29 1062_class/eco_model/HW/C4/HW3.rmd
update

--- 2018-03-29 1062_class/eco_model/HW/W3/HW3.rmd
@@
 ## Question 1
+
+> Please input the bottom length of a triangle (integer). (output)
+> 
+> 3 ⏎ (input)
+> 
+> Please input the height of the triangle (integer). (output)
+> 
+> 4 ⏎ (input)
+> 
+> The area of the triangle is 6.00. (output)
 
@@
 ```
-Download [Q1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W3/Q1.c){target="_blank"}
+Download [Q1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C4/Q1.c){target="_blank"}
 
 ## Question 2
+
+> Please input your height (cm) and weight (kg). (output)
+>
+> 172.3 ⏎ (input)
+>
+> 65.0 ⏎ (input)
+>
+> Your BMI is XXXX. (output)
+>
+> The standard BMI is assumed to be 24.0. (output)
+>
+> The difference with a standard weight is YYY kg. (output)
 
@@
 ```
-Download [Q2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W3/Q2.c){target="_blank"}
+Download [Q2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C4/Q2.c){target="_blank"}

### 2018-03-29 1062_class/eco_model/HW/C3/source2.c

@@ -8,7 +8,7 @@ int main (void) {
     scanf("%d", &age);
     scanf("%lf", &height);
 
-    printf("Your age is %d and your height is %.1f cm.\n", age, height);
+    printf("Your age is %d and your height is %.1lf cm.\n", age, height);
 
     return 0;
 }

### 2018-03-29 1062_class/eco_model/HW/C2/HW1.rmd
update

---
title: "Ecological Modeling HW1"
author: Yongfu Liao
date: March 15, 2018
output: html_document
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

> Correct the following source codes and arrange them in a readable way.

```c
#include <stdio.h>
int main (void) {Printf(“How are you? \n”); printf(“Not bad”\n):
return O;
```

```c
#include <stdio.h>

int main (void) {
	printf("How are you? \n"); 
	printf("Not bad\n");

	return 0;
}
```
Download [Q1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C2/Q1.c){target="_blank"}

## Question 2

> Write a source code, which is intended to output the following tab
separated numbers.

```c
1.2 3.4 0.5
3.5 6.0 -10
```

```c
#include <stdio.h>

int main (void) {
	printf("%.1f\t%.1f\t%.1f\n", 1.2, 3.4, 0.5);
	printf("%.1f\t%.1f\t%d\n", 3.5, 6.0, -10);

	return 0;
}
```
Download [Q2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C2/Q2.c){target="_blank"}

### 2018-04-02 1062_class/Multivariate_Analysis/HW2/Q3.Rmd
update

---
title: 'Q3: Air Pollution'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE,
                      dev='svg',
                      fig.dim=c(3.6, 3.2))
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
```

```{r}
air<- read_table2("data/T1-5.dat", col_names = FALSE)
colnames(air) <- c("wind", "radiation", "CO", "NO", "NO2", "O3", "HC")
```

PCA with Covariance Matrix vs. Correlation Matrix
================================
```{r}
PCA_cov <- prcomp(air, scale=F)
PCA_cor <- prcomp(air, scale =T)
```

```{r fig.dim=c(6, 3.3)}
library(factoextra)
library(cowplot)

p_cov <- fviz_eig(PCA_cov, choice = "eigenvalue", main="PCA with S", geom = "line")
p_cor <- fviz_eig(PCA_cor, choice = "eigenvalue", main="PCA with R", geom = "line")

plot_grid(p_cov, p_cor, nrow = 1)
```

### Principle Components(eigenvector) of Covariance Matrix
```{r}
kable(PCA_cov[["rotation"]], format = "markdown", align = "c", digits = 2)
```

### Principle Components(eigenvector) of Correlation Matrix
```{r}
kable(PCA_cor[["rotation"]], format = "markdown", align = "c", digits=2)
```

### 2018-04-02 1062_class/Multivariate_Analysis/HW2/Q5.Rmd
update

---
title: 'Q5: Food Price'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE,
                      dev='svg',
                      fig.dim=c(3.6, 3.2))
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r data_import}
fp <- read_table2("data/FOODP.txt", col_names = FALSE, 
    skip = 5)[1:24, -1]
colnames(fp) <- c("city", paste("food",1:5,sep=""))
```

(a) Scree Plot, PCs, Interpretation
=======================================
```{r scree_plot}
library(factoextra) # For Visualizing MvA
PCA <- prcomp(fp[,-1], scale=T)
# fviz_eig(PCA)

eigva <- as_data_frame(PCA[["sdev"]]^2)
scree <- cbind(1:5 , eigva)
scree <- cbind(scree, "a")
colnames(scree) <- c("PC", "var", "a")

ggplot(scree, aes(x = PC, y = var, group = a)) +
    geom_point() + geom_line() +
    scale_y_continuous(
        sec.axis = sec_axis(~ . / sum(eigva) * 100,
                            name = "Variance Accounted (%)")
                   )+
    labs(x="Principle Components",
         y=latex2exp::TeX("$\\hat{\\lambda_i}$"),
         title="Scree Plot")    
```

By either the "elbow" of the scree plot or the unity criterion, **one principle component** is sufficient, which explains **`r round(eigva[1,1]/sum(eigva)*100, 2)`%** of the total variance.

```{r PC_loadings}
pc <- PCA[["rotation"]]
kable(round(pc,3),"markdown", align = "c")
```

(b) The First Two principal component scores
===================================================

```{r}
# PCA[["x"]] returns the "rotated" score(pc score) of the original data
pc_score12 <- as.data.frame(PCA[["x"]][,1:2])
pc_score12 <- cbind(fp$city, pc_score12) %>% rename(city=`fp$city`)
kable(pc_score12, "markdown", align="c",digits = 2)
```

(c) Scatter Plot: PC1 vs. PC2
============================================
```{r fig.dim=c(7, 4)}
ggplot(pc_score12, aes(x=PC1, y=PC2))+
    geom_point()+
    geom_text(aes(label=city),
              hjust=-0.1, vjust=0, size = 3)+
    scale_x_continuous(limits = c(-4.6, 2.9), breaks = seq(-4.5,3, 0.5))+
    scale_y_continuous(limits = c(-1.7, 1.5), breaks = seq(-1.75,1.5, 0.25))+
    labs(title="Scatter Plot of PC1 & PC2",
         x="Principle Component 1",
         y="Principle Component 2")
```

(d) Food Price in Different Cities
===============================================
```{r}
## Max PC score: cheapest food price
cheap <- pc_score12$city[pc_score12$PC1 == max(pc_score12$PC1)]

## min PC score
expense <- pc_score12$city[pc_score12$PC1 == min(pc_score12$PC1)]
```

Using principle component 1 as indicator, since it has the same sign on all "weighted" food price, and it's the most important principle component in explaining the variability of the data, the x-axis of the scatter above showed that **`r cheap`** has the cheapest food price, and **`r expense`** has the most expensive food price.

### 2018-04-02 1062_class/Multivariate_Analysis/HW2/Q6.Rmd
update

---
title: 'Q6: questionare'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r data_import_rm.na}
var_content <- read_delim("data/var_masst.txt", 
    ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE)
colnames(var_content) <- NULL

response <- read.table("C:/Users/user/local_depend/1062_class/Multivariate_Analysis/HW2/data/masst.txt", quote="\"", comment.char="", na.strings=".", stringsAsFactors=FALSE) %>%
    drop_na()
```

```{r}
PCA <- prcomp(response, scale = TRUE)

std_pc <- PCA[["sdev"]] 
# std(sqrt(eigenvalue) of corr matrix) of PCs
```

(a)
===============================

### Loading of the First 5 Pricinple Components
```{r}
# First 5 PCs
pc5 <- as.data.frame(PCA[["rotation"]][,1:5])

styled_pc5 <- round(pc5,3) %>%
    mutate(
        PC1 = cell_spec(PC1, "html", color = ifelse(PC1 < 0, "red", "blue")),
        PC2 = cell_spec(PC2, "html", color = ifelse(PC2 < 0, "red", "blue")),
        PC3 = cell_spec(PC3, "html", color = ifelse(PC3 < 0, "red", "blue")),
        PC4 = cell_spec(PC4, "html", color = ifelse(PC4 < 0, "red", "blue")),
        PC5 = cell_spec(PC5, "html", color = ifelse(PC5 < 0, "red", "blue"))
                        )

loadings <- kable(styled_pc5, "html", escape = F, align="c", row.names = T) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
loadings
```

### Percentage of Variance Accounted
```{r}
per_5pc <- sum(std_pc[1:5]^2)/sum(std_pc^2)
```
The percentage accounted is `r round(per_5pc*100,2)`%.

(b)
==============================

```{r fig.show='hold'}
loadings
var_content %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
```

### 2018-04-02 DiagrammeR/graphviz_syntax.R

@@ -5,7 +5,8 @@ var <- 1:3
 grViz("
 digraph { //non-directed graph
       graph [layout = neato]  //layout = dot|neato|twopi|circo|fdp
-      
+      rankdir=BT    // TB|RL|LR, LR: Left to Right orientation
+
       node [shape = circle,
       style = filled,
       color = orange]

### 2018-04-02 DiagrammeR/prehistory timeline/timeline.R

@@ -1,0 +1,43 @@
+library(timevis)
+group_d <- data.frame(
+    id      = 1:2,
+    content = c("Stone Technology"  , "Species"),
+    title = c("Stone Technology"  , "Species")
+)
+
+data <- data.frame(
+    id      = 1:4,
+    content = c("one"  , "two"  ,"Ranged item", "One"),
+    start   = c("-10000-01-10", "-10001-01-11", "-10002-01-20", "-10003-01-11"),
+    end     = c(NA          ,           NA, "-10001-02-04", NA),
+    group   = c(1,2,2,1)
+)
+
+
+
+
+timevis(data, groups  = group_d) %>%
+    setGroups(group_d)
+
+
+#--------Googlevis
+
+library(googleVis)
+
+datTL <- data.frame(Position=c(rep("President", 3), rep("Vice", 3)),
+                    Name=c("Washington", "Adams", "Jefferson",
+                           "Adams", "Jefferson", "Burr"),
+                    start=rep(c(1000, 2000,3000),2),
+                    end=rep(c(1100, 2100,3100),2))
+
+Timeline <- gvisTimeline(data=datTL, 
+                         rowlabel="Name",
+                         barlabel="Position",
+                         start="start", 
+                         end="end",
+                         options=list(timeline="{groupByRowLabel:false}",
+                                      backgroundColor='#ffd', 
+                                      height=350,
+                                      colors="['#cbb69d', '#603913', '#c69c6e']"))
+plot(Timeline)
+

### 2018-04-03 1062_class/Multivariate_Analysis/HW2/Q1.Rmd
update

---
title: 'Q1, Q2'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE,
                      dev='svg',
                      fig.dim=c(3.6, 3.2))
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

Q1: 8.1
====================================

```{r}
covmt <- matrix(c(5,2,2,2), nrow = 2)
eig <- eigen(covmt)
```

```{r}
eigval <- eig$values
eigvec <- eig$vectors
percent <- eigval[1]/sum(eigval)
```

- First Principle Component: 
    $\lambda_1 = `r eigval[1]`$, $Y_1 = `r round(eigvec[1,1], 3)`X_1 `r round(eigvec[2,1], 3)`X_2$

- Second Principle Component:
    $\lambda_2 = `r eigval[2]`$, $Y_2 = `r round(eigvec[1,2], 3)`X_1 `r round(eigvec[2,2], 3)`X_2$

- Proprotion of variance explained by the first PC: 
    $\frac{\lambda_1}{\Sigma \lambda_i} = `r round(percent*100, 2)`$%

Q2: 8.2
=======================================

```{r}
cormt <- diag(1/sqrt(diag(covmt)))%*%covmt%*%diag(1/sqrt(diag(covmt)))
```

$\rho = diag(\Sigma)^{\frac{-1}{2}} ~ \Sigma ~ diag(\Sigma)^{\frac{-1}{2}} =
```{r results='asis'} 
xm(cormt, round=T) %_% "$"
```

### (a)
```{r}
eig <- eigen(cormt)
eigval <- eig$values
eigvec <- eig$vectors
percent <- eigval[1]/sum(eigval)
```

- First Principle Component: 
    $\lambda_1 = `r round(eigval[1],2)`$, $Y_1 = `r round(eigvec[1,1], 3)`Z_1 `r round(eigvec[2,1], 3)`Z_2$

- Second Principle Component:
    $\lambda_2 = `r round(eigval[2],2)`$, $Y_2 = `r round(eigvec[1,2], 3)`Z_1 `r round(eigvec[2,2], 3)`Z_2$

- Proprotion of variance explained by the first PC: 
    $\frac{\lambda_1}{\Sigma \lambda_i} = `r round(percent*100, 2)`$%

### (b)

Principle components from 8.1 & 8.2 are different since they came from two different matrix (covariance matrix vs. correlation matrix). Mathmetically, the difference resulted from two different matrices have different eigenvalues and eigenvectors, hence different principle component. This difference reflects the fact that scaling has an effect on the principle component.

### (c)

```{r}
e_11 <- round(eigvec[1,1],3)
sqrt_eigen_1 <- round(sqrt(eigval[1]), 3)
v11 <- eigvec[1,1]*sqrt(eigval[1])

e_12 <- round(eigvec[2,1],2)
v12 <- eigvec[2,1]*sqrt(eigval[1])

e_21 <- round(eigvec[1,2],2)
sqrt_eigen_2 <- round(sqrt(eigval[2]), 2)
v21 <- eigvec[1,2]*sqrt(eigval[2])
```

$\rho_{Y_i,~Z_k} = \frac{e_{ik} \sqrt{\lambda_i}} {\sqrt{\sigma_{kk}}}$

$\rho_{Y_1,~Z_1} = \frac{(`r e_11`)(`r sqrt_eigen_1`) }{\sqrt{1}} = `r round(v11,3)`$

$\rho_{Y_1,~Z_2} = `r round(v12,3)`$

$\rho_{Y_2,~Z_1} = `r round(v21,3)`$

### 2018-04-03 1062_class/Multivariate_Analysis/HW2/all.Rmd
update

---
title: "MultiAnaly HW2"
output: html_document
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE,
                      dev='svg',
                      fig.dim=c(3.6, 3.2))
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

Q1: 8.1
====================================

```{r}
covmt <- matrix(c(5,2,2,2), nrow = 2)
eig <- eigen(covmt)
```

```{r}
eigval <- eig$values
eigvec <- eig$vectors
percent <- eigval[1]/sum(eigval)
```

- First Principle Component: 
    $\lambda_1 = `r eigval[1]`$, $Y_1 = `r round(eigvec[1,1], 3)`X_1 `r round(eigvec[2,1], 3)`X_2$

- Second Principle Component:
    $\lambda_2 = `r eigval[2]`$, $Y_2 = `r round(eigvec[1,2], 3)`X_1 `r round(eigvec[2,2], 3)`X_2$

- Proprotion of variance explained by the first PC: 
    $\frac{\lambda_1}{\Sigma \lambda_i} = `r round(percent*100, 2)`$%

Q2: 8.2
=======================================

```{r}
cormt <- diag(1/sqrt(diag(covmt)))%*%covmt%*%diag(1/sqrt(diag(covmt)))
```

$\rho = diag(\Sigma)^{\frac{-1}{2}} ~ \Sigma ~ diag(\Sigma)^{\frac{-1}{2}} =
```{r results='asis'} 
xm(cormt, round=T) %_% "$"
```

### (a)
```{r}
eig <- eigen(cormt)
eigval <- eig$values
eigvec <- eig$vectors
percent <- eigval[1]/sum(eigval)
```

- First Principle Component: 
    $\lambda_1 = `r round(eigval[1],2)`$, $Y_1 = `r round(eigvec[1,1], 3)`Z_1 `r round(eigvec[2,1], 3)`Z_2$

- Second Principle Component:
    $\lambda_2 = `r round(eigval[2],2)`$, $Y_2 = `r round(eigvec[1,2], 3)`Z_1 `r round(eigvec[2,2], 3)`Z_2$

- Proprotion of variance explained by the first PC: 
    $\frac{\lambda_1}{\Sigma \lambda_i} = `r round(percent*100, 2)`$%

### (b)

Principle components from 8.1 & 8.2 are different since they came from two different matrix (covariance matrix vs. correlation matrix). Mathmetically, the difference resulted from two different matrices have different eigenvalues and eigenvectors, hence different principle component. This difference reflects the fact that scaling has an effect on the principle component.

### (c)

```{r}
e_11 <- round(eigvec[1,1],3)
sqrt_eigen_1 <- round(sqrt(eigval[1]), 3)
v11 <- eigvec[1,1]*sqrt(eigval[1])

e_12 <- round(eigvec[2,1],2)
v12 <- eigvec[2,1]*sqrt(eigval[1])

e_21 <- round(eigvec[1,2],2)
sqrt_eigen_2 <- round(sqrt(eigval[2]), 2)
v21 <- eigvec[1,2]*sqrt(eigval[2])
```

$\rho_{Y_i,~Z_k} = \frac{e_{ik} \sqrt{\lambda_i}} {\sqrt{\sigma_{kk}}}$

$\rho_{Y_1,~Z_1} = \frac{(`r e_11`)(`r sqrt_eigen_1`) }{\sqrt{1}} = `r round(v11,3)`$

$\rho_{Y_1,~Z_2} = `r round(v12,3)`$

$\rho_{Y_2,~Z_1} = `r round(v21,3)`$

Q3: PCA with Covariance Matrix vs. Correlation Matrix
================================
```{r}
air<- read_table2("data/T1-5.dat", col_names = FALSE)
colnames(air) <- c("wind", "radiation", "CO", "NO", "NO2", "O3", "HC")
```

```{r}
PCA_cov <- prcomp(air, scale=F)
PCA_cor <- prcomp(air, scale =T)
```

```{r fig.dim=c(6, 3.3)}
library(factoextra)
library(cowplot)

p_cov <- fviz_eig(PCA_cov, choice = "eigenvalue", main="PCA with S", geom = "line")
p_cor <- fviz_eig(PCA_cor, choice = "eigenvalue", main="PCA with R", geom = "line")

plot_grid(p_cov, p_cor, nrow = 1)
```

### Principle Components(eigenvector): Covariance Matrix
```{r}
kable(PCA_cov[["rotation"]], format = "markdown", align = "c", digits = 2)
```

### Principle Components(eigenvector): Correlation Matrix
```{r}
kable(PCA_cor[["rotation"]], format = "markdown", align = "c", digits=2)
```

Q4
==================================
```{r data_import}
sweet <- read_table2("data/T5-1.txt", col_names = FALSE)
colnames(sweet) <- c("sweet_rate", "sodium", "potassium")
```

```{r fig.dim=c(7, 4)}
source("multivariate_fc.R")
PCA <- prcomp(sweet, scale=F)
PCA_cor <- prcomp(sweet, scale=T)

p_cov <- scree_plot(PCA, "variance", addlabels=TRUE, main="Covariance mat", sub_axis_name="", axis_limits = c(0,100))
p_cor <- scree_plot(PCA_cor, "variance", addlabels=TRUE, main="Correlation mat",ylab = "", axis_limits = c(0,100))
cowplot::plot_grid(p_cov, p_cor, nrow = 1)
```

```{r}
library(mat2tex)
kable(PCA[["rotation"]], format="markdown", align="c", digits = 2)
```

```{r}
quantiles <- qnorm(p=seq(0.25,9.75, 0.5)/10) 
PC1 <- as.data.frame(PCA[["x"]][,1])
    PC1 <- cbind(rownames(PC1), PC1)
    colnames(PC1) <- c("ID", "PC1")
    PC1 <- PC1 %>% 
        arrange(PC1) %>% mutate(quantile=quantiles)

PC2 <- as.data.frame(PCA[["x"]][,2])
    PC2 <- cbind(rownames(PC2), PC2)
    colnames(PC2) <- c("ID", "PC2")
    PC2 <- PC2 %>% 
        arrange(PC2) %>% mutate(quantile=quantiles)

PC3 <- as.data.frame(PCA[["x"]][,3])
    PC3 <- cbind(rownames(PC3), PC3)
    colnames(PC3) <- c("ID", "PC3")
    PC3 <- PC3 %>% 
        arrange(PC3) %>% mutate(quantile=quantiles)
```

```{r fig.dim=c(7.5, 3.3)}
library(ggplot2)
library(scales)
library(cowplot)
library(latex2exp)

p1 <- ggplot(PC1, aes(x=quantiles, y=PC1))+
        geom_point(color=hue_pal()(3)[1])+
        geom_text(aes(label=ID),
                  hjust=-0.1, vjust=0, size = 2)+
        scale_x_continuous(breaks = seq(-2,2, 0.5))+
        scale_y_continuous(breaks = seq(-35,35, 5))+
        labs(x=TeX("$q_{(j)}$"),
             y="PC1",
             title="PC1 Q-Q Plot")+ theme

p2 <- ggplot(PC2, aes(x=quantiles, y=PC2))+
        geom_point(color=hue_pal()(3)[2])+
        geom_text(aes(label=ID),
                  hjust=-0.1, vjust=0, size = 2)+
        scale_x_continuous(breaks = seq(-2,2, 0.5))+
        scale_y_continuous(breaks = seq(-4.5,3.5, 0.5))+
        labs(x=TeX("$q_{(j)}$"),
             y="PC2",
             title="PC2 Q-Q Plot")+ theme

p3 <- ggplot(PC3, aes(x=quantiles, y=PC3))+
        geom_point(color=hue_pal()(3)[3])+
        geom_text(aes(label=ID),
                  hjust=-0.1, vjust=0, size = 2)+
        scale_x_continuous(breaks = seq(-2,2, 0.5))+
        scale_y_continuous(breaks = seq(-2,2, 0.5))+
        labs(x=TeX("$q_{(j)}$"),
             y="PC3",
             title="PC3 Q-Q Plot")+ theme

plot_grid(p1, p2, p3, nrow = 1)
```

Q5
===================================
```{r data_import2}
fp <- read_table2("data/FOODP.txt", col_names = FALSE, 
    skip = 5)[1:24, -1]
colnames(fp) <- c("city", paste("food",1:5,sep=""))
```

### (a) Scree Plot, PCs, Interpretation

```{r scree_plot}
library(factoextra) # For Visualizing MvA
PCA <- prcomp(fp[,-1], scale=T)
# fviz_eig(PCA)

eigva <- as_data_frame(PCA[["sdev"]]^2)
scree <- cbind(1:5 , eigva)
scree <- cbind(scree, "a")
colnames(scree) <- c("PC", "var", "a")

ggplot(scree, aes(x = PC, y = var, group = a)) +
    geom_point() + geom_line() +
    scale_y_continuous(
        sec.axis = sec_axis(~ . / sum(eigva) * 100,
                            name = "Variance Accounted (%)")
                   )+
    labs(x="Principle Components",
         y=latex2exp::TeX("$\\hat{\\lambda_i}$"),
         title="Scree Plot")    
```

By either the "elbow" of the scree plot or the unity criterion, **one principle component** is sufficient, which explains **`r round(eigva[1,1]/sum(eigva)*100, 2)`%** of the total variance.

```{r PC_loadings}
pc <- PCA[["rotation"]]
kable(round(pc,3),"markdown", align = "c")
```

### (b) The First Two principal component scores

```{r}
# PCA[["x"]] returns the "rotated" score(pc score) of the original data
pc_score12 <- as.data.frame(PCA[["x"]][,1:2])
pc_score12 <- cbind(fp$city, pc_score12) %>% rename(city=`fp$city`)
kable(pc_score12, "markdown", align="c",digits = 2)
```

### (c) Scatter Plot: PC1 vs. PC2

```{r fig.dim=c(7, 4)}
ggplot(pc_score12, aes(x=PC1, y=PC2))+
    geom_point()+
    geom_text(aes(label=city),
              hjust=-0.1, vjust=0, size = 3)+
    scale_x_continuous(limits = c(-4.6, 2.9), breaks = seq(-4.5,3, 0.5))+
    scale_y_continuous(limits = c(-1.7, 1.5), breaks = seq(-1.75,1.5, 0.25))+
    labs(title="Scatter Plot of PC1 & PC2",
         x="Principle Component 1",
         y="Principle Component 2")
```

### (d) Food Price in Different Cities
```{r}
## Max PC score: cheapest food price
cheap <- pc_score12$city[pc_score12$PC1 == max(pc_score12$PC1)]

## min PC score
expense <- pc_score12$city[pc_score12$PC1 == min(pc_score12$PC1)]
```

Using principle component 1 as indicator, since it has the same sign on all "weighted" food price, and it's the most important principle component in explaining the variability of the data, the x-axis of the scatter above showed that **`r cheap`** has the cheapest food price, and **`r expense`** has the most expensive food price.

Q6
================================
```{r data_import_rm.na}
var_content <- read_delim("data/var_masst.txt", 
    ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE)
colnames(var_content) <- NULL

response <- read.table("C:/Users/user/local_depend/1062_class/Multivariate_Analysis/HW2/data/masst.txt", quote="\"", comment.char="", na.strings=".", stringsAsFactors=FALSE) %>%
    drop_na()
```

```{r}
PCA <- prcomp(response, scale = TRUE)

std_pc <- PCA[["sdev"]] 
# std(sqrt(eigenvalue) of corr matrix) of PCs
```

### (a)

#### Loading of the First 5 Pricinple Components
```{r}
# First 5 PCs
pc5 <- as.data.frame(PCA[["rotation"]][,1:5])

styled_pc5 <- round(pc5,3) %>%
    mutate(
        PC1 = cell_spec(PC1, "html", color = ifelse(PC1 < 0, "red", "blue")),
        PC2 = cell_spec(PC2, "html", color = ifelse(PC2 < 0, "red", "blue")),
        PC3 = cell_spec(PC3, "html", color = ifelse(PC3 < 0, "red", "blue")),
        PC4 = cell_spec(PC4, "html", color = ifelse(PC4 < 0, "red", "blue")),
        PC5 = cell_spec(PC5, "html", color = ifelse(PC5 < 0, "red", "blue"))
                        )

loadings <- kable(styled_pc5, "html", escape = F, align="c", row.names = T) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
loadings
```

#### Percentage of Variance Accounted
```{r}
per_5pc <- sum(std_pc[1:5]^2)/sum(std_pc^2)
```
The percentage accounted is `r round(per_5pc*100,2)`%.

### (b)

```{r fig.show='hold'}
var_content %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)

### 2018-04-03 Instructions/Rmarkdown_features/rmd_features.rmd
update

@@
 author: Yongfu Liao
-date: March 18, 2018
+date: Apr 3, 2018
 bibliography: /Users/user/local_depend/citation/neanderthals.bib
@@
   html_document:
+    code_folding: show
     css: /Users/user/local_depend/style_sheets/style.css
@@
 	warning = FALSE,
-	dev='svg'
+	dev='svg',
+	fig.dim = c(5.5, 3.5)  # (width, height)
 )
+```
+
+About This Document {.tabset}
+-----------------------------
+### yaml of this Doc
+```yaml
+---
+title: "Rmarkdown Features"
+subtitle: "This is subtitle"
+author: Yongfu Liao
+date: March 18, 2018
+bibliography: /Users/user/local_depend/citation/neanderthals.bib
+csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
+link-citations: yes
+output:
+  html_document:
+    code_folding: show
+    css: /Users/user/local_depend/style_sheets/style.css
+    df_print: kable
+    toc: true
+    toc_depth: 4
+    toc_float: true
+---
+```
+
+PDF Document (Chinese) {.tabset}
+-----------------------------
+
+### yaml
+
+```yaml
+---
+output:
+  pdf_document:
+    latex_engine: xelatex    
+    includes:
+        in_header: header.tex
+documentclass: article
+urlcolor: "blue"
+fontsize: 12pt
+---
+```
+
+### header.tex
+```tex
+%加這個就可以設定字體
+\usepackage{fontspec}
+%使用xeCJK，其他的還有CJK或是xCJK
+\usepackage{xeCJK}
+
+%設定英文字型，不設的話就會使用預設的字型
+\setmainfont{Calibri}
+
+%設定中英文的字型
+%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
+\setCJKmainfont{蘋方-繁}
+
+%中文自動換行
+\XeTeXlinebreaklocale "zh"
+
+%文字的彈性間距
+\XeTeXlinebreakskip = 0pt plus 1pt
+
+%設定段落之間的距離
+\setlength{\parskip}{0.15cm}
+
+%設定行距
+\linespread{1.2}\selectfont
 ```
@@
 
-$\LaTeX$ Rendering {.tabset}
+$\LaTeX$ Math Rendering {.tabset}
 -----------------------------
@@
 2. warning
-3. warning
+3. info
 4. error
@@
 ```{html}
-<div class="error">
+<div class="info">
 some text in the colored region
@@
 
-<div class="error">
+<div class="info">
 some text in the colored region
+</div>
+
+#### Bootstrap Alert
+
+Alternatively, you can use bootstrap's default alert divs, defined by four classes:
+
+1. alert-success
+2. alert-warning
+3. alert-info
+4. alert-danger
+```{html}
+<div class="alert alert-success">
+some text in the colored region
+</div>
+```
+
+<div class="alert alert-success">
+Bootstrap-defined colored region
 </div>

### 2018-04-12 1062_class/Multivariate_Analysis/HW2/HW2.Rmd
update

---
title: "多變量分析 HW2"
author: "劉昱維, 吳冠瑋, 廖永賦, 謝靖惟, 黃奎鈞"
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
  html_document: default
css: /Users/user/local_depend/style_sheets/style.css
always_allow_html: yes
---

```{r setup, include=FALSE}
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(echo = TRUE,
                          message=FALSE,
                          warning=FALSE,
                          dev='svg',
                          fig.dim=c(3.6, 3.2))
} else {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          out.width = '70%',
                          out.height = '5.5cm')
}
options(digits = 2)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

Q1: 8.1
====================================

```{r}
covmt <- matrix(c(5,2,2,2), nrow = 2)
eig <- eigen(covmt)
```

```{r}
eigval <- eig$values
eigvec <- eig$vectors
percent <- eigval[1]/sum(eigval)
```

- First Principle Component: 
    $\lambda_1 = `r eigval[1]`$, $Y_1 = `r round(eigvec[1,1], 3)`X_1 `r round(eigvec[2,1], 3)`X_2$

- Second Principle Component:
    $\lambda_2 = `r eigval[2]`$, $Y_2 = `r round(eigvec[1,2], 3)`X_1 `r round(eigvec[2,2], 3)`X_2$

- Proprotion of variance explained by the first PC: 
    $\frac{\lambda_1}{\Sigma \lambda_i} = `r round(percent*100, 2)`$%

---------------------

Q2: 8.2
=======================================

```{r}
cormt <- diag(1/sqrt(diag(covmt)))%*%covmt%*%diag(1/sqrt(diag(covmt)))
```

$\rho = diag(\Sigma)^{\frac{-1}{2}} ~ \Sigma ~ diag(\Sigma)^{\frac{-1}{2}} =
```{r echo=FALSE, results='asis'}
xm(cormt, round=T) %_% "$"
```

### (a)
```{r}
eig <- eigen(cormt)
eigval <- eig$values
eigvec <- eig$vectors
percent <- eigval[1]/sum(eigval)
```

- First Principle Component: 
    $\lambda_1 = `r round(eigval[1],2)`$, $Y_1 = `r round(eigvec[1,1], 3)`Z_1 `r round(eigvec[2,1], 3)`Z_2$

- Second Principle Component:
    $\lambda_2 = `r round(eigval[2],2)`$, $Y_2 = `r round(eigvec[1,2], 3)`Z_1 `r round(eigvec[2,2], 3)`Z_2$

- Proprotion of variance explained by the first PC: 
    $\frac{\lambda_1}{\Sigma \lambda_i} = `r round(percent*100, 2)`$%

### (b)

Principle components from 8.1 & 8.2 are different since they came from two different matrix (covariance matrix vs. correlation matrix). Mathmetically, the difference resulted from two different matrices have different eigenvalues and eigenvectors, hence different principle component. This difference reflects the fact that scaling has an effect on the principle component.

### (c)

```{r}
e_11 <- round(eigvec[1,1],3)
sqrt_eigen_1 <- round(sqrt(eigval[1]), 3)
v11 <- eigvec[1,1]*sqrt(eigval[1])

e_12 <- round(eigvec[2,1],2)
v12 <- eigvec[2,1]*sqrt(eigval[1])

e_21 <- round(eigvec[1,2],2)
sqrt_eigen_2 <- round(sqrt(eigval[2]), 2)
v21 <- eigvec[1,2]*sqrt(eigval[2])
```

$\rho_{Y_i,~Z_k} = \frac{e_{ik} \sqrt{\lambda_i}} {\sqrt{\sigma_{kk}}}$

$\rho_{Y_1,~Z_1} = \frac{(`r e_11`)(`r sqrt_eigen_1`) }{\sqrt{1}} = `r round(v11,3)`$

$\rho_{Y_1,~Z_2} = `r round(v12,3)`$

$\rho_{Y_2,~Z_1} = `r round(v21,3)`$

----------------------------

Q3: PCA with Covariance Matrix vs. Correlation Matrix
================================
```{r}
air<- read_table2("data/T1-5.dat", col_names = FALSE)
colnames(air) <- c("wind", "radiation", "CO", "NO", "NO2", "O3", "HC")
```

```{r}
PCA_cov <- prcomp(air, scale=F)
PCA_cor <- prcomp(air, scale =T)
```

```{r fig.dim=c(6, 3)}
library(factoextra)
library(cowplot)

p_cov <- fviz_eig(PCA_cov, choice = "eigenvalue", main="PCA with S", geom = "line")
p_cor <- fviz_eig(PCA_cor, choice = "eigenvalue", main="PCA with R", geom = "line")

plot_grid(p_cov, p_cor, nrow = 1)
```

### Principle Components: Covariance Matrix
```{r}
kable(PCA_cov[["rotation"]], format = "markdown", align = ifelse(knitr::is_html_output(), "c", "l"), digits = 2)
```

### Principle Components: Correlation Matrix
```{r}
kable(PCA_cor[["rotation"]], format = "markdown", align = ifelse(knitr::is_html_output(), "c", "l"), digits=2)
```

### Interpretation

#### PCA with $\mathbf{S}$
The scree plot of PCA using $\mathbf{S}$ indicates that only one principle component is important, which explains `r 100*PCA_cov$sdev[1]^2/(PCA_cov$sdev^2 %>% sum())`% of the total variance.

The first principle component obtained by **covariance matrix** explains nearly all the variation in the data, this is probably due to the **large scale of the variable radiation** compared to orther variables. A better explanation of PCA should rely on the **correlation matrix** in this case.

#### PCA with $\mathbf{R}$
According to the unity criterion and the scree plot (a not-so-obvious elbow at the forth PC), three principle components can well summarize the data, which explains `r 100*(PCA_cor$sdev[1:3]^2 %>% sum())/(PCA_cor$sdev^2 %>% sum())`% of the total variance.

The interpretation of the first principle component obtained by the correlation matricies is straightforward: the variable **wind** constrasts with other variables consist of **pollutants**, probably because strong wind blows away pollutants, i.e. wind and polutants have opposite effect on air polution.

Interpretation of the remaining two principle components requires extensive knowledge on air pollution.

-------------------------

Q4
==================================
```{r data_import}
sweet <- read_table2("data/T5-1.txt", col_names = FALSE)
colnames(sweet) <- c("sweet_rate", "sodium", "potassium")
```

```{r fig.dim=c(7, 4)}
source("multivariate_fc.R")
PCA <- prcomp(sweet, scale=F)
PCA_cor <- prcomp(sweet, scale=T)

p_cov <- scree_plot(PCA, "variance", addlabels=TRUE, main="Covariance matrix", sub_axis_name="", axis_limits = c(0,100))
p_cor <- scree_plot(PCA_cor, "variance", addlabels=TRUE, main="Correlation matrix",ylab = "", axis_limits = c(0,100))
cowplot::plot_grid(p_cov, p_cor, nrow = 1)
```

```{r}
library(mat2tex)
kable(PCA[["rotation"]], format="markdown", align="c", digits = 2)
```

```{r}
quantiles <- qnorm(p=seq(0.25,9.75, 0.5)/10) 
PC1 <- as.data.frame(PCA[["x"]][,1])
    PC1 <- cbind(rownames(PC1), PC1)
    colnames(PC1) <- c("ID", "PC1")
    PC1 <- PC1 %>% 
        arrange(PC1) %>% mutate(quantile=quantiles)

PC2 <- as.data.frame(PCA[["x"]][,2])
    PC2 <- cbind(rownames(PC2), PC2)
    colnames(PC2) <- c("ID", "PC2")
    PC2 <- PC2 %>% 
        arrange(PC2) %>% mutate(quantile=quantiles)

PC3 <- as.data.frame(PCA[["x"]][,3])
    PC3 <- cbind(rownames(PC3), PC3)
    colnames(PC3) <- c("ID", "PC3")
    PC3 <- PC3 %>% 
        arrange(PC3) %>% mutate(quantile=quantiles)
```

```{r fig.dim=c(7.5, 3.3)}
library(ggplot2)
library(scales)
library(cowplot)
library(latex2exp)

size <- 2.3 # dot label text-size
p1 <- ggplot(PC1, aes(x=quantiles, y=PC1))+
        geom_point(color=hue_pal()(3)[1])+
        geom_text(aes(label=ID),
                  hjust=-0.1, vjust=0, size = size)+
        scale_x_continuous(breaks = seq(-2,2, 0.5))+
        scale_y_continuous(breaks = seq(-35,35, 5))+
        labs(x=TeX("$q_{(j)}$"),
             y="PC1",
             title="PC1 Q-Q Plot")+ theme

p2 <- ggplot(PC2, aes(x=quantiles, y=PC2))+
        geom_point(color=hue_pal()(3)[2])+
        geom_text(aes(label=ID),
                  hjust=-0.1, vjust=0, size = size)+
        scale_x_continuous(breaks = seq(-2,2, 0.5))+
        scale_y_continuous(breaks = seq(-4.5,3.5, 0.5))+
        labs(x=TeX("$q_{(j)}$"),
             y="PC2",
             title="PC2 Q-Q Plot")+ theme

p3 <- ggplot(PC3, aes(x=quantiles, y=PC3))+
        geom_point(color=hue_pal()(3)[3])+
        geom_text(aes(label=ID),
                  hjust=-0.1, vjust=0, size = size)+
        scale_x_continuous(breaks = seq(-2,2, 0.5))+
        scale_y_continuous(breaks = seq(-2,2, 0.5))+
        labs(x=TeX("$q_{(j)}$"),
             y="PC3",
             title="PC3 Q-Q Plot")+ theme

plot_grid(p1, p2, p3, nrow = 1)
```

### Suspect Observations?
From the three Q-Q plots above, there seems no obvious deviation from the straight lines, and there are no unique points that deviate from the main data in all three Q-Q plots. For detecting suspect observations, more techniques are needed.

--------------------------

Q5
===================================
```{r data_import2}
fp <- read_table2("data/FOODP.txt", col_names = FALSE, 
    skip = 5)[1:24, -1]
colnames(fp) <- c("city", paste("food",1:5,sep=""))
```

### (a) Scree Plot, PCs, Interpretation

```{r scree_plot}
library(factoextra) # For Visualizing MvA
PCA <- prcomp(fp[,-1], scale=T)
# fviz_eig(PCA)

eigva <- as_data_frame(PCA[["sdev"]]^2)
scree <- cbind(1:5 , eigva)
scree <- cbind(scree, "a")
colnames(scree) <- c("PC", "var", "a")

ggplot(scree, aes(x = PC, y = var, group = a)) +
    geom_point() + geom_line() +
    scale_y_continuous(
        sec.axis = sec_axis(~ . / sum(eigva) * 100,
                            name = "Variance Accounted (%)")
                   )+
    labs(x="Principle Components",
         y=latex2exp::TeX("$\\hat{\\lambda_i}$"),
         title="Scree Plot")    
```

```{r PC_loadings}
pc <- PCA[["rotation"]]
kable(round(pc,3),"markdown", align = ifelse(knitr::is_html_output(), "c", "l"))
```

#### Interpretation
By either the "elbow" of the scree plot or the unity criterion, the **first principle component** is sufficient, which explains **`r round(eigva[1,1]/sum(eigva)*100, 2)`%** of the total variance.

The data can be greatly reduced to 1 variable by the first principle component, and the "weight" of the first principle component on each variable have the same sign, indicating the price of each food has similar effect on the variation of the data.

### (b) The First Two principal component scores

```{r}
# PCA[["x"]] returns the "rotated" score(pc score) of the original data
pc_score12 <- as.data.frame(PCA[["x"]][,1:2])
pc_score12 <- cbind(fp$city, pc_score12) %>% rename(city=`fp$city`)

kable(pc_score12, align="c",digits = 2, format ="markdown")
```

### (c) Scatter Plot: PC1 vs. PC2

```{r fig.dim=c(7, 4)}
ggplot(pc_score12, aes(x=PC1, y=PC2))+
    geom_point()+
    geom_text(aes(label=city),
              hjust=-0.1, vjust=0, size = 3)+
    scale_x_continuous(limits = c(-4.6, 2.9), breaks = seq(-4.5,3, 0.5))+
    scale_y_continuous(limits = c(-1.7, 1.5), breaks = seq(-1.75,1.5, 0.25))+
    geom_segment(x=3,y=1.1,
                 xend=-4.6, yend=-0.5)+
    labs(title="Scatter Plot of PC1 & PC2",
         x="Principle Component 1",
         y="Principle Component 2")
```

Two clusters seems to be identified on the scatter plot, ignoring **Buffalo**.

### (d) Food Price in Different Cities
```{r}
## Max PC score: cheapest food price
cheap <- pc_score12$city[pc_score12$PC1 == max(pc_score12$PC1)]

## min PC score
expense <- pc_score12$city[pc_score12$PC1 == min(pc_score12$PC1)]
```

Using principle component 1 as indicator, since it has the same sign on all "weighted" food price, and it's the most important principle component in explaining the variability of the data, the x-axis of the scatter above showed that **`r cheap`** has the cheapest food price, and **`r expense`** has the most expensive food price.

----------------------

Q6
================================
```{r data_import_rm.na}
var_content <- read_delim("data/var_masst.txt", 
    ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE)
colnames(var_content) <- NULL

response <- read.table("C:/Users/user/local_depend/1062_class/Multivariate_Analysis/HW2/data/masst.txt", quote="\"", comment.char="", na.strings=".", stringsAsFactors=FALSE) %>%
    drop_na()
```

```{r}
PCA <- prcomp(response, scale = TRUE)

std_pc <- PCA[["sdev"]] 
# std(sqrt(eigenvalue) of corr matrix) of PCs
```

### (a)

#### Weight of the First 5 Pricinple Components on each Variable
```{r}
# First 5 PCs
pc5 <- as.data.frame(PCA[["rotation"]][,1:5])

styled_pc5 <- round(pc5,3) %>%
    mutate(
        PC1 = cell_spec(PC1, "html", color = ifelse(PC1 < 0, "red", "blue")),
        PC2 = cell_spec(PC2, "html", color = ifelse(PC2 < 0, "red", "blue")),
        PC3 = cell_spec(PC3, "html", color = ifelse(PC3 < 0, "red", "blue")),
        PC4 = cell_spec(PC4, "html", color = ifelse(PC4 < 0, "red", "blue")),
        PC5 = cell_spec(PC5, "html", color = ifelse(PC5 < 0, "red", "blue"))
                        )

loadings <- kable(styled_pc5, "markdown", escape = F, align="c", row.names = T) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
loadings %>%
  kableExtra::landscape()
```

#### Percentage of Variance Accounted

$\hat{\lambda_1}$ = `r std_pc[1]^2`,
$\hat{\lambda_2}$ = `r std_pc[2]^2`,
$\hat{\lambda_3}$ = `r std_pc[3]^2`,
$\hat{\lambda_4}$ = `r std_pc[4]^2`,
$\hat{\lambda_5}$ = `r std_pc[5]^2`.

```{r}
per_5pc <- sum(std_pc[1:5]^2)/sum(std_pc^2)
```
The percentage of total variance accounted by the first 5 PCs is `r per_5pc*100`%.

### (b)

```{r fig.show='hold'}
t <- var_content %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

```{r fig.dim=c(6,5)}
BrBG <- colorRampPalette(c("purple","blue","white", "red", "orange"))
hm <- function(data) {
    heatmaply::heatmaply(round(cor(data),2), margins = c(50, 50),
          k_col = 2, k_row = 2,
          colors = BrBG,
          dendrogram = "none",
          label_names=c("row", "column", "Corr."),
          column_text_angle = 60,
          fontsize_row=5, fontsize_col=5,
          limits = c(-1,1))
}
```

```{r}
factoextra::fviz_eig(PCA, choice = "variance", main="First 5 PCs", geom = "line", ncp=8, addlabels=T)+ scale_y_continuous(limits = c(4, 16))
```

#### First PC
```{r}
h <- hm(response[,c(which(pc5$PC1>0), which(pc5$PC1<0))])
if (knitr::is_html_output()) {h}
```

```{r}
t <- var_content[which(pc5$PC1>0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "contrasts"`

```{r}
t <- var_content[which(pc5$PC1<0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

The first PC group variables as:

- The variables `r paste(which(pc5$PC1>0), collapse=", ")` seem to reflect the trade-offs between cutting down energy usage and solving energy crysis.

- The variables `r paste(which(pc5$PC1<0), collapse=", ")` seem to reflect 2 attitudes: 
    1. Little can be done to change the energy crysis.
    2. Favor solving energy crysis at the cost of pollution.

#### Second PC

```{r}
h <- hm(response[,c(which(pc5$PC2>0), which(pc5$PC2<0))])
if (knitr::is_html_output()) {h}
```

```{r}
t <- var_content[which(pc5$PC2>0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "contrasts"`

```{r}
t <- var_content[which(pc5$PC2<0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

The second PC group variables as:

- The variables `r paste(which(pc5$PC2>0), collapse=", ")` mostly reflect the attitude that little can be done to solve the energy crysis.

- The variables `r paste(which(pc5$PC2<0), collapse=", ")` seem to reflect that the energy crysis is changable despite some sacrifices such as pollution.

#### Third, Forth, and Fifth PC

The third, forth, and fifth PC are not obvious and easy to interpret, and in fact, they account for only 10%, 8%, and 6% of total variance, respectively.

`r if (knitr::is_html_output()) "#### Third PC"`
```{r}
h <- hm(response[,c(which(pc5$PC3>0), which(pc5$PC3<0))])
if (knitr::is_html_output()) {h}
```

```{r}
t <- var_content[which(pc5$PC3>0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "contrasts"`

```{r}
t <- var_content[which(pc5$PC3<0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "#### Forth PC"`
```{r}
h <- hm(response[,c(which(pc5$PC4>0), which(pc5$PC4<0))])
if (knitr::is_html_output()) {h}
```

```{r}
t <- var_content[which(pc5$PC4>0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "contrasts"`

```{r}
t <- var_content[which(pc5$PC4<0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "#### Fifth PC"`
```{r}
h <- hm(response[,c(which(pc5$PC5>0), which(pc5$PC5<0))])
if (knitr::is_html_output()) {h}
```

```{r}
t <- var_content[which(pc5$PC5>0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

`r if (knitr::is_html_output()) "contrasts"`

```{r}
t <- var_content[which(pc5$PC5<0),] %>% 
kable(format = "html", align="l") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
if (knitr::is_html_output()) {t}
```

### 2018-04-12 Instructions/Rmarkdown_features/rmd_features.rmd
update

@@
 author: Yongfu Liao
-date: Apr 3, 2018
+date: "`r Sys.Date()`"
 bibliography: /Users/user/local_depend/citation/neanderthals.bib
@@
     toc: true
-    toc_depth: 4
-    toc_float: true
+    toc_depth: 3
+    toc_float:
+        collapsed: false
 ---
@@
 
-About This Document {.tabset}
+yaml Setup {.tabset}
 -----------------------------
+
+yaml metadata determines the output file format, looking, and any other additional customizing features of Rmarkdown files.
+
 ### yaml of this Doc
+
+This is the complete yaml header of this document.
+
 ```yaml
@@
 
-PDF Document (Chinese) {.tabset}
------------------------------
+### HTML Output
 
-### yaml
+```{yaml}
+output:
+  html_document:
+    css: ../style_sheets/style.css
+    df_print: kable
+    code_folding: hide
+    fig_width: 7
+    fig_height: 6
+    toc: true
+    toc_depth: 4
+    toc_float: true
+```
 
+### PDF Output
+
+You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
 ```yaml
@@
 
-### header.tex
+### PDF: header.tex{#pdf-header}
+
+The code below is for generating PDF documents written in (Traditional) Chinese.
+
 ```tex
@@
 
-yaml Setup {.tabset}
------------------------------
-Include the code in yaml header.
-
-### Citation
-
-Include the code in yaml header.
+### Bibliography
 
@@
 bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa-no-doi-no-issue.csl
+csl: ./citation/apa-no-doi-no-issue.csl # APA style sheet
 link-citations: yes
@@
 
-### HTML Output Options
-
-```{yaml}
-output:
-  html_document:
-    css: ../style_sheets/style.css
-    df_print: kable
-    code_folding: hide
-    fig_width: 7
-    fig_height: 6
-    toc: true
-    toc_depth: 4
-    toc_float: true
-```
+For citation syntax, read the section [Bibliography & Citations](#cite).
 
@@
 
-![](mat2tex.png){width=85% height=auto .rounded}
+![](mat2tex.png){width=100% height=auto}
 
@@
 
-Citations 
+Bibliographies & Citations{#cite} 
 -----------------------------
 
-To include **Citations**, [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.
+You can read the full documentation of [Bibliographies & Citations](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"} at Rstudio.
 
-The text cited [@RN9].
+### Citation syntax
 
-@RN15 主張...
+#### Classical Citation: **Author**, **year**, and **brackets**
+- `Some text [@Bib.ID].`
+    - Some text [@RN9].
+
+#### In-text Citation: **Author (year)**
+- `@Bib.ID Some text`
+    - @RN15 Some text
+
+- `@Bib.ID [p. 20] Some text.`
+    - @RN9 [p. 20] Some text.
+
+#### Year only: Suppress Author
+- `Some text [-@Bib.ID].`
+    - Some text [-@RN9]
+
+#### Two Citations
+- `Some text [@Bib.ID1; @Bib.ID2].`
+    -  Some text [@RN9; @RN15].
+
+5. Prefix & Suffix
+    - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
+        -  Some text [see @RN9 pp. 45; also, @RN15 ch. 2].
 
 ### Include `.bib` file in Reference {.tabset}
+
+Rmarkdown requires specific formats of bibliographies.
+One of the most common one is `.bib`.
+A lot of people (including me) use Endnote to manage bibliographies and have no time getting used to other open source reference managers.
+Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` from EndNote.
+
+Below are some syntax in Rmarkdown to control the display of reference in the document.
+
+#### Reference heading
+
+The body of cited reference in the `.bib` file will be shown under the header named Reference (it doesn't matter which **level** of heading you use).
+
+```markdown
+## Reference
+```
 
@@
 
-### Full Example
-```{html}
-<div class="success">
-| This is pragraph one. [**Red text**]{.red}, line 1. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
+### An Example
 
-Paragraph two starts here.
-</div>
-```
-
-<div class="success">
+````markdown
+`r ''````{block2, type="success"}
 | This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
@@
 Paragraph two starts here.
-</div>
+```
+````
+
+```{block2, type="success"}
+| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
+| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
+
+Paragraph two starts here.
+```
 
 ### Colored divs
-There are 4 choices of classes, defined in my stylesheet[^css]:
+
+#### Bootstrap Alert
+
+You can use bootstrap's default alert divs in Rmarkdown, defined with four classes:
+
+1. alert alert-success
+2. alert alert-warning
+3. alert alert-info
+4. alert alert-danger
+
+````markdown
+`r ''````{block, type="alert alert-success"}
+Bootstrap-defined colored region
+```
+````
+
+```{block, type="alert alert-success"}
+Bootstrap-defined colored region
+```
+
+#### Customized divs
+
+Alternative, you can define your own styled divs, as in my stylesheet[^css]:
+
+There are 4 choices of classes,
 
@@
 
-```{html}
-<div class="info">
+````markdown
+`r ''````{block, type="info"}
 some text in the colored region
-</div>
+```
+````
+
+```{block, type="info"}
+some text in the colored region
 ```
 
-<div class="info">
-some text in the colored region
-</div>
+### Bootstrap Callouts
 
-#### Bootstrap Alert
+Althougt it's "Bootstrap" callouts, it's not contained in default bootstrap theme. I defined it in my stylesheet.
 
-Alternatively, you can use bootstrap's default alert divs, defined by four classes:
+There are 4 choices of classes,
 
-1. alert-success
-2. alert-warning
-3. alert-info
-4. alert-danger
-```{html}
-<div class="alert alert-success">
-some text in the colored region
-</div>
+1. bs-callout bs-callout-success
+2. bs-callout bs-callout-warning
+3. bs-callout bs-callout-info
+4. bs-callout bs-callout-error
+
+````markdown
+`r ''````{block2, type="bs-callout bs-callout-warning"}
+#### Heading in Callout
+**Calleout Text** texttexttexttexttexttext
 ```
+````
 
-<div class="alert alert-success">
-Bootstrap-defined colored region
-</div>
+```{block2, type="bs-callout bs-callout-warning"}
+#### Heading in Callout
+**Calleout Text** texttexttexttexttexttext
+```
 
@@
 
-<div class="warning">
+```{block2, type="alert alert-success"}
 | Text of line 1
@@
 New paragraph
-</div>
+```
 
@@
 #### `class`
+
+Rmarkdown syntax allows attaching attributes (such as class, id, etc.) to certain elements by wrapping attributes into `{ ... }`.
+
+Elements allowed attributes to be attach (by markdown syntax directly):
+
+1. Section: Attributes are added next to **any level of heading**.
+2. Link: `[Text](LINK){attributes}`
+3. `span`: Text wrapped in `[`, `]`. e.g `[Text with class "red"]{.red}`.
+
 ```{markdown}
@@
 ```
-<div class="warning">
+
+```{block2, type="alert alert-success"}
 [**Red Bold text**]{.red}
-</div>
+```
 
@@
 ```
-<div class="warning">
+
+```{block2, type="alert alert-success"}
 Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-</div>
+```
 
@@
 
-    Subsequent paragraphs are indented to show that they
-belong to the previous footnote.
+    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
 
@@
 ```
-- Output[^longnote].
+- Read the output by clicking the superscript[^longnote].
 
@@
 ### Rounded Edge
-```{html}
+```{markdown}
 ![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
@@
 
+#### Boostrap
+```{markdown}
+![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
+```
+![Bootstrap Rounded](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
+
 ### Circle Image
-```{html}
+```{markdown}
 ![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
@@
 ![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
+
+#### Boostrap
+```{markdown}
+![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
+```
+![Bootstrap Circle](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
+
+### Thumbnail
+```{markdown}
+![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
+```
+![Bootstrap Thumbnail](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
 

### 2018-04-12 1062_class/eco_model/HW/C5/BMI.c

@@ -1,0 +1,25 @@
+#include<stdio.h>
+
+int main (void) {
+    double height, weight, BMI;
+    double height_meter;
+    
+    printf("Please input your height (cm) and weight (kg).\n");
+    scanf("%lf", &height);
+    scanf("%lf", &weight);
+    
+    height_meter = height / 100.0;
+    
+    BMI = (weight) / (height_meter * height_meter);
+    
+    printf("Your BMI is %.2lf.\n", BMI);
+    printf("The standard BMI is assumed to be 24.0.\n");
+    
+    if (BMI > 24.0) {
+        printf("I’m afraid you are overweight.\n");
+    } else {
+        printf("I’m afraid you are underweight.\n");
+    }
+    
+    return 0;
+}

### 2018-04-12 1062_class/eco_model/HW/C5/even_odd.c

@@ -1,0 +1,17 @@
+#include<stdio.h>
+
+int main (void) {
+    int input;
+    int i;
+    
+    printf("Please input an integer.\n");
+    scanf("%d", &input);
+    
+    if (input % 2 == 0) {
+        printf("%d is an even number\n", input);
+    } else {
+        printf("%d is an odd number\n", input);
+    }
+
+    return 0;
+}

### 2018-04-12 1062_class/eco_model/HW/C5/prime.c

@@ -1,0 +1,22 @@
+#include<stdio.h>
+
+int main (void) {
+    int input;
+    int i;
+    
+    printf("Please input an integer number (> 1).\n"); 
+    scanf("%d", &input);
+    
+    for (i=2; i<=input; i++){
+        if (input % i == 0 && input != i) {
+            printf("%d is not a prime number.\n", input);
+            break;
+        }//end if
+    }//end for
+    
+    if (i == input+1){
+        printf("%d is a prime number.\n", input);
+    }//end if
+    return 0;
+}
+        

### 2018-04-12 1062_class/eco_model/practice.c

@@ -1,16 +1,17 @@
 #include<stdio.h>
 
 int main (void) {
-    int d1 = 3;
-    int d2 = 4;
-    int d2_d1;
-    double div1, div2;
+    int num;
+    int sum=0;
+    int j;
     
-    div1 = d1/d2;
-    div2 = (double) d1/(double) d2;
-    d2_d1 = d1/d2;
+    printf("This program calculates the sum from 1 to input number.\n");
+    scanf("%d", &num);
     
-    printf("div1 = %lf & div2 = %lf & d2/d1 = %d\n", div1, div2, d2_d1);
+    for(j=1; j<=num; j++){
+        sum = sum + j;
+    }//end_for
     
+    printf("The sum from 1 to %d is %d.\n", num, sum);
     return 0;
 }

### 2018-04-20 1062_class/eco_model/HW/C5/HW4.rmd
update

---
title: "Ecological Modeling HW4"
author: Yongfu Liao
date: April 12, 2018
output: html_document
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

> Please input an integer number. (output)
>
> 3 (or 4) ⏎ (input)
>
> 3 (or 4) is an odd (or even) number . (output)

```c
#include<stdio.h>

int main (void) {
    int input;
    int i;

    printf("Please input an integer.\n");
    scanf("%d", &input);

    if (input % 2 == 0) {
        printf("%d is an even number\n", input);
    } else {
        printf("%d is an odd number\n", input);
    }

    return 0;
}
```
Download [even_odd.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C5/even_odd.c){target="_blank"}

## Question 2

> Please input your height (cm) and weight (kg). (output)
>
> 172.3 ⏎ (input)
>
> 65.0 ⏎ (input)
>
> Your BMI is 21.890. (output)
>
> The standard BMI is assumed to be 24.0. (output)
>
> I’m afraid you are overweight (or underweight). (output)

```c
#include<stdio.h>

int main (void) {
    double height, weight, BMI;
    double height_meter;

    printf("Please input your height (cm) and weight (kg).\n");
    scanf("%lf", &height);
    scanf("%lf", &weight);

    height_meter = height / 100.0;

    BMI = (weight) / (height_meter * height_meter);

    printf("Your BMI is %.2lf.\n", BMI);
    printf("The standard BMI is assumed to be 24.0.\n");

    if (BMI > 24.0) {
        printf("I’m afraid you are overweight.\n");
    } else {
        printf("I’m afraid you are underweight.\n");
    }

    return 0;
}
```
Download [BMI.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C5/BMI.c){target="_blank"}

## Question 3

> Please input an integer number (> 1). (output)
> 
> 7 ⏎ (input)
> 
> 7 is a prime number. (output)
> 
> Please input an integer number (> 1). (output)
> 
> 15 ⏎ (input)
>
> 15 is not a prime number. (output)

```c
#include<stdio.h>

int main (void) {
    int input;
    int i;

    printf("Please input an integer number (> 1).\n"); 
    scanf("%d", &input);

    for (i=2; i<=input; i++){
        if (input % i == 0 && input != i) {
            printf("%d is not a prime number.\n", input);
            break;
        }//end if
    }//end for

    if (i == input+1){
        printf("%d is a prime number.\n", input);
    }//end if
    return 0;
}

```
Download [prime.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C5/prime.c){target="_blank"}

### 2018-04-20 1062_class/eco_model/practice2.c

@@ -1,0 +1,15 @@
+#include <stdio.h>
+#include <math.h>
+
+#define STEP 0.2
+int main(void){
+    int j;
+    double x;
+    
+    for (j=0; j<=100; j++){
+        x = j*STEP;
+        printf("%lf\t%lf\n", x, sin(x));
+    } //end for
+    
+    return 0;    
+}//end main

### 2018-04-22 1062_class/Multivariate_Analysis/HW1_multivariate_normal/All.Rmd
up

---
title: "多變量分析: 作業一"
author: "劉昱維, 吳冠瑋, 廖永賦, 謝靖惟, 黃奎鈞"
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(latex2exp)
library(ggplot2)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
```

4.1
----------------------
### (a)
$f(x_1,x_2)=\frac{1}{1.2\sqrt{2}\pi}e^{-\frac{{x_1}^2+1.6x_1x_2+2{x_2}^2-(4.8\sqrt{2}+2)x_1-(1.6\sqrt{2}+12)x_2+4.8\sqrt{2}+19}{1.44}}$

### (b)
$\frac{{x_1}^2+1.6x_1x_2+2{x_2}^2-(4.8\sqrt{2}+2)x_1-(1.6\sqrt{2}+12)x_2+4.8\sqrt{2}+19}{0.36}$

### (c) Contour Plot
Plot $Distance^2 < \chi_2^2(.50)=1.39$:

$f(\textbf x) = \frac{1}{2 \pi det(\Sigma)^{(1/2)}} e^{- \chi_2^2(.50)/2 }$

```{r fig.height=2, fig.width=2.5}
library(ellipse)
library(latex2exp)
# mu <- c(1, 3)
# sigma <- matrix(c(2, -0.8*sqrt(2), -0.8*sqrt(2), 1), 2)
# mixtools::ellipse(mu, sigma, npoints = 1000, newplot = TRUE, alpha = 0.5,
#     pch = 16, cex = .1, xlab = TeX("x_1"), ylab = TeX("x_2"),
#     main="50% Contour Plot")

# ellipse::ellipse(corr, std(vector), centre = mu(vector), level = 0.5, npoints= 1000)
ell_data <- ellipse(-0.8, c(sqrt(2),1), centre = c(1,3), level = 0.5, npoints= 1000)
ggplot(as.data.frame(ell_data))+
    geom_point(aes(x=x, y=y),size = 0.1, color="#F8766D")+
    labs(x=TeX("$x_1$"), 
        y=TeX("$x_2$"), 
        title="50% Contour Plot") + theme+
    theme(axis.text.x = element_text(size = 7, face = "plain", angle = 0))
```

4.6
----------------------
Ans: (a)(c)(d)

- (a), (c): $\because ~Cov(X_1,X_2)=Cov(X_2,X_3)=0$

- (d): $\because ~both~X_1~and~X_3~are~independent~to~X_2$

4.19
------------------------

### (a)
$By~lecture~4~in~class,~it~follows~{\chi}^2_6$

### (b)
$By~CLT,~\overline{X}\xrightarrow{d}N_6(\mu,\frac{1}{20}\Sigma),~and~\sqrt{n}(\overline{X}-\mu)\xrightarrow{d}N_6(0,\Sigma)$

### (c)
$By~textbook,~19S~follows~Wishart~distribution~with~19~d.~f.$

4.24 (a)
----------------------
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
data <- read_table2("P1-4.txt", col_names = FALSE)
quantiles <- qnorm(p=seq(0.5,9.5, 1)/10)
QQ_1 <- cbind(x=sort(data$X1), quantiles)
QQ_2 <- cbind(x=sort(data$X2), quantiles)
QQ_3 <- cbind(x=sort(data$X3), quantiles)
```

```{r fig.height=2, fig.width=7.5}
library(ggplot2)
library(scales)
library(cowplot)
library(latex2exp)

p1 <- ggplot(as.data.frame(QQ_1))+
        geom_point(aes(x=quantiles, y=x), 
                   color=hue_pal()(3)[1])+
    scale_x_continuous(breaks = seq(-1.8,1.8, 0.45))+
    scale_y_continuous(breaks = seq(50,300, 25))+
    labs(x=TeX("$q_{(j)}$"),
         y=TeX("$x_{(j)}$"),
         title=TeX("$x_1$ Q-Q Plot"))+ theme
p2 <- ggplot(as.data.frame(QQ_2))+
        geom_point(aes(x=quantiles, y=x), 
                   color=hue_pal()(3)[2])+
    scale_x_continuous(breaks = seq(-1.8,1.8, 0.45))+
    scale_y_continuous(breaks = seq(5,30, 2))+
    labs(x=TeX("$q_{(j)}$"),
         y=TeX("$x_{(j)}$"),
         title=TeX("$x_2$ Q-Q Plot"))+ theme

p3 <- ggplot(as.data.frame(QQ_3))+
        geom_point(aes(x=quantiles, y=x), 
                   color=hue_pal()(3)[3])+
    scale_x_continuous(breaks = seq(-1.8,1.8, 0.45))+
    scale_y_continuous(breaks = seq(180,1500, 150))+
    labs(x=TeX("$q_{(j)}$"),
         y=TeX("$x_{(j)}$"),
         title=TeX("$x_3$ Q-Q Plot"))+ theme

plot_grid(p1, p2, p3, nrow = 1)
```

The distribution of $x_1$ seems to deviate from a normal distribution a lot, since the curve of the Q-Q plot isn't straight and looks much more like an S-shaped curve.

The distribution of $x_2$ is much closer to normal. If the most upper-right point is removed, the curve from the Q-Q plot would resemble a straight line.

4.26
------------------

```{r}
x_1 <- c(1,2,3,3,4,5,6,8,9,11)
x_2 <- c(18.95,19,17.95,15.54,14,12.95,8.94,7.49,6,3.99)
data <- as.data.frame(cbind(x_1,x_2))
```

```{r}
cov_mt <- cov(data)
x_b <- c(mean(x_1), mean(x_2))
mt_r <- round(cov_mt, digits = 2)
```

### (a): Equations

```{r results='asis', echo=FALSE}
library(mat2tex)
xx("\\textbf{S} = \\begin{pmatrix}
  s_{11} & s_{12} \\\\
  s_{12} & s_{22} \\\\
 \\end{pmatrix} =", mt_r, ", \\ \\overline{\\textbf{x}}=", x_b)
```

$distance^2 = (\textbf{x}_j - \overline{\textbf{x}})^T \textbf{S}^{-1} (\textbf{x}_j - \overline{\textbf{x}})
\\
= \left( 0.7538828748926251\left( {{x}_{\mathit{j2}}}-12.841\right) \\
+1.25693419723757\left( {{x}_{\mathit{j1}}}-5.2\right) \right) \left( {{x}_{\mathit{j2}}}-12.841\right) \\
+\left( {{x}_{\mathit{j1}}}-5.2\right) \left( 1.25693419723757\left( {{x}_{\mathit{j2}}}-12.841\right) \\
+2.189804123676667\left( {{x}_{\mathit{j1}}}-5.2\right) \right)$

### (b)
```{r}
x_b <- c(mean(x_1),mean(x_2))
dist <- rep(NA, 10)
for (i in 1:10) {
    dist[i] <- as.matrix(data[i,] - x_b) %*%  solve(cov_mt) %*% t(as.matrix(data[i,] - x_b))
}
```

- $distance^2 = (`r round(dist, 2)`)$

Observations **within estimated 50% probability contour ** is equivalent to observations with $distance^2 < \chi_2^2(.50) = 1.39$.

Exactly **`r sum(dist>1.39)/10*100`%** of observations fall within the estimated 50% probability contour, i.e. `r sum(dist>1.39)/10*100`% of observations have $distance^2 < \chi_2^2(.50) =1.39$.

### (c): Chi-square plot
```{r}
ordered <- sort(dist)
q_chi <- qchisq((1:10-0.5)/10, 2)
chi_plot <- as.data.frame(cbind(ordered, q_chi))
```

- **Ordered distance^2^**: `r round(ordered,2 )`

```{r fig.height=2, fig.width=2.5}
library(latex2exp)
library(ggplot2)
ggplot(chi_plot)+
    geom_point(aes(x=q_chi, y=ordered), color="#F8766D")+
    scale_x_continuous(breaks = seq(0,6.5, 0.5))+
    scale_y_continuous(breaks = seq(0,4.5, 1))+
    labs(x=TeX("$\\frac{\\chi_2^2(j-0.5)}{10}$"),
         y=TeX("$d_{(j)}^2$"),
         title="Chi-square Plot")+ theme
```

##### Plotting Source Code
R Code: https://liao961120.github.io/notes/HW.html

### 2018-04-22 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

---
title: "多變量分析 HW3"
author: "劉昱維, 吳冠瑋, 廖永賦, 謝靖惟, 黃奎鈞"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
css: /Users/user/local_depend/style_sheets/style.css
always_allow_html: yes
---

```{r setup, include=FALSE}
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          dev='svg',
                          fig.dim=c(3.6, 3.2))
} else {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          out.width = '70%',
                          out.height = '5.5cm')
}
options(digits = 4)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

Q1: 9.12
====================================

```{r Covariance_matrices}
S <- 10^(-3)*matrix(c(11.072, 8.019, 8.160,
                      8.019, 6.417, 6.005,
                      8.160, 6.005, 6.773), 
                    nrow = 3, ncol = 3)

Sn <- (23/24)*S # n = 24, Convert to Sn for M.L.E.
```

```{r results='asis', echo=FALSE}
"$\\mathbf{S_n} = \\frac{23}{24} \\mathbf{S} =" %_% xm(Sn ,5) %_% "$"
```

## (a) Specific Variances

```{r}
L <- c(.1022, .0752, .0765)
LL <- matrix(L, ncol = 1) %*% matrix(L, nrow = 1)
Psi <- diag(Sn - matrix(L, ncol = 1) %*% matrix(L, nrow = 1))
```

$\mathbf{S_n} \approx \hat{\mathbf{L}} \hat{\mathbf{L}}^T + \hat{\mathbf{\Psi}}$, where $diag(\mathbf{S_n}) = diag(\hat{\mathbf{L}} \hat{\mathbf{L}}^T) + diag(\hat{\mathbf{\Psi}})$

Hence, $\hat{\mathbf{\Psi}} = diag(\hat{\mathbf{\Psi}}) = diag(\mathbf{S_n} - \hat{\mathbf{L}} \hat{\mathbf{L}}^T)$

```{r results='asis', echo=FALSE}
"$\\hat{\\mathbf{\\Psi}} = " %_% xm(diag(Psi), 6) %_% "$"
```

## (b) Communalities

$\sigma_{ii} = \ell_{i1}^2 + \ell_{i2}^2 + ~...~ + \ell_{im}^2 + \psi_i$

$h_i^2 = \ell_{i1}^2 + \ell_{i2}^2 + ~...~ + \ell_{im}^2 = `r sum(L^2)`$

## (c) Proportion of variance explained by the factor

```{r}
p <-  sum(L^2) / (diag(Sn) %>% sum())
```

$\frac{s_{11} + s_{22} + ~...~ + s_{pp}}{h_i^2} = `r p`$

## (d) Residual Matrix

```{r}
Residual <- Sn - LL - Psi 
```

$\mathbf{S_n} - \mathbf{\hat{L}}\mathbf{\hat{L}}^T - \mathbf{\hat{\Psi}} = 
```{r results='asis'} 
xm(Residual, 6) %_% "$"
```

Q2: 9.32
====================================
```{r}
library(readr)
library(psych)
bulls <- read_table2("T1-10.dat", col_names = FALSE)
colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
                     "FtFrBody", "PrctFFB", "Frame",
                     "BkFat", "SaleHt", "SaleWt")
bulls <- bulls[,-c(1,9)]
```

### (a) S PC
```{r}
fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
#no principle component method
```

### (b) S MLE

```{r}
fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="ml", scores="regression")
```

### (c) R PC

```{r}
fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
#no principle component method
```

### (d) R MLE
```{r}
fa_1 <- factanal(bulls, factors = 1, scores = "regression", rotation = "varimax")
fa_2 <- factanal(bulls, factors = 2, scores = "regression", rotation = "varimax")
fa_3 <- factanal(bulls, factors = 3, scores = "regression", rotation = "varimax")
```

### (e) Compare

### (f) scatter plots of factor2 vs factor1 in (a) and (c)

Q3
====================================

```{r}
library(readr)
drinks <- read_table2("drinks.DAT", col_names = FALSE, skip = 2)
colnames(drinks) <- c("ID", "BRAND",
                      paste("X",1:10, sep=""))
```

```{r}
library(psych)
items <- drinks[,-(1:2)]
fa(cov(items), nfactors=3, rotate="varimax", covar = F, fm="pa", scores="regression")
```

#no principle component method

### 2018-04-22 1062_class/eco_model/HW/C6/HW5.rmd
up

---
title: "Ecological Modeling HW5"
author: Yongfu Liao
date: "`r Sys.Date()`"
output: 
    html_document:
        code_folding: hide
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
	)
```

## Question

Bifurcation:

$$N_{t+1} = N_t ~ e^{r (1-N_t)}, ~~1 \leq r  \leq 4.5 $$

### C Code
```c
#include <stdio.h>
#include <math.h>

int main (void) {

    //i_max determines the length of interval of r
    int i, i_max=175;

    //j_max determines the number of iterations under each r
    int j, j_max=1000;

    double r = 1; // population growth potential
    double N_int=0.1, N = N_int; // population size

    printf("N\tr\n");
    for (i=0; i<=i_max; i++){
        for (j=0; j<=j_max; j++){ //under specific r
            N = N * exp(r*(1 - N)); 
            if (j > j_max/1.5) { // print values only at final phase
                printf("%lf\t%lf\n", N, r);
            } 
        } // end for loop under a specific r
        N = N_int; // set N to initial value to prepare for a new loop with the next r
        r = r + 3.5/i_max; // calculate the next r
    }
    return 0;
}
```
Download [bifurcation.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C6/bifurcation.c){target="_blank"}

### R Code

#### Import Data
```{r}
bifurcation <- 
    readr::read_delim("bifurcation.txt", "\t",
                      escape_double = FALSE, 
                      trim_ws = TRUE)
```

#### Plotting
```{r dpi=1000, out.width="70%", out.height="70%"}
library(ggplot2)
library(latex2exp)
ggplot(bifurcation, aes(x=r, y=N))+
    geom_point(size = 0.01, color="#F8766D", alpha = 0.23)+
    scale_x_continuous(breaks = seq(1,5,0.5))+
    scale_y_continuous(breaks = 0:8)+
    labs(title=TeX("N_{t + 1} = N_t e^{r (1-N_t)}"),
         y=TeX("N_t"))
```

### 2018-04-22 1062_class/Multivariate_Analysis/HW3_factor_analysis/fa_functions.R

@@ -1,0 +1,18 @@
+# library(psych)
+# library(robustfa)
+bulls <- readr::read_table2("T1-10.dat", col_names = FALSE)
+colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
+                     "FtFrBody", "PrctFFB", "Frame",
+                     "BkFat", "SaleHt", "SaleWt")
+bulls <- as.data.frame(bulls[,-c(1,9)])
+
+library(robustfa)
+
+rob_cov_pfa <- factorScorePfa(bulls, factors = 3, covmat = NULL, cor = FALSE, rotation = "varimax", scoresMethod = "regression")
+
+rob_cov_pca <- factorScorePca(bulls, factors = 3, covmat = NULL, cor = FALSE, rotation = "varimax", scoresMethod = "regression")
+
+
+fa_cov_pa <- psych::fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
+
+fa_cov_mle <- psych::fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="mle", scores="regression")

### 2018-04-22 1062_class/Multivariate_Analysis/HW3_factor_analysis/multivariate_fc.R

@@ -1,0 +1,138 @@
+###### FUNCTIONS for MULTIVARIATE ANALYSIS #######
+#################################################
+
+############### QQ plot function ###################
+# input variables: x, ID="none"(vector of ID), theme=NULL, color="red"(color of point), 
+#                  text=TRUE(ID label beside points), text_adj=c(hjust=-0.1, vjust=0, size=3)
+# output: scatter ggplot with quantiles on x-axis, ordered x_value on y-axis
+
+QQplot <- function(x, ID="none", theme=NULL, color="red", 
+                    text=TRUE, text_adj=c(hjust=-0.1, vjust=0, size=3)) {
+    library(dplyr)
+    library(ggplot2)
+    
+    x <- as_data_frame(x) 
+    n <- nrow(x)
+    quantiles <- qnorm(p=seq(0.5/n, 1-0.5/n, 1/n))
+    
+    if (ID == "none") { # assign ID if not passed
+        ID <- as.character(1:n)
+    } else {
+        ID <- as_data_frame(ID)
+        ID <- as.character(ID[[colnames(ID)]])
+        }
+    
+    if (text == TRUE) {
+        text <- geom_text(aes(label=ID),
+                              hjust=text_adj[1],
+                              vjust=text_adj[2],
+                              size = text_adj[3])
+    } else {text <- NULL}
+    
+    data <- cbind(ID, x)
+    colnames(data) <- c("ID", "x")
+    data <- data %>% arrange(x) %>% mutate(quantile=quantiles)
+    
+    pl <- ggplot(data, aes(x=quantiles, y=x))+
+        geom_point(color=color)+
+        text + theme +
+        labs(x="Predicted Quantile",
+             y="x",
+             title="Q-Q Plot")
+    pl
+}
+
+
+######## Scree Plot ###############
+## X: PCA list(contains 'sdev')
+
+scree_plot <-
+    scree_plot <-
+    function (X,
+              choice = c("eigenvalue", "variance"),
+              double_axis = TRUE,
+              axis_limits=NULL,
+              sub_axis_name = "n",
+              geom = c("line"), # "bar"
+              barfill = "steelblue",
+              barcolor = "steelblue",
+              linecolor = "black",
+              ncp = 10,
+              addlabels = FALSE,
+              hjust = 0,
+              main = NULL,
+              xlab = NULL,
+              ylab = NULL,
+              ggtheme = theme_minimal(),
+              ...)
[…]

### 2018-04-22 1062_class/eco_model/HW/C6/bifurcation.c

@@ -1,0 +1,27 @@
+#include <stdio.h>
+#include <math.h>
+
+int main (void) {
+    
+    //i_max determines the length of interval of r
+    int i, i_max=175; 
+    
+    //j_max determines the number of iterations under each r
+    int j, j_max=1000;
+    
+    double r = 1; // population growth potential
+    double N_int=0.1, N = N_int; // population size
+    
+    printf("N\tr\n");
+    for (i=0; i<=i_max; i++){
+        for (j=0; j<=j_max; j++){ //under specific r
+            N = N * exp(r*(1 - N)); 
+            if (j > j_max/1.5) { // print values only at final phase
+                printf("%lf\t%lf\n", N, r);
+            } 
+        } // end for loop under a specific r
+        N = N_int; // set N to initial value to prepare for a new loop with the next r
+        r = r + 3.5/i_max; // calculate the next r
+    }
+    return 0;
+}

### 2018-04-22 1062_class/eco_model/HW/C6/HW5.rmd
up

@@
 #### Plotting
-```{r dpi=1000, out.width="70%", out.height="70%"}
+```{r dpi=700, out.width="70%", out.height="70%"}
 library(ggplot2)

### 2018-04-22 minimal_web_DataCampLight/rmarkdown/gsheet_demo.Rmd
up

---
title: "Google 表單即時回饋"
date: "`r Sys.Date()`"
output: 
    html_document:
        css: ./style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
source("./bootstrap_fc.R")
date <- lubridate::with_tz(Sys.time(), tzone = "Asia/Taipei")
```

```{r}
# Button trigger modal
button_bs("填寫表單", data_toggle="modal", data_target="#sheet", class="primary pull-left")
```

```{r}
# iframe for Google Form
iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 300px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')

modal(id="sheet", modal_header = "Google 表單", modal_body=iframe)
```

<br><br><br>

```{r}
library(htmltools)
HTML('
<script src="https://cdn.datacamp.com/datacamp-light-latest.min.js"></script>
    <div data-datacamp-exercise data-lang="r">
        <code data-type="pre-exercise-code">
            data <- readr::read_csv(url("https://docs.google.com/spreadsheets/d/e/2PACX-1vQz4zjZfhWBYYRuW2Zhhx-sXvnlrS6vpvcgP0cJPdvsQI-6eKggXmpaWbu4dgbMQgcOHv0NQxL8a_K_/pub?output=csv"))
            data <- as.data.frame(data)
            colnames(data) <- c("DateTime", "Token", "Score")
            data <- data[which(data$Score!=100),]
            score <- function(token) {
                i <- which(data$Token==token)
                data[i,]
            }
	    </code>
        <code data-type="sample-code">
            # Put Token in "". Ex: score("abcde123")
            score("Enter_your_Token")
	    </code>
    </div>
')
```

### 2018-04-22 minimal_web_DataCampLight/rmarkdown/bootstrap_fc.R

@@ -1,0 +1,123 @@
+library(htmltools)
+
+######## Button Created by <a> #############
+button_a <- function(text, class="primary", role="button") {
+    class <- paste("btn-", class, sep="")
+    a(role=role, class=paste("btn", class, sep = " "),
+           text)
+}
+
+####### Button by <button> #########
+## positioning: class="pull-right"
+
+button_bs <- function(text, class="primary", data_dismiss=NULL,
+data_toggle=NULL, data_target=NULL, data_parent=NULL,
+aria_expanded=NULL, aria_controls=NULL) {
+    class <- paste("btn", paste("btn-", class, sep=""))
+    tags$button(type="button", class=class,
+                # Modal/collapse Control
+                `data-parent`=data_parent,
+                `data-toggle`=data_toggle, #open modal
+                `data-target`=data_target, #modal ID
+                # collapse
+                `aria-expanded`=aria_expanded,
+                `aria-controls`=aria_controls,
+                `data-dismiss`=data_dismiss,
+                text)
+}
+
+################# Panel #####################
+panel <- function(content, title, color = "default") {
+    color <- paste("panel", paste("panel-", color, sep = ""))
+    div(class = color,
+        div(class = "panel-heading",
+            h3(class = "panel-title", title)),
+        div(class = "panel-body", content))
+}
+
+############### Panel-group ###############
+panel_group <- function(id, p1, p2=NULL, p3=NULL, 
+                        p4=NULL, p5=NULL, p6=NULL, 
+                        p7=NULL, p8=NULL, p9=NULL,
+                        p10=NULL) {
+    div(class="panel-group", id=id,
+        role="tablist", `aria-multiselectable`="true",p1, p2, p3, p4, p5, p6, p7, p8, p9, p10)
+}
+
+panel_sub <- function(col_tar, id_head="head", aria_label, data_parent, title, content, 
+                      color = "default",
+                      panel_coll = "panel-collapse collapse") {
+    color <- paste("panel", paste("panel-", color, sep = ""))
+    div(class = color,
+        div(class = "panel-heading", role="tab", id=id_head,
+            h4(class = "panel-title", 
+               a(role="button", `data-toggle`="collapse", `aria-expanded`="true",
+                 `data-parent`=data_parent, href=paste("#",col_tar,sep=""),
+                 `aria-controls`=col_tar,
+                 title)
+               )
+            ),
+        div(id = col_tar,
+            class = panel_coll,
+            role = "tabpanel" ,
[…]

### 2018-04-22 minimal_web_DataCampLight/rmarkdown/gsheet_demo.Rmd
up

@@
 # iframe for Google Form
-iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 300px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')
+iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 360px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')
 

### 2018-04-23 minimal_web_DataCampLight/rmarkdown/index.Rmd
up

---
title: "Google 表單即時回饋"
date: "`r Sys.Date()`"
author: "Yongfu, Liao"
output: 
    html_document:
        css: ./style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
source("C:/Users/user/local_depend/R functions/bootstrap_fc.R")
date <- lubridate::with_tz(Sys.time(), tzone = "Asia/Taipei")
library(htmltools)
```

此為 google 表單分數即時回饋的示範平台，請先點選下方「填寫表單」以填寫問卷，問卷最後會要求你輸入 **Token**, 此 **Token** 是用來查詢問卷分數的，請將其記下。

```{r}
# Button trigger modal
button_bs("填寫表單", data_toggle="modal", data_target="#sheet", class="success pull-left")
```

```{r}
# iframe for Google Form
iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 360px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')

modal(id="sheet", modal_header = "Google 表單", modal_body=iframe)
```

<br><br><br>

以下按鈕將開啟 DataCamp Light, 為輔助程式語言教學與學習的工具，可用來執行 R 或 Python。下方的例子執行的是 R 語言，並且已預先讀入資料。您僅需於`score()`中輸入金鑰，例如，若您於問卷中 Token 那題填寫「abcde123」，請於下方輸入`score("abcde123")`。若查無結果，請重新整理頁面後再輸入一次。

```{r}
# Button trigger modal: search
button_bs("查詢結果", data_toggle="modal", data_target="#search", class="primary pull-left")
```

```{r}
# iframe for Google Form
iframe <- HTML('<iframe src="./blank.html" style="position: relative; height: 360px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')

modal(id="search", modal_header = "查詢結果", modal_body=iframe)
```

### 2018-04-23 R functions/bootstrap_fc.R
up

@@ -82,7 +82,7 @@ collapse <- function(content, id, color="well", class="collapse") {
 ########### Modal ############
 ## size: modal-lg | modal-sm
 modal <-
-    function(modal_header, id, modal_body,
+    function(modal_header, id, modal_body, foot=T, head=T,
              modal_body2 = NULL, modal_body3= NULL,
              modal_body4= NULL, modal_body5= NULL,
              modal_body6= NULL, modal_footer =NULL, 
@@ -98,23 +98,25 @@ modal <-
                 role = "document",
                 # modal content
                 div(class = "modal-content",
-                    div(class = "modal-header",
-                        tags$button(type = "button",
-                                    class = "close",
-                                    `data-dismiss` = "modal",
-                                    HTML("&times;")
+                        div(class = "modal-header",
+                            tags$button(type = "button",
+                                        class = "close",
+                                        `data-dismiss` = "modal",
+                                        HTML("&times;")
+                            ),
+                            h4(class = "modal-title", modal_header)
                         ),
-                        h4(class = "modal-title", modal_header)
-                    ),
                     div(class = "modal-body",
                         modal_body, modal_body2,
                         modal_body3, modal_body4,
                         modal_body5, modal_body6),
-                    div(class = "modal-footer",
-                        button_bs("Close", class = "default",
-                                  data_dismiss = "modal"),
-                        modal_footer
-                    )
+                    if (foot==T){
+                        div(class = "modal-footer",
+                            button_bs("Close", class = "default",
+                                      data_dismiss = "modal"),
+                            modal_footer
+                        )
+                    }
                 )
             )
         )

### 2018-04-23 minimal_web_DataCampLight/rmarkdown/bootstrap_fc.R

@@ -1,123 +1,0 @@
-library(htmltools)
-
-######## Button Created by <a> #############
-button_a <- function(text, class="primary", role="button") {
-    class <- paste("btn-", class, sep="")
-    a(role=role, class=paste("btn", class, sep = " "),
-           text)
-}
-
-####### Button by <button> #########
-## positioning: class="pull-right"
-
-button_bs <- function(text, class="primary", data_dismiss=NULL,
-data_toggle=NULL, data_target=NULL, data_parent=NULL,
-aria_expanded=NULL, aria_controls=NULL) {
-    class <- paste("btn", paste("btn-", class, sep=""))
-    tags$button(type="button", class=class,
-                # Modal/collapse Control
-                `data-parent`=data_parent,
-                `data-toggle`=data_toggle, #open modal
-                `data-target`=data_target, #modal ID
-                # collapse
-                `aria-expanded`=aria_expanded,
-                `aria-controls`=aria_controls,
-                `data-dismiss`=data_dismiss,
-                text)
-}
-
-################# Panel #####################
-panel <- function(content, title, color = "default") {
-    color <- paste("panel", paste("panel-", color, sep = ""))
-    div(class = color,
-        div(class = "panel-heading",
-            h3(class = "panel-title", title)),
-        div(class = "panel-body", content))
-}
-
-############### Panel-group ###############
-panel_group <- function(id, p1, p2=NULL, p3=NULL, 
-                        p4=NULL, p5=NULL, p6=NULL, 
-                        p7=NULL, p8=NULL, p9=NULL,
-                        p10=NULL) {
-    div(class="panel-group", id=id,
-        role="tablist", `aria-multiselectable`="true",p1, p2, p3, p4, p5, p6, p7, p8, p9, p10)
-}
-
-panel_sub <- function(col_tar, id_head="head", aria_label, data_parent, title, content, 
-                      color = "default",
-                      panel_coll = "panel-collapse collapse") {
-    color <- paste("panel", paste("panel-", color, sep = ""))
-    div(class = color,
-        div(class = "panel-heading", role="tab", id=id_head,
-            h4(class = "panel-title", 
-               a(role="button", `data-toggle`="collapse", `aria-expanded`="true",
-                 `data-parent`=data_parent, href=paste("#",col_tar,sep=""),
-                 `aria-controls`=col_tar,
-                 title)
-               )
-            ),
-        div(id = col_tar,
-            class = panel_coll,
-            role = "tabpanel" ,
[…]

### 2018-04-30 1062_class/Multivariate_Analysis/HW2_PCA/Q5.Rmd
up

--- 2018-04-02 1062_class/Multivariate_Analysis/HW2/Q5.Rmd
@@
 title: 'Q5: Food Price'
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
                       warning=FALSE,
-                      dev='svg',
+                      #dev='svg',
                       fig.dim=c(3.6, 3.2))

### 2018-04-30 1062_class/eco_model/HW/C7/prey-predator.c

@@ -1,0 +1,36 @@
+#include <stdio.h>
+#include <math.h>
+
+int main (void) {
+    
+    double h = 0.001; // interval between each calculation
+    double x = 0.1, y = 0.1; //set initial population size of prey, predator
+    double k1_x, k2_x, k3_x, k4_x;
+    double k1_y, k2_y, k3_y, k4_y;
+    double r = 1.0, a = 1.0, b = 0.5, Ht = 1.0, m = 0.1;
+    double K = 1.2; // 1.0, 1.2, 2.0
+    int i, t=300000; //determine the length of time, time = t*h
+    double time = 0;
+    
+    for (i = 0; i <= t; i++) {
+        printf("%lf\t%lf\t%lf\n", time, x, y);
+        
+        k1_x = r*x*(1 - x/K) - a*(x*y) / (1 + Ht*a*x);
+        k1_y = b*(x*y)/(1 + Ht*a*x) - m*y;
+        
+        k2_x = r*(x + (h/2)*k1_x)*(1 - (x + (h/2)*k1_x)/K) - a*((x + (h/2)*k1_x)*y) / (1 + Ht*a*(x + (h/2)*k1_x));
+        k2_y = b*(x*(y + h/2*k1_y))/(1 + Ht*a*x) - m*(y + h/2*k1_y);
+        
+        k3_x = r*(x + (h/2)*k2_x)*(1 - (x + (h/2)*k2_x)/K) - a*((x + (h/2)*k2_x)*y) / (1 + Ht*a*(x + (h/2)*k2_x));
+        k3_y = b*(x*(y + h/2*k2_y))/(1 + Ht*a*x) - m*(y + h/2*k2_y);
+        
+        k4_x = r*(x + h*k3_x)*(1 - (x + h*k3_x)/K) - a*((x + h*k3_x)*y) / (1 + Ht*a*(x + h*k3_x));
+        k4_y = b*(x*(y + h*k3_y))/(1 + Ht*a*x) - m*(y + h*k3_y);
+        
+        time = time + h;
+        x = x + h * 1/6 * (k1_x + 2*k2_x + 2*k3_x + k4_x);
+        y = y + h * 1/6 * (k1_y + 2*k2_y + 2*k3_y + k4_y);
+    }
+    
+    return 0;
+}

### 2018-05-05 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

@@
 if (knitr::is_html_output()) {
-    knitr::opts_chunk$set(echo = FALSE,
-                          message=FALSE,
-                          warning=FALSE,
+    knitr::opts_chunk$set(
+	echo = FALSE,
+	fig.dim = c(3.6, 3.2),
+	message = FALSE,
+	warning = FALSE,
 	comment = "",
-                          dev='svg',
-                          fig.dim=c(3.6, 3.2))
+	dev = "svg",
+	out.width = "70%"
+)
 } else {
@@
                           comment = "",
-                          out.width = '70%',
-                          out.height = '5.5cm')
+                          out.width = '70%')
 }
@@
 bulls <- bulls[,-c(1,9)]
+source("fa_functions.R") # for formating loading mt
 ```
@@
 ```{r}
-fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
-#no principle component method
+fa_S_pc <- principal(bulls, 
+              nfactors = 2, 
+              rotate = 'varimax', 
+              covar = TRUE)
+fa_S_pc[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 30, markdown = T) %>%
+    kable("markdown",align = 'c', escape = F)
 ```
 
-### (b) S MLE
+### (b) S ML
 
 ```{r}
-fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="ml", scores="regression")
+fa_S_ml <- fa(bulls, nfactors=2, 
+              rotate="varimax", covar = T,
+              fm="ml", scores="regression")
+fa_S_ml[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 30, markdown = F) %>%
+    kable("html",align = 'c', escape = F)
 ```
@@
 ```{r}
-fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
-#no principle component method
+fa_R_pc <- principal(bulls, 
+              nfactors = 2, 
+              rotate = 'varimax', 
+              covar = F)
+fa_R_pc[["loadings"]][,]
 ```
 
-### (d) R MLE
+### (d) R ML
 ```{r}
-fa_1 <- factanal(bulls, factors = 1, scores = "regression", rotation = "varimax")
-fa_2 <- factanal(bulls, factors = 2, scores = "regression", rotation = "varimax")
-fa_3 <- factanal(bulls, factors = 3, scores = "regression", rotation = "varimax")
+fa_R_ml <- fa(bulls, nfactors=2, 
+              rotate="varimax", covar = F, 
+              fm="ml", scores="regression")
+fa_R_ml[["loadings"]][,]
 ```
@@
 items <- drinks[,-(1:2)]
-fa(cov(items), nfactors=3, rotate="varimax", covar = F, fm="pa", scores="regression")
 ```

### 2018-05-05 1062_class/Multivariate_Analysis/HW3_factor_analysis/fa_functions.R

@@ -1,18 +1,23 @@
-# library(psych)
-# library(robustfa)
-bulls <- readr::read_table2("T1-10.dat", col_names = FALSE)
-colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
-                     "FtFrBody", "PrctFFB", "Frame",
-                     "BkFat", "SaleHt", "SaleWt")
-bulls <- as.data.frame(bulls[,-c(1,9)])
+## input factor loading matrix, output df with highlighted loadings
 
-library(robustfa)
-
-rob_cov_pfa <- factorScorePfa(bulls, factors = 3, covmat = NULL, cor = FALSE, rotation = "varimax", scoresMethod = "regression")
-
-rob_cov_pca <- factorScorePca(bulls, factors = 3, covmat = NULL, cor = FALSE, rotation = "varimax", scoresMethod = "regression")
-
-
-fa_cov_pa <- psych::fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
-
-fa_cov_mle <- psych::fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="mle", scores="regression")
+format_loading_matrix <- function(loading, criterion=0.5, markdown=T) {
+    df <- as.data.frame(loading)
+    df_index <- df
+    
+    library(dplyr)
+    for (j in 1:ncol(df)){ #for1
+        for (i in 1:nrow(df)){
+            if (markdown) {  # latex output
+                if (abs(df_index[i,j]) > abs(criterion)){
+                    df[i,j] <- paste("**", df[i, j], "**", sep = "")
+                }
+            } #end latex output
+            else { # HTML output
+                if (abs(df_index[i,j]) > abs(criterion)){
+                    df[i,j] <- paste('<span style="color:red">', df[i, j], '</span>', sep="")
+                }
+            }#end html output
+        }#end for2
+    }#end for1
+df
+} #end fc

### 2018-05-07 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

@@
 
-### (a) S PC
+## (a) S PC
 ```{r}
@@
 
-### (b) S ML
+## (b) S ML
 
@@
 fa_S_ml[["loadings"]][,] %>% round(3) %>%
-    format_loading_matrix(criterion = 30, markdown = F) %>%
-    kable("html",align = 'c', escape = F)
+    format_loading_matrix(criterion = 30, markdown = T) %>%
+    kable("markdown",align = 'c', escape = F)
 ```
 
-### (c) R PC
+## (c) R PC
 
@@
               covar = F)
-fa_R_pc[["loadings"]][,]
+fa_R_pc[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 0.65, markdown = T) %>%
+    kable("markdown",align = 'c', escape = F)
 ```
 
-### (d) R ML
+## (d) R ML
 ```{r}
@@
               fm="ml", scores="regression")
-fa_R_ml[["loadings"]][,]
+fa_R_ml[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 0.6, markdown = T) %>%
+    kable("markdown",align = 'c', escape = F)
 ```
 
-### (e) Compare
+## (e) Compare **S** & **R**
 
-### (f) scatter plots of factor2 vs factor1 in (a) and (c)
+## (f) scatter plots of factor2 vs factor1 in (a) and (c)
+
+### (a) 
+```{r out.width="40%"}
+library(ggplot2)
+fa_S_pc[["scores"]] %>% as.data.frame() %>%
+    ggplot()+
+    geom_point(aes(x=RC1, y=RC2), size=1)+
+    labs(x="Factor 1", y="Factor 2", title="FA with S",
+         caption="Principle component method")
+```
+
+### (c) 
+```{r out.width="40%"}
+library(ggplot2)
+fa_R_pc[["scores"]] %>% as.data.frame() %>%
+    ggplot()+
+        geom_point(aes(x=RC1, y=RC2), size=1)+
+        labs(x="Factor 1", y="Factor 2", title="FA with R",
+             caption="Principle component method")
+```
 
@@
 
+## (a) Appropriate number of factors 
 ```{r}
@@
                       paste("X",1:10, sep=""))
+drinks <- drinks[-nrow(drinks),]
 ```
 
-```{r}
+```{r out.width="40%"}
 library(psych)
-items <- drinks[,-(1:2)]
+fa_R_pc2 <- principal(drinks[,3:12], 
+              nfactors = 4, 
+              rotate = 'varimax', 
+              covar = F)
+fa_R_pc2[["values"]] %>% 
+    cbind(X=1:10) %>% as.data.frame() %>%
+    ggplot()+
+        geom_point(aes(x=X, y=.), size=2) +
+        scale_x_continuous(breaks = 1:10)+
+        labs(x="i", y="eigenvalue",
+             title="Scree Plot")
 ```
 
-#no principle component method
+By the unity criterion we use 4 factors[^fact].
+
+```{r}
+fa_R_pc2[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 0.5, markdown = T) %>%
+    kable("markdown",align = 'c', escape = F)
+```
+
+[^fact]: Although **factor 4** is less than 1, it's eigenvalue is very close to **factor 3**, hence we retain **factor 4**.
+
+## (b) Label the Factors
+
+## (c) Average factor scores of each brand
+
+```{r index}
+br1 <- which(drinks$BRAND == "1") #index for brand 1
+br2 <- which(drinks$BRAND == "2")
+br3 <- which(drinks$BRAND == "3")
+br4 <- which(drinks$BRAND == "4")
+br5 <- which(drinks$BRAND == "5")
+br6 <- which(drinks$BRAND == "6")
+```
+
+```{r Pepsi}
+fs1 <- fa_R_pc2[["scores"]][br1,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs2 <- fa_R_pc2[["scores"]][br2,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs3 <- fa_R_pc2[["scores"]][br3,] %>% colMeans() %>% t() %>%
+    as.data.frame() 
+fs4 <- fa_R_pc2[["scores"]][br4,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs5 <- fa_R_pc2[["scores"]][br5,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs6 <- fa_R_pc2[["scores"]][br6,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+
+avg_fs <- rbind(fs1, fs2, fs3, fs4, fs5, fs6) %>% as.data.frame()
+rownames(avg_fs) <-  c("Pepsi", "Coke", "Gatorade",
+                    "Allsport", "Lipton tea", "Nestea")
+```
+
+### Average factor scores
+```{r factor-score-table}
+kable(avg_fs, "markdown", align = 'c',
+      digits = 3,
+      col.names= c("F1", "F2", "F3", "F4"),
+      row.names = T, 
+      caption = "Average Factor Scores of each brand")
+```
+
+## (d)
+
+```{r}
+data <- cbind(fa_R_pc2[["scores"]], as.factor(drinks$BRAND)) %>%
+    as.data.frame()
+colnames(data) <- c("F1", "F2", "F3", "F4", "Brand")
+
+data[data$Brand =="1", "Brand"] <- "Pepsi"
+data[data$Brand =="2", "Brand"] <- "Coke"
+data[data$Brand =="3", "Brand"] <- "Gatorade"
+data[data$Brand =="4", "Brand"] <- "Allsport"
+data[data$Brand =="5", "Brand"] <- "Lipton tea"
+data[data$Brand =="6", "Brand"] <- "Nestea"
+```
+
+```{r out.width="50%", fig.show='hold'}
+### F1, F2
+ggplot(data[,c(1,2, 5)]) +
+    geom_point(aes(x=F1, y=F2, color=Brand))
+
+### F1, F3
+ggplot(data[,c(1,3, 5)]) +
+    geom_point(aes(x=F1, y=F3, color=Brand))
+```
+
+```{r out.width="50%", fig.show='hold'}
+### F1, F4
+ggplot(data[,c(1,4, 5)]) +
+    geom_point(aes(x=F1, y=F4, color=Brand))
+
+### F2, F3
+ggplot(data[,c(2,3, 5)]) +
+    geom_point(aes(x=F2, y=F3, color=Brand))
+```
+
+```{r out.width="50%", fig.show='hold'}
+### F2, F4
+ggplot(data[,c(2,4, 5)]) +
+    geom_point(aes(x=F2, y=F4, color=Brand))
+
+### F3, F4
+ggplot(data[,c(3,4, 5)]) +
+    geom_point(aes(x=F3, y=F4, color=Brand))
+```

### 2018-05-07 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

@@
     knitr::opts_chunk$set(
-	echo = FALSE,
+	echo = TRUE,
 	fig.dim = c(3.6, 3.2),
@@
                      "BkFat", "SaleHt", "SaleWt")
-bulls <- bulls[,-c(1,9)]
+bulls <- bulls[,-c(1,2)]
 source("fa_functions.R") # for formating loading mt
@@
 fa_S_pc <- principal(bulls, 
-              nfactors = 2, 
+              nfactors = 3, 
               rotate = 'varimax', 
@@
 ```{r}
-fa_S_ml <- fa(bulls, nfactors=2, 
+fa_S_ml <- fa(bulls, nfactors=3, 
               rotate="varimax", covar = T,
@@
 fa_R_pc <- principal(bulls, 
-              nfactors = 2, 
+              nfactors = 3, 
               rotate = 'varimax', 
@@
 ```{r}
-fa_R_ml <- fa(bulls, nfactors=2, 
+fa_R_ml <- fa(bulls, nfactors=3, 
               rotate="varimax", covar = F, 
@@
 ```{r}
+source("fa_functions.R")
 fa_R_pc2[["loadings"]][,] %>% round(3) %>%
@@
 
-avg_fs <- rbind(fs1, fs2, fs3, fs4, fs5, fs6) %>% as.data.frame()
+avg_fs <- rbind(fs1, fs2, fs3, fs4, fs5, fs6) %>% 
+    as.data.frame()
 rownames(avg_fs) <-  c("Pepsi", "Coke", "Gatorade",
@@
 
-```{r}
-data <- cbind(fa_R_pc2[["scores"]], as.factor(drinks$BRAND)) %>%
-    as.data.frame()
-colnames(data) <- c("F1", "F2", "F3", "F4", "Brand")
+```{r out.width="50%", fig.show='hold'}
+avg_fs <- cbind(avg_fs, rownames(avg_fs))
+colnames(avg_fs) <- c("F1", "F2", "F3", "F4", "Brand")
 
-data[data$Brand =="1", "Brand"] <- "Pepsi"
-data[data$Brand =="2", "Brand"] <- "Coke"
-data[data$Brand =="3", "Brand"] <- "Gatorade"
-data[data$Brand =="4", "Brand"] <- "Allsport"
-data[data$Brand =="5", "Brand"] <- "Lipton tea"
-data[data$Brand =="6", "Brand"] <- "Nestea"
-```
-
-```{r out.width="50%", fig.show='hold'}
 ### F1, F2
-ggplot(data[,c(1,2, 5)]) +
-    geom_point(aes(x=F1, y=F2, color=Brand))
+ggplot(avg_fs[,c(1,2, 5)],aes(x=F1, y=F2, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none')
 
 ### F1, F3
-ggplot(data[,c(1,3, 5)]) +
-    geom_point(aes(x=F1, y=F3, color=Brand))
+ggplot(avg_fs[,c(1,3, 5)],aes(x=F1, y=F3, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none')
 ```
@@
 ### F1, F4
-ggplot(data[,c(1,4, 5)]) +
-    geom_point(aes(x=F1, y=F4, color=Brand))
+ggplot(avg_fs[,c(1,4, 5)],aes(x=F1, y=F4, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none')
 
 ### F2, F3
-ggplot(data[,c(2,3, 5)]) +
-    geom_point(aes(x=F2, y=F3, color=Brand))
+ggplot(avg_fs[,c(2,3, 5)], aes(x=F2, y=F3, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none')
 ```
@@
 ### F2, F4
-ggplot(data[,c(2,4, 5)]) +
-    geom_point(aes(x=F2, y=F4, color=Brand))
+ggplot(avg_fs[,c(2,4, 5)],aes(x=F2, y=F4, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none')
 
 ### F3, F4
-ggplot(data[,c(3,4, 5)]) +
-    geom_point(aes(x=F3, y=F4, color=Brand))
+ggplot(avg_fs[,c(3,4, 5)], aes(x=F3, y=F4, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none')
 ```

### 2018-05-07 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

--- 2018-05-05 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
@@
 output:
-  html_document: default
   pdf_document:
@@
       in_header: header.tex
+  html_document: default
 css: /Users/user/local_depend/style_sheets/style.css
 always_allow_html: yes
+fontsize: 11pt
+geometry: margin=0.7in
 ---
@@
 ```{r setup, include=FALSE}
+library(svglite)
 if (knitr::is_html_output()) {
@@
 	comment = "",
-	dev = "svg",
+	dev='svglite',
 	out.width = "70%"
@@
 } else {
+    library(showtext)
     knitr::opts_chunk$set(echo = FALSE,
@@
                           comment = "",
-                          out.width = '70%')
+                          out.width = '70%',
+                          fig.showtext = T)
 }
@@
 ## (b) Communalities
+```{r}
+h2 <- diag(Sn) - Psi
+```
 
@@
 
-$h_i^2 = \ell_{i1}^2 + \ell_{i2}^2 + ~...~ + \ell_{im}^2 = `r sum(L^2)`$
+$h_i^2 = \ell_{i1}^2 + \ell_{i2}^2 + ~...~ + \ell_{im}^2 = \ell_{i1}^2$
+
+$h_1^2 = `r h2[1]`, ~ h_2^2 = `r h2[2]`, ~ h_3^2 = `r h2[3]`$
 
@@
 
-### (a) S PC
+## (a) S PC
 ```{r}
 fa_S_pc <- principal(bulls, 
-              nfactors = 2, 
+              nfactors = 3, 
               rotate = 'varimax', 
@@
 fa_S_pc[["loadings"]][,] %>% round(3) %>%
-    format_loading_matrix(criterion = 30, markdown = T) %>%
-    kable("markdown",align = 'c', escape = F)
+    format_loading_matrix(criterion = 10, markdown = T) %>%
+    kable("markdown",align = 'l', escape = F)
 ```
 
-### (b) S ML
+\newpage
+
+## (b) S ML
 
 ```{r}
-fa_S_ml <- fa(bulls, nfactors=2, 
+fa_S_ml <- fa(bulls, nfactors=3, 
               rotate="varimax", covar = T,
@@
 fa_S_ml[["loadings"]][,] %>% round(3) %>%
-    format_loading_matrix(criterion = 30, markdown = F) %>%
-    kable("html",align = 'c', escape = F)
+    format_loading_matrix(criterion = 10, markdown = T) %>%
+    kable("markdown",align = 'l', escape = F)
 ```
 
-### (c) R PC
+## (c) R PC
 
@@
 fa_R_pc <- principal(bulls, 
-              nfactors = 2, 
+              nfactors = 3, 
               rotate = 'varimax', 
               covar = F)
-fa_R_pc[["loadings"]][,]
+fa_R_pc[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 0.65, markdown = T) %>%
+    kable("markdown",align = 'l', escape = F)
 ```
 
-### (d) R ML
+## (d) R ML
 ```{r}
-fa_R_ml <- fa(bulls, nfactors=2, 
+fa_R_ml <- fa(bulls, nfactors=3, 
               rotate="varimax", covar = F, 
               fm="ml", scores="regression")
-fa_R_ml[["loadings"]][,]
+fa_R_ml[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 0.5, markdown = T) %>%
+    kable("markdown",align = 'l', escape = F)
 ```
 
-### (e) Compare
+## (e) Compare **S** & **R**
 
-### (f) scatter plots of factor2 vs factor1 in (a) and (c)
+The results obtained using covariance matrices are hard to interpret here.
+Since there are three kinds of units used: **pound**, **inch**, and **self-defined scales(1-8)**, the factor loadings on some variables are very large and others small.
+
+Interpretation of the factors is straightforward using results obtained from the covariance matrix.  
+By (c) and (d), 
+1. factor 1 has larger loadings on **YrHgt**, **Frame**, and **SaleHt**, which are all related to the **height**s of the bulls.
+2. Factor 2 has large loadings on **FtFrBody** and **PrctFFB** and is negatively related to **BkFat** in both methods(PC & ML) of factor analysis. It might be called a **lean** factor.
+3.
+In both PC & ML method of factor analysis, the loadings of factor 3 is large on **SaleWt**.
+The loading is also large on **BkFat** from the PC method, and the loading is medium on **FtFrBody** from the ML method.
+Factor 3 might be related to the **weight**s of the bulls.
+
+\newpage
+
+## (f) scatter plots of factor2 vs factor1 in (a) and (c)
+
+The point, **51**, in the scatter plot on the left and the point, **16**, in the scatter plot on the right seem to be outliers.
+
+```{r}
+library(ggplot2)
+data <- fa_S_pc[["scores"]] %>% as.data.frame()
+p_S <- ggplot(data, aes(x=RC1, y=RC2))+
+    geom_point(size=1) +
+    geom_text(aes(label=rownames(data)),
+              hjust=0.5, vjust=-0.4, size = 2.5) +
+    theme(legend.position = 'none')+
+    labs(x="Factor 1", y="Factor 2", title="FA with S")
+```
+
+```{r}
+data <- fa_R_pc[["scores"]] %>% as.data.frame()
+p_R <- ggplot(data, aes(x=RC1, y=RC2))+
+    geom_point(size=1) +
+    geom_text(aes(label=rownames(data)),
+          hjust=0.5, vjust=-0.4, size = 2.5) +
+    theme(legend.position = 'none')+
+    labs(x="Factor 1", y="Factor 2", title="FA with R")
+```
+
+```{r out.width="50%", fig.show='hold'}
+p_S
+p_R
+```
 
@@
                       paste("X",1:10, sep=""))
+drinks <- drinks[-nrow(drinks),]
+```
+
+```{r out.width="40%"}
+library(psych)
+fa_R_pc2 <- principal(drinks[,3:12], 
+              nfactors = 4, 
+              rotate = 'varimax', 
+              covar = F)
+fa_R_pc2[["values"]] %>% 
+    cbind(X=1:10) %>% as.data.frame() %>%
+    ggplot()+
+        geom_point(aes(x=X, y=.), size=2) +
+        scale_x_continuous(breaks = 1:10)+
+        labs(x="i", y="eigenvalue",
+             title="Scree Plot")
+```
+
+By the unity criterion we use 4 factors[^fact].
+
+```{r}
+source("fa_functions.R")
+fa_R_pc2[["loadings"]][,] %>% round(3) %>%
+    format_loading_matrix(criterion = 0.5, markdown = T) %>%
+    kable("markdown",align = 'l', escape = F)
+```
+
+[^fact]: Although **factor 4** is less than 1, it's eigenvalue is very close to **factor 3**, hence we retain **factor 4**.
+
+## (b) Label the Factors
+
+- RC4: 有利成分  
+此因素在第 2, 5, 9 題有較高的因素負荷量。這些題目似乎皆與健康有關。飲料能提供營養或避免添加不健康的物質，似與此因素有關。
+
+- RC1: 有效解渴
+此因素在第 3, 7, 10 題有較高的因素負荷量，這些題目皆與飲料是否**解渴**有關。
+
+- RC2: 獨特風味  
+此因素在第 1, 4, 8 題有較高的因素負荷量，這些題目皆強調飲料的**口感**。
+
+- RC3: 綠能包裝  
+此因素僅在第 6 題有較高的因素負荷量。第 6 題是一獨特的題目，所有題目中僅其強調**環境因素**。因此一個因素僅在第 6 題有較高的因素負荷量顯得相當合理。
+
+## (c) Average factor scores of each brand
+
+```{r index}
+br1 <- which(drinks$BRAND == "1") #index for brand 1
+br2 <- which(drinks$BRAND == "2")
+br3 <- which(drinks$BRAND == "3")
+br4 <- which(drinks$BRAND == "4")
+br5 <- which(drinks$BRAND == "5")
+br6 <- which(drinks$BRAND == "6")
 ```
@@
 ```{r}
-library(psych)
-items <- drinks[,-(1:2)]
+fs1 <- fa_R_pc2[["scores"]][br1,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs2 <- fa_R_pc2[["scores"]][br2,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs3 <- fa_R_pc2[["scores"]][br3,] %>% colMeans() %>% t() %>%
+    as.data.frame() 
+fs4 <- fa_R_pc2[["scores"]][br4,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs5 <- fa_R_pc2[["scores"]][br5,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+fs6 <- fa_R_pc2[["scores"]][br6,] %>% colMeans() %>% t() %>%
+    as.data.frame()
+
+avg_fs <- rbind(fs1, fs2, fs3, fs4, fs5, fs6) %>% 
+    as.data.frame()
+rownames(avg_fs) <-  c("Pepsi", "Coke", "Gatorade",
+                    "Allsport", "Lipton tea", "Nestea")
+
+colnames(avg_fs) <- c("有利成分", "有效解渴", "獨特風味", "綠能包裝")
 ```
 
-#no principle component method
+### Average factor scores
+```{r factor-score-table}
+kable(avg_fs, "markdown", align = 'l',
+      digits = 3,
+      row.names = T, 
+      caption = "Average Factor Scores of each brand")
+```
+
+\newpage
+
+## (d) Interpret the positions of the six brands
+
+```{r out.width="50%", fig.show='hold'}
+avg_fs <- cbind(avg_fs, rownames(avg_fs))
+colnames(avg_fs) <- c("有利成分", "有效解渴", "獨特風味", "綠能包裝", "Brand")
+
+### F1, F2
+showtext::showtext.begin()
+ggplot(avg_fs[,c(1,2, 5)],aes(x=`有利成分`, y=`有效解渴`, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none') +
+    labs(x="有利成分", y="有效解渴")
+
+### F1, F3
+ggplot(avg_fs[,c(1,3, 5)],aes(x=`有利成分`, y=`獨特風味`, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none') +
+    labs(x="有利成分", y="獨特風味")
+showtext::showtext.end()
+```
+
+```{r out.width="50%", fig.show='hold'}
+### F1, F4
+showtext::showtext.begin()
+ggplot(avg_fs[,c(1,4, 5)],aes(x=`有利成分`, y=`綠能包裝`, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none') +
+    labs(x="有利成分", y="綠能包裝")
+
+### F2, F3
+ggplot(avg_fs[,c(2,3, 5)], aes(x=`有效解渴`, y=`獨特風味`, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none') +
+    labs(x="有效解渴", y="獨特風味")
+showtext::showtext.end()
+```
+
+```{r out.width="50%", fig.show='hold'}
+### F2, F4
+showtext::showtext.begin()
+ggplot(avg_fs[,c(2,4, 5)],aes(x=`有效解渴`, y=`綠能包裝`, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none') +
+    labs(x="有效解渴", y="綠能包裝")
+
+### F3, F4
+ggplot(avg_fs[,c(3,4, 5)], aes(x=`獨特風味`, y=`綠能包裝`, color=Brand)) +
+    geom_point() +
+    geom_text(aes(label=Brand),
+              hjust=0.5, vjust=-0.4, size = 3) +
+    theme(legend.position = 'none') +
+    labs(x="獨特風味", y="綠能包裝")
+showtext::showtext.end()
+```
+
+在不考慮**綠能包裝**下，可以從各散布圖中看出 3 種飲料類型：
+
+1. Pepsi, Coke: 碳酸飲料
+2. Gatorade, Allsport: 運動飲料
+3. Lipton tea, Nestea: 茶飲
+
+相同類型的飲料在散布圖中，通常位置會較為接近。例如，茶飲較為健康且有獨特風味，因此出現在出現在右上圖的右上方；碳酸飲料含糖量高，既不健康又不解渴，因此在左上圖中，出現在左下方；運動飲料則在**有效解渴**上，出現在類似的位置。

### 2018-05-11 1062_class/eco_model/HW/C8/HW8.Rmd
up

---
title: "Ecological Modeling HW8"
author: Yongfu Liao
date: "`r Sys.Date()`"
output: 
    html_document:
        code_folding: hide
css: ~/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
	)
```

## Question 1

1. Asks the user to input 5
persons’ grades (0-100) from the keyboard

2. Show the best, worst, and average grades in the display

```c
#include <stdio.h>
#include <math.h>
#define NUM 5

int main(void){
    int grades[NUM];
    int i; //for loop index for array input
    int s, t, tmp; //for loop index for bubble sorting the inputted array
    int k; // for loop index
    double avg=0; //output value from the grades array

    // input array of grades from user
    for (i=0; i<NUM; i++){
        printf("please input the grade (0-100) of the %dth student\n", i+1);
        scanf("%d", &grades[i]);
    }

    //sort the array of grades (bubble sort)
    for (s=0; s < NUM - 1; s++){
        for (t = s + 1; t < NUM; t++){
            if (grades[t] > grades[s]){
                tmp = grades[s];
                grades[s] = grades[t];
                grades[t] = tmp;
            }
        }
    }

    // return the Max, min, & avg of the grades array
    for (k=0; k<NUM; k++) avg = avg + grades[k];
    avg = avg / NUM;

    printf("The best grade is %d\n", grades[0]);
    printf("The worst grade is %d\n", grades[4]);
    printf("The average grade is %lf\n", avg);

    return 0;
}
```

## Question 2
Make a function, `double bmi(double height, double
weight)`, and write a program that can calculate BMI from
keyboard inputs.

```c
#include <stdio.h>

double bmi(double height, double weight);

int main(void){
    double h, w;

    printf("Please enter your weight (kg)\n");
    scanf("%lf", &w);
    printf("Please enter your height (cm)\n");
    scanf("%lf", &h);

    printf("Your BMI is %lf\n", bmi(h, w));

    return 0;
}

double bmi(double height, double weight){
    double BMI;
    BMI = weight / ((height/100)*(height/100));

    return BMI;
}
```

### 2018-05-11 1062_class/eco_model/HW/C8/bmi_function.c

@@ -1,0 +1,24 @@
+#include <stdio.h>
+
+double bmi(double height, double weight);
+
+int main(void){
+    double h, w;
+    
+    printf("Please enter your weight (kg)\n");
+    scanf("%lf", &w);
+    printf("Please enter your height (cm)\n");
+    scanf("%lf", &h);
+    
+    printf("Your BMI is %lf\n", bmi(h, w));
+    
+    return 0;
+}
+
+
+double bmi(double height, double weight){
+    double BMI;
+    BMI = weight / ((height/100)*(height/100));
+    
+    return BMI;
+}

### 2018-05-11 1062_class/eco_model/HW/C8/grade_array.c

@@ -1,0 +1,39 @@
+#include <stdio.h>
+#include <math.h>
+#define NUM 5
+
+int main(void){
+    int grades[NUM];
+    int i; //for loop index for array input
+    int s, t, tmp; //for loop index for bubble sorting the inputted array
+    int k; // for loop index
+    double avg=0; //output value from the grades array
+    
+    // input array of grades from user
+    for (i=0; i<NUM; i++){
+        printf("please input the grade (0-100) of the %dth student\n", i+1);
+        scanf("%d", &grades[i]);
+    }
+    
+    
+    //sort the array of grades (bubble sort)
+    for (s=0; s < NUM - 1; s++){
+        for (t = s + 1; t < NUM; t++){
+            if (grades[t] > grades[s]){
+                tmp = grades[s];
+                grades[s] = grades[t];
+                grades[t] = tmp;
+            }
+        }
+    }
+    
+    // return the Max, min, & avg of the grades array
+    for (k=0; k<NUM; k++) avg = avg + grades[k];
+    avg = avg / NUM;
+    
+    printf("The best grade is %d\n", grades[0]);
+    printf("The worst grade is %d\n", grades[4]);
+    printf("The average grade is %lf\n", avg);
+    
+    return 0;
+}

### 2018-05-11 1062_class/eco_model/HW/C8/HW8.Rmd
up

@@
         code_folding: hide
-css: ~/local_depend/style_sheets/style.css
+css: /home/liao/local_depend/style_sheets/style.css
 ---

### 2018-05-19 1062_class/eco_model/HW/C9/dynamic_memory_allocation.c
up

@@ -1,0 +1,54 @@
+#include <stdio.h>
+#include <stdlib.h> //need to be included
+
+
+void message_error(char error_text[]);
+double *d_vector(long size); //for generating double vector[1]...vector[size]
+void free_d_vector(double *x);
+    
+    
+int main(void){
+    double *v1;
+    v1 = d_vector(4);
+    
+    *(v1+1) = 3;
+    v1[4] = 40;
+    
+    printf("v1[1] = %lf\n", v1[1]); 
+    printf("*(v1+1) = %lf\n", *(v1+1));
+    printf("v1[4] = %lf\n", v1[4]); 
+    printf("*(v1+4) = %lf\n", *(v1+4));
+    
+    free_d_vector(v1);
+}
+
+
+
+
+
+/* Functions*/
+
+void message_error(char error_text[])
+/*Standard error handler*/
+{
+    printf("There are some errors...\n");
+    printf("%s\n", error_text);
+    printf("...now existing to system...\n");
+    exit(1);
+}
+
+double *d_vector(long size){ //for generating double vector[1]...vector[size]
+    double *x; //pointer
+    
+    x = malloc((size + 1)*sizeof(double));
+    //allocation of memory space to stock (size + 1) double variables & malloc returns the address of the top of the allocated memory space to x
+    //the reason to prepare (size + 1) is just to use from x[1] to x[size]
+    
+    if(x == NULL) message_error("allocation failure in d_vector()"); //if memory allocation was failed, malloc returns NULL and x becomes NULL
+    return x; //return the address of the top of the allocated memory space to x
+}
+
+void free_d_vector(double *x)
+{
+    free(x);
+}

### 2018-05-19 1062_class/eco_model/HW/C9/pointer_array.c

@@ -1,0 +1,23 @@
+#include <stdio.h>
+
+int main(void){
+    int test[5] = {10, 20, 30, 40, 50};
+    
+    printf("\nint test[5] = {10, 20, 30, 40, 50}\n\n");
+    
+    printf("test[0] = %d\n", test[0]);
+    printf("Address of test[0] is %p\n", &test[0]);
+    printf("Address of test[1] is %p\n", &test[1]);
+    printf("Address of test is %p\n", &test);
+    printf("The value of test = %p\n", test);
+    printf("The value of *test = %d\n", *test);
+    printf("The value of *(test+1) = %d\n", *(test+1));
+    
+    return 0;
+}
+
+/*
+For an array int test[num]
+&test[0] == &test == test == Address of test[0]
+ */
+

### 2018-05-19 1062_class/eco_model/HW/C9/pointer_matrix.c

@@ -1,0 +1,74 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+/* Function Declaration */
+double **d_matrix(long size_row, long size_column);
+void free_d_matrix(double **x);
+void message_error(char error_text[]);
+
+
+/* Main Function */
+int main(void){
+    int i, j;
+    double **matrix;
+    double determinant;
+    int nrow=2, ncol=2;
+    matrix = d_matrix(nrow, ncol);
+    
+    for (i=1; i<=nrow; i++){
+        for (j=1; j<=ncol; j++){
+            printf("Please enter the entry of row %d and column %d of the matrix.\n", i, j);
+            scanf("%lf", &matrix[i][j]);
+        }
+    }
+    
+    determinant = matrix[1][1]*matrix[2][2] - matrix[2][1]*matrix[1][2];
+    
+    if (determinant <= 0.000001 && determinant >= -0.000001){
+        printf("The determinant of the matrix is 0.\nThe inverse of the matrix doesn't exist.\n");
+    }else{
+        printf("The determinant of the matrix is %lf.\n", determinant);
+        printf("%lf\t%lf\n%lf\t%lf\n", matrix[2][2]/determinant, -matrix[1][2]/determinant, -matrix[2][1]/determinant, matrix[1][1]/determinant);
+    }
+    free_d_matrix(matrix);
+    
+    return 0;
+}
+
+
+
+/* Function Definition */
+
+void message_error(char error_text[])
+/*Standard error handler*/
+{
+    printf("There are some errors...\n");
+    printf("%s\n", error_text);
+    printf("...now existing to system...\n");
+    exit(1);
+}
+
+void free_d_matrix(double **x){
+    free(x[0]);
+    free(x);
+}
+
+
+double **d_matrix(long size_row, long size_column){
+    double **x;
+    long i;
+    long size_row_P = size_row + 1; 
+    long size_column_P = size_column + 1; 
+    
+    x = (double **) malloc((size_t) (size_row_P*sizeof(double *)));
+    
+    if(x == NULL) message_error("allocation failure in d_vector()");
+    
+    x[0] = (double *) malloc((size_t) (size_row_P*size_column_P*sizeof(double)));
+    
+    if(x[0] == NULL) message_error("allocation failure in d_vector()");
+    
+    for(i = 1; i < size_row_P; i++) x[i] = x[0] + i*size_column_P;
+    
+    return x;
+}

### 2018-05-19 1062_class/eco_model/HW/C9/pointers.c

@@ -1,0 +1,23 @@
+#include <stdio.h>
+
+int main(void){
+    int a = 5;
+    
+    int *pA;
+    pA = &a;
+    
+    /*
+    int *pA = &a; 
+    
+    //is equivalent to
+    
+    int *pA;
+    pA = &a;
+    */ 
+    
+    
+    printf("The value of the variable a is %d.\n", a);
+    printf("The address of the variable a is %p.\n", &a);
+    printf("The value of pointer pA is %p\n", pA);
+    printf("The pointer variable *pA is %d\n", *pA);
+}

### 2018-05-19 1062_class/eco_model/HW/C9/pointers_in_fc.c

@@ -1,0 +1,28 @@
+#include <stdio.h>
+
+void swap1 (int x, int y){
+    int tmp;
+    
+    tmp = x;
+    x = y ;
+    y = tmp;
+}
+
+void swap2 (int *pX, int *pY){
+    int tmp;
+    
+    tmp = *pX;
+    *pX = *pY;
+    *pY = tmp;
+}
+
+int main(void){
+    int num1 = 5;
+    int num2 = 10;
+    
+    swap1(num1, num2);
+    printf("(num1, num2) = (%d, %d)\n", num1, num2);
+    
+    swap2(&num1, &num2);
+    printf("(num1, num2) = (%d, %d)\n", num1, num2);
+}

### 2018-05-19 1062_class/eco_model/practice.c

@@ -1,17 +1,0 @@
-#include<stdio.h>
-
-int main (void) {
-    int num;
-    int sum=0;
-    int j;
-    
-    printf("This program calculates the sum from 1 to input number.\n");
-    scanf("%d", &num);
-    
-    for(j=1; j<=num; j++){
-        sum = sum + j;
-    }//end_for
-    
-    printf("The sum from 1 to %d is %d.\n", num, sum);
-    return 0;
-}

### 2018-05-19 1062_class/eco_model/practice2.c

@@ -1,15 +1,0 @@
-#include <stdio.h>
-#include <math.h>
-
-#define STEP 0.2
-int main(void){
-    int j;
-    double x;
-    
-    for (j=0; j<=100; j++){
-        x = j*STEP;
-        printf("%lf\t%lf\n", x, sin(x));
-    } //end for
-    
-    return 0;    
-}//end main

### 2018-05-19 GitHubPage/Instructions/Git command to change local file.Rmd
up

---
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
---

## 1) Clone Repo from GitHub

### Set Working Directory
Set current directory, so your repo can be dowload to this directory: cd \<where to clone>.
```
cd ~/GitHubPage
```

### Clone repo from GitHub
git clone \<URL>
```
git clone https://github.com/liao961120/liao961120.github.io
```

---------
## 2) Working Locally

### Set directory to (cloned) local repo
cd \<REPOSITORY-NAME>
```
cd ~/GitHubPage/liao961120.github.io
```

### (Optional) Create a new branch locally
You can create a branch other than `master` branch locally to work with.

git branch \<BRANCH-NAME>
```
git branch local
```

### Change working branch
After you create a new branch, you could change to that branch (or back), by:

git checkout \<BRANCH-NAME>
```
git checkout master
```

### Sync with Remote
git pull \<remote> \<local branch name>

`git pull` = `git fetch` + `git merge`
```
git pull https://github.com/liao961120/liao961120.github.io master
```

### Edit files locally
You can edit your files in your cloned repo just like you edit other files on your computer.

#### Update changes locally
After editing your files, you need to update changes. Use the git command:

git add \<FILE-NAME>

to update changes you have done to your file.
```
git add ~/GitHubPage/liao961120.github.io/_posts/2017-11-18-markdown-output.md
```

#### Creating new file
If you didn't edit, but want to create a brand new file, create the file with the usual way you do on your computer and use the git command:

git add -f \<FILE-NAME>
```
git add -f ~/GitHubPage/liao961120.github.io/_posts/2017-11-18-markdown-output.md
```

#### Commit change locally
After typing in all the `git add` and/or `git add -f`, type
```
git commit
```
so you can commit locally.

---------

## 3) Update Changes to GitHub

### Upload changes to your GitHub repo
After committing locally, you can update your changes to GitHub.

Use:

git push -u origin \<BRANCH-NAME>

and set \<BRANCH-NAME> to the branch you worked locally.
```
git push -u origin master
```

Now your branch is uploaded to GitHub.

You need to go to GitHub (webpage) to merge your branch to master **only if** you had created and worked on another branch (other than `master`) locally. *See below*.

### (Optional) Merging branch on GitHub

Beware:

* check that you are merging branches under your account

* `base: master` `compare: local`.

### 2018-05-19 GitHubPage/my_R_book/R Learning Notes/01-Basics.Rmd
up

# Some Basics {#Basic}

## Subsetting Vectors
### vector_name[index vector]
**index vector** can be:

1. logical vectors
2. vectors of positive integers
3. vectors of negative integers
4. vectors of character strings

```{r index_vector1}
#Logical
y <- c(1, -1, 1, 2, 3)
x <- c(NA, 1, 0, -1, 0.5)
sub.y <-  y[y > 0]
sub.x1 <- x[x > 0]
sub.x2 <- x[!is.na(x) & x > 0]
print(list(sub.y=sub.y, sub.x1=sub.x1, sub.x2=sub.x2))
```
*Note: 'NA' is not a value, it's a placeholder for an unknown quantity, the expression NA > 0 evaluates to NA*

```{r index_vector1.2}
#Logical_2: subset with quantile function
x <- runif(100, 0, 1)
df <- as.data.frame(cbind(1:100, x))
names(df) <- c("obs", "value")
df[df$value >= quantile(df$value, 0.95),]
```
-----

```{r index vector2}
# Negative Integer
x <- c("a","b","c","d")
x1 <- x[c(-2, -4)]
x2 <- x[-c(2, 4)]
print(list(x1=x1, x2=x2))
```
*Negative integers give all elements of  x EXCEPT for the 2nd and 10th elements*

-----

```{r index vector3, echo=TRUE}
# Character String
z <- c(foo = 11, bar = 12, norf = NA)
z1 <- z["bar"]
z2 <- z[2]
print(list(z1, z2))
```

## Subsetting Lists
```{r lists, echo=TRUE}
# Return a sublist
ll <- list(id=1:3, height="fdklj", weight=1)
x1 <- ll[1]
x2 <- ll["id"]
print(c(x1, x2))
```
`ll[1]` & `ll["id"]` are equivalent.

------

```{r lists2, echo=TRUE}
# Return a vector(contents in the sublist)
ll <- list(id=1:3, height="fdklj", weight=1)
x1 <- ll[[1]]
x2 <- ll[["id"]]
x3 <- ll$id
print(c(x1,x2,x3))
```
`ll[[1]]`, `ll[["id"]]` *&* `ll$id` *are equivalent.*

*Note:* `[[ ]]` *&* `$` *must go with strings(names).*

Manipulating data with Lists is often difficult. Using `[[ ]]` & `$` lets you manipulate the elements in the List(i.e. vectors).

## Concatinating & Printing
### paste()
The `paste` function combines different vectors(more than 2 vectors as input) into **one** character string. The value of the argument `sep` is used to seperate the inputs.
```{r paste 1, echo=TRUE}
symbol <- "A B C"
num <- 1                           # a numeric vector
x <- paste(symbol, num, sep="\n")  # \n: new line in regex
cat(x)                             # cat is similar to print
```

When the input vector(s) contains multiple elements, and given the `collapse` argument, `paste` collapses the input vector into a single string, seperated by the value of `collapse`. **Beware the element-wise operation(recycle rule)**.
```{r paste 2, echo=TRUE}
x <- 1:3
y <- c("x","y","z")
paste(x,y, sep=":",collapse = ", ")
```
The result of `paste` follows the pattern: `"x[1]:y[1], x[2]:y[2], x[3]:y[3]"`

### cat()

### 2018-05-19 GitHubPage/my_R_book/R Learning Notes/03-Manipulation.Rmd
up

# Data Manipulation {#Manipulate}

## Explore Data
### View()
View data in new window, `sleep` is a built-in data in R.
```{r, echo=TRUE}
View(sleep)
```
*Note the capital 'V' in `View`.*

### with()
The two lines of code below are equvalent.
```{r with, echo=TRUE}
x1 <- with(airquality,cor(Temp, Wind))
x2 <- cor(airquality$Temp, airquality$Wind)
print(c(x1, x2))
```

### aggragate(y~x, data, function)

Split Temp by Month in data(airquality), then compute mean of Temp split by Month.
```{r aggregate, echo=TRUE}
aggregate(Temp~Month, airquality, mean)
```

### names()
A function to get & change names of an object.
```{r names, echo=TRUE}
x <- c(1, 2, 3)
y1 <- names(x)  # evaluates to NULL
names(x) <- c('a', 'b', 'c')
y2 <- names(x)
print(list(y1=y1, y2=y2))
```

## Handle with missing values
### is<span>.na()
The function returns logical: "TRUE" or "FALSE", indicating whether each element in the data is an 'NA'.
*NA(Not Available) is not a value, but a placeholder for a quantity not available. Hence, **No logical operations with NAs !!!***

R represents 'TRUE' as the number 1 and 'FALSE' as the number 0. Hence, for example, `sum(is.na(sleep))` returns an integer indicating the number of 'NA'.

#### Example: Removing NAs
```{r remove NA1, echo=TRUE}
x <- c(1, 2, NA, 4, NA, 5)
bad <- is.na(x)
x.NA_removed <- x[!bad]
print(list(bad=bad, NA_removed=x.NA_removed))
```

### complete.cases()
The function returns TRUE if the row(in data.frame sense) of the data has no NA.
```{r remove NA2}
# Vector example
x <- c(1, NA, 2)
y <- c("a", "b", NA)
good <- complete.cases(x, y)
good
```

#### Example: Remove rows which contains NAs in data frames
```{r airquality head, echo=FALSE}
head(airquality)
```
```{r remove NA3, echo=TRUE}
good <- complete.cases(airquality)
head(airquality[good,])
```
*Note: `good` is a logical vector containing 153 entries(153 rows from airquality)*

## strings

### regular expressions
| Code   | Meaning   |
| :---:  | --------- |
| \\     | excape    |
| \\w    | a-e & 0-9 |
| \\.    | .         |

### 2018-05-19 GitHubPage/my_R_book/R Learning Notes/Chi-Square.Rmd
up

---
title: "Chi-square"
author: "Yongfu, Liao"
date: "2018年5月3日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## chi-square

### test of goodness-of-fit

Let there be 3 types of flower A, B, C, and we want to know whether the 3 types of flower follow a specific distribution, let it be P(A) = 1/6, P(B) = 1/3, P(C) = 1/2.

To test my hypothesis, 60 flowers were collected, and their types recorded, with 12, 18, 30 of each types (A, B, C), respectively.

```{r}
# chisq.test(x, p)
chisq.test(c(12, 18, 30), p = c(1/6, 1/3, 1/2))
```

### test of independence

```{r}
library(dplyr)
contin_table <- tibble(
    male = c(50, 78),
    female = c(65, 56)) %>% 
    as.data.frame()

rownames(contin_table) <- c("pizza", "cake")
```

```{r}
# chisq.test(contingency_table)
chisq.test(contin_table)
```

#### `table`

```{r}
fct <- c("A", "A", "B", "B","A", "C", "B")
table(fct)
```

```{r}
fq <- table(fct) %>% as.vector()
fq
```

```{r}
fct_name <- table(fct) %>% names()
fct_name
```

```{r}
fq_table <- as.data.frame(fq) %>%
    cbind(fct_name)
fq_table
```

### 2018-05-19 GitHubPage/my_R_book/R Learning Notes/Life table example/Tidy data.Rmd
up

---
title: "Constructing Life Tables Using R"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I have been using the package `dplyr` to handle with data for a while, and I thought I can use it with ease until I was stuck with my homework on **contructing a life table**. I found it easy to do it with spreadsheets, and was embarrassed that I spent that much time dealing it with R. It was due to my unfamiliarity with some functions in R and also insufficient practice.

I will illustrate how I did my homework with R, and you'll find out how easy it is.

## Load Packages

You need these packages to  construct a Life table.
```{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(knitr)
```

## Load data
Load the csv file to `life_table`. The raw data contains 3 columns: **Age**, **Survivorship at Age x (lx)**, and **Fecundity at Age x (mx)**. I added `options(scipen=999)` because seeing scientific notations annoys me.
```{r, echo=TRUE, message=FALSE, warning=FALSE, comment=NA}
options(scipen=999)  # Disable Scientific Notation
life_table <- read_csv("life_table.csv")
life_table
```

## Variables to Construct

Here are the variables that need to be calculated.

|               Statistic               |      Notation     |                         Calculation Formula                        |
|:--------------------------------:|:-----------------:|:------------------------------------------------------------------:|
|                                  |     $l_x m_x$     |                                                                    |
|                                  |    $x l_x m_x$    |                                                                    |
|                                  | $l_x m_x e^{-rx}$ |                                                                    |
| Average survivorship<br>(age class) |       $L_x$       |                      $L_x = (l_x + l_{x+1})/2$                     |
|          Life expectancy         |       $e_x$       |              $e_x = (L_x + L_{x+1} + … + L_{max})/l_x$             |
|        Reproductive value        |       $V_x$       | $\displaystyle \frac{\sum_{y=x}^{max\hspace{0.3mm}x} e^{-ry} l_y m_y}{e^{-rx} l_x}$ |
|       Net reproductive rate      |       $R_0$       |                       $\sum_{all \hspace{0.3mm} x} l_x m_x$                       |
|          Generation time         |        $G$        |                $\frac{\sum_{all \hspace{0.3mm} x} x l_x m_x}{R_0}$                |
|    Intrinsic rate of increase    |  Approximate $r$  |                    $r \approx \frac{ln(R_0)}{G}$                   |
|    Intrinsic rate of increase    |      (True) $r$     |                  $\displaystyle \sum_{all \hspace{0.3mm} x} e^{-rx}l_x m_x = 1$                 |

$l_x*m_x*e^{-rx}$ and $V_x$ will be calculated twice for the approximate and the true $r$.

## Constructing Variables

### `mutate`: Creating new columns

Using the pipe `%>%` and the function `mutate` in package `dplyr`, I first construct 7 new variables. Note the dependencies of the variables, so that I can't construct the life tables just at once.
```{r, echo=TRUE, message=FALSE, warning=FALSE, comment=NA}
life_table <- life_table %>%
    mutate("lx*mx"=lx*mx,
           "x*lx*mx"=Age*lx*mx,
           "Lx"=(lx+lead(lx))/2,
           "Lx"=replace(Lx, 10, 0),
           "ex"=rev(cumsum(rev(Lx)))/lx,
           "R0"=sum(lx*mx),
           "G"=sum(Age*lx*mx)/R0,
           "approx.r"=log(R0)/G
           )
```

Two things worth noting in the `mutate` function:

1. The code `"Lx"=(lx+lead(lx))/2, "Lx"=replace(Lx, 10, 0)`
    * `lead(lx)` shifts the whole column of lx to its next value, i.e. the column lx becomes lx+1.
    * Due to `lead(lx)`, the last entry of the new column `Lx` must be a `NA`, so I have to assign `0` to it (otherwise all calculations based on it will become `NA`s).

2. The code `"ex"=rev(cumsum(rev(Lx)))/lx` (This is where I was stuck)
    1. The numerator of `ex` is calculated by summing over $L_x$ to $L_{max}$, the maximum age of $L_x$. This is not so intuitive when working with R. 
    2. `rev(Lx)` reverse the order of $L_x$, and `cumsum()` is for *cummulative sum*. `cumsum(rev(Lx))` then is equivalent to summing $L_x$ backwards (i.e. from $L_{max}$ to $L_x$). 
    3. But since $L_x$ is reversed in the first place, `cumsum(rev(Lx))` is also in reverse order. Reversing `cumsum(rev(Lx))` with `rev()` then gives what I want.

### Calculating $r$ by while loop

By the **Eular-Lotka equation**, I can calculate $r$.
$$\displaystyle \sum_{all \hspace{0.3mm} x} e^{-rx}l_x m_x = 1$$

Using `while` loop and Approximate $r$ calculated earlier as the starting value for `r`, $r$ is calculated below. 
```{r, comment=NA}
df <- as.data.frame(life_table)
r <- 0.0812198
x <- sum(exp(-r*df$Age)*df$`lx*mx`)
while (abs(x-1) >= 0.000001) {
    if (x-1>0){
        r <- r+0.00000001
    }
    else{
        r <- r-0.00000001
    }
    x <- sum(exp(-r*df$Age)*df$`lx*mx`)
    r
}
```

The rest is simple, and the logic applied is the same.
```{r, message=FALSE, warning=FALSE, comment=NA}
life_table <- life_table %>%
    mutate(
        "approx.r"=log(R0)/G,
        "r"=r,
        "Vx"=rev(cumsum(rev(exp(-r*Age)*lx*mx)))/exp(-r*Age)*lx,
        "lx*mx*e^-rx"= lx*mx*exp(-r*Age),
        "approx.Vx"=rev(cumsum(rev(exp(-approx.r*Age)*lx*mx)))/exp(-approx.r*Age)*lx,
        "approx.lx*mx*e^-rx"= lx*mx*exp(-approx.r*Age)
    )
```
Now, the life table is done.

## Printing pretty Life Table

```{r, echo=TRUE}
kable(life_table,format="markdown",align="c")
```

### 2018-05-19 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

--- 2018-04-12 Instructions/Rmarkdown_features/rmd_features.rmd
@@
   html_document:
+    includes:
+        before_body: mathjax_bm.tex
     css: ../style_sheets/style.css
@@
 You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
-```yaml
+```{yaml}
 ---
@@
 fontsize: 12pt
+geometry: a5paper, headheight=0pt, margin=0.4in
 ---
@@
 
-```tex
+```{tex}
 %加這個就可以設定字體
@@
 \usepackage{xeCJK}
+
+\usepackage{multicol}
+\usepackage{bm}
 
@@
 
+knitr Parameters
+--------------------------------
+
+### Root
+```r
+knitr::opts_knit$set(root.dir='..')
+```
+The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default.
+In the case above, I changed it to  the **directory that is parent to the default directory**.
+
+### Code Chunk & Figure Options
+```r
+library(svglite) 
+knitr::opts_chunk$set(
+	echo = FALSE, # No display code chunks
+	message = FALSE,
+	warning = FALSE,
+	dev='svg', # or 'svglite' for multibite characters
+	comment="",
+	fig.dim = c(3.5, 3.5)  # (width, height)
+)
+options(digits = 2) # auto round to 2 decimals when printed
+```
+
 Dynamic Variables
@@
 Add `results='asis'` to r code chunk option.
-```{r results='asis'}
+
+````r
+`r ''````{r results='asis', echo=FALSE}
+library(mat2tex)
+mt <- c(1,2)
+"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
+```
+````
+
+```{r echo=FALSE, results='asis'}
 library(mat2tex)
@@
 
-![](mat2tex.png){width=100% height=auto}
+````r
+This is the variable `mt`,
+`r ''````{r results='asis', echo=FALSE}
+library(mat2tex)
+mt <- matrix(1:4, 2,2)
+"$A =" %_% xm(mt,0) %_%"^{-1}$"
+```
+, which is a matrix.
+````
 
@@
 
+Display Code Chunk with Code Chunk
+--------------------------------------------
+
+```{r include=F}
+code <- htmltools::HTML("<code>`r ''`</code>")
+```
+
+Wrap the code chunk you want to display (without running the code inside) inside **four ticks**:
+
+`````rmd
+````Rmd
+`r code````{r}
+Some R Code
+```
+````
+`````
+
+The code `r code` is for suppressing the execution of the r code chunk after it.
+
 Bibliographies & Citations{#cite} 
------------------------------
+-----------------------------------------
 

### 2018-05-19 GitHubPage/my_R_book/graphics/ggplot.Rmd
up

---
title: "ggplot quick guide"
author: "Yongfu, Liao"
date: "`r Sys.Date()`"
output: 
    html_document:
        code_folding: show
css: /Users/user/local_depend/style_sheets/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = 'svg'
)
```

ggplot color theme
--------------------------------
```{r}
scales::hue_pal()(3)
```

Data 
----------------------------------
```{r}
library(ellipse)
library(dplyr)

All_contours <- c(NA, NA, NA) ## Set empty start for appending ##

ell_data <- ellipse(0.8, c(1, 1), centre = c(1, 3), level = 0.5, npoints = 800) ## npoints: bigger contours with more points ##

ell_data <- as.data.frame(ell_data) %>%
    mutate(class = "50% contour")

## Change to data.frame BEFORE cbind, or coersion happens ##

All_contours <- rbind(All_contours, ell_data)[-1,]
```

Adding Lines & Curves to a plot
-------------------------------------

```{r}
library(latex2exp)
library(ggplot2)

sum_xy <- All_contours %>%
    mutate(sum=x+y) %>% select(sum)

max <- which(sum_xy == max(sum_xy))[1]
min <- which(sum_xy == min(sum_xy))[1]

p <- ggplot(data = All_contours) +
    geom_point(aes(x = x, y = y, color = class),
               size = 0.1,
               color="black")+
    labs(color = "Contours", 
         title = "Contour Plot",
         x = TeX("$x_1$"), y = TeX("$x_2$")
    )

p + geom_segment(aes(x=All_contours$x[max], 
                     y=All_contours$y[max], 
                     xend =All_contours$x[min], 
                     yend = All_contours$y[min], 
                     color = "Major Axis")) +
    geom_segment(aes(x=0.6342645, 
                     y=3.378911, 
                     xend =1.370133, 
                     yend = 2.625475, 
                     color = "Minor Axis")) +
    annotate("text", x = 1.5, y = 3.7, 
             label =TeX("$c\\sqrt{\\lambda_1}$"),
             alpha =0.7,
             size = 2.8,
             color = "red")+
    coord_fixed() # fix x-axis/y-axis to 1
```

### 2018-05-19 GitHubPage/my_R_book/graphics/ggplot_1.Rmd
up

---
title: "Advanced Graphics"
output:
  html_document:
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "Advanced Graphics/")
```
```{r, include=FALSE}
library(ggplot2)
library(dplyr)
```

## Six Principles of Graphing
1. Comparison

2. Mechanism

3. Multivariate Data

4. Integrating evidence: <br/>Different forms of expressions

5. Credibility: <br/>Describing and documenting the evidence with sources       appropriate labels, and scales.

6. Content is King: <br/>Garbage in, garbage out.

## Exploratory Graphs 
1. DON'T use exploratory graphs to communicate results.

2. Initial step in an investigation:<br/>Used to point the data scientist in a fruitful direction.

## ggplot2
### Grammar(template) of ggplot2
```{r, eval=FALSE}
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(
     mapping = aes(<MAPPINGS>),
     stat = <STAT>, 
     position = <POSITION>
  ) +
  <COORDINATE_FUNCTION> +
  <FACET_FUNCTION>
```

### Aestheics
An aesthetic is a **visual property** of the objects in the plot. Aesthetics include things like the size, the shape, the color, and transparency of the points.

Each `geom_` function has its suitable aesthetics, which can be found by typing `?geom_name` in the console.

`alpha` sets transparency.

`color` adds color to points and lines, color boarder to bars.

`fill` fills color in histogram or bar chart.

### Coordinate Functions
```r
coord_cartesian(xlim=c(x_min,x_max), ylim=c(y_min,y_max))
```
sets the range of x and y-axis.

### Example: box plot
```{r, echo=TRUE}
ggplot(data = mpg) +
    geom_boxplot(
      mapping = aes(x = reorder(class, hwy, FUN = median), 
                    y = hwy)) +
    coord_flip()  # 將x, y軸對調
```

### Example: geom_smooth
```{r}
ggplot(diamonds, 
aes(x=carat, 
    y=price, 
    color=clarity)) +
geom_smooth(method="lm", formula=y~poly(x, 2))

ggplot(diamonds, 
aes(x=carat, 
    y=price, 
    color=clarity)) +
geom_smooth(method="lm", formula=y~poly(x, 5))
```

### Example: lable on grapgh
```{r}
ggplot(mtcars, aes(x=wt, y=mpg)) +  geom_label(label=rownames(mtcars), nudge_y=0.5) + geom_point()
```
`nudge_y = `, `nudge_x = ` adjust the position of the lable.

## Interactive Graphic

```{r}
library(plotly)
gp=ggplot(mtcars, aes(x=wt, y=mpg)) +
  geom_point(aes(text=rownames(mtcars)))
ggplotly(gp)
```
**plotly** is compatible with **ggplot2**.

### 2018-05-19 GitHubPage/my_R_book/table_manipulate.R

@@ -1,0 +1,19 @@
+library(readr)
+data <- read_csv("C:/Users/user/Desktop/data.csv")
+
+type <- data[2:nrow(data), c(2, 5, 8)]
+
+new_data <- c(type$`演苦李腳黨_1`, 
+  type$`飽組每姐採_1`, 
+  type$闖偶轉久往_1) %>% as.data.frame()
+
+name <- c(rep("test1", 28),
+              rep("test2", 28),
+              rep("test3", 28)) %>% as.data.frame()
+new_data <- cbind(name, new_data)
+colnames(new_data) <- c("test_type", "say_type")
+    
+
+t1 <- table(type$`演苦李腳黨_1`)
+t2 <- table(type$`飽組每姐採_1`)
+t3 <- table(type$`闖偶轉久往_1`, type$`飽組每姐採_1`)

### 2018-05-23 1062_class/lang_social_mid/doc.Rmd
up

---
title: "語言與社會期中作業"
author: "廖永賦"
date: "`r Sys.Date()`"
output:
  pdf_document:
    includes:
      in_header: header.tex
    latex_engine: xelatex
  html_document:
    df_print: paged
documentclass: article
geometry: margin=1in
link-citations: yes
csl: /home/liao/local_depend/style_sheets/apa_ch.csl
bibliography: lang_social.bib
urlcolor: blue
---

## 8

### 幸福路上

《幸福路上》以閩南語作為日常生活中的主要語言，我覺得相當符合當時社會的情況。電影中的地點設定為臺北，臺北作為一個移居者匯集的地區，生活中的語言使用應以當時最流通的語言為主（溝通指數最高），而閩南語應為當時民間最流通的語言。

電影中另一個有趣的語言現象即為主角小琪的語言。《幸福路上》以小琪的故事作為主幹，而小琪的故事其實就是《幸福路上》導演宋欣穎自身的成長故事[-@2018; -@2018a; -@2018b; -@2018c]。根據導演的受訪，馬上就可以回答電影中這個「奇怪」的語言現象—為何生長在父母皆使用閩南語的家庭，小琪仍然較常使用中文（漢語）？電影忠實地呈現了**導演宋欣穎自身語言使用的情況**：

> 我的外婆是個有原住民血統、吃檳榔的外婆，可是我家裡都講台語，而事實上我自己又不太會講（台語）。等我到了美國，看到他們的移民家庭裡，父母都使用母語，除了中文還有西班牙語、和甚至非洲語等等，可是小孩都用英文回答他們，我覺得這很有趣，怎麼會跟我們家一樣？[-@2018a]

小琪的現象或許並非罕見。例如，研究顯示通常同儕相對於父母對使用何種語言有較大的影響力[＠standford2008]，或許在當時的國語政策下，同儕間（在學校）的溝通語言變成漢語為主，造成小琪日後以漢語作為主要語言。另一可能的原因為性別。以我所知的例子，
1. 我外公為外省籍的老兵，不會講閩南語，但其常不在家。我外婆為本省籍，講閩南語[^grandma]。因此可合理推測我母親幼時，家庭應該以閩南語為主。然我母親雖會講閩南語，但不算是最流利的那種（少了點母語使用者那種流暢的口音，某些詞彙也不清楚）。
2. 這學期我聽中文系的張麗麗老師提及她自身的狀況：與我母親相同，老師也是在外省（父）—本省閩南（母）家庭長大的。老師說她以及妹妹不會閩南語，但她的兄弟皆會流利的閩南語。

[^grandma]: 有趣的是，我外婆跟我（還有跟我目前 8 歲的表弟）說話時，會自動改成使用漢語。而我小時候在外婆家住過一段時間，那時正好是我開始學會講話的時間。不知道這是否與我低落的閩南語程度有關。

## 9

語言與思維的關係相當複雜。縱使最極端版本的 Sapir-Whorf Hypothesis—語言決定論（Linguistic determinism）被認為是錯誤的，語言仍有可能以其他更細微的方式影響思維。依據思維相對於語言運作的時機，可將之區分為「說話前的思考（Thinking for speaking）」、「運用語言思考（Thinking with language）」、「語言對思考的後續影響（Thinking after language)」[@wolff2010]。以下簡單各舉一例：

1. 說話前的思考：有些語將動作的方式（manner）表示於動詞，而將動作的方向（path）表示於其它詞類（如副詞），英語、中文即為這種語言（「run out」、「跑出去」）。另一些語言比較重視動作的方向（path）而將其用於動詞，將動作的方式（manner）表示於其它詞類，如法語、日語、希臘語。這些不同語言上的結構差異，造成其使用者開始說話前，注意力關注的焦點不同。例如，希臘語使用者比起英語使用者更傾向注意動作的方向（path）[@papafragou2008]。

2. 運用語言的思考：運用語言的思考最顯著的一個例子是「精確」的數量。人類以及許多其他動物，天生就對極小的數量（小於3或4）的數量有絕對的概念；對大量的數量有約略的概念；但對精確的「數字」，如「33」，是後天習得的。明確的證據指出精確的數字概念與語言之間的關聯 [@dehaene1999; @spelke2001; @frank2008]。沒有語言，或語言中不具有數字系統，人類將無法以精確的數量進行思考。

3. 語言對思考的後續影響：前述兩種語言與思維之間的關係直接與語言有所關聯，即思考本身是為了表達，或是透過語言進行思考，語言似乎直接參與了思考歷程。「語言對思考的後續影響」指的則是不涉及語言本身的思考：在長期使用特定語言下，是否會對思維產生影響。其中一項支持的證據來自語言中是否舉有單複數。日語、中文等語言的名詞，沒有單數或複數型態的差別；英語則必須指出名詞為單數或複數。因此，英語使用者可能會傾向將注意力集中在「個體」的特質，而日語或中文的使用者則可能傾向將注意力集中在「共同」的特質。例如，英語使用者可能較注意椅子的形狀，而日語、中文使用者則較注意椅子的材質。此假設受到 @li2009 的研究支持。

這些研究證據顯示語言以不同種方式影響思維的可能。然關於 Daniel Everett 對於 Pirahã 人的想法：「他們的語言沒有時態，他們真正活在當下之中」，似乎隱含更複雜的因素。首先，我同意這句話的後半段：人類在進入大規模社會後，先是曆法，接著時鐘的發明似乎改變人類對於時間的概念，大家開始擔心時間的流逝，並且開始「預約未來」（排行事曆、約會時間等）。Pirahã 人生活在沒有現代時間概念的社會中，且其生活方式也無須擔心是否有事情未完成，因此其「活在當下」顯得相當合理。然我認為難以使用「他們的語言沒有時態」作為理由。從 Pirahã 人的文化可以很明顯地發現其許多部份皆支持著 Pirahã 人「活在當下」，例如簡單的物質技術（所以不須從事大規模的生產）、從事漁獵採集（所以比起農耕更加不勞力密集）、沒有強烈的物質需求（只向 Everett 要求一些簡單的物資）等。文化本身即是強而有力的解釋，能夠說明 Pirahã 人「活在當下」。忽略這些文化因素而單以語言的結構作為解釋顯得相當不合理。

## 參考資料{#reference}

### 2018-05-23 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 date: "`r Sys.Date()`"
-bibliography: /Users/user/local_depend/citation/neanderthals.bib
-csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
+bibliography: /home/liao/local_depend/citation/neanderthals.bib
+csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
 link-citations: yes
@@
     code_folding: show
-    css: /Users/user/local_depend/style_sheets/style.css
+    css: /home/liao/local_depend/style_sheets/style.css
     df_print: kable
@@
 date: March 18, 2018
-bibliography: /Users/user/local_depend/citation/neanderthals.bib
-csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
+bibliography: /home/liao/local_depend/citation/neanderthals.bib
+csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
 link-citations: yes
@@
 
+Note that Latex only accepts fontsize of 10pt, 11pt, or 12pt. See [this](https://github.com/rstudio/rmarkdown/issues/878) for more detail.
+
 ### PDF: header.tex{#pdf-header}
@@
 
-\usepackage{multicol}
-\usepackage{bm}
+\usepackage[fontsize=13pt]{scrextend}
 
@@
 %字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
-\setCJKmainfont{蘋方-繁}
+% AR PL KaitiM Big5 標楷體
+% .PingFang TC
+% Noto Sans CJK TC
+\setCJKmainfont{AR PL KaitiM Big5}
 
@@
 ```
-![](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
+![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
 
@@
 ```
-![Bootstrap Rounded](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
+![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
 
@@
 ```
-![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
+![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
 
@@
 ```
-![Bootstrap Circle](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
+![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
 
@@
 ```
-![Bootstrap Thumbnail](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
+![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
 

### 2018-05-25 1062_class/lang_social_mid/doc.Rmd
up

@@
 
+## 5
+我覺得到了我們這一代 (1990 年後出生)應已達成階段 6「不再遭受歧視性的行為」的同化。其實對於臺灣的社會，從階段 4 過渡到階段 6 之間應該非常快速，這應與種族間的體質特徵（如膚色）差異程度有關。由於臺灣的各族群之間，外觀差異相當小，唯一能辨識族群差異的特徵大概只剩語言以及（相同語言下）發音的差異。當無法辨識出族群的差異，歧視性的態度或行為就沒有立基處，因而也就不會發生。
+
+藉由觀察上一代的長輩們（40 歲以上），有時還能夠由漢語發音上的特徵推測其家庭的組成，但在我這一代中（20 歲左右）我已無法從發音中去區別族群。同時，相較我父母那輩會在意「誰是外省、誰是客家」，我們這代已不會談論這種事情。我們反而比較常（沒有惡意）自嘲或揶揄「誰是『天龍人』」。在我們這代沒有族群的區別[^abori]，只有「地域上（縣市）」的區別。
+
+[^abori]: 這裡可能有個例外，是關於原住民的特殊身份。我認為這算是政府保障原住民的兩難。由於保障原住民的權益需標示出原住民的身份。有了原住民的標籤就有了差異的基礎，有了差異的基礎就有發生歧視的可能。在學校中，班上同學都會知道誰是原住民(通常不是因為特殊的口音或是可辨別的長相，總之就是會由其他同學那裡得知)，有意識或無意識可能也會對其有不同的行為。縱使行為者本身不帶任何惡意，是否構成歧視，我認為還是需由當事人本身的感受進行評斷。我不是原住民所以我不確定歧視是否發生。
+
+## 6
+就時間軸上來說，我認為這份比較表算是完整。然而由於此比較表主要是以「事件」為主，造成一些重要的限制。我認為其未能夠突顯出「日語運動」與「北京話運動」之間的一項重要差異：對於本土語言造成的衝擊。
+
+從今日的觀點來看，「北京話運動」要比「日語運動」成功太多。這一大部份的原因也根植於這兩種語言與臺灣本土語言（此以閩南語為主）的差異程度：「閩南語與北京話差異小，而與日語差異非常大」。這個本質性上的差異造成兩個國語運動有的一項重要差異：「日語運動（必須）透過閩南語教導臺灣人日語；北京話運動不需要透過閩南語，直接以漢語教學」。因為如此，日語運動並未以強烈的手段打壓閩南語，同時也保留漢文課且以閩南語教導古文、文言文。這進一步顯示出何以兩個「國語運動」會對本土語言帶來不同的衝擊：「透過閩南語教導文言文使其與『高雅』文化有直接關聯。與高知識份子之文化結合的閩南語，其語言位階將不會是今日的情況。今日的閩南語因為北京話運動而失去與『高雅』文化的連結，而僅能作為日常生活中的溝通語言，被排除在正式教育以及學術界[^scholar]之外」。因此，閩南語被與較粗俗、低下的概念相連結，漢語則與高雅的文化相關聯。這加強了兩種語言之間的位階關係。
+
+[^scholar]: 這裡並非獨尊「學術界」的重要性，而是指出臺灣人對於「學術界」或「知識份子」抱有較「好」或「上層」感覺的現象。這原因應根植於臺灣長期受到漢人文化的影響。
+
+## 7
+### (A)
+兩個語言無法互通的人第一次遇見之時要能溝通應是個漫長而緩慢的過程。要能溝通的第一個先決條件是兩者之間至少要有一些「共同」的地方。好險我們都是人類，在認知的結構上至少會有相似之處[^comon]。最明顯的共同結構即是 joint attention：嬰兒時期即可見於人類身上的特質，嬰兒會注意到周圍之人的注意力焦點，並且望向他人注目的方向。例如，嬰兒的視線常常跟隨著母親的視線。joint attention 也是「指涉」能在人類溝通時運作的基礎。原住民與荷蘭人第一次接觸時，最早的溝通應始於比手畫腳的「指涉」，接著透過有系統性地配對語音與「類似但有些微差異」的動作逐步累積詞彙，例如：
+
+1. 拿著一片葉子並說出：「L」
+2. 拿著一片葉子再使其落下，並說出：「L D」
+3. 拿著一根樹枝並說出：「B」
+4. 拿著一根樹枝再使其落下，並說出：「B D」
+
+如此便可慢慢累積詞彙，雖然勢必會製造許多歧異，然至少應可做到最為簡略的溝通。
+
+### (B)
+透過上述緩慢的學習，任一方皆有可能學會另一方的語言。然而就歷史上的關係而言，原住民似乎沒有動機要學會荷蘭語，荷蘭人因為經濟利益的需求，較有可能具備動機學習原住民的語言。而歷史遺留下來的資料也支持這個想法。荷屬東印度公司在臺灣三十多年，透過傳教士傳入基督教以及書寫系統。傳教士為方便傳教與傳達政令，學習原住民語言並且編撰字典將新港語透過羅馬拼音文字化。文字化後的新港文更為日後西拉雅族用於契約簽訂，形成了新港文書[@2018d; @2018e]。
+
+[^comon]: 有關 Bonus 題的題外話： 或許人類根本不可能與 heptapods 成功溝通。Dr.
+Banks 與 heptapods 之間的溝通始於「指涉」（Banks 指向自己並寫著 Louise），然而外星人要理解這個動作的意義必須先有「指涉」的概念，且其注意力運作的方式需與人類類似（當 Banks 指向自己時，heptapods需要知道必須將注意力放在 Banks 「手」指之處而非「手肘關節」指向之處）。
+
 ## 8
@@
 
-小琪的現象或許並非罕見。例如，研究顯示通常同儕相對於父母對使用何種語言有較大的影響力[＠standford2008]，或許在當時的國語政策下，同儕間（在學校）的溝通語言變成漢語為主，造成小琪日後以漢語作為主要語言。另一可能的原因為性別。以我所知的例子，
+小琪的現象或許並非罕見。例如，研究顯示通常同儕相對於父母對使用何種語言有較大的影響力[@stanford2008]，或許在當時的國語政策下，同儕間（在學校）的溝通語言變成漢語為主，造成小琪日後以漢語作為主要語言。另一可能的原因為性別。以我所知的例子，
 1. 我外公為外省籍的老兵，不會講閩南語，但其常不在家。我外婆為本省籍，講閩南語[^grandma]。因此可合理推測我母親幼時，家庭應該以閩南語為主。然我母親雖會講閩南語，但不算是最流利的那種（少了點母語使用者那種流暢的口音，某些詞彙也不清楚）。
@@
 
+## Bonus
+電影中不只一次出現語言與意圖的關係—詞彙不只帶有字面上的意義，隨著使用者的不同意圖或是既存的偏見，造成字彙有不同的詮釋意義。例如，電影開始不久後，Colonel Weber 兩度拜訪 Dr. Banks 時，Banks 提及梵語（Sanskrit）「戰爭（war)」的詞彙以及意義：
+
+> (Colonel 從學校離開前的對話)  
+> **Louise**: Are you going to ask Danvers next?...Before you commit to him, ask him the Sanskrit word for war and its translation. 
+> 
+> (Colonel 半夜搭直昇機拜訪 Dr. Banks)  
+> **Colonel**: He says it means "an argument". What do you say it means?  
+> **Louise**: A desire for more cows.
+
+我認為這裡展現出電影對於語言的多義性的重視，以及其對於人類的影響。對相同詞彙的不同翻譯，展現出非常不一樣的意圖：一個表現出「敵意」（"argument"），另一個則相對和平（"desire for more cows"）—在一念之間，不同的詮釋可能造成衝突或和平。
+
+語言與意圖之間的關聯在電影中的另一個地方更加地被突顯了出來：
+
+> (Dr. Banks 在翻譯擷取的中文)  
+> **Louise**: Colonel, those are all tile sets in mah-jongg. Are they using a game to converse with their heptapods?  
+> **Colonel**: Maybe. Why?  
+> **Louise**: Well, let's say that I taught them chess instead of English. Every conversation would be a game. Every idea expressed through opposition, victory, defeat.  
+> **Louise**: You see the problem?  
+> **Louise**: If all I ever gave you was a hammer...  
+> **Colonel**: Everything's a nail.
+
+這裡更加入了語言的「譬喻」特性，透過譬喻語言的意義得到了驚人的擴充。「譬喻」在這裡或許也顯示出人類喜好尋找語言的「言外之意」的特性，也顯示溝通過程中從來不是簡單的「送出」與「接收」，而是在過程中相互不斷進行揣摩與推論。語言與溝通是一個非常動態的過程。
+
+電影中的其它部份，主要闡述人類的思考如何受限於我們生存的世界、概念以及語言。電影中代有非常強烈的沃爾夫的色彩，認為學習一種結構非常特異的語言能為大腦帶來全面性的改變，甚至超越我們所生存的三度空間，感知超越「現在」的時空。我想這邊屬於電影比較浪漫、自由創造的部份，也同時是這部電影中最吸引人的地方，縱使我多半不認同這些主張。
+
 ## 參考資料{#reference}

### 2018-05-25 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 author: Yongfu Liao
-date: March 18, 2018
+date: "`r Sys.Date()`"
 bibliography: /home/liao/local_depend/citation/neanderthals.bib

### 2018-05-25 GitHubPage/lang_social_survey/techniques.R

@@ -1,0 +1,20 @@
+library(dplyr)
+
+############ How to find out the most fluent language ############
+df <- data_frame(
+    x1 = rnorm(10), #lang1
+    x2 = rnorm(10), #lang2
+    x3 = rnorm(10)  #lang3
+    )
+
+df <- df %>%
+    rowwise() %>%
+    mutate(best_val = max(x1, x2, x3)) %>%
+    ungroup() %>%
+    mutate(best = if_else(x1 == best_val, "x1",
+                          if_else(x2 == best_val, "x2",
+                                  "x3")
+                          )
+           ) %>%
+    select(-best_val)
+##################################################################

### 2018-05-28 1062_class/Multivariate_Analysis/HW4_classification/multivarite_hw4.Rmd
up

---
title: "多變量分析 HW4"
author: "劉昱維, 吳冠瑋, 廖永賦, 謝靖惟, 黃奎鈞"
css: /home/liao/local_depend/style_sheets/style.css
output:
  bookdown::pdf_document2:
    number_sections: no
    includes:
      in_header: /home/liao/local_depend/pdf_document/header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    includes:
      before_body: mathjax_bm.tex
    number_sections: no
geometry: margin=0.7in
fontsize: 11pt
always_allow_html: yes
---

```{r setup, include=FALSE}
library(svglite)
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(
	echo = FALSE,
	fig.dim = c(7, 4),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev='svg',
	out.width = "100%"
)
} else {
    library(showtext)
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          out.width = '70%',
                          fig.showtext = T)
}
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme_light() +
    theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
```

## 11.1
+ a) $~~~~\hat{y} = (\bar{x_1} - \bar{x_2})^{\prime}S^{-1}_{pooled}x = \hat{a}^{\prime}x$<br>
     $~~~~~~~S^{-1}_{pooled} = \begin{bmatrix} 2 & -1 \\ -1 & 1 \end{bmatrix}$<br>
     $~~~~~~~\begin{bmatrix} -2 & -2 \end{bmatrix}\begin{bmatrix} 2 & -1 \\ -1 & 1 \end{bmatrix}x = -2x_1$
+ b) $~~~~\hat{m} = \frac{1}{2}(\hat{y_1}+\hat{y_2}) = -8$<br>
     $~~~~~~-2(2) = -4 > -8 \Rightarrow assign~to~\pi_1$

## 11.4
+ a) $~~~~(\frac{c(1\mid 2)}{c(2\mid 1)})(\frac{p_2}{p_1}) = 0.5$<br>
     $~~~~~~~\Rightarrow assign~to~\pi_1~if~\frac{f_1(x)}{f_2(x)}\geq0.5,~otherwise~assign~to~\pi_2$
+ b) $~~~~\frac{f_1(x)}{f_2(x)} = \frac{0.3}{0.5} = 0.6 > 0.5\Rightarrow assign~to~\pi_1$

## 11.19
+ b) $~~~~\hat{y_0} = \hat{a}^{\prime}x_0 = -0.33x_1+0.67x_2$<br>
     $~~~~~~~where~\hat{m} = 4.5$<br>
     $~~~~~~~assign~to~\pi_1~if~-0.33x_1+0.67x_2-4.5\geq 0,~otherwise~assign~to~\pi_2$

| | $\pi_1$ | | | $\pi_2$ | |
|---|---|---|---|---|---|
|obs.| $−0.33x_1+0.67x_2−4.5$ | class. | obs. | $−0.33x_1+0.67x_2−4.5$ | class.|
| 1 | 2.83 | $\pi_1$ | 1 | -1.5 | $\pi_2$ |
| 2 | 0.83 | $\pi_1$ | 2 | 0.5 | $\pi_1$ |
| 3 | -0.17 | $\pi_2$ | 3 | -2.5 | $\pi_2$ |

+ c) $~~~~D^2_i(x) = (x - \bar{x_i})^{\prime}S^{-1}_{pooled}(x - \bar{x_i})$

|  | | $\pi_1$ | | | $\pi_2$ | | |
|---|---|---|---|---|---|
|obs.| $D^2_1$ | $D^2_2$ | class. | obs. | $D^2_1$ | $D^2_2$ | class.|
| 1 | 1.33 | 7 | $\pi_1$ | 1 | 4.33 | 1.33 | $\pi_2$ |
| 2 | 1.33 | 3 | $\pi_1$ | 2 | 0.33 | 1.33 | $\pi_1$ |
| 3 | 1.33 | 1 | $\pi_2$ | 3 | 6.33 | 1.33 | $\pi_2$ |

## 11.32
```{r}
hemo <- readr::read_table2("T11-8.DAT", col_names = FALSE,
                           col_types = cols(X1 = col_character())
                           ) %>%
    set_names(c("group", "activity", "antigen"))
```

### (a) Bivariate plot
```{r}
pl <- ggplot(hemo) +
    geom_point(aes(x=activity, y=antigen, shape=group, color=group))+
    labs(color="Group",shape="Group",
         x = expression('log'[10]*'(AHF activity)'),
         y = expression('log'[10]*'(AHF antigen)')
         )
pl + theme_light()
```

The bivariate plot doesn't seem to fit well into a bivariate normal distribution.

#### SAS `pool=test`

```{r out.width=c("40%","70%"), fig.show='hold'}
include_graphics("p2.png")
include_graphics("p1.png")
```

Test not significant. The covariance of the two groups are assumed to be equal.

#### SAS `manova`

```{r out.width="50%"}
include_graphics("p3.png")
```

Means of two groups are not equal.

### (b) linear disciminant function
```{r}
x1_bar <- hemo[hemo$group == "1",2:3] %>% colMeans()
x2_bar <- hemo[hemo$group == "2",2:3] %>% colMeans()
sum <- x1_bar + x2_bar

S1 <- hemo[hemo$group == "1", 2:3] %>% cov()
S2 <- hemo[hemo$group == "2", 2:3] %>% cov()

n1 <- hemo[hemo$group == "1",] %>% nrow
n2 <- hemo[hemo$group == "2",] %>% nrow

S_pool <- ((n1 - 1)*S1 + (n2 - 1)*S2)/(n1 + n2 - 2)

a <- solve(S_pool) %*% (x1_bar - x2_bar)
cutoff <- .5 * (x1_bar - x2_bar) %*% solve(S_pool) %*% (x1_bar + x2_bar)
```

\begin{equation}
\begin{split}
\hat{y} &= (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ \bm{x}_0 \\
&= \bm{a}^T \bm{x}_0 \\
&= \begin{pmatrix}
`r a[1] %>% round(3)` & `r a[2] %>% round(3)`
\end{pmatrix}
\bm{x}_0
\end{split}
(\#eq:ref-1)
\end{equation}

Then allocate $\bm{x}_0$ to $\pi_1$ if:

\begin{equation}
\begin{split}
\hat{y} &\geq \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) \\
&= \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2)
= `r cutoff %>% round(3)`
\end{split}
(\#eq:ref-2)
\end{equation}

where, $\bar{\bm{x}}_1 =\begin{pmatrix}
`r x1_bar[1] %>% round(3)`  \\
`r x1_bar[2] %>% round(3)` 
\end{pmatrix}, 
\bar{\bm{x}}_2 = \begin{pmatrix}
`r x2_bar[1] %>% round(3)`  \\
`r x2_bar[2] %>% round(3)` 
\end{pmatrix}$

The linear discriminant function is:

\begin{equation}
`r round(a[1],3)` x_{0,1} `r round(a[2],3)` x_{0,1} + `r -round(cutoff,3)`
(\#eq:discri-1)
\end{equation}

```{r}
library(MASS)
lda_hold <- lda(formula = group ~ activity + antigen, 
                CV=TRUE, prior=c(1,1)/2, data = hemo)

confus_mt_hold <- table(hemo$group, lda_hold$class, 
      dnn = c('Actual Group','Predicted Group'))
```

The confusion matrix constructed with the holdout procedure is
```{r}
confus_mt_hold %>% 
    knitr::kable(row.names = T, 
                 format = "markdown", align = "c",
                 col.names = c("Group 1", "Group 2"))
```

, and the estimated error rate is **`r (confus_mt_hold[1,2] + confus_mt_hold[2,1]) / sum(confus_mt_hold)`**.

The misclassified observations are **No. `r which(hemo$group != lda_hold$class %>% paste(sep=", "))`**, labeled "M" in the plot below.
```{r misclassified}
index <- which(hemo$group != lda_hold$class)
pl +
    geom_text(aes(x=activity, y=antigen, label = "M"),
              data = hemo[index,],
              size = 2, nudge_x = 0.01) + theme_light()
```

### (c)

```{r}
x0 <- c(-0.112 , -0.279)
y0 <- (t(a) %*% x0)[1,1]
```

By eq. \@ref(eq:ref-1) and eq. \@ref(eq:ref-2), $\hat{y}_0 = `r y0 %>% round(3)` \geq `r cutoff %>% round(3)`$. Hence, it is allocated to **Group 1**.

### (d)
```{r}
library(mvtnorm)
f1_x0 <- dmvnorm(x = x0, mean = x1_bar, sigma = S1)
f2_x0 <- dmvnorm(x = x0, mean = x2_bar, sigma = S2)
```

Classification rule based on posterior probabilities is equivalent to classification rule based on minimizing TPM.

Since the prior probabilities are assumed to be equal, the posterior probabilities are calculated as:

\begin{equation}
\begin{split}
p(\pi_1|\bm{x}_0) &= \frac{ f_1(\bm{x}_0)}{f_1(\bm{x}_0) + f_2(\bm{x}_0)} = `r f1_x0/(f1_x0 +f2_x0) %>% round(3)` \\
p(\pi_2|\bm{x}_0) &= 1 - p(\pi_1|\bm{x}_0)
= `r f2_x0/(f1_x0 +f2_x0) %>% round(3)`
\end{split}
(\#eq:posterior)
\end{equation}

, where the densities $f_1(\bm{x}_0)$ and $f_2(\bm{x}_0)$ are assumed to be normal and are estimated using $\bar{\bm{x}}_1, \bar{\bm{x}}_2, \bm{S}_1, \bm{S}_2$.

By $p(\pi_1|\bm{x}_0) > p(\pi_2|\bm{x}_0)$, $\bm{x}_0$ is classified as **Group 1**.

### (e)

By eq. \@ref(eq:ref-1), eq. \@ref(eq:ref-2), and [c](#c), the linear discriminant score is calculated as $\hat{y}_0 - \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) = `r (y0 - cutoff) %>% round(3)`$.

### (f)
Assume $p_1 = 0.75$ and $p_2 = 0.25$, then allocate $\bm{x}_0$ to $\pi_1$ if:

\begin{equation}
\begin{split}
\hat{y} &\geq \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + 
ln (\frac{c(1|2) p_2}{c(2|1) p_1}) \\
&= \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + ln (\frac{0.25}{0.75})
= `r (cutoff + log(0.25/0.75)) %>% round(3)`
\end{split}
(\#eq:uneq-prior)
\end{equation}

where, $\bar{\bm{x}}_1 =\begin{pmatrix}
`r x1_bar[1] %>% round(3)`  \\
`r x1_bar[2] %>% round(3)` 
\end{pmatrix}, 
\bar{\bm{x}}_2 = \begin{pmatrix}
`r x2_bar[1] %>% round(3)`  \\
`r x2_bar[2] %>% round(3)` 
\end{pmatrix}$

The linear discriminant function is:

\begin{equation}
`r round(a[1],3)` x_{0,1} `r round(a[2],3)` x_{0,1} + `r -round(cutoff + log(0.25/0.75), 3)`
(\#eq:discri-2)
\end{equation}

```{r}
lda_hold <- lda(formula = group ~ activity + antigen, 
                CV=TRUE, prior=c(0.75,0.25), data = hemo)

confus_mt_hold <- table(hemo$group, lda_hold$class, 
      dnn = c('Actual Group','Predicted Group'))
```

The confusion matrix constructed with the holdout procedure is
```{r}
confus_mt_hold %>% 
    knitr::kable(row.names = T, 
                 format = "markdown", align = "c",
                 col.names = c("Group 1", "Group 2"))
```

, and the estimated error rate is **`r (confus_mt_hold[1,2] + confus_mt_hold[2,1]) / sum(confus_mt_hold)`**.

The misclassified observations are **No. `r which(hemo$group != lda_hold$class %>% paste(sep=", "))`**, labeled "M" in the plot below.
```{r misclassified2}
index <- which(hemo$group != lda_hold$class)
pl +
    geom_text(aes(x=activity, y=antigen, label = "M"),
              data = hemo[index,],
              size = 2, nudge_x = 0.01) + theme_light()
```

### (g)

```{r}
x0 <- c(-0.112 , -0.279)
y0 <- (t(a) %*% x0)[1,1]
dis_score <- y0 - (cutoff + log(0.25/0.75))
```

By eq. \@ref(eq:ref-1) and eq. \@ref(eq:uneq-prior), $\hat{y}_0 - [ \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + ln (\frac{0.25}{0.75}) ] = `r dis_score %>% round(3)` > 0$. Hence, it is allocated to **Group 1**.

### (h)
```{r}
library(mvtnorm)
f1_x0 <- dmvnorm(x = x0, mean = x1_bar, sigma = S1)
f2_x0 <- dmvnorm(x = x0, mean = x2_bar, sigma = S2)
p1 <- 0.75
p2 <- 0.25
```

Classification rule based on posterior probabilities is equivalent to classification rule based on minimizing TPM.

The posterior probabilities are calculated as:

\begin{equation}
\begin{split}
p(\pi_1|\bm{x}_0) &= \frac{ p_1 f_1(\bm{x}_0)}{p_1 f_1(\bm{x}_0) + p_2 f_2(\bm{x}_0)} = `r p1*f1_x0/(p1*f1_x0 + p2*f2_x0) %>% round(3)` \\
p(\pi_2|\bm{x}_0) &= 1 - p(\pi_1|\bm{x}_0)
= `r p2*f2_x0/(p1*f1_x0 + p2*f2_x0) %>% round(3)`
\end{split}
(\#eq:posterior2)
\end{equation}

, where the densities $f_1(\bm{x}_0)$ and $f_2(\bm{x}_0)$ are assumed to be normal and are estimated using $\bar{\bm{x}}_1, \bar{\bm{x}}_2, \bm{S}_1, \bm{S}_2$.

By $p(\pi_1|\bm{x}_0) > p(\pi_2|\bm{x}_0)$, $\bm{x}_0$ is classified as **Group 1**.

### (i)

By eq. \@ref(eq:ref-1), eq. \@ref(eq:uneq-prior), and [g](#g), the linear discriminant score is calculated as $\hat{y}_0 - [ \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + ln (\frac{0.25}{0.75}) ] = `r y0 - (cutoff + log(0.25/0.75)) %>% round(3)`$.

### (j)
```{r out.width="50%", fig.show='hold'}
fc_eq <- function(x) -a[1]*x/a[2] + cutoff[1,1]/a[2] 
fc_uneq <- function(x) -a[1]*x/a[2] + (cutoff[1,1] + log(0.25/0.75))/a[2]

pl+stat_function(fun = fc_eq) +
    geom_point(aes(x=-0.112 , y=-0.279))+
    geom_text(aes(x=-0.112 , y=-0.279, 
                  label="(-0.112 , -0.279)"),
              nudge_x=0.09, size=3) +
    labs(title="Equal Prior Probabilities")+
    xlim(c(-0.75,0.25))+
    ylim(c(-0.50, 0.5))+ theme_light()

pl+stat_function(fun = fc_uneq)+
    geom_point(aes(x=-0.112 , y=-0.279))+
    geom_text(aes(x=-0.112 , y=-0.279, 
                  label="(-0.112 , -0.279)"),
              nudge_x=0.09, size=3) +
    labs(title="P1 = 0.75, P2 = 0.25")+
    xlim(c(-0.75,0.25))+
    ylim(c(-0.50, 0.5))+ theme_light()
```

When the prior probability $p_1$ changes from 0.5 to 0.75, the discriminant function shifts parallelly to the upper-left direction.

### 2018-05-28 1062_class/lang_social_mid/doc.Rmd
up

@@
 ---
+
+```{r setup, include=FALSE}
+library(svglite) 
+knitr::opts_chunk$set(
+    echo = FALSE, # No display code chunks
+    message = FALSE,
+    warning = FALSE,
+    dev='svglite', # or 'svglite' for multibite characters
+    comment="",
+    fig.dim = c(6, 4)  # (width, height)
+)
+options(digits = 4) # auto round to 2 decimals when printed
+library(dplyr)
+```
+
+## 3
+### (A)
+黃宣範老師對於人口結構的推論幾乎著重在估計外省人口數。關於外省人口數的推論，我認為黃老師做足了功課，包含參考許多人口學者的估計，甚至也考慮到更改成外省籍的臺灣婦女。然而，比較另我困惑的是要如何處理通婚人口所生之子女？黃老師避過了此問題，而以獨立的方式處理人口結構：每個族群依照各自的族群成長率成長。當然，要處理通婚人口所生之子女會使事情便得非常複雜，因為需假定各族群的通婚情況。總體而言，我認為黃老師已在其能夠取得的資料下，做出最詳細的推論。
+
+### (B)
+根據內政部 1993 至 2017 的人口統計資料（人口總數、自然增加率）[@neizhengbuhuzhengsi]，並假設
+
+1. 各族群間自由通婚（假設通婚為隨機的）
+2. 各族群自然增加率相同（依據內政部資料，每年自然增加率逐年下降）
+
+則使用 1993 年內政部統計之總人口數 20995416 為起始，並以「閩南人：73.3%；外省人：13%；客家人：12%；原住民： 1.7%」的比例計算出該年各族群人口做為開始。接著以內政部統計之每年自然增加率計算，可得 2017 人口比例如下表：
+```{r}
+pop <- readr::read_csv("pop.csv") %>% 
+    mutate(growth = growth/1000,
+           tw_pop = pop_size*0.733,
+           ch_pop = pop_size*0.13,
+           hk_pop = pop_size*0.12,
+           abroi_pop = pop_size*0.017)
+
+pop_size <- pop$pop_size[1]
+growth <- pop$growth
+tw_pop <- pop$tw_pop[1]
+ch_pop <- pop$ch_pop[1]
+abroi_pop <- pop$abroi_pop[1]
+hk_pop <- pop$hk_pop[1]
+
+for (i in 2:26){
+
+    tw_pop[i] <- (1+growth[i-1])*pop_size[i-1]*((tw_pop[i-1]/pop_size[i-1])^2 +
+        (tw_pop[i-1]/pop_size[i-1])*(hk_pop[i-1]/pop_size[i-1]) +
+        (tw_pop[i-1]/pop_size[i-1])*(ch_pop[i-1]/pop_size[i-1]) +
+        (tw_pop[i-1]/pop_size[i-1])*(abroi_pop[i-1]/pop_size[i-1]))
+
+    hk_pop[i] <- (1+growth[i-1])*pop_size[i-1]*((hk_pop[i-1]/pop_size[i-1])^2 +
+        (hk_pop[i-1]/pop_size[i-1])*(tw_pop[i-1]/pop_size[i-1]) +
+        (hk_pop[i-1]/pop_size[i-1])*(ch_pop[i-1]/pop_size[i-1]) +
+        (hk_pop[i-1]/pop_size[i-1])*(abroi_pop[i-1]/pop_size[i-1]))
+
+    ch_pop[i] <- (1+growth[i-1])*pop_size[i-1]*((ch_pop[i-1]/pop_size[i-1])^2 +
+        (ch_pop[i-1]/pop_size[i-1])*(hk_pop[i-1]/pop_size[i-1]) +
+        (ch_pop[i-1]/pop_size[i-1])*(tw_pop[i-1]/pop_size[i-1]) +
+        (ch_pop[i-1]/pop_size[i-1])*(abroi_pop[i-1]/pop_size[i-1]))
+
+    abroi_pop[i] <- (1+growth[i-1])*pop_size[i-1]*((abroi_pop[i-1]/pop_size[i-1])^2 +
+        (abroi_pop[i-1]/pop_size[i-1])*(ch_pop[i-1]/pop_size[i-1]) +
+        (abroi_pop[i-1]/pop_size[i-1])*(tw_pop[i-1]/pop_size[i-1]) +
+        (abroi_pop[i-1]/pop_size[i-1])*(abroi_pop[i-1]/pop_size[i-1]))
+
+    pop_size[i] <- sum(tw_pop[i], hk_pop[i], ch_pop[i], abroi_pop[i])
+}
+df <- cbind(1993:2018, tw_pop, hk_pop, ch_pop, abroi_pop) %>% as_data_frame()
+
+table <- df[25, 2:5]/sum(df[25,])*100
+knitr::kable(paste(table %>% round(3),"%", sep = "") %>% t(),
+             "markdown", align = "c", 
+             col.names = c("閩南","客家","外省","原住民"),
+             caption = "總人口數：`r sum(df[25,])`"
+             )
+```
+
+對照原委會資料[@yuanzhuminzuweiyuanhui2018]，2018 年 4 月原住民人數為 561,327，與這裡的`r df$abroi_pop[25] %>% as.integer` 有相當大的差距。這顯示原住民在保存自己文化上的動力比起預設（隨機通婚）還強上許多，或許是個值得高興的現象。
+
+## 4
+
+> 事件一（1988.10.9）：影片「舊情綿綿」因台語使用過多，片商無法爭取到普通級，只能以輔導級映演……新聞局怕他們（十三歲以下學童）會忘記國語，或拒絕使用國語。
+
+此事件只是縱多類似事件的翻版：政府因為抱持著許多荒謬的信念，而做出許多滑稽可笑的規定。跳脫此事件，如果歷史上的政策規定，有這麼多是依據這些毫無根據的信念所制定，那真的對臺灣帶來很大的傷害。國語政策的背後，抱持著（國民政府心中的）漢文化是最「好」的、上下齊心（透過統一文化及語言）的國家是最強大的概念。結果就是造成臺灣多元的文化快速流失，逐步朝向單一化。臺灣是一個小國，不具備大國那種人海資源，因而小國的生存之道僅能仰賴創新。多元是創新的根本[@leung2008; @leung2010]，逐漸失去多元性的臺灣如同在扼殺自己的生存空間。
+
+> 事件二（1988.10.27）：僑選立委簡漢聲呼籲政府推展閩南語、客語、國語並進之雙語、三語教學，以使外省子弟能夠有學習本地方言的機會，使省級歧見消弭於無形……外省子定更因沒有機會學習方言，而在就業等方面受到限制與歧視。
+
+此事件讓我記憶特別深的原因是它以我平常比較少接觸到的角度顯示國語政策帶來的影響。根據既往成見，總是會認為只有臺灣方言使用者是國語政策下的受害者，然而這裡以外省第二代的角度說明了國語政策的影響，外省子弟也是遭受歧視的一群人。這位僑選立委的發言，更隱含了一個非常有遠見的想法：消弭族群隔閡的方式並非只有將其同化成單一族群，讓每個族群互相學習可能會是種更好的方法。
 

### 2018-05-28 GitHubPage/lang_social_survey/animate.Rmd
up

---
title: "animate test"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r results='hide', message=FALSE, warning=FALSE, paged.print=FALSE}
source("shape.R")
```

```{r include=FALSE}
animation::saveGIF(for (i in colnames(sp)[c(2,3)]) plot(sp[i]),
        movie.name = "plot.gif", img.name = "plott",
        ani.dev = function(...){png(res=130*1.2,...)})
```

```{r, fig.width=8}
knitr::include_graphics("plot.gif")
```

### 2018-05-28 1062_class/Multivariate_Analysis/HW4_classification/classify_2_linear.R

@@ -1,0 +1,63 @@
+hemo <- readr::read_table2("T11-8.DAT", col_names = FALSE,
+                           col_types = cols(X1 = col_character())
+)
+
+###### APER (lda) #####
+library(MASS)
+lda <- lda(formula = group ~ activity + antigen,
+           prior=c(1,1)/2, data = hemo)
+lda_prdict <- predict(lda)$class
+
+confus_mt <- table(hemo$group, lda_prdict, dnn = c('Actual Group','Predicted Group'))
+(confus_mt[1,2] + confus_mt[2,1])/sum(confus_mt)
+
+####### Holdout Procedure(lda) ######
+lda_hold <- lda(formula = group ~ activity + antigen, 
+                CV=TRUE, prior=c(1,1)/2, data = hemo)
+
+confus_mt_hold <- table(hemo$group, lda_hold$class, 
+      dnn = c('Actual Group','Predicted Group'))
+## Error Rate: Exp_AER
+(confus_mt_hold[1,2] + confus_mt_hold[2,1])/sum(confus_mt_hold)
+
+######## Holdout Procedure (Manual) ######
+data <- hemo
+n1_m <- 0 # holdouts misclassified as 2 in n1
+n2_m <- 0 # holdouts misclassified as 2 in n1
+pre_group_vec <- vector(mode = "character",length = nrow(data))
+for (i in 1:nrow(data)){
+    holdout <- data[i,]
+    data <- data[-i,]
+    
+    library(MASS)
+    r2 <- lda(formula = group ~ activity + antigen, 
+              data = data)
+    predicted_group <- predict(r2, newdata = holdout)$class
+    pre_group_vec[i] <- predicted_group
+    if (predicted_group != holdout$group) {
+        if (holdout$group == "1") n1_m = n1_m + 1
+        else n2_m = n2_m + 1
+    }
+    data <- hemo
+}
+confu_mt <- table(data$group, pre_group_vec, 
+                  dnn = c('Actual Group','Predicted Group'))
+Exp_AER <- (n1_m + n2_m)/nrow(data)
+
+
+####### Calculate discriminant fc (Pure manual) #######
+x1_bar <- hemo[hemo$group == "1",2:3] %>% colMeans()
[…]

### 2018-05-28 GitHubPage/lang_social_survey/shape.R

@@ -1,0 +1,16 @@
+library(sf)
+library(dplyr)
+library(readr)
+
+##### Extract zipcode from TOWN_zip.kml in order to combine to shp ####
+# the extracted df is saved to ./spatial_data/zipcode_towncode.csv #
+
+# zip <- st_read("./shape/TOWN_zip.kml")[,c("TOWNCODE","ZIPCODE", "COUNTYNAME","TOWNNAME")] %>% st_set_geometry(NULL) %>% arrange(ZIPCODE)
+# write_csv(zip, "./spatial_data/zipcode_towncode.csv")
+zip <- read_csv("spatial_data/zipcode_towncode.csv", 
+    col_types = cols(ZIPCODE = col_character()))[,2:4]
+sp <- st_read("./shape/TOWN_MOI_1070330.shp")
+
+sp <- sp %>% 
+    left_join(zip, by = c("COUNTYNAME","TOWNNAME")) %>%
+    select(COUNTYNAME, TOWNNAME, ZIPCODE)

### 2018-05-28 GitHubPage/lang_social_survey/techniques.R

@@ -1,5 +1,19 @@
 library(dplyr)
 
+############ How to find out languages more fluent than chinese ############
+df <- data_frame(
+    x1 = sample(0:5, 10, replace = T), #lang1 ch
+    x2 = sample(0:5, 10, replace = T), #lang2 tw
+    x3 = sample(0:5, 10, replace = T)  #lang3 hk
+    )
+
+df <- df %>%
+    mutate(x2_domin = if_else(x2 >= x1, T, F),
+           x3_domin = if_else(x3 >= x1, T, F))
+
+##################################################################
+library(dplyr)
+
 ############ How to find out the most fluent language ############
 df <- data_frame(
     x1 = rnorm(10), #lang1

### 2018-05-28 travis/preinstall.sh

@@ -1,0 +1,2 @@
+sudo apt-get install libcairo2-dev
+sudo apt-get install libxt-dev

### 2018-05-29 1062_class/eco_model/HW/C10/rk4.Rmd
up

---
title: "Two Resource one Predator"
author: "Yongfu Liao"
date: "`r Sys.Date()`"
css: /home/liao/local_depend/style_sheets/style.css
output:
  bookdown::html_document2:
    includes:
      before_body: /home/liao/local_depend/style_sheets/mathjax_bm.tex
    number_sections: no
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.dim = c(7, 4),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = "svg",
	out.width = "100%"
)
```

```{r}
library(magrittr)
library(readr)
coexi <- read_delim("data_coexi.txt", 
    "\t", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE) %>%
    set_names(c("time", "R1", "R2", "Predator"))

R1_win <- read_delim("data_R1_exclude_R2.txt", 
    "\t", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE) %>%
    set_names(c("time", "R1", "R2", "Predator"))

R2_win <- read_delim("data_R2_exclude_R1.txt", 
    "\t", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE) %>%
    set_names(c("time", "R1", "R2", "Predator"))
```

## Model

\begin{equation}
\begin{split}
&\frac{d R_1}{dt} = [r_1 (1 - \frac{R_1}{K_1}) - a_1 P] ~ R_1 \\
&\frac{d R_2}{dt} = [r_2 (1 - \frac{R_2}{K_2}) - a_2 P] ~ R_2 \\
&\frac{d P}{dt} = (b_1 R_1 + b_2 R_2 - m) ~ P
\end{split}
\end{equation}

## C code

Download [rk4.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C10/rk4.c){target="_blank"}

```c
#include <stdio.h>
#include <stdlib.h>
#include <math.h>
double floor(double x);

//Fc declaration

	//Memory allocation
void message_error(char error_text[]);
double *d_vector(long size); //for generating double vector[1]...vector[size]
void free_d_vector(double *x);

	//Solving ODE
void differential (double time, double in[], double out[]);
double dx_dt(double time, double vr[]);
double dy_dt(double time, double vr[]);
void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) );

// Global variables
int j_x = 1, j_y = 2, j_p = 3; //index for x, y, p
double a1=0.7, a2=0.7, b1=1.0, b2=1.0;
double r1=0.8, r2=0.85, K1=1.2, K2=1.2, m=0.8; // model parameter
double t=0.0; //time
double deltat=0.01; //time step for rk4
double *N; // initialize array for population size
double *dfdt;

// Main function
int main(void){

	dfdt = d_vector(3); //set vector for 'differential' output
	N = d_vector(3);
	N[j_x] = 1.0; //set initial population size
	N[j_y] = 1.0; //set initial population size
	N[j_p] = 1.0; //set initial population size

	int i; //for loop index
	double T=300.2; // T: time of simulation

	for (i=0; i < T/deltat; i++){

		if (i % (int)floor(0.1/deltat) == 0 || i == 0){
			printf("%lf\t%lf\t%lf\t%lf\n", t, N[j_x], N[j_y], N[j_p]);
		}
		differential(t, N, dfdt);
		rk4(N, dfdt, 3, t, deltat, N, differential); //first N is input, second N is output
		t += deltat;
	}; //end for: end solving DE

	free_d_vector(N);
	free_d_vector(dfdt);
	return 0;
};

/* ODE Solver Functions */

double dx_dt(double time, double vr[]){
	return (r1*(1.0 - vr[j_x]/K1) - a1*vr[j_p])*vr[j_x];
};

double dy_dt(double time, double vr[]){
	return (r2*(1.0 - vr[j_y]/K2) - a2*vr[j_p])*vr[j_y];
};

double dp_dt(double time, double vr[]){
	return (b1*vr[j_x] + b2*vr[j_y] - m)*vr[j_p]; //DE for predator
};

void differential (double time, double in[], double out[]){
	out[j_x] = dx_dt(time, in);
	out[j_y] = dy_dt(time, in);
	out[j_p] = dp_dt(time, in);
};

/* 
void (*diff)(double, double [], double []) is a function pointer.
In order to use functions as inputs, it is included in the parameter of the function 'rk4'.
In this case, the function 'differential' is taken as input to the function 'rk4'.
*/

void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) )
{
	int i;
	double *k2, *k3, *k4, *D;
	// n: dimension of the ode
	// N_in: input population size ni. For 2-dim case n1=(pop. size of x); n2=(pop. size of y)
	// k1: parameter of rk4;  k1 = f(D,t); i.e. the output from differential is input of rk4
	k2 = d_vector(n); // rk4 k2
	k3 = d_vector(n); // rk4 k3
	k4 = d_vector(n); // rk4 k4
	D = d_vector(n); // Dummy variable for calculating coefficients of k_i in rk4

	for (i=1;i<=n;i++) D[i] = N_in[i] + (h/2.0)*k1[i];
	(*diff)(t+h/2.0, D, k2);
	for (i=1;i<=n;i++) D[i] = N_in[i] + (h/2.0)*k2[i];
	(*diff)(t+h/2.0, D, k3);
	for (i=1;i<=n;i++) D[i] = N_in[i] + h*k3[i];
	(*diff)(t+h, D, k4);

	for (i=1;i<=n;i++) N_out[i] = N_in[i] + (h/6.0)*(k1[i] + 2.0*k2[i] + 2.0*k3[i] + k4[i]);

	free_d_vector(D);
	free_d_vector(k2);
	free_d_vector(k3);
	free_d_vector(k4);

};

/* Memory Allocation Functions */

void message_error(char error_text[])
/*Standard error handler*/
{
    printf("There are some errors...\n");
    printf("%s\n", error_text);
    printf("...now existing to system...\n");
    exit(1);
};

double *d_vector(long size){ //for generating double vector[1]...vector[size]
    double *x; //pointer

    x = malloc((size + 1)*sizeof(double));
    //allocation of memory space to stock (size + 1) double variables & malloc returns the address of the top of the allocated memory space to x
    //the reason to prepare (size + 1) is just to use from x[1] to x[size]

    if(x == NULL) message_error("allocation failure in d_vector()"); //if memory allocation was failed, malloc returns NULL and x becomes NULL
    return x; //return the address of the top of the allocated memory space to x
};

void free_d_vector(double *x)
{
    free(x);
};
```

### R~1~ R~2~ Coexist
```c
double a1=0.7, a2=0.7, b1=1.0, b2=1.0;
double r1=0.8, r2=0.85, K1=1.2, K2=1.2, m=0.8;
```

```{r}
library(ggplot2)
ggplot(coexi)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[1]*' R'[2]*' Coexist'))
```

### R~1~ Exclude R~2~
```c
double a1=0.5, a2=0.5, b1=1.5, b2=1.0;
double r1=1.0, r2=0.7, K1=1.2, K2=1.2, m=0.5;
```
```{r}
ggplot(R1_win)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[1]*' Exclude'*' R'[2]))
```

### R~2~ Exclude R~1~
```c
double a1=0.5, a2=0.3, b1=0.7, b2=1.1;
double r1=0.7, r2=0.7, K1=1.2, K2=1.2, m=0.5;
```
```{r}
ggplot(R2_win)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[1]*' Exclude'*' R'[2]))
```

### 2018-05-29 1062_class/lang_social_mid/doc.Rmd
up

@@
 geometry: margin=1in
-link-citations: yes
+link-citations: no
 csl: /home/liao/local_depend/style_sheets/apa_ch.csl
@@
 
-## 3
-### (A)
+## 1 《語言、社會、與族群意識》在第一章中提到台灣國名的困境。請從你的觀點闡述國名的困境有什麼方法可以獲得解決。
+
+坦白說，我並不認為目前有任何方法可以解決國名的困境。原因非常明顯，對岸是目前世界上拳頭最大的國家之一，對於臺灣的國名幾乎擁有絕對的否決權。黃宣範老師書中的討論似乎認為臺灣對於國名還有部份的自主權，然而我認為今日的情況並非如此樂觀，我們似乎只有在少數的非政府組織（規模還不能太大）才可能有國名的自主權。因此，縱使臺灣民眾對於國名有了共識，只要其不符中共的口味，此國名皆無法在國際上代表臺灣。
+
+## 2 《語言、社會、與族群意識》的書中第16頁的圖3提出了對於台灣語言位階圖的看法，請你回答下列問題。
+
+### (A) Diglossia
+
+雙言結構最核心的概念是語言之間存在「位階」的關係。在許多雙語或多語的社會中，語言的使用與社會階級、社交場域有所關聯：特定的語言（通常只有一種）往往用於上層社會階級；正式場合，如新聞媒體、教育場所等；且通常有組織（如政府）對此語言進行規範，如規定標準讀音、文字化等。另一些語言則用於日常生活中，為家人、朋友之間溝通的語言，常常是語言使用者的母語。由於與特定的社會結構、場域以及政治力量結合，前述的第一種語言通常被認為「位階較高」，其它用於非正式場合的語言則被認為「位階較低」。雙言結構常出現於曾受殖民統治的地區，統治階級所屬的語言位於「高位階」而被統治的當地居民的語言則位於「低位階」，例如 12 至 15 世紀英格蘭當時的英語（低）與法語（高）、當代許多位於非洲、拉丁美洲曾被殖民的國家等。
+
+### (B)
+
+- 媒體  
+臺灣的新聞媒體主要使用華語，然會於固定時段播出閩南語新聞（公視、民視、台視、華視）。另外有特別設置客家電視台與原住民族電視台（原視）。
+
+- 語言教育  
+臺灣的語言教育以華語為主，小學有鄉土語言的課程[^local]，同時也有英語課程。有趣的是，許多學生會用課餘時間補習英文。
+
+- 公領域  
+公領域，如在學校、公司等，以使用華語為主。這一部分原因可能是華語為臺灣目前最通行的語言。
+
+整體而言，我認為很難從媒體語言、語言教育以及公領域的使用語言來說明圖 3 的語言位階。我認為這有很大一部份是因為時代的差距，今日的華語普及率已遠勝 25 年前，因此「語言教育」及「公領域的使用語言」皆以華語為主很難說是雙言結構的現象，因為今日許多家庭以華語為主，華語是臺灣許多人的第一語言。
+
+另一方面，圖 3 將「臺灣國語」列為最低位階的語言。這點在今日的情況可能比較複雜，原因同樣也與華語普及有關。今日，「臺灣國語」應可分為兩種，第一種應比較接近圖 3 中的臺灣國語，是母語非華語的人為了溝通需求而發展出帶有濃厚臺灣腔的華語，主要見於今日六、七十歲以上的人們；另一種「臺灣國語」則見於今日大多數的臺灣人，是具有臺灣特色的華語，且為許多人年幼時即學會的語言，例如「ㄣ」、「ㄥ」不分，有些人「朋」讀作「ㄆㄨㄥ2」。此第二種臺灣國語應為今日臺灣地區的主要語言，而其與閩南語、客家語之間似乎沒有存在明顯的位階關係（或許是我的偏見），例如，今日同學之間似乎不會發生誰笑誰講「某某語言」的現象。第一種臺灣國語在今日的印象中，似乎已融入方言：聽到這種口音代表眼前這位的母語是臺灣方言。
+
+最後，關於圖 3 的洋化國語，我認為很難將其放入語言位階圖當中。洋化國語的出現是因為專業術語的需求，而專業術語可見於各行各業、用於圈內人。然我們並不會將含有專業術語的語言獨立成一套語言再將其置於語言位階圖中（例如，修車技師的術語不會被當作一套語言）。換句話說，我認為洋化國語並不能被當作「一種」語言，例如，醫生的肯定無法用洋化國語和物理學家進行溝通，因為「物理學家的洋化國語」和「醫生的洋化國語」是不相同的。洋化國語比較像是全球化帶來的現象，是在地語言的延伸，它和語族之間的統治與政治關係無關。
+
+[^local]: 依臺北市的規定[@zotero-80]，小學依學生意願就閩南語、客家語、原住民族語等三種本土語言。
+
+[^group]: 雖然透過現有的社會結構，洋化國語可能較常出現於特定族群身上，然而洋化國語
+
+## 3 在研究語言與社會的議題時，人口的結構非常重要，因為人口的多少與語言的權力有很大的關係。
+
+### (A) 從書中的討論，你認為黃宣範教授的推論合理嗎？有任何需要修正之處嗎？
 黃宣範老師對於人口結構的推論幾乎著重在估計外省人口數。關於外省人口數的推論，我認為黃老師做足了功課，包含參考許多人口學者的估計，甚至也考慮到更改成外省籍的臺灣婦女。然而，比較另我困惑的是要如何處理通婚人口所生之子女？黃老師避過了此問題，而以獨立的方式處理人口結構：每個族群依照各自的族群成長率成長。當然，要處理通婚人口所生之子女會使事情便得非常複雜，因為需假定各族群的通婚情況。總體而言，我認為黃老師已在其能夠取得的資料下，做出最詳細的推論。
 
-### (B)
+### (B) 從本書出版到現在，已經過了25年，請用各種資料說明，台灣的人口結構與比例，以百分比例呈現應該是多少？
+
 根據內政部 1993 至 2017 的人口統計資料（人口總數、自然增加率）[@neizhengbuhuzhengsi]，並假設
@@
 
-## 4
+### (c) 你認為台灣目前的平埔族完全消失了嗎？
+
+平埔族因為生存於臺灣的平原地區，長久以來多數應以漢化，少部份的平埔族文化融入地方文化中。極少數的平埔族保存自己的文化，例如，宜蘭的噶瑪蘭族可能因為地域關係的緣故而較能保有其文化。關於臺灣的平埔族是否完全消失，我認為其中一個很好的判定標準是其是否仍保有其族語。依此標準，「噶瑪蘭」、「巴則海[^baz]」、「噶哈巫」三個平埔族仍具有族語使用者[@2018f]，或許能作為臺灣平埔族尚未消失的證據之一。
+
+[^baz]: 巴則海語目前沒有第一語言使用者。
+
+## 4 《語言、社會、與族群意識》第53-73頁中舉出了台灣過去歷史上的語言衝突事件。請找出讓你感觸最大的事件的兩至三件。說明為何這些衝突現象讓你特別有感觸
 
@@
 
-## 5
+## 5 《語言、社會、與族群意識》書中的第79頁提到同化的7個步驟，並在第80頁提到，「台灣兩大族群之間同化（或融合）目前正處於（3）婚姻同化與（4）認同同化之間」。
+
 我覺得到了我們這一代 (1990 年後出生)應已達成階段 6「不再遭受歧視性的行為」的同化。其實對於臺灣的社會，從階段 4 過渡到階段 6 之間應該非常快速，這應與種族間的體質特徵（如膚色）差異程度有關。由於臺灣的各族群之間，外觀差異相當小，唯一能辨識族群差異的特徵大概只剩語言以及（相同語言下）發音的差異。當無法辨識出族群的差異，歧視性的態度或行為就沒有立基處，因而也就不會發生。
@@
 
-## 6
+## 6 《語言、社會、與族群意識》第118-119頁中有「日語運動與北京話運動比較表」，當然這個比較表是把比較重要的點提出來。
+
 就時間軸上來說，我認為這份比較表算是完整。然而由於此比較表主要是以「事件」為主，造成一些重要的限制。我認為其未能夠突顯出「日語運動」與「北京話運動」之間的一項重要差異：對於本土語言造成的衝擊。
@@
 
-[^scholar]: 這裡並非獨尊「學術界」的重要性，而是指出臺灣人對於「學術界」或「知識份子」抱有較「好」或「上層」感覺的現象。這原因應根植於臺灣長期受到漢人文化的影響。
+[^scholar]: 這裡並非獨尊「學術界」的重要性，而是指出臺灣人對於「學術界」或「知識份子」抱有較「好」或「上層」感覺的現象。這原因或許根植於臺灣長期受到漢人文化的影響。
 
 ## 7
-### (A)
+### (A) 請想像，在台灣的歷史上，當原住民與荷蘭人第一次接觸時，他們如何溝通？
 兩個語言無法互通的人第一次遇見之時要能溝通應是個漫長而緩慢的過程。要能溝通的第一個先決條件是兩者之間至少要有一些「共同」的地方。好險我們都是人類，在認知的結構上至少會有相似之處[^comon]。最明顯的共同結構即是 joint attention：嬰兒時期即可見於人類身上的特質，嬰兒會注意到周圍之人的注意力焦點，並且望向他人注目的方向。例如，嬰兒的視線常常跟隨著母親的視線。joint attention 也是「指涉」能在人類溝通時運作的基礎。原住民與荷蘭人第一次接觸時，最早的溝通應始於比手畫腳的「指涉」，接著透過有系統性地配對語音與「類似但有些微差異」的動作逐步累積詞彙，例如：
@@
 
-### (B)
+### (B) 隨著時間的推進，原住民與荷蘭人的語言溝通如何進行？
 透過上述緩慢的學習，任一方皆有可能學會另一方的語言。然而就歷史上的關係而言，原住民似乎沒有動機要學會荷蘭語，荷蘭人因為經濟利益的需求，較有可能具備動機學習原住民的語言。而歷史遺留下來的資料也支持這個想法。荷屬東印度公司在臺灣三十多年，透過傳教士傳入基督教以及書寫系統。傳教士為方便傳教與傳達政令，學習原住民語言並且編撰字典將新港語透過羅馬拼音文字化。文字化後的新港文更為日後西拉雅族用於契約簽訂，形成了新港文書[@2018d; @2018e]。
@@
 
-## 8
+## 8 請選擇下列至少兩部電影，闡述電影中語言的使用現象為何？並說明電影中的語言使用符合當時的歷史背景嗎？
 
@@
 
-電影中另一個有趣的語言現象即為主角小琪的語言。《幸福路上》以小琪的故事作為主幹，而小琪的故事其實就是《幸福路上》導演宋欣穎自身的成長故事[-@2018; -@2018a; -@2018b; -@2018c]。根據導演的受訪，馬上就可以回答電影中這個「奇怪」的語言現象—為何生長在父母皆使用閩南語的家庭，小琪仍然較常使用中文（漢語）？電影忠實地呈現了**導演宋欣穎自身語言使用的情況**：
+電影中另一個有趣的語言現象即為主角小琪的語言。《幸福路上》以小琪的故事作為主幹，而小琪的故事其實就是《幸福路上》導演宋欣穎自身的成長故事[-@2018; -@2018a; -@2018b; -@2018c]。根據導演的受訪，馬上就可以回答電影中這個「奇怪」的語言現象—為何生長在父母皆使用閩南語的家庭，小琪仍然較常使用中文（漢語）？電影忠實地呈現了導演宋欣穎自身語言使用的情況：
 
@@
 
-## 9
+## 9 你覺得語言結構會如何影響思維？
 
@@
 2.
-運用語言的思考：運用語言的思考最顯著的一個例子是「精確」的數量。人類以及許多其他動物，天生就對極小的數量（小於3或4）的數量有絕對的概念；對大量的數量有約略的概念；但對精確的「數字」，如「33」，是後天習得的。明確的證據指出精確的數字概念與語言之間的關聯 [@dehaene1999; @spelke2001; @frank2008]。沒有語言，或語言中不具有數字系統，人類將無法以精確的數量進行思考。
+運用語言的思考：運用語言的思考最顯著的一個例子是對於「精確」數量的概念。人類以及許多其他動物，天生就對極小的數量（小於3或4）的數量有絕對的概念、對大量的數量有約略的概念。但對精確的「數字」，如「33」，卻只有人類能透過後天習得。明確的證據指出精確的數字概念與語言之間的關聯 [@dehaene1999; @spelke2001; @frank2008]。沒有語言，或語言中不具有數字系統，人類將無法以精確的數量進行思考。
 
 3.
-語言對思考的後續影響：前述兩種語言與思維之間的關係直接與語言有所關聯，即思考本身是為了表達，或是透過語言進行思考，語言似乎直接參與了思考歷程。「語言對思考的後續影響」指的則是不涉及語言本身的思考：在長期使用特定語言下，是否會對思維產生影響。其中一項支持的證據來自語言中是否舉有單複數。日語、中文等語言的名詞，沒有單數或複數型態的差別；英語則必須指出名詞為單數或複數。因此，英語使用者可能會傾向將注意力集中在「個體」的特質，而日語或中文的使用者則可能傾向將注意力集中在「共同」的特質。例如，英語使用者可能較注意椅子的形狀，而日語、中文使用者則較注意椅子的材質。此假設受到 @li2009 的研究支持。
+語言對思考的後續影響：前述兩種語言與思維之間的關係直接與語言有所關聯，即思考本身是為了表達，或是透過語言進行思考，語言似乎直接參與了思考歷程。「語言對思考的後續影響」指的則是不涉及語言本身的思考：在長期使用特定語言下，是否會對思維產生影響。其中一項支持的證據來自語言中是否具備單複數型態。日語、中文等語言的名詞，沒有單數或複數型態的差別；英語則必須指出名詞為單數或複數。因此，英語使用者可能會傾向將注意力集中在「個體」的特質，而日語或中文的使用者則可能傾向將注意力集中在「共同」的特質。例如，英語使用者可能較注意椅子的形狀，而日語、中文使用者則較注意椅子的材質。此假設受到 @li2009 的研究支持。
 
-這些研究證據顯示語言以不同種方式影響思維的可能。然關於 Daniel Everett 對於 Pirahã 人的想法：「他們的語言沒有時態，他們真正活在當下之中」，似乎隱含更複雜的因素。首先，我同意這句話的後半段：人類在進入大規模社會後，先是曆法，接著時鐘的發明似乎改變人類對於時間的概念，大家開始擔心時間的流逝，並且開始「預約未來」（排行事曆、約會時間等）。Pirahã 人生活在沒有現代時間概念的社會中，且其生活方式也無須擔心是否有事情未完成，因此其「活在當下」顯得相當合理。然我認為難以使用「他們的語言沒有時態」作為理由。從 Pirahã 人的文化可以很明顯地發現其許多部份皆支持著 Pirahã 人「活在當下」，例如簡單的物質技術（所以不須從事大規模的生產）、從事漁獵採集（所以比起農耕更加不勞力密集）、沒有強烈的物質需求（只向 Everett 要求一些簡單的物資）等。文化本身即是強而有力的解釋，能夠說明 Pirahã 人「活在當下」。忽略這些文化因素而單以語言的結構作為解釋顯得相當不合理。
+這些研究證據顯示語言以不同種方式影響思維的可能。然關於 Daniel Everett 對於 Pirahã 人的想法：「他們的語言沒有時態，他們真正活在當下之中」，似乎隱含更複雜的因素。首先，我同意這句話的後半段：人類在進入大規模社會後，先是曆法、接著時鐘的發明似乎改變人類對於時間的概念，大家開始擔心時間的流逝，並且開始「預約未來」（排行事曆、約會時間等）。Pirahã 人生活在沒有現代時間概念的社會中，且其生活方式也無須擔心是否有事情未完成，因此其「活在當下」顯得相當合理。然我認為難以使用「他們的語言沒有時態」作為理由。從 Pirahã 人的文化可以很明顯地發現其許多部份皆支持著 Pirahã 人「活在當下」，例如簡單的物質技術（所以不須從事大規模的生產）、從事漁獵採集（所以比起農耕更加不勞力密集）、沒有強烈的物質需求（只向 Everett 要求一些簡單的物資）等。文化本身即是強而有力的解釋，能夠說明 Pirahã 人「活在當下」。忽略這些文化因素而單以語言的結構作為解釋顯得相當不合理，而這也正是為何沃爾夫被認為是錯誤的原因：「他太過強調語言對思維的影響，認為語言的影響甚至強過外在環境的影響—外在環境無法決定能否分辨顏色，但語言中的顏色字卻可以」。
 
@@
 ## 參考資料{#reference}
+
+---
+nocite: |
+  @*
+...

### 2018-05-29 1062_class/eco_model/HW/C10/rk4.c

@@ -1,0 +1,143 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+double floor(double x);
+
+//Fc declaration
+
+	//Memory allocation
+void message_error(char error_text[]);
+double *d_vector(long size); //for generating double vector[1]...vector[size]
+void free_d_vector(double *x);
+
+	//Solving ODE
+void differential (double time, double in[], double out[]);
+double dx_dt(double time, double vr[]);
+double dy_dt(double time, double vr[]);
+void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) );
+
+
+// Global variables
+int j_x = 1, j_y = 2, j_p = 3; //index for x, y, p
+double a1=0.5, a2=0.3, b1=0.7, b2=1.1; 		  // model parameter
+double r1=0.7, r2=0.7, K1=1.2, K2=1.2, m=0.5; // model parameter
+double t=0.0; //time
+double deltat=0.01; //time step for rk4
+double *N; // initialize array for population size
+double *dfdt;
+
+
+// Main function
+int main(void){
+	
+	dfdt = d_vector(3); //set vector for 'differential' output
+	N = d_vector(3);
+	N[j_x] = 1.0; //set initial population size
+	N[j_y] = 1.0; //set initial population size
+	N[j_p] = 1.0; //set initial population size
+
+	int i; //for loop index
+	double T=300.2; // T: time of simulation
+
+	for (i=0; i < T/deltat; i++){
+		
+		if (i % (int)floor(0.1/deltat) == 0 || i == 0){
+			printf("%lf\t%lf\t%lf\t%lf\n", t, N[j_x], N[j_y], N[j_p]);
+		}
+		differential(t, N, dfdt);
+		rk4(N, dfdt, 3, t, deltat, N, differential); //first N is input, second N is output
+		t += deltat;
+	}; //end for: end solving DE
+
+
+	free_d_vector(N);
+	free_d_vector(dfdt);
+	return 0;
+};
+
+
+
+/* ODE Solver Functions */
+
+double dx_dt(double time, double vr[]){
+	return (r1*(1.0 - vr[j_x]/K1) - a1*vr[j_p])*vr[j_x];
+};
+
+double dy_dt(double time, double vr[]){
+	return (r2*(1.0 - vr[j_y]/K2) - a2*vr[j_p])*vr[j_y];
+};
+
+double dp_dt(double time, double vr[]){
[…]

### 2018-05-29 1062_class/eco_model/HW/C10/rk4_fc.c

@@ -1,0 +1,34 @@
+/* 
+void (*diff)(double, double [], double []) is a function pointer.
+In order to use functions as inputs, it is included in the parameter of the function 'rk4'.
+In this case, the function 'differential' is taken as input to the function 'rk4'.
+*/
+
+void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) )
+{
+	int i;
+	double *k2, *k3, *k4, *D;
+
+	// N_in: input population size ni. For 2-dim case n1=(pop. size of x); n2=(pop. size of y)
+	// k1: parameter of rk4;  k1 = f(D,t); i.e. the output from differential is input of rk4
+	k2 = d_vector(n); // rk4 k2
+	k3 = d_vector(n); // rk4 k3
+	k4 = d_vector(n); // rk4 k4
+	D = d_vector(n); // Dummy variable for calculating coefficients of k_i in rk4 
+
+
+	for (i=1;i<=n;i++) D[i] = N_in[i] + (h/2.0)*k1[i];
+	(*diff)(t+h/2.0, D, k2);
+	for (i=1;i<=n;i++) D[i] = N_in[i] + (h/2.0)*k2[i];
+	(*diff)(t+h/2.0, D, k3);
+	for (i=1;i<=n;i++) D[i] = N_in[i] + h*k3[i];
+	(*diff)(t+h, D, k4);
+
+	for (i=1;i<=n;i++) N_out[i] = N_in[i] + (h/6.0)*(k1[i] + 2.0*k2[i] + 2.0*k3[i] + k4[i]);
+
+	free_d_vector(D);
+	free_d_vector(k2);
+	free_d_vector(k3);
+	free_d_vector(k4);
+
+}

### 2018-06-03 1062_class/eco_model/HW/monte-carlo/monte-carlo.Rmd
up

---
title: "Monte Carlo simulation"
author: "Yongfu Liao"
date: "`r Sys.Date()`"
css: /home/liao/local_depend/style_sheets/style.css
output:
  bookdown::html_document2:
    includes:
      before_body: /home/liao/local_depend/style_sheets/mathjax_bm.tex
    number_sections: no
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.dim = c(7, 4),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = "png", dpi = 600,
	out.width = "100%"
)
library(ggplot2)
library(tidyr)
library(readr)
library(magrittr)
library(dplyr)
```

## Ranked Genes
```{r}
ranked_gene <- read_delim("ranked_gene.txt", 
    "\t", escape_double = FALSE, trim_ws = TRUE)

ggplot(ranked_gene, aes(x=rank, y=num_of_species))+
    geom_bar(stat = "identity")+
    labs(x="Ranked Gene ID",
         y="Number of Species wiht this gene")
```

## Random Community
```{r}
random_community <- read_delim("random_community.txt", 
    "\t", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE)[,-53] %>%
    set_names(1:52)

df <- gather(random_community, key="Number of Species", value = "Number of genes",
            paste(1:52)) %>%
    mutate(`Number of Species` = `Number of Species` %>% as.numeric()) %>%
    filter(`Number of genes` != 0)

ggplot(df)+
    geom_point(aes(x=`Number of Species`,
                   y=`Number of genes`),
               size=0.5)+
    labs(y="Number of Genes")

```

## C code
Download **[main.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/monte-carlo/main.c){target="_blank"}**, [vector_matrix.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/monte-carlo/vector_matrix.c){target="_blank"}

```c
#include <stdio.h>
#include <stdlib.h>
#include "./dSFMT-src-2.1/dSFMT.c"
#include "./vector_matrix.c"
#define NUM_R 10000
#define NUM_C 52
#define replicate 100

void shuffle(int *array, int n);
int random_k_species(int k, double **mat);

dsfmt_t dsfmt; //variable for random number generator. Defined as global variable to be used in 'shuffle'.

int main(int argc, char *argv[])
{
	FILE *fp_mat, *fp_sort, *fp_commu;
	double **mat;
	int i, j ,k, h;
	int s, t, tmp; //for loops in bubble sorting
	double n_species, *n_Sp_gene;
	double **rand_commu;
	int num_gene2=0;
	double num_sp = 0.0;
	int col; // index for selecting speicies in community
	int	index[NUM_C+1] = {0};

	// Initialize random number generator
	int seed;
	seed= 2018;//time(NULL);
	//if(seed==0)seed= 1;
	dsfmt_init_gen_rand(&dsfmt,seed);

	mat = d_matrix(NUM_R, NUM_C);
	n_Sp_gene = d_vector(NUM_R); //number of species with a particular gene
	rand_commu = d_matrix(replicate, NUM_C); //value = # of genes, col= # of species in the community

// Read File
	if(argc != 2) message_error("Number of parameter is incompatible.");
	fp_mat = fopen(argv[1], "r"); //open file
	if (fp_mat == NULL) message_error("File cannot be opened.");

	for(i = 1; i <= NUM_R; i++)
	{
		for(j = 1; j <= NUM_C; j++) fscanf(fp_mat, "%lf,", &mat[i][j]);
	}
	fclose(fp_mat);  //close file

// count number of species possessing a gene
	for (i = 1; i <= NUM_R; i++){
		n_species = 0;
		for (j = 1; j <= NUM_C; j++) n_species += mat[i][j];
		n_Sp_gene[i] = n_species;
	}

	// bubble sort to rank "n_Sp_gene"
	for(s = 1; s <= NUM_R; s++) {
		for(t = s + 1; t <= NUM_R; t++) {
			if(n_Sp_gene[t] > n_Sp_gene[s]) {
				tmp = n_Sp_gene[t];
				n_Sp_gene[t] = n_Sp_gene[s];
				n_Sp_gene[s] = tmp;
				}//end if
		}//end for t
	}//end for s

	// write file
	fp_sort = fopen("ranked_gene.txt", "w");
	if(fp_sort == NULL) message_error("File cannot be opened\n");
	fprintf(fp_sort, "rank\tnum_of_species\n");
	for(i = 1; i <= NUM_R; i++) {
		fprintf(fp_sort, "%d\t%f\n", i, n_Sp_gene[i]);
	}
	fclose(fp_sort);

	free_d_vector(n_Sp_gene);

// random community
	for (k=2; k<=50; k++){
		for (i=1; i<=replicate; i++) rand_commu[i][k] = random_k_species(k, mat);
	}

	// community with 1 species
	for (j=1; j<=NUM_C; j++){
		for (i=1; i<=NUM_R; i++) if (mat[i][j] > 0.01) num_gene2 += 1;
		rand_commu[j][1] = num_gene2;
		num_gene2 = 0;
	}

	// community with 51 species
	for (k=1; k<=NUM_C; k++)
	{
		//prepare an array of index for 51 species by removing the kth species
		for (j=1; j<k; j++) index[j] = j; 
		for (h=k; h<=NUM_C-1; h++) index[h] = h+1;

		// count the number of genes in the community of the 51 species
		for (i=1; i<=NUM_R; i++) //loop over every row(gene) of 'mat'
		{ 
			num_sp = 0.0;
			for (j=1; j<=NUM_C-1; j++) // loop over 51 columns(species) of 'mat'
			{ 				
				col = index[j];
				num_sp = num_sp + mat[i][col]; // for every row(gene), count num of species having this gene 
			}
			if (num_sp > 0.01) num_gene2 += 1;	// add 1 if the number of species having this gene > 0.
		}
		rand_commu[k][51] = num_gene2; //num of genes in the community(without the kth species)
		num_gene2 = 0;
	}

	// community with 52 species(all)
	rand_commu[1][NUM_C] = random_k_species(NUM_C, mat);

// write file
	fp_commu = fopen("random_community.txt", "w");
	if (fp_commu == NULL) message_error("File cannot be opened\n");
	for (i = 1; i <= replicate; i++) 
	{
		for (j=1; j<=NUM_C; j++) fprintf(fp_commu, "%lf\t", rand_commu[i][j]);
		fprintf(fp_commu, "\n");
	}

	fclose(fp_commu);

	free_d_matrix(rand_commu);
	free_d_matrix(mat);
	return 0;
}

/////////// Function Definitions //////////
/* 
randomly select k species
return the number of functional genes 
in the community consist of these k species.
*/
int random_k_species(int k, double **mat)
{
	int col;
	double num_sp = 0.0;
	int num_gene = 0;
	int index[NUM_C+1] = {0};
	int i,j;

	for (i=1; i<=NUM_C; i++) 
	{	
		index[i] = i; //assign value 1-52 to array "index"
	}
	shuffle(index, NUM_C);
	for (i=1; i<=NUM_R; i++){ //loop over every row
		num_sp = 0.0;
		for (j=1; j<=k; j++){ // loop over k columns(species randomly picked)
			col = index[j];
			num_sp = num_sp + mat[i][col]; // for every row(gene), count num of species having this gene 
			//printf("%lf\t%lf\n", num_sp, mat[i][col]);
		}
		if (num_sp > 0.01) num_gene += 1;
	}
	return num_gene;
}

/*
Take an array and its (size-1)(skipping index '0') as input,
shuffle the array.
*/
void shuffle(int *array, int n)
{

    double rand; //random number from uniform [0,1)

    if (n > 1) 
    {
        int i,j,t;
        for (i = 1; i < n; i++) 
        {
            rand = dsfmt_genrand_close_open(&dsfmt);
            int j = i + (n-i+1)*rand;
            int t = array[j];
            array[j] = array[i];
            array[i] = t;
        }
    }
}
```

### 2018-06-03 1062_class/eco_model/HW/monte-carlo/main.c

@@ -1,0 +1,196 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include "./dSFMT-src-2.1/dSFMT.c"
+#include "./vector_matrix.c"
+#define NUM_R 10000
+#define NUM_C 52
+#define replicate 100
+
+void shuffle(int *array, int n);
+int random_k_species(int k, double **mat);
+
+dsfmt_t dsfmt; //variable for random number generator. Defined as global variable to be used in 'shuffle'.
+
+
+int main(int argc, char *argv[])
+{
+	FILE *fp_mat, *fp_sort, *fp_commu;
+	double **mat;
+	int i, j ,k, h;
+	int s, t, tmp; //for loops in bubble sorting
+	double n_species, *n_Sp_gene;
+	double **rand_commu;
+	int num_gene2=0;
+	double num_sp = 0.0;
+	int col; // index for selecting speicies in community
+	int	index[NUM_C+1] = {0};
+
+	// Initialize random number generator
+	int seed;
+	seed= 2018;//time(NULL);
+	//if(seed==0)seed= 1;
+	dsfmt_init_gen_rand(&dsfmt,seed);
+
+
+	mat = d_matrix(NUM_R, NUM_C);
+	n_Sp_gene = d_vector(NUM_R); //number of species with a particular gene
+	rand_commu = d_matrix(replicate, NUM_C); //value = # of genes, col= # of species in the community
+
+
+// Read File
+	if(argc != 2) message_error("Number of parameter is incompatible.");
+	fp_mat = fopen(argv[1], "r"); //open file
+	if (fp_mat == NULL) message_error("File cannot be opened.");
+
+	for(i = 1; i <= NUM_R; i++)
+	{
+		for(j = 1; j <= NUM_C; j++) fscanf(fp_mat, "%lf,", &mat[i][j]);
+	}
+	fclose(fp_mat);  //close file
+
+
+// count number of species possessing a gene
+	for (i = 1; i <= NUM_R; i++){
+		n_species = 0;
+		for (j = 1; j <= NUM_C; j++) n_species += mat[i][j];
+		n_Sp_gene[i] = n_species;
+	}
+
+	// bubble sort to rank "n_Sp_gene"
+	for(s = 1; s <= NUM_R; s++) {
+		for(t = s + 1; t <= NUM_R; t++) {
+			if(n_Sp_gene[t] > n_Sp_gene[s]) {
+				tmp = n_Sp_gene[t];
+				n_Sp_gene[t] = n_Sp_gene[s];
[…]

### 2018-06-03 1062_class/eco_model/HW/monte-carlo/random.c

@@ -1,0 +1,17 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include "./dSFMT-src-2.1/dSFMT.c"
+
+int main (void) {
+
+	int i, seed;
+	double x1, x2;
+	dsfmt_t dsfmt;
+	seed = 1;
+	
+	dsfmt_init_gen_rand(&dsfmt, seed);
+	x1 = dsfmt_genrand_close_open(&dsfmt);
+	x2 = dsfmt_genrand_open_open(&dsfmt);
+
+	printf("%lf\t%lf\n",x1, x2);
+}

### 2018-06-03 1062_class/eco_model/HW/monte-carlo/read_array_matrix.c

@@ -1,0 +1,55 @@
+#include <stdio.h>
+#include <stdlib.h>
+#define NUM_R 5
+#define NUM_C 3
+
+int main(int argc, char *argv[])
+{
+	FILE *fp1, *fp2;
+	double *vector_test;
+	double **matrix_test;
+	int i, j, k;
+	vector_test = d_vector(SIZE_V); //allocation of memory
+	matrix_test = d_matrix(NUM_R, NUM_C); //allocation of memory
+	
+	if(argc != 3) message_error("Number of parameter is incompatible.");
+	fp1 = fopen(argv[1], "r");
+	fp2 = fopen(argv[2], "r");
+
+	if (fp1 == NULL) message_error("File cannot be opened.");
+	if (fp2 == NULL) message_error("File cannot be opened.");
+	
+	#ifdef VECTOR
+	for(i = 1; i <= SIZE_V; i++) 
+	{
+		fscanf(fp1, "%lf,", &vector_test[i]); //for file with comma separation
+	}
+	for(i = 1; i <= SIZE_V; i++) 
+	{
+		printf("%lf\n", vector_test[i]);
+	}
+	#endif
+//end if of VECTOR
+
+	#ifdef MATRIX
+	for(i = 1; i <= NUM_R; i++) {
+		for(j = 1; j <= NUM_C; j++) {
+			fscanf(fp2, "%lf;", &matrix_test[i][j]);
+		}
+	}
+	for(i = 1; i <= NUM_R; i++) {
+		for(j = 1; j <= NUM_C; j++) {
+			printf("%lf\t", matrix_test[i][j]);
+		}
+		printf("\n");
+	}
+	#endif
+	//end if of MATRIX
+
+	close(fp1);
+	close(fp2);
+	return 0;
+}
+
+
+

### 2018-06-03 1062_class/eco_model/HW/monte-carlo/vector_matrix.c

@@ -1,0 +1,55 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+/* Function Definition */
+
+void message_error(char error_text[])
+/*Standard error handler*/
+{
+    printf("There are some errors...\n");
+    printf("%s\n", error_text);
+    printf("...now existing to system...\n");
+    exit(1);
+}
+
+double *d_vector(long size){ //for generating double vector[1]...vector[size]
+    double *x; //pointer
+    
+    x = malloc((size + 1)*sizeof(double));
+    //allocation of memory space to stock (size + 1) double variables & malloc returns the address of the top of the allocated memory space to x
+    //the reason to prepare (size + 1) is just to use from x[1] to x[size]
+    
+    if(x == NULL) message_error("allocation failure in d_vector()"); //if memory allocation was failed, malloc returns NULL and x becomes NULL
+    return x; //return the address of the top of the allocated memory space to x
+}
+
+void free_d_vector(double *x)
+{
+    free(x);
+}
+
+
+void free_d_matrix(double **x){
+    free(x[0]);
+    free(x);
+}
+
+
+double **d_matrix(long size_row, long size_column){
+    double **x;
+    long i;
+    long size_row_P = size_row + 1; 
+    long size_column_P = size_column + 1; 
+    
+    x = (double **) malloc((size_t) (size_row_P*sizeof(double *)));
+    
+    if(x == NULL) message_error("allocation failure in d_vector()");
+    
+    x[0] = (double *) malloc((size_t) (size_row_P*size_column_P*sizeof(double)));
+    
+    if(x[0] == NULL) message_error("allocation failure in d_vector()");
+    
+    for(i = 1; i < size_row_P; i++) x[i] = x[0] + i*size_column_P;
+    
+    return x;
+}

### 2018-06-03 GitHubPage/lang_social_survey/ggplot_age_pyramid.R

@@ -1,47 +1,0 @@
-library(dplyr)
-library(tidyr)
-library(magrittr)
-library(ggplot2)
-library(gganimate)
-theme_set(theme_bw())
-
-
-df <- data.frame(
-    gender = sample(c("男","女"), 100, replace = T),
-    age = sample(10:90, 100, replace = T),
-    mand = sample(0:5, 100, replace = T),
-    tw = sample(0:5, 100, replace = T),
-    hk = sample(0:5, 100, replace = T),
-    abori = sample(0:5, 100, replace = T),
-    sa = sample(0:5, 100, replace = T),
-    eng = sample(0:5, 100, replace = T)
-)
-df$group <- cut(df$age, breaks = seq(0,90,by=10), right = TRUE)
-
-pl <- df %>% group_by(gender, group) %>%
-    summarise(mean(mand), mean(tw), 
-              mean(hk), mean(abori), 
-              mean(sa), mean(eng)) %>%
-    set_names(c("gender", "age_group",
-                "Mandarin", "Taiwanese",
-                "Hakka", "Aborigine", 
-                "South_east", "English")) %>%
-    gather("Mandarin", "Taiwanese","Hakka",
-           "Aborigine","South_east", "English", 
-           key = "lang", 
-           value = "avg_fluency") %>%
-ggplot(aes(x = age_group, fill = gender,
-           y = ifelse(gender=="男",
-                      avg_fluency, -avg_fluency),
-           frame = lang)
-       ) + 
-    geom_bar(stat = "identity", position = "identity")+
-    scale_y_continuous(limits = c(-5,5),
-                       breaks = seq(-5,5,1), 
-                       labels=abs(seq(-5,5,1))
-                     ) + 
-  coord_flip() + 
-  scale_fill_brewer(palette = "Set1") + 
-  theme_minimal()
-
-gganimate(pl,ani.width=800, ani.height=400, "~/local_depend/GitHubPage/lang_social_survey/age_pyramid.gif")

### 2018-06-03 GitHubPage/lang_social_survey/shape.R

@@ -1,16 +1,0 @@
-library(sf)
-library(dplyr)
-library(readr)
-
-##### Extract zipcode from TOWN_zip.kml in order to combine to shp ####
-# the extracted df is saved to ./spatial_data/zipcode_towncode.csv #
-
-# zip <- st_read("./shape/TOWN_zip.kml")[,c("TOWNCODE","ZIPCODE", "COUNTYNAME","TOWNNAME")] %>% st_set_geometry(NULL) %>% arrange(ZIPCODE)
-# write_csv(zip, "./spatial_data/zipcode_towncode.csv")
-zip <- read_csv("spatial_data/zipcode_towncode.csv", 
-    col_types = cols(ZIPCODE = col_character()))[,2:4]
-sp <- st_read("./shape/TOWN_MOI_1070330.shp")
-
-sp <- sp %>% 
-    left_join(zip, by = c("COUNTYNAME","TOWNNAME")) %>%
-    select(COUNTYNAME, TOWNNAME, ZIPCODE)

### 2018-06-03 GitHubPage/lang_social_survey/techniques.R

@@ -1,34 +1,0 @@
-library(dplyr)
-
-############ How to find out languages more fluent than chinese ############
-df <- data_frame(
-    x1 = sample(0:5, 10, replace = T), #lang1 ch
-    x2 = sample(0:5, 10, replace = T), #lang2 tw
-    x3 = sample(0:5, 10, replace = T)  #lang3 hk
-    )
-
-df <- df %>%
-    mutate(x2_domin = if_else(x2 >= x1, T, F),
-           x3_domin = if_else(x3 >= x1, T, F))
-
-##################################################################
-library(dplyr)
-
-############ How to find out the most fluent language ############
-df <- data_frame(
-    x1 = rnorm(10), #lang1
-    x2 = rnorm(10), #lang2
-    x3 = rnorm(10)  #lang3
-    )
-
-df <- df %>%
-    rowwise() %>%
-    mutate(best_val = max(x1, x2, x3)) %>%
-    ungroup() %>%
-    mutate(best = if_else(x1 == best_val, "x1",
-                          if_else(x2 == best_val, "x2",
-                                  "x3")
-                          )
-           ) %>%
-    select(-best_val)
-##################################################################

### 2018-06-03 1062_class/eco_model/HW/monte-carlo/monte-carlo.Rmd
up

@@
 	comment = "",
-	dev = "png", dpi = 600,
-	out.width = "100%"
+	dev = "png", dpi = 300,
+	out.width = "90%"
 )
@@
 	}
-
 	fclose(fp_commu);
@@
 
-/////////// Function Definitions //////////
+//////// Function Definitions ////////
 /* 
@@
 {
-
     double rand; //random number from uniform [0,1)

### 2018-06-03 1062_class/lang_social_mid/doc.Rmd
up

@@
 
-[^local]: 依臺北市的規定[@zotero-80]，小學依學生意願就閩南語、客家語、原住民族語等三種本土語言。
+[^local]: 依臺北市的規定[2013]，小學依學生意願就閩南語、客家語、原住民族語等三種本土語言。
 
@@
 
-根據內政部 1993 至 2017 的人口統計資料（人口總數、自然增加率）[@neizhengbuhuzhengsi]，並假設
+根據內政部 1993 至 2017 的人口統計資料（人口總數、自然增加率）[@neizhengbuhuzhengsi2018]，並假設
 
@@
 
-則使用 1993 年內政部統計之總人口數 20995416 為起始，並以「閩南人：73.3%；外省人：13%；客家人：12%；原住民： 1.7%」的比例計算出該年各族群人口做為開始。接著以內政部統計之每年自然增加率計算，可得 2017 人口比例如下表：
+則使用 1993 年內政部統計之總人口數 20995416 為起始，並以「閩南人：73.3%；外省人：13%；客家人：12%；原住民： 1.7%」的比例計算出該年各族群人口做為開始。接著以內政部統計之每年自然增加率計算，可得 2017 人口比例如下表[^code]：
+
+[^code]: 計算族群數量及比例之程式碼請見 https://github.com/liao961120/local_depend/blob/master/1062_class/lang_social_mid/doc.Rmd
+
 ```{r}

### 2018-06-06 1062_class/lang_social_mid/doc.Rmd
up

@@
 
-這些研究證據顯示語言以不同種方式影響思維的可能。然關於 Daniel Everett 對於 Pirahã 人的想法：「他們的語言沒有時態，他們真正活在當下之中」，似乎隱含更複雜的因素。首先，我同意這句話的後半段：人類在進入大規模社會後，先是曆法、接著時鐘的發明似乎改變人類對於時間的概念，大家開始擔心時間的流逝，並且開始「預約未來」（排行事曆、約會時間等）。Pirahã 人生活在沒有現代時間概念的社會中，且其生活方式也無須擔心是否有事情未完成，因此其「活在當下」顯得相當合理。然我認為難以使用「他們的語言沒有時態」作為理由。從 Pirahã 人的文化可以很明顯地發現其許多部份皆支持著 Pirahã 人「活在當下」，例如簡單的物質技術（所以不須從事大規模的生產）、從事漁獵採集（所以比起農耕更加不勞力密集）、沒有強烈的物質需求（只向 Everett 要求一些簡單的物資）等。文化本身即是強而有力的解釋，能夠說明 Pirahã 人「活在當下」。忽略這些文化因素而單以語言的結構作為解釋顯得相當不合理，而這也正是為何沃爾夫被認為是錯誤的原因：「他太過強調語言對思維的影響，認為語言的影響甚至強過外在環境的影響—外在環境無法決定能否分辨顏色，但語言中的顏色字卻可以」。
+這些研究證據顯示語言以不同種方式影響思維的可能。然關於 Daniel Everett 對於 Pirahã 人的想法：「他們的語言沒有時態，他們真正活在當下之中」，似乎隱含更複雜的因素。首先，我同意這句話的後半段：人類在進入大規模社會後，先是曆法、接著時鐘的發明似乎改變人類對於時間的概念，大家開始擔心時間的流逝，並且開始「預約未來」（排行事曆、約會時間等）。Pirahã 人生活在沒有現代時間概念的社會中，且其生活方式也無須擔心是否有事情未完成，因此其「活在當下」顯得相當合理。然我認為難以使用「他們的語言沒有時態」作為理由。從 Pirahã 人的文化可以很明顯地發現其許多部份皆支持著 Pirahã 人「活在當下」，例如簡單的物質技術（所以不須從事大規模的生產）、從事漁獵採集（所以比起農耕更加不勞力密集）、沒有強烈的物質需求（只向 Everett 要求一些簡單的物資）等。文化本身即是強而有力的解釋，能夠說明 Pirahã 人「活在當下」。忽略這些文化因素而單以語言的結構作為解釋顯得相當不合理，而這也正是為何沃爾夫被認為是錯誤的原因：「他太過強調語言對思維的影響，認為語言的影響甚至強過外在環境的影響—外在環境無法決定能否分辨顏色，但語言中的顏色字卻可以」。整體而言，我認為 Pirahã 人沒有「精確」的時間概念[^time]，原因為 (1) Pirahã 本身的文化特質造成其不需要「精確的時間概念」; (2) 其語言中沒有數字系統。然對於 Pirahã 完全不具備時間的概念（如約略的「過去」、「現在」、「未來」）且原因是語言中缺乏時態的想法，我認為此主張太過大膽，需要更多嚴謹的證據加以檢視。
+
+[^time]: 這與其語言中沒有數字系統也有相當大的關聯。上文提及語言與數字概念之間的關聯，而沒有數字的概念可合理推測其不可能有「精確的時間概念」。
 

### 2018-06-14 1062_class/Multivariate_Analysis/HW5_Clustering/multivarite_hw4.Rmd
up

--- 2018-05-28 1062_class/Multivariate_Analysis/HW4_classification/multivarite_hw4.Rmd
@@
 title: "多變量分析 HW4"
-author: "劉昱維, 吳冠瑋, 廖永賦, 謝靖惟, 黃奎鈞"
+author: "劉昱維, 吳冠瑋, 廖永賦, 謝靖惟"
 css: /home/liao/local_depend/style_sheets/style.css
@@
 ```
-
-## 11.1
-+ a) $~~~~\hat{y} = (\bar{x_1} - \bar{x_2})^{\prime}S^{-1}_{pooled}x = \hat{a}^{\prime}x$<br>
-     $~~~~~~~S^{-1}_{pooled} = \begin{bmatrix} 2 & -1 \\ -1 & 1 \end{bmatrix}$<br>
-     $~~~~~~~\begin{bmatrix} -2 & -2 \end{bmatrix}\begin{bmatrix} 2 & -1 \\ -1 & 1 \end{bmatrix}x = -2x_1$
-+ b) $~~~~\hat{m} = \frac{1}{2}(\hat{y_1}+\hat{y_2}) = -8$<br>
-     $~~~~~~-2(2) = -4 > -8 \Rightarrow assign~to~\pi_1$
-
-## 11.4
-+ a) $~~~~(\frac{c(1\mid 2)}{c(2\mid 1)})(\frac{p_2}{p_1}) = 0.5$<br>
-     $~~~~~~~\Rightarrow assign~to~\pi_1~if~\frac{f_1(x)}{f_2(x)}\geq0.5,~otherwise~assign~to~\pi_2$
-+ b) $~~~~\frac{f_1(x)}{f_2(x)} = \frac{0.3}{0.5} = 0.6 > 0.5\Rightarrow assign~to~\pi_1$
-
-## 11.19
-+ b) $~~~~\hat{y_0} = \hat{a}^{\prime}x_0 = -0.33x_1+0.67x_2$<br>
-     $~~~~~~~where~\hat{m} = 4.5$<br>
-     $~~~~~~~assign~to~\pi_1~if~-0.33x_1+0.67x_2-4.5\geq 0,~otherwise~assign~to~\pi_2$
-
-| | $\pi_1$ | | | $\pi_2$ | |
-|---|---|---|---|---|---|
-|obs.| $−0.33x_1+0.67x_2−4.5$ | class. | obs. | $−0.33x_1+0.67x_2−4.5$ | class.|
-| 1 | 2.83 | $\pi_1$ | 1 | -1.5 | $\pi_2$ |
-| 2 | 0.83 | $\pi_1$ | 2 | 0.5 | $\pi_1$ |
-| 3 | -0.17 | $\pi_2$ | 3 | -2.5 | $\pi_2$ |
-
-+ c) $~~~~D^2_i(x) = (x - \bar{x_i})^{\prime}S^{-1}_{pooled}(x - \bar{x_i})$
-
-|  | | $\pi_1$ | | | $\pi_2$ | | |
-|---|---|---|---|---|---|
-|obs.| $D^2_1$ | $D^2_2$ | class. | obs. | $D^2_1$ | $D^2_2$ | class.|
-| 1 | 1.33 | 7 | $\pi_1$ | 1 | 4.33 | 1.33 | $\pi_2$ |
-| 2 | 1.33 | 3 | $\pi_1$ | 2 | 0.33 | 1.33 | $\pi_1$ |
-| 3 | 1.33 | 1 | $\pi_2$ | 3 | 6.33 | 1.33 | $\pi_2$ |
-
-## 11.32
-```{r}
-hemo <- readr::read_table2("T11-8.DAT", col_names = FALSE,
-                           col_types = cols(X1 = col_character())
-                           ) %>%
-    set_names(c("group", "activity", "antigen"))
-```
-
-### (a) Bivariate plot
-```{r}
-pl <- ggplot(hemo) +
-    geom_point(aes(x=activity, y=antigen, shape=group, color=group))+
-    labs(color="Group",shape="Group",
-         x = expression('log'[10]*'(AHF activity)'),
-         y = expression('log'[10]*'(AHF antigen)')
-         )
-pl + theme_light()
-```
-
-The bivariate plot doesn't seem to fit well into a bivariate normal distribution.
-
-#### SAS `pool=test`
-
-```{r out.width=c("40%","70%"), fig.show='hold'}
-include_graphics("p2.png")
-include_graphics("p1.png")
-```
-
-Test not significant. The covariance of the two groups are assumed to be equal.
-
-#### SAS `manova`
-
-```{r out.width="50%"}
-include_graphics("p3.png")
-```
-
-Means of two groups are not equal.
-
-### (b) linear disciminant function
-```{r}
-x1_bar <- hemo[hemo$group == "1",2:3] %>% colMeans()
-x2_bar <- hemo[hemo$group == "2",2:3] %>% colMeans()
-sum <- x1_bar + x2_bar
-
-S1 <- hemo[hemo$group == "1", 2:3] %>% cov()
-S2 <- hemo[hemo$group == "2", 2:3] %>% cov()
-
-n1 <- hemo[hemo$group == "1",] %>% nrow
-n2 <- hemo[hemo$group == "2",] %>% nrow
-
-S_pool <- ((n1 - 1)*S1 + (n2 - 1)*S2)/(n1 + n2 - 2)
-
-a <- solve(S_pool) %*% (x1_bar - x2_bar)
-cutoff <- .5 * (x1_bar - x2_bar) %*% solve(S_pool) %*% (x1_bar + x2_bar)
-```
-
-\begin{equation}
-\begin{split}
-\hat{y} &= (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ \bm{x}_0 \\
-&= \bm{a}^T \bm{x}_0 \\
-&= \begin{pmatrix}
-`r a[1] %>% round(3)` & `r a[2] %>% round(3)`
-\end{pmatrix}
-\bm{x}_0
-\end{split}
-(\#eq:ref-1)
-\end{equation}
-
-Then allocate $\bm{x}_0$ to $\pi_1$ if:
-
-\begin{equation}
-\begin{split}
-\hat{y} &\geq \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) \\
-&= \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2)
-= `r cutoff %>% round(3)`
-\end{split}
-(\#eq:ref-2)
-\end{equation}
-
-where, $\bar{\bm{x}}_1 =\begin{pmatrix}
-`r x1_bar[1] %>% round(3)`  \\
-`r x1_bar[2] %>% round(3)` 
-\end{pmatrix}, 
-\bar{\bm{x}}_2 = \begin{pmatrix}
-`r x2_bar[1] %>% round(3)`  \\
-`r x2_bar[2] %>% round(3)` 
-\end{pmatrix}$
-
-The linear discriminant function is:
-
-\begin{equation}
-`r round(a[1],3)` x_{0,1} `r round(a[2],3)` x_{0,1} + `r -round(cutoff,3)`
-(\#eq:discri-1)
-\end{equation}
-
-```{r}
-library(MASS)
-lda_hold <- lda(formula = group ~ activity + antigen, 
-                CV=TRUE, prior=c(1,1)/2, data = hemo)
-
-confus_mt_hold <- table(hemo$group, lda_hold$class, 
-      dnn = c('Actual Group','Predicted Group'))
-```
-
-The confusion matrix constructed with the holdout procedure is
-```{r}
-confus_mt_hold %>% 
-    knitr::kable(row.names = T, 
-                 format = "markdown", align = "c",
-                 col.names = c("Group 1", "Group 2"))
-```
-
-, and the estimated error rate is **`r (confus_mt_hold[1,2] + confus_mt_hold[2,1]) / sum(confus_mt_hold)`**.
-
-The misclassified observations are **No. `r which(hemo$group != lda_hold$class %>% paste(sep=", "))`**, labeled "M" in the plot below.
-```{r misclassified}
-index <- which(hemo$group != lda_hold$class)
-pl +
-    geom_text(aes(x=activity, y=antigen, label = "M"),
-              data = hemo[index,],
-              size = 2, nudge_x = 0.01) + theme_light()
-```
-
-### (c)
-
-```{r}
-x0 <- c(-0.112 , -0.279)
-y0 <- (t(a) %*% x0)[1,1]
-```
-
-By eq. \@ref(eq:ref-1) and eq. \@ref(eq:ref-2), $\hat{y}_0 = `r y0 %>% round(3)` \geq `r cutoff %>% round(3)`$. Hence, it is allocated to **Group 1**.
-
-### (d)
-```{r}
-library(mvtnorm)
-f1_x0 <- dmvnorm(x = x0, mean = x1_bar, sigma = S1)
-f2_x0 <- dmvnorm(x = x0, mean = x2_bar, sigma = S2)
-```
-
-Classification rule based on posterior probabilities is equivalent to classification rule based on minimizing TPM.
-
-Since the prior probabilities are assumed to be equal, the posterior probabilities are calculated as:
-
-\begin{equation}
-\begin{split}
-p(\pi_1|\bm{x}_0) &= \frac{ f_1(\bm{x}_0)}{f_1(\bm{x}_0) + f_2(\bm{x}_0)} = `r f1_x0/(f1_x0 +f2_x0) %>% round(3)` \\
-p(\pi_2|\bm{x}_0) &= 1 - p(\pi_1|\bm{x}_0)
-= `r f2_x0/(f1_x0 +f2_x0) %>% round(3)`
-\end{split}
-(\#eq:posterior)
-\end{equation}
-
-, where the densities $f_1(\bm{x}_0)$ and $f_2(\bm{x}_0)$ are assumed to be normal and are estimated using $\bar{\bm{x}}_1, \bar{\bm{x}}_2, \bm{S}_1, \bm{S}_2$.
-
-By $p(\pi_1|\bm{x}_0) > p(\pi_2|\bm{x}_0)$, $\bm{x}_0$ is classified as **Group 1**.
-
-### (e)
-
-By eq.
-\@ref(eq:ref-1), eq.
-\@ref(eq:ref-2), and [c](#c), the linear discriminant score is calculated as $\hat{y}_0 - \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) = `r (y0 - cutoff) %>% round(3)`$.
-
-### (f)
-Assume $p_1 = 0.75$ and $p_2 = 0.25$, then allocate $\bm{x}_0$ to $\pi_1$ if:
-
-\begin{equation}
-\begin{split}
-\hat{y} &\geq \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T S_{pool}^{-1} ~ (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + 
-ln (\frac{c(1|2) p_2}{c(2|1) p_1}) \\
-&= \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + ln (\frac{0.25}{0.75})
-= `r (cutoff + log(0.25/0.75)) %>% round(3)`
-\end{split}
-(\#eq:uneq-prior)
-\end{equation}
-
-where, $\bar{\bm{x}}_1 =\begin{pmatrix}
-`r x1_bar[1] %>% round(3)`  \\
-`r x1_bar[2] %>% round(3)` 
-\end{pmatrix}, 
-\bar{\bm{x}}_2 = \begin{pmatrix}
-`r x2_bar[1] %>% round(3)`  \\
-`r x2_bar[2] %>% round(3)` 
-\end{pmatrix}$
-
-The linear discriminant function is:
-
-\begin{equation}
-`r round(a[1],3)` x_{0,1} `r round(a[2],3)` x_{0,1} + `r -round(cutoff + log(0.25/0.75), 3)`
-(\#eq:discri-2)
-\end{equation}
-
-```{r}
-lda_hold <- lda(formula = group ~ activity + antigen, 
-                CV=TRUE, prior=c(0.75,0.25), data = hemo)
-
-confus_mt_hold <- table(hemo$group, lda_hold$class, 
-      dnn = c('Actual Group','Predicted Group'))
-```
-
-The confusion matrix constructed with the holdout procedure is
-```{r}
-confus_mt_hold %>% 
-    knitr::kable(row.names = T, 
-                 format = "markdown", align = "c",
-                 col.names = c("Group 1", "Group 2"))
-```
-
-, and the estimated error rate is **`r (confus_mt_hold[1,2] + confus_mt_hold[2,1]) / sum(confus_mt_hold)`**.
-
-The misclassified observations are **No. `r which(hemo$group != lda_hold$class %>% paste(sep=", "))`**, labeled "M" in the plot below.
-```{r misclassified2}
-index <- which(hemo$group != lda_hold$class)
-pl +
-    geom_text(aes(x=activity, y=antigen, label = "M"),
-              data = hemo[index,],
-              size = 2, nudge_x = 0.01) + theme_light()
-```
-
-### (g)
-
-```{r}
-x0 <- c(-0.112 , -0.279)
-y0 <- (t(a) %*% x0)[1,1]
-dis_score <- y0 - (cutoff + log(0.25/0.75))
-```
-
-By eq.
-\@ref(eq:ref-1) and eq.
-\@ref(eq:uneq-prior), $\hat{y}_0 - [ \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + ln (\frac{0.25}{0.75}) ] = `r dis_score %>% round(3)` > 0$.
-Hence, it is allocated to **Group 1**.
-
-### (h)
-```{r}
-library(mvtnorm)
-f1_x0 <- dmvnorm(x = x0, mean = x1_bar, sigma = S1)
-f2_x0 <- dmvnorm(x = x0, mean = x2_bar, sigma = S2)
-p1 <- 0.75
-p2 <- 0.25
-```
-
-Classification rule based on posterior probabilities is equivalent to classification rule based on minimizing TPM.
-
-The posterior probabilities are calculated as:
-
-\begin{equation}
-\begin{split}
-p(\pi_1|\bm{x}_0) &= \frac{ p_1 f_1(\bm{x}_0)}{p_1 f_1(\bm{x}_0) + p_2 f_2(\bm{x}_0)} = `r p1*f1_x0/(p1*f1_x0 + p2*f2_x0) %>% round(3)` \\
-p(\pi_2|\bm{x}_0) &= 1 - p(\pi_1|\bm{x}_0)
-= `r p2*f2_x0/(p1*f1_x0 + p2*f2_x0) %>% round(3)`
-\end{split}
-(\#eq:posterior2)
-\end{equation}
-
-, where the densities $f_1(\bm{x}_0)$ and $f_2(\bm{x}_0)$ are assumed to be normal and are estimated using $\bar{\bm{x}}_1, \bar{\bm{x}}_2, \bm{S}_1, \bm{S}_2$.
-
-By $p(\pi_1|\bm{x}_0) > p(\pi_2|\bm{x}_0)$, $\bm{x}_0$ is classified as **Group 1**.
-
-### (i)
-
-By eq.
-\@ref(eq:ref-1), eq.
-\@ref(eq:uneq-prior), and [g](#g), the linear discriminant score is calculated as $\hat{y}_0 - [ \frac{1}{2} \bm{a}^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) + ln (\frac{0.25}{0.75}) ] = `r y0 - (cutoff + log(0.25/0.75)) %>% round(3)`$.
-
-### (j)
-```{r out.width="50%", fig.show='hold'}
-fc_eq <- function(x) -a[1]*x/a[2] + cutoff[1,1]/a[2] 
-fc_uneq <- function(x) -a[1]*x/a[2] + (cutoff[1,1] + log(0.25/0.75))/a[2]
-
-pl+stat_function(fun = fc_eq) +
-    geom_point(aes(x=-0.112 , y=-0.279))+
-    geom_text(aes(x=-0.112 , y=-0.279, 
-                  label="(-0.112 , -0.279)"),
-              nudge_x=0.09, size=3) +
-    labs(title="Equal Prior Probabilities")+
-    xlim(c(-0.75,0.25))+
-    ylim(c(-0.50, 0.5))+ theme_light()
-
-pl+stat_function(fun = fc_uneq)+
-    geom_point(aes(x=-0.112 , y=-0.279))+
-    geom_text(aes(x=-0.112 , y=-0.279, 
-                  label="(-0.112 , -0.279)"),
-              nudge_x=0.09, size=3) +
-    labs(title="P1 = 0.75, P2 = 0.25")+
-    xlim(c(-0.75,0.25))+
-    ylim(c(-0.50, 0.5))+ theme_light()
-```
-
-When the prior probability $p_1$ changes from 0.5 to 0.75, the discriminant function shifts parallelly to the upper-left direction.

### 2018-06-14 1062_class/Multivariate_Analysis/HW5_Clustering/clustering.R

@@ -1,0 +1,15 @@
+library(clValid)
+
+PC_scores <- readr::read_csv("PC_scores.csv")
+
+clusters_sing <- hclust(dist(PC_scores[, -1]), method = "single")
+clusters_comp <- hclust(dist(PC_scores[, -1]), method = "complete")
+clusters_avg <- hclust(dist(PC_scores[, -1]), method = "average")
+clusters_ward <- hclust(dist(PC_scores[, -1]), method = "ward.D2")
+
+
+methods <- c("ward", "single", "complete", "average")
+intern <- clValid(scale(PC_scores[,-1]), nClust = 1:10, 
+              clMethods = "hierarchical", 
+              validation = "internal",
+              method = "ward")

### 2018-06-14 1062_class/eco_model/ppt/class11_c/complex_test0.c

@@ -1,0 +1,21 @@
+#include <stdio.h>
+#include <math.h>
+#include <stdlib.h>
+#include <time.h>
+#include <complex.h>
+#define PAI_A 3.14159265358979 
+int main(void){
+	
+	double complex x, y, z;
+	
+	x = 3.0 + I*4.0;
+	
+	y = I*PAI_A;
+	z = cexp(y);
+	
+	printf("real=%lf\timg=%lf\tabsolute value = %lf\n", creal(x), cimag(x), cabs(x));
+
+	printf("real=%lf\timg=%lf\n", creal(z), cimag(z));
+	
+	return 0;	
+}

### 2018-06-14 1062_class/eco_model/ppt/class11_c/logistic_error.c

@@ -1,0 +1,28 @@
+//this is a function for checking numerical error for logistic map
+#include <stdio.h>
+#include <math.h>
+#include <stdlib.h>
+#include "/Users/miki/Dropbox/new_util/nrutil_new.h"
+#include "/Users/miki/Dropbox/new_util/nrutil_new.c"
+
+
+int main(void){
+	
+	int j = 0;
+	float x = 0.1;
+	double y = 0.1;
+	double lammda = 3.8;
+	
+	printf("%d\t%.15lf\t%.15lf\t%.15lf\n", j , x, y, fabs(x-y));
+	for(j = 1; j <= 100; j++) {
+		x = lammda*x*(1.0 - x);
+		y = lammda*y*(1.0 - y);
+	
+		printf("%d\t%.15lf\t%.15lf\t%.15lf\n", j , x, y, fabs(x-y));
+	}
+	
+	return 0.0;
+	
+	
+}
+

### 2018-06-14 1062_class/eco_model/ppt/class11_c/solver_test0.c

@@ -1,0 +1,89 @@
+//this is a function for cubic equation
+#include <stdio.h>
+#include <math.h>
+#include <stdlib.h>
+#include <time.h>
+#include <complex.h>
+//#include "/Users/miki/Dropbox/new_util/nrutil_new.h"
+//#include "/Users/miki/Dropbox/new_util/nrutil_new.c"
+
+#define EPS 1.0e-15	//constant for minimum value
+void quadratic_solver(double a2, double a1, double a0, double complex root[]);
+void quadratic_bad_solver(double a2, double a1, double a0, double complex root[]);
+
+int main(void){
+	
+	double complex root_test[2];
+	double complex root_test2[2];
+	double aa2, aa1, aa0;
+	int j;
+			
+	
+	//solution should be 1, 5;	
+	aa2 = 1.0;
+	aa1 = - (1.0 + 5.0);
+	aa0 = 5.0;
+
+	//solution should be 1, 1.001;	
+	aa2 = 1.0;
+	aa1 = - (1.0 + 1.001);
+	aa0 = 1.001;
+	
+	//for complex solution
+	/*aa2 = 1.0;
+	aa1 = 1.0;
+	aa0 = 1.0;*/
+		
+
+	
+	//for showing the loss of sigfinicant digits
+	aa2 = 1.0;
+	aa1 = -(1.2345678912345e-10 + 1.0e+6);
+	aa0 = 1.2345678912345e-4;
+	
+	quadratic_solver(aa2, aa1, aa0, root_test);
+	quadratic_bad_solver(aa2, aa1, aa0, root_test2);
+
+	for(j = 0; j < 2; j++) printf("root[%d] = %.25e\t + i x %.25e\n", j, creal(root_test[j]), cimag(root_test[j]));	
+	for(j = 0; j < 2; j++) printf("root[%d] = %.25e\t + i x %.25epwd \n", j, creal(root_test2[j]), cimag(root_test2[j]));
+	//for(j = 0; j < 4; j++) printf("difference in root[%d] = %.25lf\t + i x %.25lf\n", j, creal(root_test[j] - root_test2[j]), cimag(root_test[j] - root_test2[j]));
+	
+	return 0;	
+}
+
+void quadratic_solver(double a2, double a1, double a0, double complex root[])
+{
+	double Dd;
[…]

### 2018-07-01 1062_class/Multivariate_Analysis/final_note/test_note.Rmd
up

---
documentclass: article
fontsize: 9pt
geometry: a4paper, headheight=0pt, margin=0.4in
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(knitr)
```

$N_p(\bm{\mu}, \bm{\Sigma}) = \frac{1}{(2 \pi)^{p/2} |\bm{\Sigma}|^{1/2}} 
~e^{\frac{-(\bm{X} - \bm{\mu})^T \bm{\Sigma}^{-1} (\bm{X} - \bm{\mu})} {2}}$

General Classification Rules
--------------------------------

### Expected Cost of Misclassification (ECM)

\begin{equation}
\begin{split}
ECM &= c(2|1) ~ p_1 ~ \int_{R_2} f_1(\bm{x}) d \bm{x} ~ + ~ c(1|2) ~ p_2 ~ \int_{R_1} f_2(\bm{x}) d \bm{x} \\
&= c(2|1) ~ p_1 ~ p(2|1) + c(1|2) ~ p_2 ~ p(1|2)
\end{split}
\end{equation}

#### Total Probability of Misclassifiaction (TPM)
TPM is equivalent to ECM with equal costs.

\begin{equation}
\begin{split}
TPM = p_1~p(2|1) + p_2~p(1|2)
\end{split}
\end{equation}

#### ECM Minimization Rule (general)

Classify observation $\bm{x}$ as $\pi_1$ if: 
$\frac{f_1(\bm{x})}{f_2(\bm{x})} > \frac{c(1|2)~p_2}{c(2|1)~p_1}$

#### Allocation by Posterior Probabilities

Allocate observation $\bm{x}$ to population ($\pi_1$ or $\pi_2$) with the largest $p(\pi_i|\bm{x})$

Classify observation $\bm{x}$ as $\pi_1$ if:

\begin{equation}
\begin{split}
p(\pi_1|\bm{x}) > p(\pi_2|\bm{x}), 
~~~where ~~  p(\pi_i|\bm{x}) = \frac{p_i ~ f_i(\bm{x})}{p_1 ~ f_1(\bm{x}) + p_2 ~ f_2(\bm{x})}
\end{split}
\end{equation}

is equivalent to TPM.

Classification with MV Normal Populations ($\bm{\Sigma}_1 = \bm{\Sigma}_2 = \bm{\Sigma}$. Linear)
-------------------------------------

\begin{equation}
\begin{split}
\frac{f_1(\bm{x})}{f_2(\bm{x})} = exp[(\bm{\mu}_1 - \bm{\mu}_2)^T \bm{\Sigma}^{-1} \bm{x} - \frac{1}{2} (\bm{\mu}_1 - \bm{\mu}_2)^T \bm{\Sigma}^{-1} (\bm{\mu}_1 + \bm{\mu}_2)]
\end{split}
\end{equation}

By taking natural logarithm, we get the ECM minimization rule.

Classify observation $\bm{x}$ as $\pi_1$ if:

\begin{equation}
\begin{split}
(\bm{\mu}_1 - \bm{\mu}_2)^T \bm{\Sigma}^{-1} \bm{x} - \frac{1}{2} (\bm{\mu}_1 - \bm{\mu}_2)^T \bm{\Sigma}^{-1} (\bm{\mu}_1 + \bm{\mu}_2) \geq
ln (\frac{c(1|2)~p_2}{c(2|1)~p_1})
\end{split}
(\#eq:ecm-normal)
\end{equation}

The sample version is obtained by replacing $\bm{\mu_i}$, $\bm{\Sigma}$ with $\bm{\bar{\bm{x}}_i}$, $\bm{S}_{pool} = \frac{n_1 - 1}{n_1 + n_2 - 2} \bm{S}_1 + \frac{n_2 - 1}{n_1 + n_2 - 2} \bm{S}_2$, respectively.

### Fisher's Discriminant Function

Maximize $\frac{(\bar{y}_1 - \bar{y}_2)^2}{S_y^2}$ by choosing the linear combination $\bar{y}_i = a^T \bar{\bm{x}}_i$,  
where $a^T = (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T \bm{S}_{pool}^{-1}$.

Classify observation $\bm{x}_0$ as $\pi_1$ if:
\begin{equation}
\begin{split}
\hat{y}_0 = (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T \bm{S}_{pool}^{-1} \bm{x}_0
&> \frac{1}{2} [a^T \bar{\bm{x}}_1 + a^T \bar{\bm{x}}_2]
= \frac{1}{2} a^T (\bar{\bm{x}}_1 + \bar{\bm{x}}_2)  \\
&= \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T \bm{S}_{pool}^{-1} (\bar{\bm{x}}_1 + \bar{\bm{x}}_2)
\end{split}
\end{equation}

equivalent to Equation \@ref(eq:ecm-normal) with $ln (\frac{c(1|2)~p_2}{c(2|1)~p_1}) = 0$ (equal costs, equal priors).

Classification with MV Normal Populations ($\bm{\Sigma}_1 \neq \bm{\Sigma}_2$. Quadratic)
-------------------------------------

Classify observation $\bm{x}$ as $\pi_1$ if:

\begin{equation}
\begin{split}
&\frac{-1}{2} \bm{x}^T (\bm{\Sigma}_1^{-1} - \bm{\Sigma}_2^{-1}) \bm{x} + (\bm{\mu}_1^T \bm{\Sigma}_1^{-1} - \bm{\mu}_2^T \bm{\Sigma}_2^{-1}) \bm{x} - k > ln (\frac{c(1|2)~p_2}{c(2|1)~p_1}), \\
&where ~~ k = \frac{1}{2} ln (\frac{|\bm{\Sigma}_1|}{|\bm{\Sigma}_2|}) + \frac{1}{2} (\bm{\mu}_1^T \bm{\Sigma}_1^{-1} \bm{\mu}_1 - \bm{\mu}_2^T \bm{\Sigma}_2^{-1} \bm{\mu}_2)
\end{split}
\end{equation}

Evaluate Classification Functions
--------------------------------

### Actual Error Rate (AER)
\begin{equation}
\begin{split}
&AER = p_1 ~ \int_{\hat{R}_2} f_1(\bm{x}) d \bm{x} + p_2 ~ \int_{\hat{R}_1} f_2(\bm{x}) d \bm{x}, \\
&where ~~~ \hat{R}_1 : (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T \bm{S}_{pool} \bm{x} - \frac{1}{2} (\bar{\bm{x}}_1 - \bar{\bm{x}}_2)^T \bm{S}_{pool} (\bar{\bm{x}}_1 + \bar{\bm{x}}_2) > ln (\frac{c(1|2)~p_2}{c(2|1)~p_1})
\end{split}
\end{equation}

Apparent error rate (APER) is just the misclassification rate in the training set. 
$APER = \frac{n_{1M} + n_{2M}}{n_1 + n_2}$

### Lachenbruch's Holdout Procedure

Lachenbruch's Holdout Procedure gives a nearly unbiased estimate of $E(ARE)$ for moderate sample size. The procedure is as follow:

1. Start with $\pi_1$ group. Omit 1 obs.(holdout) and then construct a classification function based on the remaining $n_1 - 1$ obs.
2. Classify the omitted obs. with the function constructed in step 1.
3. Repeat 1. and 2. untill all obs. in $\pi_1$ are classified. ($n_{1M}^{(H)}$: number of holdout obs. misclassified in $\pi_1$)
4. Repeat 1. to 3. for $\pi_2$ obs.

\begin{equation}
\hat{P}(2|1) = \frac{n_{1M}^{(H)}}{n_1}, ~~~~ \hat{P}(1|2) = \frac{n_{2M}^{(H)}}{n_2}, ~~~~
\hat{E}(AER) = \frac{n_{1M}^{(H)} + n_{2M}^{(H)}}{n_1 + n_2}
\end{equation}

Clustering
-------------------------------

### Similarity Coefficients

|           |  **k = 1** | **k = 0** |           |
|:---------:|:----------:|:---------:|:---------:|
| **i = 1** |      a     |     b     |   a + b   |
| **i = 0** |      c     |     d     |   c + d   |
|           |    a + c   |   b + d   | p (or n)  |

Item i, k measured by **p binary variables**. **Similarity between item i and item k** can be defined as $\frac{a+d}{p}$, $\frac{2(a+d)}{2(a+d) + b + c}$, $\frac{a}{p}$, etc.

Variable i, k with **n items**. **Similarity between variable i and variable k** can be defined as the **correlation** between the two variables:  
$r = \frac{ad -bc}{\sqrt{(a+b)(c+d)(a+c)(b+d)}}$

### Linkage Method (Hierarchical Clustering)

Clustering N objects with agglomerative hierachical clustering algorithm:

1. Start with N clusters and an $N \times N$ symmetric matrix of distances $\bm{D} = {d_{ik}}$.
2. Search for the nearest (most similar) pair of clusters in the distance matrix. Let the distance between these two clusters (U and V) be $d_{UV}$.
3. Merge cluster U and V into cluster (UV). Update the distance matrix by removing rows and columns corresponding to U and V, and add a row and a column giving the distances between (UV) and the remaining clusters.
4. Record the identity of the merged clusters and the distance at which the clusters merged. Repeat until all objects merged into 1 cluster.

**Single Linkage**  
$d_{(UV)W} = min\{d_{UW}, d_{VW}\}$

**Complete Linkage**  
$d_{(UV)W} = max\{d_{UW}, d_{VW}\}$

**Average Linkage**  
$d_{(UV)W} = \frac{\sum_{i} \sum_{k} d_{ik}}{N_{(UV)} N_W}$

**Ward's Method**  
For a given k, $ESS_k$ is the sum of squared deviations of every item from the mean (centroid) in cluster k. $ESS = \sum_{k = 1}^{K} ESS_k$. For every step, the two clusters whose combination results in the smallest increase in ESS are joined.

### K-means Method (Nonhierarchical Clustering)
K-means Method can **only be used to group items**.

Algorithm:

1. Partition items into K initial clusters (randomly).
2. Proceed through the list of items. Assign an item to the cluster whose mean (centroid) is nearest. Recalculate the centroids for **the cluster receiving the item** and the **cluster losing the item**.
3. Repeat step 2 until ni more reassignment takes place.

Formulas for updating cluster centroids:

For the ith coordinate, i = 1, 2, ..., p,
\begin{equation}
\begin{split}
&\bar{x}_{i, new} = \frac{n \bar{x}_i + x_{ji}}{n + 1} ~~~~~~~~~ if~~the~~jth~~item~~is~~added~~to~~this~~group\\
&\bar{x}_{i, new} = \frac{n \bar{x}_i - x_{ji}}{n - 1} ~~~~~~~~~ if~~the~~jth~~item~~is~~removed~~from~~this~~group
\end{split}
\end{equation}

Comapare 1 Population with a constant vector
---------------------------------------------

### Hotelling's T^2^
Let $\bm{X}_1$, $\bm{X}_2$, ..., $\bm{X}_n$ be i.i.d. from $N_p(\bm{\mu}, \bm{\Sigma})$.
\begin{equation}
\begin{split}
T^2 &= (\bm{\bar{X}} - \bm{\mu})^T (\frac{\bm{S}}{n})^{-1} (\bm{\bar{X}} - \bm{\mu}) \\
&= n (\bm{\bar{X}} - \bm{\mu})^T \bm{S} (\bm{\bar{X}} - \bm{\mu}) ~~~~ \sim ~~~
\frac{(n-1)p}{n-p} F_{p, n-p}
\end{split}
\end{equation}

, regardless of the true value of $\bm{\mu}$ and $\bm{\Sigma}$.  
$\bm{\bar{x}} = \frac{1}{n} \sum_{j=1}^{n} \bm{x}_j$, $\bm{S} = \frac{1}{n-1} \sum_{j=1}^{n} (\bm{x}_j - \bm{\bar{x}}) (\bm{x}_j - \bm{\bar{x}})^T$.

#### Testing H~0~: $\bm{\mu} = \bm{\mu_0}$

Calculate T^2^ = $n (\bm{\bar{x}} - \bm{\mu}_0)^T \bm{S} (\bm{\bar{x}} - \bm{\mu}_0)$. Reject H~0~ if T^2^ > $\frac{(n-1)p}{n-p} F_{p, n-p}(\alpha)$.

#### Confidence Region (ellipsoid)
\begin{equation}
\begin{split}
n (\bm{\bar{x}} - \bm{\mu})^T \bm{S} (\bm{\bar{x}} - \bm{\mu}) \leq \frac{(n-1)p}{n-p} F_{p, n-p}(\alpha)
\end{split}
\end{equation}

**Axes of confidence ellipsoid**  
\begin{equation}
\begin{split}
\pm \sqrt{\lambda_i} \sqrt{\frac{(n-1)p}{(n-p)n} F_{p, n-p}(\alpha)} ~~ \bm{e}_i 
~~~~~~ \bm{S} \bm{e}_i = \lambda_i \bm{e}_i, ~~ i = 1, 2, ..., p
\end{split}
\end{equation}

#### Simultaneous Confidence Intervals
Let $\bm{X}_1$, $\bm{X}_2$, ..., $\bm{X}_n$ be i.i.d. from $N_p(\bm{\mu}, \bm{\Sigma})$, then **for all $\bm{a}$ simultaneously**, the interval between the values
$\bm{a}^T \pm \sqrt{\frac{(n-1)p}{n-p} F_{p, n-p}(\alpha) \bm{a}^T \frac{\bm{S}}{n} \bm{a}}$
will contain $\bm{a}^T \bm{\mu}$ with probability $1 - \alpha$. e.g., for $\bm{a}^T = [1 ~~ 0 ~~ 0 ~~\cdots ~~ 0]$,

\begin{equation}
\begin{split}
\bar{x}_1 - \sqrt{\frac{(n-1)p}{n-p} F_{p, n-p}(\alpha) \frac{S_{11}}{n} } < ~ \mu_1 ~ < 
\bar{x}_1 + \sqrt{\frac{(n-1)p}{n-p} F_{p, n-p}(\alpha) \frac{S_{11}}{n} }
\end{split}
(\#eq:simultaneous)
\end{equation}

#### Bonferroni Method
\begin{equation}
\begin{split}
\bar{x}_i - t_{n-1}(\frac{\alpha}{2m}) \sqrt{\frac{S_{ii}}{n}} < ~ \mu_i ~ < 
\bar{x}_i + t_{n-1}(\frac{\alpha}{2m}) \sqrt{\frac{S_{ii}}{n}}  ~~~~~~~~~~ 
i = 1,~2,~...,~m
\end{split}
(\#eq:bonferroni)
\end{equation}

Compare 2 Population Means
---------------------------------

### Paired Comaprisons (Multivariate paired t-test)

Let $\bm{D}_j = \begin{pmatrix} D_{j1} \\ D_{j2} \\ \vdots  \\ D_{jp} \end{pmatrix} = \begin{pmatrix} X_{1j1} - X_{2j1} \\ X_{1j2} - X_{2j2} \\ \vdots  \\ X_{1j3} - X_{2j3} \end{pmatrix}$.
$j$ means the jth subject,
$X_{2j3}$ is the response of the **jth subject** on **varable 3** in the **2nd treatment**.
$D_{j2}$ is the **difference in the response** on the **2nd variable** between the 2 treatments.

Let $E(\bm{D_j}) = \bm{\delta}$, $Cov(\bm{D_j}) = \bm{\Sigma}_d$, 
and $\bm{D_1}$, $\bm{D_2}$, ..., $\bm{D_n}$ be i.i.d. from $N_p(\bm{\delta}, \bm{\Sigma}_d)$, then
\begin{equation}
\begin{split}
T^2 &= (\bm{\bar{D}} - \bm{\delta})^T (\frac{\bm{S_d}}{n})^{-1} (\bm{\bar{D}} - \bm{\delta}) \\
&= n (\bm{\bar{D}} - \bm{\delta})^T \bm{S_d} (\bm{\bar{D}} - \bm{\delta}) 
~~~~ \sim ~~~ \frac{(n-1)p}{n-p} F_{p, n-p}
\end{split}
\end{equation}

If n, n-p are large, $T^2 \xrightarrow{} \chi_p^2$

Simultaneous C.I. and Bonferroni intervals follows directly from Equation \@ref(eq:simultaneous) & \@ref(eq:bonferroni) by replacing $\bm{x}_i$ with $\bm{D}_i$.

### Two Independent Populations ($\bm{\Sigma}_1 = \bm{\Sigma}_2 = \bm{\Sigma}$)

Let $\bm{\bar{x}}_1 = \frac{1}{n_1} \sum_{j=1}^{n_1} \bm{x}_{1j}$, 
$\bm{S}_1 = \frac{1}{n_1-1} \sum_{j=1}^{n_1} (\bm{x}_{1j} - \bm{\bar{x}}_1) (\bm{x}_{1j} - \bm{\bar{x}}_1)^T$, 
where $\bm{x}_{11}$, $\bm{x}_{12}$, ... , $\bm{x}_{1n_1}$ 
$\sim N_p(\bm{\mu}_1, \Sigma)$.
Then, $\bm{S}_{pool}$ estimates $\bm{\Sigma}$
(see formulas for $\bm{S}_{pool}$ under eq \@ref(eq:ecm-normal)).

#### Test H~0~: $\bm{\mu}_1 - \bm{\mu}_2 = \bm{\delta}_0$

\begin{equation}
\begin{split}
T^2 &= (\bm{\bar{X}}_1 - \bm{\bar{X}}_2 - \bm{\delta})^T [(\frac{1}{n_1} + \frac{1}{n_2}) \bm{S}_{pool})]^{-1} (\bm{\bar{X}}_1 - \bm{\bar{X}}_2 - \bm{\delta}) 
~~~~ \sim ~~~ \frac{(n_1+n_2-2)p}{n_1+n_2-p-1} F_{p, n_1+n_2-p-1}
\end{split}
\end{equation}

#### Simultaneous Intervals

Let $c^2 = \frac{(n_1 + n_2 - 2)p}{n_1 + n_2 - p - 1} F_{p,n_1+n_2-p-1}(\alpha)$.

\begin{equation}
\begin{split}
\bm{a}^T (\bm{\bar{X}}_1 - \bm{\bar{X}}_2) \pm c \sqrt{\bm{a}^T (\frac{1}{n_1} + \frac{1}{n_2} )\bm{S}_{pool} \bm{a}} ~~~~~~ or ~~~~~~
(\bar{X}_{1i} - \bar{X}_{2i}) \pm c \sqrt{(\frac{1}{n_1} + \frac{1}{n_2}) S_{ii, pool}}  ~~~~ i = 1,2,...,p
\end{split}
\end{equation}

The Bonferroni method is done by replacing $c$ with $t_{n_1 + n_2 - 2}(\frac{\alpha}{2p})$ in the second part of the equation above.

One-way MANOVA
-------------------
\begin{equation}
\begin{split}
\bm{X}_{{\ell}j} - \bm{\mu} &= \bm{\tau}_{\ell} + \bm{e}_{{\ell}j}, ~~~~~~~ j=1,2,...,n ~~~~~ {\ell}=1,2,...,g \\
\sum_{{\ell}=1}^g \sum_{j=1}^{n_{\ell}} (\bm{x}_{{\ell}j} - \bm{\bar{x}}) (\bm{x}_{{\ell}j} - \bm{\bar{x}})^T &= 
\sum_{{\ell}=1}^g n_{\ell} (\bm{\bar{x}}_{\ell} - \bm{\bar{x}})(\bm{\bar{x}}_{\ell} - \bm{\bar{x}})^T +
\sum_{{\ell}=1}^g \sum_{j=1}^{n_{\ell}} (\bm{x}_{{\ell}j} - \bm{\bar{x}}_{\ell}) (\bm{x}_{{\ell}j} - \bm{\bar{x}}_{\ell})^T
\end{split}
(\#eq:manova-model)
\end{equation}

|     Source    |  **SSP** (matrix) |         **d.f.**        |
|:-------------:|:-----------------:|:-----------------------:|
| **Treatment** |         B         |          g - 1          |
|  **Residual** |         W         | $$\sum_{\ell=1}^{g} n_{\ell} - g$$ |
|   **Total**   |       B + W       | $$\sum_{\ell=1}^{g} n_{\ell} - 1$$ |

$\Lambda^* = \frac{|W|}{|B+W|}$

#### Simultaneous C.I. (Bonferroni)
Test $\tau_{ki} - \tau_{\ell i}$ (treatment $k$, $\ell$ on response variable $i$)

\begin{equation}
\begin{split}
C.I.: ~~
\bar{x}_{ki} - \bar{x}_{\ell i} \pm t_{n-g}(\frac{\alpha}{pg(g-1)}) \sqrt{\frac{w_{ii}}{n-g} (\frac{1}{n_k} + \frac{1}{n_{\ell}})}, ~~~~~
i = 1,2,...,p ~~~~ w_{ii}: ith~diagonal~element~of~W
\end{split}
\end{equation}

### 2018-07-01 1062_class/anthro_final/article.Rmd
up

---
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
urlcolor: blue
always_allow_html: yes
---

## 緒論

## 歷史背景

## 開源社群的運作

### 個人動機

### 禮物交換

### 2018-07-01 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 
+### PDF Output2
+This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
+```{yaml}
+---
+output:
+  bookdown::pdf_document2:
+    number_sections: FALSE
+    toc: False
+    includes:
+      in_header: header.tex
+    latex_engine: xelatex
+  bookdown::html_document2:
+    number_sections: FALSE
+    includes:
+      before_body: mathjax_bm.tex
+urlcolor: blue
+always_allow_html: yes
+---
+```
+
 ### PDF: header.tex{#pdf-header}
@@
 %設定行距
-\linespread{1.2}\selectfont
+\linespread{1.2}
+
+%suppress page number
+%\pagenumbering{gobble}
 ```

### 2018-07-01 1062_class/travel_map/kml_test.R

@@ -1,47 +1,0 @@
-library(sf)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(tmap)
-
-sp <- st_read("./shape/TOWN_MOI_1070330.shp") %>% 
-    select(COUNTYNAME, TOWNNAME)
-border <- st_read("COUNTY_BORDER.gpkg")[,-2] %>%
-    mutate(TOWNAME = COUNTYNAME)
-taitung <- st_read("taitung.kml")
-
-
-
-idx <- sp$COUNTYNAME=="臺東縣" & sp$TOWNNAME %in% c("臺東市", "東河鄉", "綠島鄉", "蘭嶼鄉")
-color <- tmaptools::get_brewer_pal("RdYlGn", n = 16)
-color <- color[c(4:5, 12:13)]
-curve <- c(121.19205, 22.79167, 121.507004, 22.0574483,
-           121.4723663, 22.6595601)
-
-pl <- ggplot()+
-    geom_sf(data = sp, colour="grey50", 
-            fill = "grey80", lwd=0.05) +
-    geom_sf(data = border, 
-            colour="grey30", fill=NA, lwd=0.08) +
-    geom_sf(data = sp[idx,], fill=color, colour=NA)+
-    #geom_sf(data = taitung,  size=0.01) +
-    scale_x_continuous(limits = c(119.85, 122.2), 
-                       breaks = 0)+
-    scale_y_continuous(limits = c(21.7, 25.3),
-                       breaks = 0) +
-    geom_curve(aes(x = curve[1], y = curve[2], 
-                   xend = curve[3], yend = curve[4], 
-                   colour = "臺東至蘭嶼"),
-               lwd=0.2, curvature = 0.2)+
-    geom_curve(aes(x = curve[3], y = curve[4], 
-                   xend = curve[5], yend = curve[6], 
-                   colour = "蘭嶼至綠島"), 
-               lwd=0.2, curvature = 0.2)+
-    guides(colour = guide_legend(override.aes = list(lwd=1)))+
-    scale_color_manual(values = color[c(4,1)]) +
-    labs(colour = "", x="", y="")+
-    theme(panel.background = element_rect(fill = "transparent"),
-          plot.background = element_rect(fill = "transparent")
-    )
-
-ggsave("plot_travel_location.png", pl, dpi = 800)

### 2018-07-01 1062_class/anthro_final/article.Rmd
up

@@
 ---
+title: "開源社群："
+author: "廖永賦"
+date: "`r Sys.Date()`"
 output:
@@
 always_allow_html: yes
+bibliography: anthro.bib
+csl: apa_ch.csl
+link-citations: yes
 ---
 
+## 摘要
+
+\pagenumbering{gobble}
+\newpage 
+\pagenumbering{arabic}
+
 ## 緒論
+自由與開源軟體[@2018h]不同於版權軟體（如微軟的 Office、Google 的 Gmail 等），是開放原始碼[^sourcecode]的軟體。開放原始碼意味使用者能自由的使用軟體，例如，根據自己的喜好修改軟體以符合使用的需求或偏好，並且也能向軟體開發者提供修改軟體的建議或程式碼。開源軟體因而能吸收來自網路上眾多「駭客」[^hacker]的貢獻，增加其修改軟體缺陷的速度與能力[@raymond1999]，而產生許多優秀的開源軟體。
+
+開源社群則是圍繞著開源軟體的開發而產生的社群，由一群對軟體開發有熱情的人組成。他們願意將其所開發的軟體以開放原始碼的形式釋出，並且接受來自網路上使用者的回饋以及修正。開源社群最大、也最引人注目的特色在於其參與者並無法直接從開發軟體中獲利（因為開源軟體開放任何人能夠使用），但卻有非常多的人從事開源軟體的開發。以下，本文將先回顧開源社群形成的脈絡；接著再以個人動機以及禮物交換的邏輯探討開源社群的運作；最後則探討代表資本主義的商業公司與開源社群互動、結合的現象。
+
+[^sourcecode]: 軟體的原始碼是由高階的程式語言所撰寫，如常見的 C++ 語言、Java 等，這些語言是人類能夠「看懂」的語言。一個軟體要能在電腦上運行，需要將高階的程式語言轉換成低階的機械碼。機械碼是電腦「看的懂」的語言（全部由 0 或 1 組成），但人類很難讀懂的語言，且機械碼也無法被轉換回高階語言。因此，私有的版權軟體為保護自己的智慧財產，通常僅以機械碼的形式將軟體發布給使用者。開源軟體則會公開其原始碼，讓使用者能夠修改該軟體。
+[^hacker]: 駭客（hacker）並非大眾媒體上所指「破解電腦以竊取資料」的電腦高手，其正確的詞彙應為 'cracker'[@raymond]。駭客在開源社群或更廣泛的駭客社群中，是帶有正面意義與認同的詞彙。
 
 ## 歷史背景
+
+開源社群的出現與電腦資訊科技息息相關。1960-1970 年代的電腦作業系統與網際網路的開發，多由大學以及私人公司資助的實驗室（如貝爾實驗室）進行。當時的研究人員時常分享彼此的原始碼，以非正式的方式授權不同機構的人們互相使用程式碼。
+
+隨著資訊科技的逐漸發展，1980 年美國將軟體納入智慧財產的保障，私人公司開始封閉其所擁有軟體之原始碼。Richard Stallman 對於此現象感到不滿，他認為自由地使用、修改軟體是每個人的權利，而封閉原始碼阻止了人們修改程式碼，是不道德的。因此，Stallman 推動了自由軟體運動（Free Software Movement）並成立了自由軟體基金會（Free Software Foundation），旨在推廣自由軟體開發。其中一個最能代表 Stallman 理念的例子是 GPL 條款：「使用 GPL 授權的軟體，容許其使用者自由地修改、複製、發布軟體的衍生版本（即需開放原始碼）。修改過的軟體，必須使用 GPL 作為授權條款」。透過 GPL 條款，一個軟體可以一直維持開源的狀況，為開源軟體的發展提供了一項保障。
+
+1990 年代，隨著網際網路的普及，開源社群的發展也更加蓬勃。同時，商業公司與開源社群的互動開始變得更加密切，這也反映在開源軟體運動（Open-Software Movement）的出現。不同於自由軟體運動的理念，開源軟體運動認為開源軟體不應該排拒閉源軟體，例如，其認為軟體的授權條款不應該限制軟體組成部份應使用何種授權條款， GPL 條款即不符合開源軟體運動的精神，因為其要求修改過之軟體必須以 GPL 條款釋出。開源軟體運動的出現，提倡使用較寬鬆的授權條款，使得開源軟體專案可以使用私人閉源軟體作為其部分。
 
@@
 ### 禮物交換
+
+## 資本主義
+
+## 參考資料{#reference}

### 2018-07-02 1062_class/anthro_final/article.Rmd
up

--- 2018-07-01 1062_class/anthro_final/article.Rmd
@@
 always_allow_html: yes
+bibliography: anthro.bib
+csl: apa_ch.csl
+link-citations: yes
 ---
 
+## 摘要
+
+\pagenumbering{gobble}
+\newpage 
+\pagenumbering{arabic}
+
 ## 緒論
+自由與開源軟體[@2018h]不同於版權軟體（如微軟的 Office、Google 的 Gmail 等），是開放原始碼[^sourcecode]的軟體。開放原始碼意味使用者能自由的使用軟體，例如，根據自己的喜好修改軟體以符合使用的需求或偏好，並且也能向軟體開發者提供修改軟體的建議或程式碼。開源軟體因而能吸收來自網路上眾多「駭客」[^hacker]的貢獻，增加其修改軟體缺陷的速度與能力[@raymond1999]，而產生許多優秀的開源軟體。手機作業系統 Android、辦公室軟體 LibreOffice、統計語言 R、影音播放器 VLC 等，是幾個知名的開源軟體。
+
+開源社群則是圍繞著開源軟體開發而產生的社群，由一群對軟體開發有熱情的人組成。他們所開發的軟體以開放原始碼的形式釋出，並且接受來自網路上使用者的回饋以及修正。開源社群最大、也最引人注目的特色在於其參與者並無法直接從開發軟體中獲利（因為開源軟體開放任何人能夠使用），但卻有非常多的人從事開源軟體的開發，且社群正穩定地成長與擴大。這在許多研究者眼中顯得相當不可思議，因此引發了許多研究，企圖了解開源社群的運作。以下，本文將先回顧開源社群形成的脈絡；接著再以個人動機以及禮物交換的邏輯探討開源社群的運作；最後探討代表資本主義的商業公司與開源社群互動、結合的現象。
+
+[^sourcecode]: 軟體的原始碼是由高階的程式語言所撰寫，如常見的 C++ 語言、Java 等，這些語言是人類能夠「看懂」的語言。一個軟體要能在電腦上運行，需要將高階的程式語言轉換成低階的機械碼。機械碼是電腦「看的懂」的語言（全部由 0 或 1 組成），但人類很難讀懂的語言，且機械碼也無法被轉換回高階語言。因此，私有的版權軟體為保護自己的智慧財產，通常僅以機械碼的形式將軟體發布給使用者。開源軟體則會公開其原始碼，讓使用者能夠修改該軟體。
+[^hacker]: 駭客（hacker）並非大眾媒體上所指「破解電腦以竊取資料」的電腦高手，其正確的詞彙應為 'cracker'[@raymond2004]。駭客在開源社群或更廣泛的駭客社群中，是帶有正面意義與認同的詞彙。
 
@@
 
+開源社群的出現與電腦資訊科技息息相關。1960-1970 年代的電腦作業系統與網際網路的開發，多由大學以及私人公司資助的實驗室（如貝爾實驗室）進行。當時的研究人員時常分享彼此的原始碼，以非正式的方式授權不同機構的人們互相使用程式碼。因此，開源社群最早的形式是一群互相分享原始碼的研究人員，亦即，開源社群起源於學術界。如今，開源社群的一些特色也顯示其源自學術界的特性，例如，強調「研究[^reproduce]可複製」的重要性[@peng2011]、軟體開發時的同儕審查機制[^peer][@bergquistmagnus2008]等。
+
+隨著資訊科技的逐漸發展，1980 年美國將軟體納入智慧財產的保障[@2018i]，私人公司開始封閉其所擁有軟體之原始碼。Richard Stallman 對於此現象感到不滿，他認為自由地使用、修改軟體是每個人的權利，而封閉原始碼阻止了人們修改程式碼，是不道德的[@2018l]。因此，Stallman 推動了自由軟體運動（Free Software Movement）並成立了自由軟體基金會（Free Software Foundation），旨在推廣自由軟體開發。其中一個最能代表 Stallman 理念的例子是 GPL 條款：「使用 GPL 授權的軟體，容許其使用者自由地修改、複製、發布軟體的衍生版本（即需開放原始碼）。修改過的軟體，必須使用 GPL 作為授權條款」。透過 GPL 條款，一個軟體可以一直維持開源的狀況，為開源軟體的發展提供了一項保障。
+
+1990 年代，隨著網際網路的普及，開源社群的發展也更加蓬勃。同時，商業公司與開源社群的互動開始變得更加密切，這也反映在開源軟體運動（Open-Software Movement）的出現。不同於自由軟體運動的理念，開源軟體運動認為開源軟體不應該排拒閉源軟體，例如，其認為軟體的授權條款不應該限制軟體各組成部份應使用何種授權條款。 GPL 條款即不符合開源軟體運動的精神，因為其要求修改過之軟體必須以 GPL 條款釋出。開源軟體運動的出現，提倡使用較寬鬆的授權條款，使得開源軟體專案可以使用私人閉源軟體作為其部分。
+
+[^reproduce]: 這裡的「研究」在強調軟體開發的開源社群中變成「程式碼」，亦即，任何人皆能夠在自己的電腦上透過該程式碼得到相同的結果。
+[^peer]: 軟體開發專案的擁有者能決定是否採用其他人對於軟體的修改。
+
 ## 開源社群的運作
+
+開源社群的出現與長期下來的穩定成長，造成許多學者的關注，包含對於社群成員之內在動機的探討[[@lakhani2003; @lerner2001; @lernerjosh2003]、對於社群內運作之探討[@zeitlyn2003; @bergquistmagnus2008]以及對於私人公司與開源社群互動之探討[@andersen-gott2012; @daveelder-vass2015]。本文以個人動機切入，企圖透過個體了解開源社群的文化與核心概念，以嘗試理解禮物交換的邏輯如何運作於開源社群之內。
+
+在進入的詳細的討論前，先了解開源軟體專案的運作模式有很大的幫助。一個典型的開源軟體專案通常會將軟體的原始碼託管在 GitHub 上，讓所有人透過網路即能檢視該軟體如何被寫成。軟體專案通常具有一位或少數幾位管理者，通常也是該軟體專案的創建者。軟體的絕大部份由這些人撰寫，並且在軟體開發成熟後轉換為軟體的維護者，整合來自各方所提出對於修改軟體的建議。一個好的軟體會吸引許多使用者，隨著使用者的增加，改進該軟體會變得更加容易，因為使用者會向軟體管理者回報使用上遇到的程式漏洞（bug）。少數具備優秀程式能力的使用者更會自己修改軟體，並將修改過後的程式碼提交[^pl]給管理者，其中的更少數可能因為經常提交修改而被邀請加入軟體管理者的行列。
+
+[^pl]: 這在版本控制系統 Git 以及應運而生的 GitHub 出現後變得非常容易進行。 軟體管理者可以清楚地看到軟體修改前後的差異，並決定是否將此變更整合進原本的軟體，或是需要更進一步地修改。
 

### 2018-07-02 1062_class/anthro_final/article.Rmd
up

@@
 
-開源社群的出現與長期下來的穩定成長，造成許多學者的關注，包含對於社群成員之內在動機的探討[[@lakhani2003; @lerner2001; @lernerjosh2003]、對於社群內運作之探討[@zeitlyn2003; @bergquistmagnus2008]以及對於私人公司與開源社群互動之探討[@andersen-gott2012; @daveelder-vass2015]。本文以個人動機切入，企圖透過個體了解開源社群的文化與核心概念，以嘗試理解禮物交換的邏輯如何運作於開源社群之內。
+以下簡述開源軟體專案的開發如何進行：
 
-在進入的詳細的討論前，先了解開源軟體專案的運作模式有很大的幫助。一個典型的開源軟體專案通常會將軟體的原始碼託管在 GitHub 上，讓所有人透過網路即能檢視該軟體如何被寫成。軟體專案通常具有一位或少數幾位管理者，通常也是該軟體專案的創建者。軟體的絕大部份由這些人撰寫，並且在軟體開發成熟後轉換為軟體的維護者，整合來自各方所提出對於修改軟體的建議。一個好的軟體會吸引許多使用者，隨著使用者的增加，改進該軟體會變得更加容易，因為使用者會向軟體管理者回報使用上遇到的程式漏洞（bug）。少數具備優秀程式能力的使用者更會自己修改軟體，並將修改過後的程式碼提交[^pl]給管理者，其中的更少數可能因為經常提交修改而被邀請加入軟體管理者的行列。
+> 一個典型的開源軟體專案通常會將軟體的原始碼託管在 GitHub 上，讓所有人透過網路即能檢視該軟體如何被寫成。軟體專案通常具有一位或少數幾位管理者，通常也是該軟體專案的創建者。軟體的絕大部份由這些人撰寫，並且在軟體開發成熟後轉換為軟體的維護者，整合來自各方所提出對於修改軟體的建議。一個好的軟體會吸引許多使用者，隨著使用者的增加，改進該軟體會變得更加容易，因為使用者會向軟體管理者回報使用上遇到的程式漏洞（bug）。少數具備優秀程式能力的使用者更會自己修改軟體，並將修改過後的程式碼提交[^pl]給管理者，其中的更少數可能因為經常提交修改而被邀請加入軟體管理者的行列。
+
+開源社群的出現與長期下來的穩定成長，造成大眾對於其夢幻般的想像[^altruism]，也引起許多學者的關注，包含對於社群成員之內在動機的探討[@lakhani2003; @lerner2001; @lernerjosh2003]、對於社群內運作之探討[@zeitlyn2003; @bergquistmagnus2008]以及對於私人公司與開源社群互動之探討[@andersen-gott2012; @daveelder-vass2015]。本文以個人動機切入，企圖透過個體了解開源社群的文化與核心概念，以嘗試理解禮物交換的邏輯如何運作於開源社群之內。
 
 [^pl]: 這在版本控制系統 Git 以及應運而生的 GitHub 出現後變得非常容易進行。 軟體管理者可以清楚地看到軟體修改前後的差異，並決定是否將此變更整合進原本的軟體，或是需要更進一步地修改。
+[^altruism]: 例如，大眾普遍對於開源社群有烏托邦式的正面印象，認為其由一群無私、具有共同信念、為追求更美好社會的一群人所組成。這在許多學者眼中顯得不盡合理。
 
 ### 個人動機
+
+Lakhani 與 Wolf[@lakhani2003]針對開源軟體專案的開發者進行了問卷調查，辨識出幾個重要的動機因素，其重要性依序為：「使用者[^user]需求」、「尋求腦力激盪與刺激」、「增進程式能力」、「相信開放原始碼的價值」、「作為開源社群一員的義務[^obligation]」。前述的這些動機因素，包含了實際因素、內在動機以及社群價值等幾種類型。進一步的分析可以發現這些不同類型的動機因素事實上呈現了開源社群異質的組成：開源社群的組成大致可區分成「受雇進行開源軟體開發」、「個人使用需求」、「尋求腦力激盪與增進程式能力」、「信奉開源軟體價值」四種類型。開源社群的組成因而並非如大眾所想像，是一群同質、抱持共同價值的「駭客」所組成，事實上，這也顯得相當合理，因為開源社群是公開的，透過網路，任何人皆有可能成為其中的一員。
+
+[^user]: 如上對於開源軟體開發的簡述，開源軟體的使用者部份也具有優秀的程式能力，進而加入軟體開發的行列。有許多甚至因為目前沒有類似的程式能提供解決問題的辦法而自行創立了一個軟體開發專案。此外，這個項目亦包含「開發者受雇進行開源軟體開發」的情況，例如，公司的營運可能需仰賴某些開源軟體，因此公司可能會聘請專門的工程師負責解決使用開源軟體所可能遇到的問題，如一些軟體漏洞。
+[^obligation]: 「作為開源社群一員」在此指「作為開源軟體的使用者」。
 

### 2018-07-02 1062_class/anthro_final/article.Rmd
up

@@
 
-開源社群的出現與電腦資訊科技息息相關。1960-1970 年代的電腦作業系統與網際網路的開發，多由大學以及私人公司資助的實驗室（如貝爾實驗室）進行。當時的研究人員時常分享彼此的原始碼，以非正式的方式授權不同機構的人們互相使用程式碼。因此，開源社群最早的形式是一群互相分享原始碼的研究人員，亦即，開源社群起源於學術界。如今，開源社群的一些特色也顯示其源自學術界的特性，例如，強調「研究[^reproduce]可複製」的重要性[@peng2011]、軟體開發時的同儕審查機制[^peer][@bergquistmagnus2008]等。
+開源社群的出現與電腦資訊科技息息相關。1960-1970 年代的電腦作業系統與網際網路的開發，多由大學以及私人公司資助的實驗室（如貝爾實驗室）進行。當時的研究人員時常分享彼此的原始碼，以非正式的方式授權不同機構的人們互相使用程式碼。因此，開源社群最早的形式是一群互相分享原始碼的研究人員，亦即，開源社群起源於學術界。如今，開源社群的一些特色也顯示其源自學術界的特性，例如，強調「研究[^reproduce]可複製」的重要性[@peng2011]、軟體開發時的同儕審查機制[^peer][@bergquistmagnus2001]等。
 
@@
 
-開源社群的出現與長期下來的穩定成長，造成大眾對於其夢幻般的想像[^altruism]，也引起許多學者的關注，包含對於社群成員之內在動機的探討[@lakhani2003; @lerner2001; @lernerjosh2003]、對於社群內運作之探討[@zeitlyn2003; @bergquistmagnus2008]以及對於私人公司與開源社群互動之探討[@andersen-gott2012; @daveelder-vass2015]。本文以個人動機切入，企圖透過個體了解開源社群的文化與核心概念，以嘗試理解禮物交換的邏輯如何運作於開源社群之內。
+開源社群的出現與長期下來的穩定成長，造成大眾對於其夢幻般的想像[^altruism]，也引起許多學者的關注，包含對於社群成員之內在動機的探討[@lakhani2003; @lerner2001; @lernerjosh2003]、對於社群內運作之探討[@zeitlyn2003; @bergquistmagnus2001]以及對於私人公司與開源社群互動之探討[@andersen-gott2012; @daveelder-vass2015]。本文以個人動機切入，企圖透過個體了解開源社群的組成，並嘗試理解禮物交換的邏輯如何運作於開源社群之內。
 
@@
 
-Lakhani 與 Wolf[@lakhani2003]針對開源軟體專案的開發者進行了問卷調查，辨識出幾個重要的動機因素，其重要性依序為：「使用者[^user]需求」、「尋求腦力激盪與刺激」、「增進程式能力」、「相信開放原始碼的價值」、「作為開源社群一員的義務[^obligation]」。前述的這些動機因素，包含了實際因素、內在動機以及社群價值等幾種類型。進一步的分析可以發現這些不同類型的動機因素事實上呈現了開源社群異質的組成：開源社群的組成大致可區分成「受雇進行開源軟體開發」、「個人使用需求」、「尋求腦力激盪與增進程式能力」、「信奉開源軟體價值」四種類型。開源社群的組成因而並非如大眾所想像，是一群同質、抱持共同價值的「駭客」所組成，事實上，這也顯得相當合理，因為開源社群是公開的，透過網路，任何人皆有可能成為其中的一員。
+Lakhani 與 Wolf[-@lakhani2003]針對開源軟體專案的開發者進行了問卷調查，辨識出幾個重要的動機因素，其重要性依序為：「使用者[^user]需求」、「尋求腦力激盪與刺激」、「增進程式能力」、「相信開放原始碼的價值」、「作為開源社群一員的義務[^obligation]」。前述的這些動機因素，包含了實際因素、內在動機以及社群價值等幾種類型。進一步的分析可以發現這些不同類型的動機因素事實上呈現了開源社群異質的組成：開源社群的組成大致可區分成「受雇進行開源軟體開發」、「個人使用需求」、「尋求腦力激盪與增進程式能力」、「信奉開源軟體價值」四種類型。開源社群的組成因而並非如大眾所想像，是一群同質、抱持共同價值的「駭客」所組成。事實上，這顯得相當合理，因為開源社群是公開的，透過網路，任何人皆有可能成為其中的一員，每個人可能因為各自的目的而加入，例如，上述「尋求腦力激盪與增進程式能力」可能主要由學生組成。容許成員組成的異質性可能也是開源社群能穩定存在的重要原因之一。
 
@@
 
+我們可以透過個人動機辨識出開源社群組成的異質性，然即使社群內存在相當的差異，開源軟體的開發仍依循著前述的固定方式。開源軟體的開發過程背後似乎隱含著某種人際關係的流動，透過程式碼交換認同及地位的方式進行。
+
+開源軟體運動的推動者 Eric Raymond 最早指出開源社群中禮物交換的現象[@raymond1999]。其指出在開源社群中，社會地位的高低是由所貢獻（給出）的程式碼所決定。透過提交修改過之軟體的原始碼，提交者以程式碼交換了名譽與聲望，提高了社會地位[@bergquistmagnus2001]。
+
+Bergquist 與 Ljungberg[-@bergquistmagnus2001] 指出開源社群中，禮物交換的運作方式比起以物品作為交換的社會來得更加抽象—禮物的形式並非實體的物品，並且會在不同形式之間轉換。以下，將分別以「軟體專案主要開發者」以及「提出軟體修改者（非軟體專案管理者）」的角度描述禮物交換進行的邏輯。
+
+#### 軟體專案主要開發者
+
+如前所述，軟體專案的主要開發者通常也是軟體的創立者、管理者與維護者。禮物交換在此以很簡單的邏輯進行：軟體開發者透過發布軟體（程式碼）交換社群中的認可。社群中的軟體使用者雖不需以任何物質形式報償軟體開發者，然社群所抱持的共同價值會造成社群對軟體開發者的崇敬。例如，開發 Linux 的 Linus Torvalds 在開源社群擁有極高的聲望。
+
+#### 提出軟體修改者
+
+禮物交換在開源軟體開發的另一個重要組成—提出軟體修改者，顯得稍微複雜一些。這些軟體使用者發現程式錯誤並提交修正的程式碼，並不會要求該程式碼的接受者—軟體專案管理者「回贈」以表達感謝。相對的，提交修正程式碼所交換而來的，同樣是來自整個社群的認可：提交優秀的程式碼以改進現有的軟體證明了提交者的能力，因此其獲得了社群地位的提昇。在此，軟體專案管理者與提出軟體修改者有明顯的上下權力關係：軟體專案管理者擁有審查提交之程式碼的權力，因此掌握著軟體修改者是否能被社群所認可。另一方面，軟體專案管理者也透過軟體修改者提供的程式碼改進其軟體，而更好的軟體將吸引更多使用者，進而提昇軟體專案管理者的聲望。
+
 ## 資本主義

### 2018-07-02 1062_class/anthro_final/article.Rmd
up

@@
 ## 緒論
-自由與開源軟體[@2018h]不同於版權軟體（如微軟的 Office、Google 的 Gmail 等），是開放原始碼[^sourcecode]的軟體。開放原始碼意味使用者能自由的使用軟體，例如，根據自己的喜好修改軟體以符合使用的需求或偏好，並且也能向軟體開發者提供修改軟體的建議或程式碼。開源軟體因而能吸收來自網路上眾多「駭客」[^hacker]的貢獻，增加其修改軟體缺陷的速度與能力[@raymond1999]，而產生許多優秀的開源軟體。手機作業系統 Android、辦公室軟體 LibreOffice、統計語言 R、影音播放器 VLC 等，是幾個知名的開源軟體。
+自由與開源軟體[@2018h]不同於版權軟體（如微軟的 Office、Google 的 Gmail 等），是開放原始碼[^sourcecode]的軟體。開放原始碼意味使用者能自由的使用軟體，例如，根據自己的喜好修改軟體以符合使用的需求或偏好，並且也能向軟體開發者提供修改軟體的建議或程式碼。開源軟體因而能吸收來自網路上眾多「駭客」[^hacker]的貢獻，增加其修改軟體缺陷的速度與能力[@raymond1999]，而產生許多優秀的開源軟體。手機作業系統 Android、瀏覽器 Firefox、辦公室軟體 LibreOffice、統計語言 R、影音播放器 VLC 等，是幾個知名的開源軟體。
 
@@
 
+另外值得注意的是，撰寫程式本身即為非常吸引人的事情，例如，對於大多數（60 %）的開發者而言，如果時間有額外的時間，其願意將時間花在撰寫程式上[@lakhani2003]，而進行開源軟體開發的好處在於自己（通常）有自由決定從事何種軟體開發[@lernerjosh2003]，因而更加強了個人動機。這顯示以市場經濟的方邏輯—花費額外時間「成本」進行開源軟體開發的論述，可能並不適用此情境。
+
 [^user]: 如上對於開源軟體開發的簡述，開源軟體的使用者部份也具有優秀的程式能力，進而加入軟體開發的行列。有許多甚至因為目前沒有類似的程式能提供解決問題的辦法而自行創立了一個軟體開發專案。此外，這個項目亦包含「開發者受雇進行開源軟體開發」的情況，例如，公司的營運可能需仰賴某些開源軟體，因此公司可能會聘請專門的工程師負責解決使用開源軟體所可能遇到的問題，如一些軟體漏洞。
@@
 
-我們可以透過個人動機辨識出開源社群組成的異質性，然即使社群內存在相當的差異，開源軟體的開發仍依循著前述的固定方式。開源軟體的開發過程背後似乎隱含著某種人際關係的流動，透過程式碼交換認同及地位的方式進行。
+我們可以透過個人動機辨識出開源社群組成的異質性，然即使社群內存在相當的差異，開源軟體的開發仍依循著前述的固定方式。開源軟體的開發過程背後似乎隱含著某種人際關係的流動，透過程式碼交換社群認同的方式進行。
 
@@
 
-Bergquist 與 Ljungberg[-@bergquistmagnus2001] 指出開源社群中，禮物交換的運作方式比起以物品作為交換的社會來得更加抽象—禮物的形式並非實體的物品，並且會在不同形式之間轉換。以下，將分別以「軟體專案主要開發者」以及「提出軟體修改者（非軟體專案管理者）」的角度描述禮物交換進行的邏輯。
+Bergquist 與 Ljungberg[-@bergquistmagnus2001]指出開源社群中，禮物交換的運作方式比起以物品作為交換的社會來得更加抽象—禮物的形式並非實體的物品，並且會在不同形式之間轉換。以下，將分別以「軟體專案主要開發者」以及「提出軟體修改者（非軟體專案管理者）」的角度描述禮物交換進行的邏輯。
 
@@
 
-如前所述，軟體專案的主要開發者通常也是軟體的創立者、管理者與維護者。禮物交換在此以很簡單的邏輯進行：軟體開發者透過發布軟體（程式碼）交換社群中的認可。社群中的軟體使用者雖不需以任何物質形式報償軟體開發者，然社群所抱持的共同價值會造成社群對軟體開發者的崇敬。例如，開發 Linux 的 Linus Torvalds 在開源社群擁有極高的聲望。
+如前所述，軟體專案的主要開發者通常也是軟體的創立者、管理者與維護者。禮物交換在此以很簡單的邏輯進行：軟體開發者透過發布軟體（程式碼）交換社群中的認可。社群中的軟體使用者雖不需以任何物質形式報償軟體開發者，然社群所抱持的共同價值會促使社群對軟體開發者的崇敬。例如，開發 Linux 的 Linus Torvalds 在開源社群擁有極高的聲望。如此，軟體專案開發者透過釋出開源軟體獲得社群的認可，進而增強其與社群成員之間的連結：一種身為開源社群一員的意識。
 
@@
 
-禮物交換在開源軟體開發的另一個重要組成—提出軟體修改者，顯得稍微複雜一些。這些軟體使用者發現程式錯誤並提交修正的程式碼，並不會要求該程式碼的接受者—軟體專案管理者「回贈」以表達感謝。相對的，提交修正程式碼所交換而來的，同樣是來自整個社群的認可：提交優秀的程式碼以改進現有的軟體證明了提交者的能力，因此其獲得了社群地位的提昇。在此，軟體專案管理者與提出軟體修改者有明顯的上下權力關係：軟體專案管理者擁有審查提交之程式碼的權力，因此掌握著軟體修改者是否能被社群所認可。另一方面，軟體專案管理者也透過軟體修改者提供的程式碼改進其軟體，而更好的軟體將吸引更多使用者，進而提昇軟體專案管理者的聲望。
+禮物交換在開源軟體開發的另一個重要組成—提出軟體修改者，顯得稍微複雜一些。這些軟體使用者發現程式錯誤並提交修正的程式碼，並不會要求該程式碼的接受者—軟體專案管理者「回贈」以表達感謝。相對的，提交修正程式碼所交換而來的，同樣是來自整個社群的認可：提交優秀的程式碼以改進現有的軟體證明了提交者的能力，因此其獲得了社群認可。在此，軟體專案管理者與提出軟體修改者的關係十分有趣：軟體專案管理者擁有審查提交之程式碼的權力，因此掌握著軟體修改者是否能被社群所認可。另一方面，軟體專案管理者也透過軟體修改者提供的程式碼改進其軟體，而更好的軟體將吸引更多使用者，進而能提昇軟體專案管理者的聲望。不管是「接受他人的修正」或是「所提出之修正被接受」，這對形成開源社群的團體意識具有很大的重要性，一方面，前者體驗到團體合作的可貴；後者則體驗到被肯定的感受。
+不管是軟體專案管理者或是提出軟體修改者，藉由禮物交換的進行，他們皆與開源社群建立了越加緊密的關係。
 
-## 資本主義
+## 私人公司與開源社群的結合
+
+@lakhani2003指出其所收集的問卷中，約有 40 % 的開發者是受雇進行開源軟體的開發，這顯示商業公司在開源社群中扮演相當重要的角色。例如，當今市占率最高的手機作業系統 Android （以 Linux 為基礎的作業系統）由 Google 所領導進行開發；Linux 作業系統則佔據了大多數伺服器與超級電腦的市場，而伺服器與超級電腦幾乎為商業公司所擁有，也因此作為自由軟體的 Linux 接受許多商業公司的資助[@2018m]。事實上，Linus Torvalds，Linux 的作者同時也是維護者，受雇於 Linux Foundation 以全心全意投入 Linux 的維護，而 Linux Foundation 的資金來自許多大型公司，如 Google、IBM、AT&T微軟、Intel、三星、華為、甲骨文公司等[@2018n]。
+
+Andersen-Gott 等 [-@andersen-gott2012]調查了公司投入開源軟體開發的動機。其指出三種商業上的利益，包含「增強創新能力」、「降低軟體開發成本」以及「提供開源軟體支援服務」。這裡需要強調的是，公司在開源社群中的角色，並非如寄生蟲一般消極地撈取利益，因為開源社群運作的方式，最重要的推力在於軟體本身的吸引力，沒有吸引力的軟體在社群中會被遺忘、淘汰。公司因此仍需投資相當大的經歷在開發及維護開源軟體專案，期望如此能吸引更多使用者來幫助除錯、改進軟體[@andersen-gott2012; @daveelder-vass2015]。值得注意的是，Andersen-Gott 等 [-@andersen-gott2012]發現在這些商業利益之外，這些公司參與開源軟體專案的動機也包含了開源社群中的理念：認為自己有義務將軟體貢獻給開源社群。這似乎顯示公司與開源社群的互動並非只有「技術性」的：公司利用開源社群的特性開發新的獲利方式或增強競爭力；與此同時，開源社群的理念也滲透到公司之內：在公司除了抱有獲利的概念之外，也增添了其它價值觀念。
+
+公司開始帶有開源社群理念可以透過組成公司的員工來理解：受聘於公司的工程師學習程式相關知識時，許多教育資源來自開源社群，主要是因為資源是免費的，且開源社群相當樂於分享相關資源給予新手。因此，組成公司的這些員工，本身即在開源社群的影響之下學習，自然帶有許多開源社群的理念。此外，公司與員工之間的關係不一定是上對下的支配關係，公司的決策方向也有可能受到員工的影響。例如，Google 在其員工反對的壓力之下，放棄參與五角大廈的軍事計畫 Project Maven[@wakabayashi2018]。
+
+在這裡似乎看見了資本主義與開源社群結合。當代的資訊科技公司規模是前所未見的巨大，其投入、領導開源軟體的開發是造成開源社群持續擴大最直接的原因。如今開源社群所抱持的理念，與其當初興起之時並無明顯轉變。相反的，代表資本主義的公司則開始轉變，從原本保護軟體原始碼的態度，轉向支持、領導開源軟體的開發。當代看到的是私人公司所代表的資本主義與開源社群的結合，開源社群的許多專案因為有商業資本的投入而穩定成長，而私人公司除了找到新的獲利方式之外，也藉此改變自己的形象。這似乎暗示著兩種不互斥的可能性：第一種是資本主義將利用開源社群持續地壯大自己、依據自己的利益主導開源軟體發展的方向；第二種是資本主義吸納開源社群的精神，緩和資本主義過於強調獲利與競爭的一面，而彰顯開源社群所強調的合作與人際關係。
 

### 2018-07-02 1062_class/anthro_final/article.Rmd
up

@@
 ---
-title: "開源社群："
-author: "廖永賦"
-date: "`r Sys.Date()`"
+title: "開源社群"
+subtitle: "發展、運作以及與資本主義的互動"
+author: "廖永賦$^1$"
 output:
   bookdown::pdf_document2:
-    number_sections: FALSE
-    toc: False
+    number_sections: TRUE
+    toc: TRUE
     includes:
@@
 
-## 摘要
+$\\$
+
+# 摘要{-}
+
+開源社群是圍繞著開源軟體開發而形成的社群，其最引人注目的特徵在於開源社群的參與者無法透過銷售其所開發之軟體獲利，然開源社群卻持續穩定成長。研究指出開源社群的運作與社群成員動機、社群內的禮物交換之間的關係。此外，當代私人公司與開源社群的結合的現象日益明顯，開源社群的壯大與資本投入有直接關聯，而私人公司也受到開源社群的影響，顯示資本主義與開源社群理念之間的互動。
+
+$\\$  $\\$  $\\$ $\\$  [^1]
+
+[^1]: 系級：心理三  \ \ 學號：B04207003
 
@@
 
-## 緒論
+# 緒論
 自由與開源軟體[@2018h]不同於版權軟體（如微軟的 Office、Google 的 Gmail 等），是開放原始碼[^sourcecode]的軟體。開放原始碼意味使用者能自由的使用軟體，例如，根據自己的喜好修改軟體以符合使用的需求或偏好，並且也能向軟體開發者提供修改軟體的建議或程式碼。開源軟體因而能吸收來自網路上眾多「駭客」[^hacker]的貢獻，增加其修改軟體缺陷的速度與能力[@raymond1999]，而產生許多優秀的開源軟體。手機作業系統 Android、瀏覽器 Firefox、辦公室軟體 LibreOffice、統計語言 R、影音播放器 VLC 等，是幾個知名的開源軟體。
 
-開源社群則是圍繞著開源軟體開發而產生的社群，由一群對軟體開發有熱情的人組成。他們所開發的軟體以開放原始碼的形式釋出，並且接受來自網路上使用者的回饋以及修正。開源社群最大、也最引人注目的特色在於其參與者並無法直接從開發軟體中獲利（因為開源軟體開放任何人能夠使用），但卻有非常多的人從事開源軟體的開發，且社群正穩定地成長與擴大。這在許多研究者眼中顯得相當不可思議，因此引發了許多研究，企圖了解開源社群的運作。以下，本文將先回顧開源社群形成的脈絡；接著再以個人動機以及禮物交換的邏輯探討開源社群的運作；最後探討代表資本主義的商業公司與開源社群互動、結合的現象。
+開源社群則是圍繞著開源軟體開發而產生的社群，由一群對軟體開發有熱情的人組成。他們所開發的軟體以開放原始碼的形式釋出，並且接受來自網路上使用者的回饋以及修正。開源社群最大、也最引人注目的特色在於其參與者並無法直接從開發軟體中獲利（因為開源軟體開放任何人能夠使用），但卻有非常多的人從事開源軟體的開發，且社群正穩定地成長與擴大。這在許多研究者眼中顯得相當不可思議，因此引發了許多研究，企圖了解開源社群的運作。以下，本文將先回顧開源社群形成的脈絡；接著再以個人動機以及禮物交換的邏輯探討開源社群的運作；最後探討代表資本主義的私人公司與開源社群互動、結合的現象。
 
-[^sourcecode]: 軟體的原始碼是由高階的程式語言所撰寫，如常見的 C++ 語言、Java 等，這些語言是人類能夠「看懂」的語言。一個軟體要能在電腦上運行，需要將高階的程式語言轉換成低階的機械碼。機械碼是電腦「看的懂」的語言（全部由 0 或 1 組成），但人類很難讀懂的語言，且機械碼也無法被轉換回高階語言。因此，私有的版權軟體為保護自己的智慧財產，通常僅以機械碼的形式將軟體發布給使用者。開源軟體則會公開其原始碼，讓使用者能夠修改該軟體。
+[^sourcecode]: 軟體的原始碼是由程式語言所撰寫，如常見的 C++ 語言、Java 等，這些是人類能夠「看懂」的語言。一個軟體要能在電腦上運行，需要將程式語言轉換成機械碼。機械碼是電腦「看的懂」的語言（全部由 0 或 1 組成）但人類很難讀懂的語言，且機械碼也無法被轉換回程式語言。因此，私有的版權軟體為保護自己的智慧財產，通常僅以機械碼的形式將軟體發布給使用者。開源軟體則會公開其原始碼，讓使用者能夠修改該軟體。
 [^hacker]: 駭客（hacker）並非大眾媒體上所指「破解電腦以竊取資料」的電腦高手，其正確的詞彙應為 'cracker'[@raymond2004]。駭客在開源社群或更廣泛的駭客社群中，是帶有正面意義與認同的詞彙。
 
-## 歷史背景
+# 歷史背景
 
@@
 
-## 開源社群的運作
+# 開源社群的運作
 
@@
 
-### 個人動機
+## 個人動機
 
@@
 
-### 禮物交換
+## 禮物交換
 
@@
 
-#### 軟體專案主要開發者
+###### **軟體專案主要開發者**{-}
 
@@
 
-#### 提出軟體修改者
+###### **提出軟體修改者**{-}
 
@@
 
-## 私人公司與開源社群的結合
+# 私人公司與開源社群的結合
 
-@lakhani2003指出其所收集的問卷中，約有 40 % 的開發者是受雇進行開源軟體的開發，這顯示商業公司在開源社群中扮演相當重要的角色。例如，當今市占率最高的手機作業系統 Android （以 Linux 為基礎的作業系統）由 Google 所領導進行開發；Linux 作業系統則佔據了大多數伺服器與超級電腦的市場，而伺服器與超級電腦幾乎為商業公司所擁有，也因此作為自由軟體的 Linux 接受許多商業公司的資助[@2018m]。事實上，Linus Torvalds，Linux 的作者同時也是維護者，受雇於 Linux Foundation 以全心全意投入 Linux 的維護，而 Linux Foundation 的資金來自許多大型公司，如 Google、IBM、AT&T微軟、Intel、三星、華為、甲骨文公司等[@2018n]。
+@lakhani2003 指出其所收集的問卷中，約有 40 % 的開發者是受雇進行開源軟體的開發，這顯示商業公司在開源社群中扮演相當重要的角色。例如，當今市占率最高的手機作業系統 Android （以 Linux 為基礎的作業系統）由 Google 所領導進行開發；Linux 作業系統則佔據了大多數伺服器與超級電腦的市場，而伺服器與超級電腦幾乎為商業公司所擁有，也因此作為自由軟體的 Linux 接受許多商業公司的資助[@2018m]。事實上，Linus Torvalds，Linux 的作者同時也是維護者，受雇於 Linux Foundation 以全心全意投入 Linux 的維護，而 Linux Foundation 的資金來自許多大型公司，如 Google、IBM、AT&T微軟、Intel、三星、華為、甲骨文公司等[@2018n]。
 
@@
 
-## 參考資料{#reference}
+# 參考資料{#reference}

### 2018-07-04 1062_class/eco_model/HW/rk4/rk4.Rmd
up

--- 2018-05-29 1062_class/eco_model/HW/C10/rk4.Rmd
@@
 
+## R~1~, R~2~ Coexist
+```c
+double a1=0.7, a2=0.7, b1=1.0, b2=1.0;
+double r1=0.8, r2=0.85, K1=1.2, K2=1.2, m=0.8;
+```
+
+```{r}
+library(ggplot2)
+ggplot(coexi)+
+    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
+    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
+    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
+    guides(colour = 
+            guide_legend(override.aes =
+                             list(size=2)))+
+    scale_x_continuous(
+        breaks = seq(0,300,50))+
+    labs(x="Time", y="Abundance",color="",
+         title=expression('R'[1]*' R'[2]*' Coexist'))
+```
+
+## R~1~ Exclude R~2~
+```c
+double a1=0.5, a2=0.5, b1=1.5, b2=1.0;
+double r1=1.0, r2=0.7, K1=1.2, K2=1.2, m=0.5;
+```
+```{r}
+ggplot(R1_win)+
+    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
+    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
+    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
+    guides(colour = 
+            guide_legend(override.aes =
+                             list(size=2)))+
+    scale_x_continuous(
+        breaks = seq(0,300,50))+
+    labs(x="Time", y="Abundance",color="",
+         title=expression('R'[1]*' Exclude'*' R'[2]))
+```
+
+## R~2~ Exclude R~1~
+```c
+double a1=0.5, a2=0.3, b1=0.7, b2=1.1;
+double r1=0.7, r2=0.7, K1=1.2, K2=1.2, m=0.5;
+```
+```{r}
+ggplot(R2_win)+
+    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
+    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
+    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
+    guides(colour = 
+            guide_legend(override.aes =
+                             list(size=2)))+
+    scale_x_continuous(
+        breaks = seq(0,300,50))+
+    labs(x="Time", y="Abundance",color="",
+         title=expression('R'[2]*' Exclude'*' R'[1]))
+```
+
 ## C code
 
-Download [rk4.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C10/rk4.c){target="_blank"}
+**Download [rk4.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C10/rk4.c){target="_blank"}**
 
@@
 ```
-
-### R~1~ R~2~ Coexist
-```c
-double a1=0.7, a2=0.7, b1=1.0, b2=1.0;
-double r1=0.8, r2=0.85, K1=1.2, K2=1.2, m=0.8;
-```
-
-```{r}
-library(ggplot2)
-ggplot(coexi)+
-    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
-    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
-    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
-    guides(colour = 
-            guide_legend(override.aes =
-                             list(size=2)))+
-    scale_x_continuous(
-        breaks = seq(0,300,50))+
-    labs(x="Time", y="Abundance",color="",
-         title=expression('R'[1]*' R'[2]*' Coexist'))
-```
-
-### R~1~ Exclude R~2~
-```c
-double a1=0.5, a2=0.5, b1=1.5, b2=1.0;
-double r1=1.0, r2=0.7, K1=1.2, K2=1.2, m=0.5;
-```
-```{r}
-ggplot(R1_win)+
-    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
-    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
-    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
-    guides(colour = 
-            guide_legend(override.aes =
-                             list(size=2)))+
-    scale_x_continuous(
-        breaks = seq(0,300,50))+
-    labs(x="Time", y="Abundance",color="",
-         title=expression('R'[1]*' Exclude'*' R'[2]))
-```
-
-### R~2~ Exclude R~1~
-```c
-double a1=0.5, a2=0.3, b1=0.7, b2=1.1;
-double r1=0.7, r2=0.7, K1=1.2, K2=1.2, m=0.5;
-```
-```{r}
-ggplot(R2_win)+
-    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
-    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
-    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
-    guides(colour = 
-            guide_legend(override.aes =
-                             list(size=2)))+
-    scale_x_continuous(
-        breaks = seq(0,300,50))+
-    labs(x="Time", y="Abundance",color="",
-         title=expression('R'[1]*' Exclude'*' R'[2]))
-```

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/spatial_model.Rmd
up

---
title: "Spatial Population Dynamics"
subtitle: "Reaction-Diffusion model"
author: "Yongfu Liao"
date: "`r Sys.Date()`"
css: /home/liao/local_depend/style_sheets/style.css
output:
  bookdown::html_document2:
    includes:
      before_body: /home/liao/local_depend/style_sheets/mathjax_bm.tex
    number_sections: no
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.dim = c(7, 4),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = "png", dpi = 350,
	out.width = "100%"
)
library(ggplot2)
library(tidyr)
library(readr)
library(magrittr)
library(dplyr)
```

## Model Equations

\begin{equation}
\begin{split}
&\frac{\partial N(x, t)}{\partial t} = r N(x, t) + D \frac{\partial^2 N(x, t)}{\partial x^2} \\
& D=1, ~ 0<x<L=10.0, ~ t>0 \\
\\
& Fixed ~ Boundary ~ Conditions: ~~ N(0,t)=0=N(L,t) \\
& Initial ~ Conditions: ~~if~ i=M/2=50, ~n(i,0)>0. ~~ Otherwise ~ n(i,0)=0
\end{split}
(\#eq:partial)
\end{equation}

### Discretization

\begin{equation}
\begin{split}
\frac{d N_i(t)}{d t} &= r N_i(t) + \frac{D}{(\Delta x)^2} [n_{i+1}(t) - 2 n_{i}(t) + n_{i-1}(t)] \\
\Delta x &= x_{i+1} - x_i = \frac{L}{M}
\end{split}
(\#eq:discrete)
\end{equation}

### Critical Value

The population goes extinct if:

\begin{equation}
\begin{split}
L &< \pi \sqrt{\frac{D}{r}}~,~~ or ~~
r &< \frac{D \pi^2}{L^2} = \frac{1 \pi^2}{10^2} = 0.098696
\end{split}
\end{equation}

## Case 1: Population Extinct

$r=0.09, ~ N_{50}(t=0) = 100$

```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
library(tidyr)
data_extinct <- readr::read_delim("data_0.09.txt", "\t", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE) %>%
    set_names(c("time", paste0("",seq(1,100,1))))

df <- data_extinct %>% 
    gather(key=i, value=N, -time) %>%
    mutate(i = as.integer(i)) %>%
    arrange(time, i)

ggplot(df, aes(x=time, y=i, z = N))+
    stat_contour(geom = "polygon", 
                 aes(fill = ..level..),
                 bins = 4000) +
    scale_fill_distiller(palette="Spectral", 
                         trans="log10")+
    geom_contour(aes(colour = ..level..), 
                 binwidth=0.25,
                 lwd=0.3, show.legend = F)+
    scale_color_distiller(palette="Spectral", 
                         trans="log10")+
    labs(x="Time", y="Position", fill="Pop. Size",
         caption= "Diff. between 2 contours = 0.25")+
    theme_bw()
```

## Case 2: Population Growth

$r=0.12, ~ N_{50}(t=0) = 100$

```{r}
data_growth <- readr::read_delim("data_0.12.txt", "\t", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE) %>%
    set_names(c("time", paste0("",seq(1,100,1))))

df <- data_growth %>% 
    gather(key=i, value=N, -time) %>%
    mutate(i = as.integer(i)) %>%
    arrange(time, i)

ggplot(df, aes(x=time, y=i, z = N))+
    stat_contour(geom = "polygon", 
                 aes(fill = ..level..),
                 bins = 4000) +
    scale_fill_distiller(palette="RdYlGn", 
                         trans="log10")+
    geom_contour(aes(colour = ..level..), 
                 binwidth=2,
                 lwd=0.25, show.legend = F)+
    scale_color_distiller(palette="RdYlGn", 
                         trans="log10")+
    labs(x="Time", y="Position (x)", fill="Pop. Size",
         caption = "Diff. between 2 contours = 2")+
    theme_bw()
```

## C Code

Download **[spatial_model.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/spatial_PDE/spatial_model.c){target="_blank"}**

```c
#include <stdio.h>
#include <stdlib.h>
#include <math.h>

double floor(double x);

//Fc declaration

	//Memory allocation
void message_error(char error_text[]);
double *d_vector(long size); //for generating double vector[1]...vector[size]
void free_d_vector(double *x);

	//Solving ODE
void differential (double time, double in[], double out[]);
double dn_dt(int j_idx, double time, double n[]);
void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) );

// Global variables
double r=0.09, D=1.0, delta_x=0.1; //model parameter
double t=0.0;                     //time
double deltat=0.001;              //time step for rk4
double *N;                        //initialize array for population size
double *dfdt;
int j_idx;

// Main function
int main(void){

	dfdt = d_vector(100); //set vector for 'differential' output
	N = d_vector(100);
	for (j_idx=1;j_idx<=100;j_idx++) N[j_idx] = 0.0; //set initial condition
	N[50] = 100.0; //set initial condition

	int i; //for loop index
	double T=100.2; // T: time of simulation

	for (i=0; i < T/deltat; i++){

		if (i % (int)floor(0.1/deltat) == 0 || i == 0){
			printf("%lf\t", t);
			for (j_idx=1;j_idx<=99;j_idx++) printf("%lf\t", N[j_idx]);
			printf("%lf\n", N[100]);
		}
		differential(t, N, dfdt);
		rk4(N, dfdt, 100, t, deltat, N, differential); //first N is input, second N is output
		t += deltat;
	}; //end for: end solving DE

	free_d_vector(N);
	free_d_vector(dfdt);
	return 0;
};

/* ODE Solver Functions */

double dn_dt(int j_idx, double time, double n[]){
	if (j_idx == 1 || j_idx == 100) return 0;
	else {
		return r*n[j_idx] + (D/(delta_x*delta_x)) * (n[j_idx+1] - 2*n[j_idx] + n[j_idx-1]);
	}
};

void differential (double time, double in[], double out[]){
	for (j_idx=1;j_idx<=100;j_idx++) out[j_idx] = dn_dt(j_idx, time, in);
};

/* 
void (*diff)(double, double [], double []) is a function pointer.
In order to use functions as inputs, it is included in the parameter of the function 'rk4'.
In this case, the function 'differential' is taken as input to the function 'rk4'.
*/

void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) )
{
	int i;
	double *k2, *k3, *k4, *D;
	// n: dimension of the ode
	// N_in: input population size ni. For 2-dim case n1=(pop. size of x); n2=(pop. size of y)
	// k1: parameter of rk4;  k1 = f(D,t); i.e. the output from differential is input of rk4
	k2 = d_vector(n); // rk4 k2
	k3 = d_vector(n); // rk4 k3
	k4 = d_vector(n); // rk4 k4
	D = d_vector(n); // Dummy variable for calculating coefficients of k_i in rk4

	for (i=1;i<=n;i++) D[i] = N_in[i] + (h/2.0)*k1[i];
	(*diff)(t+h/2.0, D, k2);
	for (i=1;i<=n;i++) D[i] = N_in[i] + (h/2.0)*k2[i];
	(*diff)(t+h/2.0, D, k3);
	for (i=1;i<=n;i++) D[i] = N_in[i] + h*k3[i];
	(*diff)(t+h, D, k4);

	for (i=1;i<=n;i++) N_out[i] = N_in[i] + (h/6.0)*(k1[i] + 2.0*k2[i] + 2.0*k3[i] + k4[i]);

	free_d_vector(D);
	free_d_vector(k2);
	free_d_vector(k3);
	free_d_vector(k4);

};

/* Memory Allocation Functions */

void message_error(char error_text[])
/*Standard error handler*/
{
    printf("There are some errors...\n");
    printf("%s\n", error_text);
    printf("...now existing to system...\n");
    exit(1);
};

double *d_vector(long size){ //for generating double vector[1]...vector[size]
    double *x; //pointer

    x = malloc((size + 1)*sizeof(double));
    //allocation of memory space to stock (size + 1) double variables & malloc returns the address of the top of the allocated memory space to x
    //the reason to prepare (size + 1) is just to use from x[1] to x[size]

    if(x == NULL) message_error("allocation failure in d_vector()"); //if memory allocation was failed, malloc returns NULL and x becomes NULL
    return x; //return the address of the top of the allocated memory space to x
};

void free_d_vector(double *x)
{
    free(x);
};

```

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/plotting.R

@@ -1,0 +1,25 @@
+library(ggplot2)
+library(dplyr)
+library(magrittr)
+library(tidyr)
+data_extinct <- readr::read_delim("data_0.09.txt", "\t", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE) %>%
+    set_names(c("time", paste0("",seq(1,100,1))))
+
+df <- data_extinct %>% 
+    gather(key=i, value=N, -time) %>%
+    mutate(i = as.integer(i)) %>%
+    arrange(time, i)
+
+ggplot(df, aes(x=time, y=i, z = N))+
+    stat_contour(geom = "polygon", 
+                 aes(fill = ..level..),
+                 bins = 4000) +
+    scale_fill_distiller(palette="Spectral", 
+                         trans="log10")+
+    geom_contour(aes(colour = ..level..), 
+                 binwidth=0.25,
+                 lwd=0.3, show.legend = F)+
+    scale_color_distiller(palette="Spectral", 
+                         trans="log10")+
+    labs(x="Time", y="Position", fill="Pop. Size")+
+    theme_bw()

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/spatial_model.c

@@ -1,0 +1,133 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+double floor(double x);
+
+//Fc declaration
+
+	//Memory allocation
+void message_error(char error_text[]);
+double *d_vector(long size); //for generating double vector[1]...vector[size]
+void free_d_vector(double *x);
+
+	//Solving ODE
+void differential (double time, double in[], double out[]);
+double dn_dt(int j_idx, double time, double n[]);
+void rk4(double N_in[], double k1[], int n, double t, double h, double N_out[], void (*diff)(double, double [], double []) );
+
+
+// Global variables
+double r=0.09, D=1.0, delta_x=0.1; //model parameter
+double t=0.0;                     //time
+double deltat=0.001;              //time step for rk4
+double *N;                        //initialize array for population size
+double *dfdt;
+int j_idx;
+
+
+// Main function
+int main(void){
+	
+	dfdt = d_vector(100); //set vector for 'differential' output
+	N = d_vector(100);
+	for (j_idx=1;j_idx<=100;j_idx++) N[j_idx] = 0.0; //set initial condition
+	N[50] = 100.0; //set initial condition
+
+	int i; //for loop index
+	double T=100.2; // T: time of simulation
+
+	for (i=0; i < T/deltat; i++){
+		
+		if (i % (int)floor(0.1/deltat) == 0 || i == 0){
+			printf("%lf\t", t);
+			for (j_idx=1;j_idx<=99;j_idx++) printf("%lf\t", N[j_idx]);
+			printf("%lf\n", N[100]);
+		}
+		differential(t, N, dfdt);
+		rk4(N, dfdt, 100, t, deltat, N, differential); //first N is input, second N is output
+		t += deltat;
+	}; //end for: end solving DE
+
+	free_d_vector(N);
+	free_d_vector(dfdt);
+	return 0;
+};
+
+
+
+/* ODE Solver Functions */
+
+double dn_dt(int j_idx, double time, double n[]){
+	if (j_idx == 1 || j_idx == 100) return 0;
+	else {
+		return r*n[j_idx] + (D/(delta_x*delta_x)) * (n[j_idx+1] - 2*n[j_idx] + n[j_idx-1]);
+	}
+};
+
+void differential (double time, double in[], double out[]){
+	for (j_idx=1;j_idx<=100;j_idx++) out[j_idx] = dn_dt(j_idx, time, in);
+};
+
+
+/* 
[…]

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/spatial_model.Rmd
up

@@
 
-## Case 1: Population Extinct
+## Case 1: Population Extinction
 
-$r=0.09, ~ N_{50}(t=0) = 100$
+$r=0.09, ~ N_{50}(0) = 100$
 
@@
                  aes(fill = ..level..),
-                 bins = 4000) +
+                 bins = 6000) +
     scale_fill_distiller(palette="Spectral", 
@@
 
-$r=0.12, ~ N_{50}(t=0) = 100$
+$r=0.12, ~ N_{50}(0) = 100$
 

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/plotting.R

@@ -13,7 +13,7 @@ df <- data_extinct %>%
 ggplot(df, aes(x=time, y=i, z = N))+
     stat_contour(geom = "polygon", 
                  aes(fill = ..level..),
-                 bins = 4000) +
+                 bins = 900) +
     scale_fill_distiller(palette="Spectral", 
                          trans="log10")+
     geom_contour(aes(colour = ..level..), 

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/spatial_model.c

@@ -35,7 +35,7 @@ int main(void){
 	N[50] = 100.0; //set initial condition
 
 	int i; //for loop index
-	double T=100.2; // T: time of simulation
+	double T=200.2; // T: time of simulation
 
 	for (i=0; i < T/deltat; i++){
 		

### 2018-07-08 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 title: "Rmarkdown Features"
-subtitle: "This is subtitle"
-author: Yongfu Liao
+subtitle: "A Compact Reference"
+author: "[Yongfu Liao](https://liao961120.github.io/)"
 date: "`r Sys.Date()`"
 bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
+csl: /home/liao/local_depend/style_sheets/apa.csl
 link-citations: yes
 output:
-  html_document:
+  bookdown::html_document2:
     code_folding: show
@@
     toc: true
-    toc_depth: 3
+    toc_depth: 2
     toc_float:
@@
 )
+str_date <- "`r Sys.Date()`"
 ```
 
-yaml Setup {.tabset}
------------------------------
+# yaml Setup {.tabset}
 
@@
 
-### yaml of this Doc
+## yaml of this Doc {-}
 
@@
 title: "Rmarkdown Features"
-subtitle: "This is subtitle"
-author: Yongfu Liao
-date: "`r Sys.Date()`"
+subtitle: "A Compact Reference"
+author: "[Yongfu Liao](https://liao961120.github.io/)"
+date: "`r str_date`"
 bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
+csl: /home/liao/local_depend/style_sheets/apa.csl
 link-citations: yes
 output:
-  html_document:
+  bookdown::html_document2:
     code_folding: show
@@
 
-### HTML Output
+## HTML Output {-}
 
@@
 
-### PDF Output
+## PDF Output {-}
 
@@
 
-### PDF Output2
+## PDF Output2 {-}
 This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
@@
 
-### PDF: header.tex{#pdf-header}
+## PDF: header.tex{- #pdf-header}
 
@@
 
-### Bibliography
+## Bibliography {-}
 
@@
 
-knitr Parameters
---------------------------------
+# knitr Parameters
 
-### Root
+## Root
 ```r
@@
 In the case above, I changed it to  the **directory that is parent to the default directory**.
+This is useful if you build websites with [R Markdown Websites](https://rmarkdown.rstudio.com/rmarkdown_websites.htm), since **R Markdown Websites** doesn't allow hierarchical website structure.
+By changing the root directory, you can more easly organize your project directory structure without violating the requirement of **R Markdown Websites**.
+This is especially true when you source a lot of Rscripts in the `.Rmd` files.
 
-### Code Chunk & Figure Options
+## Code Chunk & Figure Options
 ```r
@@
 
-Dynamic Variables
------------------------------
+# Dynamic Variables
 
@@
 
-$\LaTeX$ Math Rendering {.tabset}
------------------------------
-### Passing Matrix Object
+# Some $\LaTeX$ for PDF output
 
-#### Setup
+- `\pagenumbering{gobble}`
+This LaTeX code suppress the page number.
+
+- `\pagenumbering{arabic}`
+'Turn on' page number closed by `\pagenumbering{gobble}`.
+
+- `\newpage`: Start a new page
+
+The 3 type of code can be useful in the situation below:
+
+```tex
+---
+title: "A Title"
+author: "Someone"
+date: "`r str_date`"
+---
+
+... Some content in the first page (title page) ...
+
+\pagenumbering{gobble} % Suppress page number on the title page
+\newpage               % Start a new page
+
+... Some content in the second page ...
+
+\pagenumbering{arabic} % Revert suppression of page number
+                       % Now, the page num starts with '2'
+```
+
+# $\LaTeX$ Math {.tabset}
+
+## Passing Matrix Object {-}
+
+### Setup {-}
 
@@
 
-#### Include Matrix in Text
+### Include Matrix in Text {-}
 
@@
 
-### kable
+## kable {-}
 ```{r}
@@
 
-### Plotting Expression
+## Plotting Expression {-}
 ```{r fig.height=3}
@@
 
-Display Code Chunk with Code Chunk
---------------------------------------------
+# Display Code Chunk with Code Chunk
 
@@
 
-Bibliographies & Citations{#cite} 
------------------------------------------
+# Bibliographies & Citations{#cite}
 
@@
 
-### Citation syntax
+## Citation syntax
 
-#### Classical Citation: **Author**, **year**, and **brackets**
+### Classical Citation: **Author**, **year**, and **brackets** {-}
 - `Some text [@Bib.ID].`
@@
 
-#### In-text Citation: **Author (year)**
+### In-text Citation: **Author (year)** {-}
 - `@Bib.ID Some text`
@@
 
-#### Year only: Suppress Author
+### Year only: Suppress Author {-}
 - `Some text [-@Bib.ID].`
@@
 
-#### Two Citations
+### Two Citations {-}
 - `Some text [@Bib.ID1; @Bib.ID2].`
@@
 
-5. Prefix & Suffix
+- Prefix & Suffix
     - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
@@
 
-### Include `.bib` file in Reference {.tabset}
+## Include `.bib` file in Reference {.tabset}
 
@@
 
-#### Reference heading
+### Reference heading {-}
 
@@
 
-#### Specific Refs
+### Specific Refs {-}
 Include specific references that were **not cited** in the body of text.
@@
 
-#### All Refs
+### All Refs {-}
 Include **All references** in the body of text.
@@
 
-Emphasis {.tabset}
------------------------------
+# Emphasis {.tabset}
 
-### An Example
+## An Example {-}
 
@@
 
-### Colored divs
+## Colored divs {-}
 
-#### Bootstrap Alert
+### Bootstrap Alert {-}
 
@@
 
-#### Customized divs
+### Customized divs {-}
 
@@
 
-### Bootstrap Callouts
+## Bootstrap Callouts {-}
 
@@
 `r ''````{block2, type="bs-callout bs-callout-warning"}
-#### Heading in Callout
+### Heading in Callout
 **Calleout Text** texttexttexttexttexttext
@@
 ```{block2, type="bs-callout bs-callout-warning"}
-#### Heading in Callout
+### Heading in Callout
 **Calleout Text** texttexttexttexttexttext
@@
 
-### New Line
+## New Line {-}
 ```{markdown}
@@
 
-### Attach Attributes
+## Attach Attributes {-}
 By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.
 
-#### `class`
+### `class` {-}
 
@@
 
-#### Other Attributes
+### Other Attributes {-}
 ```{markdown}
@@
 
-Footnotes with Paragraphs
------------------------------
+# Footnotes with Paragraphs
+
 Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
@@
 
-Shaped Images {.tabset}
------------------------------
+# Shaped Images {.tabset}
 
-### Rounded Edge
+## Rounded Edge {-}
 ```{markdown}
@@
 
-#### Boostrap
+### Boostrap {-}
 ```{markdown}
@@
 
-### Circle Image
+## Circle Image {-}
 ```{markdown}
@@
 
-### Thumbnail
+## Thumbnail {-}
 ```{markdown}
@@
 
-Figures
------------------------------
+# Figures
 
-### Captions
+## Captions
+
 Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
-```{r fig.cap='An Caption of the Plot'}
+````r
+`r ''````{r fig.cap='An Caption of the Plot'}
+library(ggplot2)
+ggplot(iris) +
+    geom_point(aes(x = Sepal.Length,
+                   y = Sepal.Width,
+                   color = Species)
+               )
+```
+````
+
+```{r echo=FALSE, fig.cap='An Caption of the Plot'}
 library(ggplot2)
@@
 
-References
------------------------------
+# References

### 2018-07-10 GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.Rmd
up

---
title: "Create Beamer Slide with R Markdown"
subtitle: "A Reproducible Example"
author: "Yongfu, Liao"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
institute: "National Taiwan University"
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: true
    latex_engine: xelatex
    includes:
        in_header: header_beamer.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
date_text <- "format(Sys.Date(), '%B %d, %Y')"
```

## Reproduce This slide: yaml Header

```yaml
---
title: "Create Beamer Slide with R Markdown"
subtitle: "A Reproducible Example"
author: "Yongfu, Liao"
date: "`r date_text`"
institute: "National Taiwan University"
```

## Reproduce This slide: yaml Header (Cont.)
```yaml
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structurebold"
    incremental: true
    latex_engine: xelatex
    includes:
        in_header: header_beamer.tex
---
```

> - Links  
[header_beamer.tex](https://github.com/liao961120/local_depend/blob/master/style_sheets/header_beamer.tex)  
[Source Dir](https://github.com/liao961120/local_depend/tree/master/GitHubPage/my_R_book/Rmarkdown_features/beamer)

## Two-Column Layout

\begin{columns}
\column{0.75\textwidth}

```{r out.width="75%"}
library(ggplot2)
ggplot(iris, aes(x = Sepal.Width, y = Sepal.Length)) +
    geom_point(aes(color=Species), show.legend = F)
```

\column{0.25\textwidth}
Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text.
\end{columns}

## Two-Column Layout: Code

```tex
\begin{columns}
\column{0.75\textwidth}
```
    `r ''````{r out.width="75%"}
    library(ggplot2)
    ggplot(iris, aes(x = Sepal.Width,
                     y = Sepal.Length)) +
        geom_point(aes(color = Species),
                   show.legend = F)
    ```
```tex
\column{0.25\textwidth}
Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text.
\end{columns}
```

## Various Blocks

\begin{alertblock}{Red Block}
$\frac{\int_{-\infty}^{\infty} f(x)dx}{b}$
\end{alertblock}

\begin{examples}
Example Blocks are green.
\end{examples}

### Blue Block
Paragraph 1

Paragraph 2

## Various Blocks: Code

**Red Block**: Can set titles
```tex
\begin{alertblock}{Red Block}
$\frac{\int_{-\infty}^{\infty} f(x)dx}{b}$
\end{alertblock}
```

**Examples**: Can't change title
```tex
\begin{examples}
Example Blocks are green.
\end{examples}
```

**Blue Block**: h3 level Headings[^h3]
```markdown
### Blue Block
Paragraph 1: Text In Box

Paragraph 2: Blahblahblah
```

[^h3]: Note this only works in 'Madrid' theme in R markdown.

## Incremental Bullets

Remember to set `incremental: true` in the yaml header if you want this feature.

1. Item 1

2. Item 2

3. Item 3

### 2018-07-10 GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.Rmd
up

@@
     fonttheme: "structurebold"
-    incremental: true
+    incremental: false
     latex_engine: xelatex
@@
 knitr::opts_chunk$set(echo = FALSE)
-date_text <- "format(Sys.Date(), '%B %d, %Y')"
+date_text <- "`r format(Sys.Date(), '%B %d, %Y')`"
 ```
@@
 
-> - Links  
-[header_beamer.tex](https://github.com/liao961120/local_depend/blob/master/style_sheets/header_beamer.tex)  
-[Source Dir](https://github.com/liao961120/local_depend/tree/master/GitHubPage/my_R_book/Rmarkdown_features/beamer)
+- Links
+    - [header_beamer.tex](https://github.com/liao961120/local_depend/blob/master/style_sheets/header_beamer.tex)
+    - [Source Directory](https://github.com/liao961120/local_depend/tree/master/GitHubPage/my_R_book/Rmarkdown_features/beamer) of this Presentation
+    - [More](https://liao961120.github.io/notes/rmd_features.html) about R Markdown
 
@@
 \column{0.25\textwidth}
-Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text Some Text.
+R is a collaborative project with many contributors.
+Type `contributors()` for more information and
+`citation()` on how to cite R or R packages in publications.
 \end{columns}
@@
 
-Remember to set `incremental: true` in the yaml header if you want this feature.
+> 1. Item 1
 
-1. Item 1
+> 2. Item 2
 
-2. Item 2
+> 3. Item 3
 
-3. Item 3
+## Contact
+
+```{r out.width="10%"}
+knitr::include_graphics("tux.png")
+```
+
+\
+
+Where You can find me:
+
+- [GitHub](https://github.com/liao961120)
+
+- [Personal Page](https://liao961120.github.io/)

### 2018-07-10 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 ---
-title: "Rmarkdown Features"
+title: "R Markdown Features"
 subtitle: "A Compact Reference"
@@
 )
-str_date <- "`r Sys.Date()`"
+str_date <- "`r format(Sys.Date(), '%B %d, %Y')`"
 ```
@@
 
-# Shaped Images {.tabset}
+# Shaped Images (HTML) {.tabset}
 
@@
 
+# Beamer Slide (PDF)
+
+<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width="550" height="500" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:5px; max-width: 100%;" allowfullscreen></iframe>
+
+[Download](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
+
 # References

### 2018-07-11 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r Sys.Date()`"
+date: "`r format(Sys.Date(), '%B %d, %Y')`"
 bibliography: /home/liao/local_depend/citation/neanderthals.bib
@@
 - Prefix & Suffix
-    - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
-    -  Some text [see @RN9 pp. 45; also, @RN15 ch. 2].
+    - `Text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
+    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].
 
@@
 
-<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width="550" height="500" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:5px; max-width: 100%;" allowfullscreen></iframe>
+<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width=90%" height="440" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>
 
-[Download](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
+Note: In full screen mode (on PC), you can use arrow keys to navigate through the slides.
+
+[Download Beamer Slide](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
 

### 2018-07-11 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 
-Include **R Code Chunks' Variables** in the body of text.
+Include **R Code Chunk Variables** in the body of text. This can be a really useful feature for writing thesis or research paper:
+
+- No need to copy & paste the outcomes, such as the statistics. This greatly reduce the risk of error, and it also largely boosts efficiency.
+
+- Automatically updates the results in the paper when the data are updated.
+This also boosts efficiency and, more importantly, increases the **reproducibility** of the research: you can be confident that the results come directly from the data (unless there are errors in the *code*, which can be 'seen', whereas **errors from copy-&-paste's are invisible**).
+
+Below is a simple demonstration of this feature.
 
 ```{r}
-alpha <- 1:3
-text <- c("a", "b")
+tr1 <- rnorm(n=25, mean=1.1) #data of treatment1
+tr2 <- rnorm(n=25, mean=0.9) #data of treatment2
+ttest <- t.test(tr1, tr2, paired = T)
+diff <- ttest[["estimate"]][["mean of the differences"]]
+p_val <- ttest[["p.value"]]
 ```
 
-1. The numeric variable $\alpha =$ `r alpha[1]`.
-    ```{yaml}
-    # The numeric variable $\alpha =$ `r alpha[1]`.
+1. The mean difference between the two groups is `r round(diff, 3)`.
+    ```{latex}
+    The mean difference between the two treatments is `r round(diff, 3)`.
     ```
 
-2. The string variable $text =$ `r text[1]`.
-    ```{yaml}
-    # The string variable $text =$ `r text[1]`.
+2. The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
+    ```{latex}
+        The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
     ```
@@
 ### Classical Citation: **Author**, **year**, and **brackets** {-}
-- `Some text [@Bib.ID].`
+- `Some text [@citekey].`
     - Some text [@RN9].
@@
 ### In-text Citation: **Author (year)** {-}
-- `@Bib.ID Some text`
+- `@citekey Some text`
     - @RN15 Some text
 
-- `@Bib.ID [p. 20] Some text.`
+- `@citekey [p. 20] Some text.`
     - @RN9 [p. 20] Some text.
@@
 ### Year only: Suppress Author {-}
-- `Some text [-@Bib.ID].`
+- `Some text [-@citekey].`
     - Some text [-@RN9]
@@
 ### Two Citations {-}
-- `Some text [@Bib.ID1; @Bib.ID2].`
+- `Some text [@citekey1; @citekey2].`
     -  Some text [@RN9; @RN15].
@@
 - Prefix & Suffix
-    - `Text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
+    - `Text [see @citekey1 pp.45; also, @citekey2 ch. 2].`
     -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].
@@
 
-<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" width=90%" height="440" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>
+<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" height="400px" width="100%" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>
 

### 2018-07-11 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 One of the most common one is `.bib`.
-A lot of people (including me) use Endnote to manage bibliographies and have no time getting used to other open source reference managers.
-Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` from EndNote.
+A lot of people (including me) use Endnote to manage bibliographies.
+Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` files from EndNote.
+
+However, you can't control the format of the **citation key** generated by Endnote.
+Having a well-structured format of citation key greatly enhance efficiency, which can be done by using **[Zotero](https://www.zotero.org/)** and its extension **[Better BibTeX](https://retorque.re/zotero-better-bibtex/)**.
+I strongly recommend using this approach, since the learning curve isn't steep and it only hurts once.
+The payoff is a long-term efficiency boost.
 

### 2018-07-12 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 
-<iframe src="https://www.slideshare.net/slideshow/embed_code/key/1xBpPrD61JbE0w" height="400px" width="100%" frameborder="0" marginwidth="0" marginheight="0" scrolling="no" style="border:0px solid #FFFFFF; border-width:0px; margin-bottom:0px; max-width: 100%;" allowfullscreen></iframe>
+<embed src="beamer.pdf" type="application/pdf" width="90%" height="420px">
 
-Note: In full screen mode (on PC), you can use arrow keys to navigate through the slides.
+Note: You can use (left & right) arrow keys to navigate through the slides page-by-page.
 
-[Download Beamer Slide](https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
+[Download This Slide](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
 

### 2018-07-12 Ubuntu_16.04_setup/mylinux.Rmd
up

---
title: "My Linux Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
```

Navigation
=====

## Soft Link

Syntax: `ln -s <target> <link-name>`

e.g.
```bash
ln -s $(pwd)/blah.txt ~/Desktop/blah-sym
```

Network
=====

## SSH

### Server Setup{-}
Install SSH Server (so be connected by a remote client):
```bash
sudo apt-get install openssh-server
```

Configure:
```bash
sudo gedit /etc/ssh/sshd_config
```

> Port 22
> PasswordAuthentication yes
> PermitRootLogin yes

Findout IP address locally:
```bash
hostname -I | awk '{print $1}'
```

### Client Setup{-}

Access from remote via SSH:

Syntax: `ssh <server-user-account>@<ip>`

e.g.
```bash
ssh liao961120@192.168.2.110
```

Remote Control Via SSH
=====

1. Fix floating IP
2. configurate prompt
3. Auto Turn on

### 2018-07-12 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 
-Findout IP address locally:
-```bash
-hostname -I | awk '{print $1}'
-```
+Findout IP address locally: `hostname -I`
 
@@
 1. Fix floating IP
-2. configurate prompt
-3. Auto Turn on
+(Alternative: auto push IP address when turned on
+https://superuser.com/questions/471253/ubuntu-how-to-run-a-terminal-command-on-boot)
+2. Auto Turn-on Computer at 
+	- Enter `BIOS` > `Power Management Setup` > Enable `Power on by RTC Alarm` > Set `Date & Time`[^utc]
+
+[^utc]: Note the date time is in [Coordinated Universal Time (UTC) Standard](https://en.wikipedia.org/wiki/Coordinated_Universal_Time), so it's -8 hrs from the time in Taiwan.

### 2018-07-13 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 
-## SSH
+## Setup SSH
 
@@
 
+## Hardware Configuration
+
 1. Fix floating IP
@@
 https://superuser.com/questions/471253/ubuntu-how-to-run-a-terminal-command-on-boot)
-2. Auto Turn-on Computer at 
+2. Enable Auto Turn-on Computer at 
 	- Enter `BIOS` > `Power Management Setup` > Enable `Power on by RTC Alarm` > Set `Date & Time`[^utc]
@@
 [^utc]: Note the date time is in [Coordinated Universal Time (UTC) Standard](https://en.wikipedia.org/wiki/Coordinated_Universal_Time), so it's -8 hrs from the time in Taiwan.
+
+## wakeonlan
+
+wakeonlan -i <broadcast-ip> <MAC>
+
+```bash
+wakeonlan -i 192.168.2.255 44:87:fc:a1:0b:cc
+wakeonlan -i $rm_ip_b $rm_MAC
+```
+
+## SSH login
+
+ssh liao961120@<ip>
+
+```bash
+ssh liao961120@192.168.2.110
+ssh $ssh_pc
+```
+
+## SSH logout & suspend computer
+
+1. `sudo bash -c "sleep 15s; pm-suspend" &`: Set buffer time for suspend
+2. `Ctrl+D`: Use the 15 sec to logout
+
+## Variable Definition (in `~/.bashrc`)
+```bash
+rm_MAC="44:87:fc:a1:0b:cc"
+rm_ip="192.168.2.110"
+rm_ip_b=`bash ~/ip2ipb.sh 196.168.2.110`
+ssh_pc="liao961120@$rm_ip"
+```

### 2018-07-14 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 https://superuser.com/questions/471253/ubuntu-how-to-run-a-terminal-command-on-boot)
-2. Enable Auto Turn-on Computer at 
-	- Enter `BIOS` > `Power Management Setup` > Enable `Power on by RTC Alarm` > Set `Date & Time`[^utc]
+2. Enable WakeOnLane(WOL) at BIOS: 
+	1. `Power Management Setup` > `WOL: enabled`[^wol]
+	2. `Power Management Setup` > `deep power off mode: disabled`[^poff]
 
+[^wol]: There may be different names for WOL, such as 'Wake Up on Lan', 'Automatic Power Up', 'Resume by LAN', 'Power Up On PCI Device', 'PME Event Wake Up', etc.
+[^poff]: This keeps the power for NIS to turn on the computer when receiving a signal from web.
 [^utc]: Note the date time is in [Coordinated Universal Time (UTC) Standard](https://en.wikipedia.org/wiki/Coordinated_Universal_Time), so it's -8 hrs from the time in Taiwan.
@@
 
-1. `sudo bash -c "sleep 15s; pm-suspend" &`: Set buffer time for suspend
-2. `Ctrl+D`: Use the 15 sec to logout
+Use `sudo shutdown 0` to leave. Remember to enable `Power of Mode` in BIOS, so you can WOL to open the computer again.
 
@@
 rm_ip="192.168.2.110"
-rm_ip_b=`bash ~/ip2ipb.sh 196.168.2.110`
+rm_ip_b=`bash ~/ip2ipb.sh $rm_ip`
 ssh_pc="liao961120@$rm_ip"

### 2018-07-14 Ubuntu_16.04_setup/mybashrc.sh

@@ -1,0 +1,21 @@
+alias app_link='xdg-open /usr/share/applications/'
+alias screen_shot='xdg-open ~/Pictures/'
+alias cp_rmd='cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.html ~/liao961120.github.io/notes/rmd_features.html; cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf ~/liao961120.github.io/notes/beamer.pdf'
+alias timecal='bash ~/sh_program/time_cal.sh'
+alias dict='goldendict'
+alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
+export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
+PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
+export PS1
+
+# Define variables for SSH remote pc.
+### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
+
+rm_MAC="44:87:fc:a1:0b:cc" #MAC address of remote pc
+rm_ip="`head -1 ~/local_depend/hostname/hostname.txt`" #Now floating IP, needs to change to static
+rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
+ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
+
+
+# Backup self-defined cmd in git repo (prt lines after 'line 120')
+tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh

### 2018-07-14 Ubuntu_16.04_setup/mybashrc.sh
up

@@ -4,6 +4,7 @@ alias cp_rmd='cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_feat
 alias timecal='bash ~/sh_program/time_cal.sh'
 alias dict='goldendict'
 alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
+alias r='Rscript -e' #Note capital 'R' is for running R in bash
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
 export PS1

### 2018-07-14 hostname/autohost.sh
up

@@ -1,0 +1,5 @@
+cd ~/local_depend/hostname
+echo -e `hostname -I`'\n'liao@pc'\n'`date` > /home/liao961120/local_depend/hostname/hostname.txt
+git add hostname.txt
+git commit -m "new ip"
+git push origin master

### 2018-07-21 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 
+Common Techniques
+========
+
+## Copy Previous Command to file
+
+```bash
+cat ~/foo.txt >> doc.Rmd
+echo "!!" >> file.txt
+```
+
+Then the command appends literal `cat ~/foo.txt >> doc.Rmd
+echo "!!" >> file.txt` to the end of `file.txt`.
+
+## Expansion with text
+
+Download all web pages starting from `www.millionbook.net/wx/j/jingyong/sdxl/001.htm` to `www.millionbook.net/wx/j/jingyong/sdxl/041.htm`:
+
+```bash
+url=http://www.millionbook.net/wx/j/jingyong/sdxl/
+wget "$url"{001..041}".htm"
+```
+
 Navigation
-=====
+========
+
+## File Manipulation
+
+### Recursive Rename
+
+Systematically rename multiple files by `for` loop.
+
+Original files in the working dir:
+```
+dir2/
+01-file.txt
+02-file.txt
+.
+.
+41-file.txt
+README.md
+```
+
+```bash
+for i in {01..41}
+do 
+	mv $(echo $i'*') $(echo $i'.txt')
+done
+```
+
+After executing the code above:
+```
+dir2/
+01.txt
+02.txt
+.
+.
+41.txt
+README.md
+```
 
@@
 Network
-=====
+========
 
@@
 Remote Control Via SSH
-=====
+========
 

### 2018-07-21 Ubuntu_16.04_setup/mybashrc_man.sh

@@ -25,3 +25,7 @@ ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
 tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
 alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
+
+
+
+#### Backup Time	Sat Jul 21 11:34:19 CST 2018 ####

### 2018-07-21 Ubuntu_16.04_setup/mybashrc.sh
up

@@ -1,12 +1,11 @@
 alias app_link='xdg-open /usr/share/applications/'
-alias screen_shot='xdg-open ~/Pictures/'
-alias cp_rmd='cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.html ~/liao961120.github.io/notes/rmd_features.html; cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf ~/liao961120.github.io/notes/beamer.pdf'
 alias timecal='bash ~/sh_program/time_cal.sh'
 alias dict='goldendict'
 alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
 alias render_mylinux='bash ~/sh_program/render_mylinux.sh'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
-alias rbook='cd /home/liao/local_depend/GitHubPage/my_R_book/Rmarkdown_features'
+alias render_rmdbk='bash ~/sh_program/render_rmarkdown_book.sh'
+alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
 alias new_rmd='bash ~/sh_program/append_head_rmd.sh'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
@@ -25,3 +24,6 @@ ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
 tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
 alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
+# Backup ~/sh_program
+cp -r ~/sh_program ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
+

### 2018-07-21 Ubuntu_16.04_setup/mybashrc_man.sh

@@ -1,12 +1,11 @@
 alias app_link='xdg-open /usr/share/applications/'
-alias screen_shot='xdg-open ~/Pictures/'
-alias cp_rmd='cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.html ~/liao961120.github.io/notes/rmd_features.html; cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf ~/liao961120.github.io/notes/beamer.pdf'
 alias timecal='bash ~/sh_program/time_cal.sh'
 alias dict='goldendict'
 alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
 alias render_mylinux='bash ~/sh_program/render_mylinux.sh'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
-alias rbook='cd /home/liao/local_depend/GitHubPage/my_R_book/Rmarkdown_features'
+alias render_rmdbk='bash ~/sh_program/render_rmarkdown_book.sh'
+alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
 alias new_rmd='bash ~/sh_program/append_head_rmd.sh'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
@@ -25,7 +24,10 @@ ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
 tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
 alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
+# Backup ~/sh_program
+cp -r ~/sh_program ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
 
 
 
-#### Backup Time	Sat Jul 21 11:34:19 CST 2018 ####
+
+#### Backup Time	Sat Jul 21 12:15:55 CST 2018 ####

### 2018-07-21 Ubuntu_16.04_setup/sh_program_bak/append_head_rmd.sh

@@ -1,0 +1,8 @@
+if [[ $2 =~ ^(pdf|PDF)$ ]]
+then
+    cat ~/local_depend/style_sheets/Rmd-head-pdf.txt > $1
+    echo -e "Use PDF\nFile: $1"
+else
+    cat ~/local_depend/style_sheets/Rmd-head-htm.txt > $1
+    echo -e "Use HTML\nFile: $1"
+fi

### 2018-07-21 Ubuntu_16.04_setup/sh_program_bak/render_rmarkdown_book.sh

@@ -1,0 +1,5 @@
+Rscript -e "rmarkdown::render('~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd')"
+
+mv ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.html ~/liao961120.github.io/notes/rmd_features.html
+
+cp ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf ~/liao961120.github.io/notes/beamer.pdf

### 2018-07-21 Ubuntu_16.04_setup/mybashrc.sh
up

@@ -1,16 +1,15 @@
 alias app_link='xdg-open /usr/share/applications/'
-alias timecal='bash ~/sh_program/time_cal.sh'
 alias dict='goldendict'
 alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
-alias render_mylinux='bash ~/sh_program/render_mylinux.sh'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
-alias render_rmdbk='bash ~/sh_program/render_rmarkdown_book.sh'
+alias render_rmdbk='~/bin/render_rmarkdown_book'
 alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
-alias new_rmd='bash ~/sh_program/append_head_rmd.sh'
+alias new_rmd='~/bin/append_head_rmd'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
 export PS1
+export PATH=~/bin:"$PATH"
 
 # Define variables for SSH remote pc.
 ### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
@@ -21,9 +20,10 @@ rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
 ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 
 
+# Backup ~/sh_program
+cp -r ~/bin ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
+
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
 tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
 alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
-# Backup ~/sh_program
-cp -r ~/sh_program ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
 

### 2018-07-21 Ubuntu_16.04_setup/mybashrc_man.sh

@@ -1,16 +1,15 @@
 alias app_link='xdg-open /usr/share/applications/'
-alias timecal='bash ~/sh_program/time_cal.sh'
 alias dict='goldendict'
 alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
-alias render_mylinux='bash ~/sh_program/render_mylinux.sh'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
-alias render_rmdbk='bash ~/sh_program/render_rmarkdown_book.sh'
+alias render_rmdbk='~/bin/render_rmarkdown_book'
 alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
-alias new_rmd='bash ~/sh_program/append_head_rmd.sh'
+alias new_rmd='~/bin/append_head_rmd'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
 export PS1
+export PATH=~/bin:"$PATH"
 
 # Define variables for SSH remote pc.
 ### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
@@ -21,13 +20,14 @@ rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
 ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 
 
+# Backup ~/sh_program
+cp -r ~/bin ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
+
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
 tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
 alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
-# Backup ~/sh_program
-cp -r ~/sh_program ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
 
 
 
 
-#### Backup Time	Sat Jul 21 12:15:55 CST 2018 ####
+#### Backup Time	Sat Jul 21 19:21:20 CST 2018 ####

### 2018-07-21 Ubuntu_16.04_setup/sh_program_bak/sh_program/render_mylinux.sh

@@ -1,0 +1,2 @@
+Rscript -e "rmarkdown::render('~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd')"
+mv ~/local_depend/Ubuntu_16.04_setup/mylinux.html ~/liao961120.github.io/notes/mylinux.html

### 2018-07-21 Ubuntu_16.04_setup/sh_program_bak/sh_program/time_cal.sh

@@ -1,0 +1,12 @@
+if [[ $# -eq 3 ]]
+then
+	expr 60 \* 60 \* $1 + 60 \* $2 + $3
+elif [[ $# -eq 2 ]]
+then
+	expr 60 \* $1 + $2
+elif [[ $# -eq 1 ]]
+then	
+	expr $1
+else
+	echo "Input Error"
+fi

### 2018-07-23 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
   bookdown::html_document2:
+    highlight: haddock
     css: /home/liao/local_depend/style_sheets/style.css
@@
 	warning = FALSE,
+	comment = ">",
 	dev='svg',
@@
 ```bash
-cat ~/foo.txt >> doc.Rmd
-echo "!!" >> file.txt
+cat ~/bash_pract/rmd-head.txt >> ~/bash_pract/doc.Rmd
+echo "!!" >> ~/bash_pract/cmd_hist
 ```
 
-Then the command appends literal `cat ~/foo.txt >> doc.Rmd
-echo "!!" >> file.txt` to the end of `file.txt`.
+Then the command appends literal `cat ~/bash_pract/rmd-head.txt >> ~/bash_pract/doc.Rmd` to the end of `cmd_hist`. Note that this **works only on the command line**, not shell scripts.
 
@@
 
-Original files in the working dir:
-```
-dir2/
-01-file.txt
-02-file.txt
-.
-.
-41-file.txt
-README.md
+```{bash, preprocess-dir, include=FALSE}
+cd ~/bash_pract && rm -r dir
+mkdir dir dir/dir2
+touch dir/{01..03}-file.txt dir/README
 ```
 
-```bash
-for i in {01..41}
-do 
+Original files in the working dir:
+```{bash}
+ls ~/bash_pract/dir
+```
+
+Then, running the code below:
+```{bash}
+cd ~/bash_pract/dir
+
+for i in {01..03}; do 
 	mv $(echo $i'*') $(echo $i'.txt')
 done
-```
 
-After executing the code above:
-```
-dir2/
-01.txt
-02.txt
-.
-.
-41.txt
-README.md
+ls
 ```
@@
 e.g.
-```bash
-ln -s $(pwd)/blah.txt ~/Desktop/blah-sym
+```{bash}
+cd ~/bash_pract
+echo "Before:
+$(ls -l)"
+
+ln -s $(pwd)/dir/foo.txt $(pwd)/foo-sym
+
+echo "
+After:
+$(ls -l)"
+```
+
+```{bash include=FALSE}
+rm ~/bash_pract/foo-sym
 ```
@@
 > Port 22
+>
 > PasswordAuthentication yes
+>
 > PermitRootLogin yes

### 2018-07-23 Ubuntu_16.04_setup/mybashrc.sh

@@ -1,6 +1,5 @@
 alias app_link='xdg-open /usr/share/applications/'
 alias dict='goldendict'
-alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
 alias render_rmdbk='~/bin/render_rmarkdown_book'
 alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
@@ -9,7 +8,7 @@ alias new_rmd='~/bin/append_head_rmd'
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
 export PS1
-export PATH=~/bin:"$PATH"
+export PATH=~/bin:"$PATH"  #Add ~/bin to PATH so custom shell programs can be found
 
 # Define variables for SSH remote pc.
 ### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
@@ -20,7 +19,7 @@ rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
 ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 
 
-# Backup ~/sh_program
+# Backup ~/bin (Custom shell programs)
 cp -r ~/bin ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
 
 # Backup self-defined cmd in git repo (prt lines after 'line 120')

### 2018-07-23 Ubuntu_16.04_setup/mybashrc_man.sh

@@ -1,6 +1,5 @@
 alias app_link='xdg-open /usr/share/applications/'
 alias dict='goldendict'
-alias mylinux='vim ~/local_depend/Ubuntu_16.04_setup/mylinux.Rmd'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
 alias render_rmdbk='~/bin/render_rmarkdown_book'
 alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
@@ -9,7 +8,7 @@ alias new_rmd='~/bin/append_head_rmd'
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
 export PS1
-export PATH=~/bin:"$PATH"
+export PATH=~/bin:"$PATH"  #Add ~/bin to PATH so custom shell programs can be found
 
 # Define variables for SSH remote pc.
 ### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
@@ -20,7 +19,7 @@ rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
 ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
 
 
-# Backup ~/sh_program
+# Backup ~/bin (Custom shell programs)
 cp -r ~/bin ~/local_depend/Ubuntu_16.04_setup/sh_program_bak
 
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
@@ -30,4 +29,4 @@ alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybash
 
 
 
-#### Backup Time	Sat Jul 21 19:21:20 CST 2018 ####
+#### Backup Time	Sun Jul 22 18:39:06 CST 2018 ####

### 2018-07-23 1062_class/anthro_final/article.Rmd
up

@@
 subtitle: "發展、運作以及與資本主義的互動"
-author: "廖永賦$^1$"
+author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B04207003}"
 output:
@@
 開源社群是圍繞著開源軟體開發而形成的社群，其最引人注目的特徵在於開源社群的參與者無法透過銷售其所開發之軟體獲利，然開源社群卻持續穩定成長。研究指出開源社群的運作與社群成員動機、社群內的禮物交換之間的關係。此外，當代私人公司與開源社群的結合的現象日益明顯，開源社群的壯大與資本投入有直接關聯，而私人公司也受到開源社群的影響，顯示資本主義與開源社群理念之間的互動。
-
-$\\$  $\\$  $\\$ $\\$  [^1]
-
-[^1]: 系級：心理三  \ \ 學號：B04207003
 

### 2018-07-23 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 ---
+author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
 output:
@@
 
-# Beamer Slide (PDF)
+# Beamer Slide
 

### 2018-07-29 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 
+Common Syntax
+========
+
+## Branching
+
+### case
+```bash
+case "$var" in
+	pattern_1)
+		commands
+		;;
+	pattern_2)
+		commands
+		;;
+esac
+```
+
+### if
+```bash
+if [[ ]]; then
+	commands
+elif [[ ]]; then
+	commands
+else
+	commands
+fi
+```
+
+## Loops
+
+### for
+
+#### With Sequence of Numbers
+
+**Tradional Type**
+```bash
+for i in {1..3}; do
+	commands
+done
+```
+
+**C lang Type**
+```bash
+for (( i=0; i<=5; ++i )); do
+	commands
+done
+```
+
+#### Other Sequences
+
+```bash
+for i in A B C D; do
+	commands
+done
+```
+
+```bash
+for i in {A..D}{1..3}; do
+	commands
+done
+```
+
 Common Techniques
 ========
+
+## Parameter Expansions
+
+### Match the last expresion
+```{bash}
+> ~/Desktop/foo.txt
+file_path=~/Desktop/foo.txt
+echo ${file_path##*/}
+```
 

### 2018-07-29 post_source/quanteda-chinese/quanteda-tutorial.Rmd
up

---
link-citations: yes
bibliography: ref.bib
output:
  html_fragment:
    includes:
    number_sections: no
---

<!--yaml
---
layout: post
mermaid: true
mathjax2: false
mathjax: false
highlight: true
title: "Text Mining 前處理：中文、R 與 quanteda"
description: "因為中文的特性，使得中文 Text Mining 的前處理較為複雜。此文以 R, quanteda, jiebaR 進行部落格文章的前處理，提供一套中文文本前處理的架構。"
tags: [R, DS, bash, 中文]
---
yaml-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.dim = c(7, 4),
	message = FALSE,
	warning = FALSE,
	comment = "",
	out.width = "100%"
)
library(knitr)
```

中文 Text Mining 的前處理比起其它以拉丁字母為主的文本困難許多，參考資源也相對龐雜不全。
這裡以較晚近出現的[`quanteda`](https://quanteda.io/)套件為根據，依其需求進行中文文本前處理<!--more-->。

選擇 `quanteda`而非其它較流行的套件如`tm`的原因是因為其[多語言支持](https://github.com/quanteda/stopwords)較佳，譬如其內建的 tokenizer 能直接對中文進行斷詞。然而，由於 [`jieba`](https://github.com/fxsjy/jieba)的社群資源以及斷詞效果較佳，此文還是以[`jiebaR`](https://github.com/qinwf/jiebaR)進行斷詞。

此外，因為使用的語料是簡體字，這裡也提到簡體、繁體轉換處理的相關資源。
我希望這篇文章能整理出一套中文文本前處理的架構，試圖減輕未來可能遇到的問題。

## 流程

```{r echo=FALSE}
library(htmltools)
HTML('
<div class="mermaid">
graph LR
html("HTML")
html -.->|"rvest"| df0
subgraph 前處理
df1("斷詞 data_frame")
df0("data_frame")
df0 -.->|"<br>     jiebaR <br>   (保留標點)<br>"| df1
df1 -.->|"ropencc <br> 簡轉繁"| df1
end
corp("Corpus")
token("Tokens")
subgraph quanteda
df1 -.->|"quanteda <br> corpus()"| corp
corp -.->|"quanteda <br> tokenize()"| token
end
html -.- bls(" ")
style bls fill:none,stroke:none
style html fill:#ccbdb9
style df1 fill:#92ff7f
linkStyle 5 stroke-width:0px,fill:none;
</div>
')
```

## 資料爬取

這邊使用 [RStudio](https://www.rstudio.com/) 軟體工程師 [Yihui](https://yihui.name/en/about/)的[中文部落格](https://yihui.name/cn/)文章作為練習素材。首先需要取得文章的網址，因此先到部落格的文章列表頁面(https://yihui.name/cn/)，使用瀏覽器的[開發者工具](https://developers.google.com/web/tools/chrome-devtools/?hl=zh-tw)(按`Ctrl + Shift + I`開啟)進行**觀察**。

接著使用[`rvest`](https://github.com/hadley/rvest)套件擷取網頁中所有文章的連結，並將文章網址儲存成`list_of_post.txt`：
```{r}
library(dplyr)
library(rvest)

list_of_posts <- read_html("https://yihui.name/cn/") %>% 
    html_nodes(".archive") %>% # 列表在 div.archive 之下
    html_nodes("p") %>% # 文章標題在 <div> 下之 <p>
    html_nodes("a") %>% html_attr("href") # 文章連結在 <p> 下之 <a>

readr::write_lines(list_of_posts, "yihui/list_of_post.txt")
```

```{r}
head(list_of_posts, 2)
tail(list_of_posts, 2)
length(list_of_posts)
```

可以看到總共有 `r length(list_of_posts)` 篇文章，時間從 2005 年到今年七月都有發文的紀錄。

由於文章數量相當多，因此之後僅會下載部分文章，**避免造成伺服器負擔過大**。下載網頁時，可以在 R 中直接使用`rvest`(見下文**資料前處理**)，但我比較建議使用 Bash[^bash]的`wget`指令，才不會因為重複下載網頁造成伺服器負擔。

[^bash]: Mac 和 Linux 內建有 Bash，但 Windows 沒有。

在下載前，需先決定目標文章的網址`sub_list`：
```{r}
library(stringr)
set.seed(2018) # 設隨機種子 固定隨機函數的結果

idx <- str_detect(list_of_posts, "2018|2015|2010")
sub_list <- list_of_posts[idx]
sub_list <- sub_list[sample(seq_along(sub_list), 20)]  %>% # 抽出 20 篇
    str_replace_all(pattern = "^/", # 將站內連結改為完整 url
                    replacement = "https://yihui.name/") %>%
    str_replace_all(pattern = "/$", "/index.html")

readr::write_lines(sub_list, "yihui/sublist.txt")

# 給 Bash 用的
sub_list %>%
    str_replace_all("https://yihui.name/cn/", "") %>%
    str_replace_all("/index.html", "") %>%
    str_replace_all("/", "-") %>% 
    str_replace_all("-$", "") %>%
    readr::write_lines("yihui/sublist_name.txt")
```

### Bash 指令下載網頁

> 無法使用 bash 指令者，可跳過此節

為了自動化下載網頁，我寫了一個簡單的 Bash script `wget_list`，用法如下:

- `wget_list <網址文字檔> <檔名文字檔>`[^chmod]
    - `<網址文字檔>`： 每一列(row)由一個網址組成
    - `<檔名文字檔>`： 每一列由一個名稱組成，每個名稱與`<網址文字檔>`的網址對應

<!--FOOTNOTE START-->
[^chmod]: 要能直接執行`wget_list`需先給予其執行的權限，因此需設置`chmod 755 <path to wget_list>`，並且將`wget_list`置於 shell 會自動搜尋程式的地方(如`/usr/bin/`)。

    另一個方法是不設置權限，直接執行`wget_list`：  
    `bash <path to wget_list> <file1> <file2>`
<!--FOOTNOTE END-->

在這裡，執行下列指令即可下載網頁
```{bash eval=FALSE}
cd yihui/html
wget_list ../sublist.txt ../sublist_name.txt
cd -
```

**`wget_list`**:
```{bash eval=FALSE}
#!/bin/bash

#<<< wget_list: dowload webpages listed in a file >>>#
### Argument 1 is the file of links, 1 url per row   ###
### Argument 2 is the file of names, 1 name per row  ###

file1=$1
file2=$2

## Get the number of lines in the link list
num_lines=$(wc -l $file1 | egrep -o '^[0-9]*')

## loop over the lines in file1, dowload the the file & name them as listed in file2
for (( i=1; i<=${num_lines}; ++i )); do
     wget "$(sed -n ${i}p $file1)" \
         -O "$(sed -n ${i}p $file2)"
done
```

## 資料前處理

在清理資料之前，需先剖析網頁結構(就如同之前剖析文章列表頁面一樣)。
這邊觀察[這篇文章](https://yihui.name/cn/2015/11/peer-review/)，大致可以找出這些資訊：
```{r}
path <- "https://yihui.name/cn/2015/11/peer-review/"
all <- read_html(path) %>%
    html_nodes("article")
header <- all %>% html_nodes("header")

title <- header %>%      # 文章標題
    html_nodes("h1") %>% html_text()

post_date <- header %>%  # 發文日期
    html_node("h3") %>% html_text() %>%
    str_extract("201[0-9]-[0-9]{2}-[0-9]{2}")

article <- all %>%       # 內文
    html_nodes("p") %>% 
    html_text() %>% paste(collapse = "\n") 
    # 這裡將 chr vector collapse 至 1 個字串，
    # 簡化資料結構，並以分行符號保留段落資訊

num_sec <- all %>%      # 內文段落數
    html_nodes("p") %>% length

links <- all %>% html_nodes("p") %>% # 內文連結  
    html_nodes("a") %>% html_attr("href")
link_text <- all %>% html_nodes("p") %>% # 內文連結標題
    html_nodes("a") %>% html_text()
```

```{r}
library(tibble)
df <- data_frame(title = title,
           date = post_date,
           content = article,
           num_sec = num_sec,
           links = list(links),
           link_text = list(link_text)
           )
df %>%
    mutate(title = str_trunc(title, 8),
           content = str_trunc(content, 8),
           links = str_trunc(links, 8),
           link_text = str_trunc(link_text, 8)) %>%
    kable("markdown", align = "c")
```

我們可以將上面的程式碼改寫成函數`post_data()`，自動讀取文章並輸出 data frame：
```{r fc-post_data}
post_data <- function (path) {
    all <- read_html(path) %>%
        html_nodes("article")
    header <- all %>% html_nodes("header")

    title <- header %>%      # 文章標題
        html_nodes("h1") %>% html_text()

    post_date <- header %>%  # 發文日期
        html_node("h3") %>% html_text() %>%
        str_extract("201[0-9]-[0-9]{2}-[0-9]{2}")

    article <- all %>%       # 內文
        html_nodes("p") %>% 
        html_text() %>% paste(collapse = "\n")
        # 這裡將 chr vector collapse 至 1 個字串，
        # 簡化資料結構，並以分行符號保留段落資訊

    num_sec <- all %>%      # 內文段落數
        html_nodes("p") %>% length

    links <- all %>% html_nodes("p") %>% # 內文連結  
        html_nodes("a") %>% html_attr("href")
    link_text <- all %>%     # 內文連結標題
        html_nodes("p") %>% 
        html_nodes("a") %>% html_text()

    df <- tibble::data_frame(title = title,
                             date = post_date,
                             content = article,
                             num_sec = num_sec,
                             links = list(links),
                             link_text = list(link_text)
                             )
}
```

接著，將所有文章讀取至一個 data frame `all_post`：

```{r}
library(dplyr)
library(tidyr)

html_list <- list.files("yihui/html/") # 列出資料夾下的檔案
all_post <- vector("list", length(html_list))

for (i in seq_along(html_list)) {
    path <- paste0("yihui/html/", html_list[i])
    all_post[[i]] <- post_data(path)
}

all_post <- bind_rows(all_post) %>% arrange(desc(date))

head(all_post) %>%
    mutate(title = str_trunc(title, 8),
           content = str_trunc(content, 8),
           links = str_trunc(links, 8),
           link_text = str_trunc(link_text, 8)) %>%
    kable("markdown", align = "c")
```

### 直接從網路讀取

如果無法使用 Bash 指令下載網頁，可將上面程式碼的`html_list`改為讀取`sublist.txt`中的 url，並修改`for`迴圈中的`path`：

```{r eval=FALSE}
html_list <- read_lines("yihui/sublist.txt") # 讀取 url 
all_post <- vector("list", length(html_list))

for (i in seq_along(html_list)) {
    path <- html_list[i]
    all_post[[i]] <- post_data(path)
}

all_post <- bind_rows(all_post) %>% arrange(desc(date))
```

### 斷詞

在處理中文、日語等文本資料，需先經過斷詞處理，因為其不像英語等歐洲語言的文本，以空格表示字詞的界線。

我們將使用`jiebaR`套件的`segment()`進行斷詞。由`?segment()`查看其 documentation 可知**`segment()`只吃文字檔或 一個句子**，因此需先搞清楚`all_post`的結構才能進行斷詞：

`all_post`: 20*5 的`data_frame`，每列(row)為一篇文章
    - $title: 每列為 1 個值
    - $date: 每列為 1 個值
    - $content: 每列為 1 個值，段落資訊藏在字串中的`\n`符號
    - $links: 每列為 1 個 list
    - $link_text: 每列為 1 個 list

`all_post$content`的結構相當簡單(一篇文章一個字串)，因此不須經過額外處理。其它變項不須斷詞處理，因此在此不加細談。

#### jiebaR::segment (optional)

因為`all_post$content`簡單的結構符合`jiebaR`套件的預設需求，但有時資料會比較複雜，因此記錄下來供未來參考。

前面提到`jiebaR::segment`只吃一個句子(一個字串)或文字檔，那如果丟一個 vector 給它會怎樣？答案是看`worker()`的設定：
```{r}
library(jiebaR)
seg <- worker(symbol = T, bylines = F)
segment(c("妳很漂亮", "我不喜歡你"), seg)
```

```{r}
seg <- worker(symbol = T, bylines = T)
segment(c("妳很漂亮", "我不喜歡你"), seg)
```

1. `bylines = F`：回傳 1 個 chr vector，其每個元素為 1 個詞。

2. `bylines = T`：回傳 1 個 list，其長度(元素的數量)等於輸入之 vector 的長度，每個元素為一個 chr vector。

`bylines = F`的設定在此符合我們的需求，並且為配合`quanteda`套件的特性而將斷詞結果以一個字串(以空格分開字詞)而非一個 chr vector 的形式儲存。
以下**對第一篇文章進行斷詞**：
```{r}
library(jiebaR)
all_post_seg <- all_post
seg <- worker(symbol = T, bylines = F)

all_post_seg$content[1] <- all_post$content[1] %>%
    segment(seg) %>% paste(collapse = " ")

all_post$content[1] %>% str_trunc(20)
all_post_seg$content[1] %>% str_trunc(30)
```

要處理所有文章，僅需外包一個 for loop：
```{r}
all_post_seg <- all_post
seg <- worker(symbol = T, bylines = F)

idx <- seq_along(all_post$content)
for (i in idx){
    all_post_seg$content[i] <- all_post$content[i] %>%
        segment(seg) %>% paste(collapse = " ")
}

head(all_post$content, 3) %>% str_trunc(20)
head(all_post_seg$content, 3) %>% str_trunc(30)
```

### 簡轉繁

[OpenCC](https://github.com/BYVoid/OpenCC) 是一個簡體字與繁體字轉換的專案，非常優秀，因為其不僅是單純字轉字，甚至處理了地區性的用法(如「軟體」vs.「软件」)。因此，其簡繁轉換的選項有非常多：

* `s2t.json` Simplified Chinese to Traditional Chinese 簡體到繁體
* `t2s.json` Traditional Chinese to Simplified Chinese 繁體到簡體
* `s2tw.json` Simplified Chinese to Traditional Chinese (Taiwan Standard) 簡體到臺灣正體
* `tw2s.json` Traditional Chinese (Taiwan Standard) to Simplified Chinese 臺灣正體到簡體
* `s2hk.json` Simplified Chinese to Traditional Chinese (Hong Kong Standard) 簡體到香港繁體（香港小學學習字詞表標準）
* `hk2s.json` Traditional Chinese (Hong Kong Standard) to Simplified Chinese 香港繁體（香港小學學習字詞表標準）到簡體
* `s2twp.json` Simplified Chinese to Traditional Chinese (Taiwan Standard) with Taiwanese idiom 簡體到繁體（臺灣正體標準）並轉換爲臺灣常用詞彙
* `tw2sp.json` Traditional Chinese (Taiwan Standard) to Simplified Chinese with Mainland Chinese idiom 繁體（臺灣正體標準）到簡體並轉換爲中國大陸常用詞彙
* `t2tw.json` Traditional Chinese (OpenCC Standard) to Taiwan Standard 繁體（OpenCC 標準）到臺灣正體
* `t2hk.json` Traditional Chinese (OpenCC Standard) to Hong Kong Standard 繁體（OpenCC 標準）到香港繁體（香港小學學習字詞表標準）

[`ropencc`](https://github.com/qinwf/ropencc)套件是 OpenCC 的 R 語言接口，其不在 CRAN 上，需以`devtools`從 GitHub 下載：
```{r eval=FALSE}
devtools::install_github("qinwf/ropencc")
```

使用上非常容易：
```{r}
library(ropencc)
trans <- converter(TW2SP) # 臺灣用法轉大陸用法
run_convert(trans, "開放中文轉換軟體")

trans <- converter(T2S)   # 單純繁轉簡
run_convert(trans, "開放中文轉換軟體")

trans <- converter(S2TWP) # 簡轉臺灣用法
run_convert(trans, "开放中文转换软件")
```

在此我使用`S2TWP`轉換`$content`；`S2T`轉換`$title`：
```{r}
library(ropencc)
all_post_seg$content <- run_convert(converter(S2TWP),
                                    all_post_seg$content)
all_post_seg$title <- run_convert(converter(S2T),
                                  all_post_seg$title)

head(all_post_seg) %>%
    mutate(title = str_trunc(title, 8),
           content = str_trunc(content, 8),
           links = str_trunc(links, 8),
           link_text = str_trunc(link_text, 8)) %>%
    kable("markdown", align = "c")
```

## quanteda

我們前面進行的資料前處理，已經將資料整理成符合[`quanteda::corpus()`輸入的格式](https://tutorials.quanteda.io/basic-operations/corpus/corpus/)：

> A data frame consisting of a character vector for documents, and additional vectors for document-level variables

因此，依以下指令即可將`all_post_seg`轉換成`corpus`物件：
```{r}
library(quanteda)
corp <- corpus(all_post_seg, 
               docid_field = "title", 
               text_field = "content")

corp %>% summary() %>% as_data_frame() %>% 
    head(3) %>%
    mutate(links = str_trunc(links, 8),
           link_text = str_trunc(link_text, 8)) %>%
    kable("markdown", align = "c")
```

有了`corpus`的資料結構後，即進入了下圖`quanteda`的分析架構，也結束了資料前處理的階段，開始進入 EDA 的階段。

```{r echo=FALSE}
HTML('
<div class="mermaid">
    graph TD
    C(Corpus)
    token(Tokens)
    AP["Positional analysis"]
    AN["Non-positional analysis"]
    dfm(DFM)
    tidy("Tidy Text Format")
    vis("Visualize")
    C --> token 
    token --> dfm
    token -.-> AP
    dfm -.-> AN
    tidy -->|"cast_dfm()"| dfm
    dfm -->|"tidy()"| tidy
    dfm -.- vis
    tidy -.-> vis
    AP -.- vis
    style C stroke-width:0px,fill:#6bbcff
    style token stroke-width:0px,fill:#6bbcff
    style dfm stroke-width:0px,fill:#6bbcff
    style tidy stroke-width:0px,fill:orange
    linkStyle 6 stroke-width:0px,fill:none;
    linkStyle 8 stroke-width:0px,fill:none;
</div>
')
```

[quanteda](https://quanteda.io/) 有相當完整的[教學資源](https://tutorials.quanteda.io/)，且有很多有用的函數。同時，[`tidytext`](https://github.com/juliasilge/tidytext) 套件也能輕易與 `quanteda` 配合，在 `document-feature matrix` 與`tidytext`所提倡的 **tidy data frame**(one-token-per-document-per-row) 兩種資料結構間自由轉換。**tidy data frame** 的格式與[`ggplot2`](https://github.com/tidyverse/ggplot2)相吻合，有助於資料視覺化的進行。

這裡選擇以`quanteda`而非`tidytext`作為主要架構的原因在於`tidytext`的架構僅容許 **bag-of-words** 的架構，但`quanteda`除了 **bag-of-words** 之外，還保有** Positional analysis** 的潛力。

由於篇幅有限，這裡不多加細談`quanteda`套件[^future]。關於`quanteda`的使用，可以參考 [quanteda tutorial](https://tutorials.quanteda.io/)，內容非常詳盡。

[^future]: 未來可能會發一篇續作。

<p style="text-align:right;font-size:7px;margin-top:0px;margin-bottom:0px;padding-top:0px;padding-bottom:1px">
上次更新：`r Sys.Date()`
</p>

## 參考資料

---
nocite: |
  @*
...

### 2018-07-29 post_source/quanteda-chinese/quanteda-tutorial.Rmd
up

@@
 
-選擇 `quanteda`而非其它較流行的套件如`tm`的原因是因為其[多語言支持](https://github.com/quanteda/stopwords)較佳，譬如其內建的 tokenizer 能直接對中文進行斷詞。然而，由於 [`jieba`](https://github.com/fxsjy/jieba)的社群資源以及斷詞效果較佳，此文還是以[`jiebaR`](https://github.com/qinwf/jiebaR)進行斷詞。
+選擇`quanteda`而非其它較流行的套件如`tm`的原因是因為其[多語言支持](https://github.com/quanteda/stopwords)較佳，譬如其內建的 tokenizer 能[直接對中文進行斷詞](https://koheiw.net/?p=339)。然而，由於 [`jieba`](https://github.com/fxsjy/jieba)的社群資源以及斷詞效果較佳，此文還是以[`jiebaR`](https://github.com/qinwf/jiebaR)進行斷詞。
 
@@
 
+## Reproduce
+
+這篇文章的原始碼在我的 [GitHub](https://github.com/liao961120/local_depend/tree/master/post_source/quanteda-chinese)，歡迎下載至自己的電腦執行。
+
 <p style="text-align:right;font-size:7px;margin-top:0px;margin-bottom:0px;padding-top:0px;padding-bottom:1px">

### 2018-07-30 post_source/quanteda-chinese/quanteda-tutorial.Rmd
up

@@
 
-這邊使用 [RStudio](https://www.rstudio.com/) 軟體工程師 [Yihui](https://yihui.name/en/about/)的[中文部落格](https://yihui.name/cn/)文章作為練習素材。首先需要取得文章的網址，因此先到部落格的文章列表頁面(https://yihui.name/cn/)，使用瀏覽器的[開發者工具](https://developers.google.com/web/tools/chrome-devtools/?hl=zh-tw)(按`Ctrl + Shift + I`開啟)進行**觀察**。
+這邊使用 [RStudio](https://www.rstudio.com/) 軟體工程師 [Yihui](https://yihui.name/en/about/) 的[中文部落格](https://yihui.name/cn/)文章作為練習素材。首先需要取得文章的網址，因此先到部落格的文章列表頁面(https://yihui.name/cn/)，使用瀏覽器的[開發者工具](https://developers.google.com/web/tools/chrome-devtools/?hl=zh-tw)(按`Ctrl + Shift + I`開啟)進行**觀察**。
 
@@
 
-#### jiebaR::segment (optional)
+#### jiebaR::segment
 
@@
 
-這裡選擇以`quanteda`而非`tidytext`作為主要架構的原因在於`tidytext`的架構僅容許 **bag-of-words** 的架構，但`quanteda`除了 **bag-of-words** 之外，還保有** Positional analysis** 的潛力。
+這裡選擇以`quanteda`而非`tidytext`作為主要架構的原因在於`tidytext`的架構僅容許 **bag-of-words** 的架構，但`quanteda`除了 **bag-of-words** 之外，還保有 **Positional analysis** 的潛力。
 

### 2018-07-31 post_source/quanteda-chinese/quanteda-tutorial.R
up

@@ -1,0 +1,293 @@
+## ----setup, include=FALSE------------------------------------------------
+knitr::opts_chunk$set(
+	echo = TRUE,
+	fig.dim = c(7, 4),
+	message = FALSE,
+	warning = FALSE,
+	comment = "",
+	out.width = "100%"
+)
+library(knitr)
+
+## ----echo=FALSE----------------------------------------------------------
+library(htmltools)
+HTML('
+<div class="mermaid">
+graph LR
+html("HTML")
+html -.->|"rvest"| df0
+subgraph 前處理
+df1("斷詞 data_frame")
+df0("data_frame")
+df0 -.->|"<br>     jiebaR <br>   (保留標點)<br>"| df1
+df1 -.->|"ropencc <br> 簡轉繁"| df1
+end
+corp("Corpus")
+token("Tokens")
+subgraph quanteda
+df1 -.->|"quanteda <br> corpus()"| corp
+corp -.->|"quanteda <br> tokenize()"| token
+end
+html -.- bls(" ")
+style bls fill:none,stroke:none
+style html fill:#ccbdb9
+style df1 fill:#92ff7f
+linkStyle 5 stroke-width:0px,fill:none;
+</div>
+')
+
+## ------------------------------------------------------------------------
+library(dplyr)
+library(rvest)
+
+list_of_posts <- read_html("https://yihui.name/cn/") %>% 
+    html_nodes(".archive") %>% # 列表在 div.archive 之下
+    html_nodes("p") %>% # 文章標題在 <div> 下之 <p>
+    html_nodes("a") %>% html_attr("href") # 文章連結在 <p> 下之 <a> 
+
+readr::write_lines(list_of_posts, "yihui/list_of_post.txt")
+
+## ------------------------------------------------------------------------
+head(list_of_posts, 2)
+tail(list_of_posts, 2)
+length(list_of_posts)
+
+## ------------------------------------------------------------------------
+library(stringr)
+set.seed(2018) # 設隨機種子 固定隨機函數的結果
+
+idx <- str_detect(list_of_posts, "2018|2015|2010")
+sub_list <- list_of_posts[idx]
+sub_list <- sub_list[sample(seq_along(sub_list), 20)]  %>% # 抽出 20 篇
+    str_replace_all(pattern = "^/", # 將站內連結改為完整 url
+                    replacement = "https://yihui.name/") %>%
+    str_replace_all(pattern = "/$", "/index.html")
+
[…]

### 2018-07-31 post_source/quanteda-chinese/quanteda-tutorial.R
up

@@ -1,3 +1,6 @@
+### Source Code pulled from "quanteda-tutorial.Rmd" by  ###
+### purl("quanteda-tutorial.Rmd", documentation = 2L)   ###
+
 ## ----setup, include=FALSE------------------------------------------------
 knitr::opts_chunk$set(
 	echo = TRUE,

### 2018-07-31 post_source/jieba-dict/jieba-dict.rmd
up

---
link-citations: yes
output:
  html_fragment:
    includes:
    number_sections: no
---

<!--yaml
---
layout: post
mermaid: false
mathjax2: false
mathjax: false
highlight: true
title: "jieba：使用自訂詞庫斷詞"
description: ""
tags: [Text, Mining, R, 中文]
---
yaml-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.dim = c(7, 4),
	message = FALSE,
	warning = FALSE,
	comment = "",
	out.width = "100%"
)
library(knitr)
```

在進行中文 Text Mining 前處理時，必須先經過斷詞處理。社群當中存在相當好的斷詞處理工具，如 [jieba](https://github.com/fxsjy/jieba)。但斷詞時常遇到一個問題：**文本中重要的詞彙因為不常見於其它地方而被斷開，像是人物角色名稱**。要處理這個問題，需將自訂詞庫提供給斷詞套件，其才不會將重要詞彙斷開。
<!--more-->

這邊將使用 [jiebaR](https://github.com/qinwf/jiebaR)，介紹使用自訂詞庫的斷詞方式。同時也提供一種自訂詞庫的製作方式。

## 示範語料

這裡使用金庸**[神雕俠侶](https://zh.wikipedia.org/wiki/%E7%A5%9E%E9%B5%B0%E4%BF%A0%E4%BE%B6)第三十二回 --- 情是何物**作為斷詞的文本。武俠小說在此是個很好的例子，因為裡面有許多人物名稱和專有名詞。

## 維基百科角色列表

[神鵰俠侶角色列表](https://zh.wikipedia.org/wiki/%E7%A5%9E%E9%B5%B0%E4%BF%A0%E4%BE%B6%E8%A7%92%E8%89%B2%E5%88%97%E8%A1%A8)

```{r}
library(readr)
library(rvest)
library(stringr)
library(dplyr)
library(jiebaR)

data <- read_html("神鵰俠侶角色列表.html") %>%
    html_nodes("ul") %>% html_nodes("li") %>%
        html_nodes("a") %>% html_text()
```

```{r}
data <- unique(data)

data[1:3]
data[21:25]
data[207:211]
```

```{r}
data <- as_data_frame(data)
data <- data[43:548,] %>% unique()
data <- data[-c(2, 22, 128, 139,200:209),] %>% rbind("過兒")
write_csv(data, "sdxl_wordlist.csv")
```

<p style="text-align:right;font-size:8px;margin-top:0px; margin-bottom:0px;padding-top:0px;padding-bottom:0px">
上次更新：`r Sys.Date()`
</p>

### 2018-07-31 post_source/quanteda-chinese/quanteda-tutorial.Rmd
up

@@
 description: "因為中文的特性，使得中文 Text Mining 的前處理較為複雜。此文以 R, quanteda, jiebaR 進行部落格文章的前處理，提供一套中文文本前處理的架構。"
-tags: [R, DS, bash, 中文]
+tags: [Text Mining, R, bash, 中文]
 ---

### 2018-07-31 post_source/jieba-dict/jieba-dict.rmd
up

@@
 
+在此因為著作權問題[^right]，語料的原始檔(`032.txt`)將不會出現在本文的 [GitHub repo](https://github.com/liao961120/local_depend/tree/master/post_source/jieba-dict) 中。
+
+[^right]: 本文目的僅在促進教育與學術，並無營利導向。且本文僅顯示極少的小說內容，應在合理使用的範圍內。若有侵犯著作權的疑慮，麻煩透過 [Email](mailto:liaomovie2@gmail.com) 與我聯絡。
+
 ## 維基百科角色列表
@@
 ```
-
-<p style="text-align:right;font-size:8px;margin-top:0px; margin-bottom:0px;padding-top:0px;padding-bottom:0px">
-上次更新：`r Sys.Date()`
-</p>

### 2018-07-31 post_source/jieba-dict/jieba-dict.rmd
up

@@
 title: "jieba：使用自訂詞庫斷詞"
-description: ""
-tags: [Text, Mining, R, 中文]
+description: "提供自訂詞庫製作方式以及 jiebaR 自訂詞庫斷詞示範"
+tags: [Text Mining, R, 中文]
 ---
@@
 )
-library(knitr)
 ```
@@
 
-## 維基百科角色列表
+## 製作自訂詞庫
 
-[神鵰俠侶角色列表](https://zh.wikipedia.org/wiki/%E7%A5%9E%E9%B5%B0%E4%BF%A0%E4%BE%B6%E8%A7%92%E8%89%B2%E5%88%97%E8%A1%A8)
+取得小說這類文本的角色名稱與特殊名詞乍看之下可能非常耗工耗時，但有些時候其實相當容易，尤其是著名的小說。這要歸功於[維基百科](https://en.wikipedia.org/wiki/Main_Page)，因為越是著名的小說，其越有可能有詳盡的維基百科頁面，而**維基百科對製作詞庫最重要的特色在於其頁面的超連結**，因為通常只有**專有名詞才會成為一個維基頁面上的超連結**。
 
+這邊使用維基百科的[神鵰俠侶角色列表](https://zh.wikipedia.org/wiki/%E7%A5%9E%E9%B5%B0%E4%BF%A0%E4%BE%B6%E8%A7%92%E8%89%B2%E5%88%97%E8%A1%A8)作為詞庫的來源。以下使用`rvest`套件清理此頁面：
 ```{r}
-library(readr)
 library(rvest)
-library(stringr)
 library(dplyr)
-library(jiebaR)
+library(magrittr)
+library(knitr)
 
-data <- read_html("神鵰俠侶角色列表.html") %>%
+path <- "神鵰俠侶角色列表.html" 
+# 這裡已先行下載網頁，若無可直接使用網址
+
+data <- read_html(path) %>% 
     html_nodes("ul") %>% html_nodes("li") %>%
@@
 ```
+觀察頁面後，可發現多數與小說相關的詞彙都位在 unordered list 下的連結內文(<a> tag)，因此透過 3 個`html_nodes()`取得連結，並用`html_text()`擷取連結內文。
 
+接著看看擷取的詞彙，可以發現這些詞彙依照順序大致可區分成三個來源：
+
+1. 自維基頁面的**目錄**擷取之連結
+2. 內文的連結(這是我們要的)
+3. 其它連結
+    - 對應至頁面最下方，與小說有關但並非小說主要內容的連結，如，射鵰英雄。另外，也包含維基百科頁面的固定連結，如「編輯」、「討論」、「下載為PDF」等。
 ```{r}
@@
 
+我們要的內容介在`data[21]`(`r data[21]`)至`data[206]`(`r data[206]`)之間。此外，亦可手動加入連結中沒有的詞彙：
 ```{r}
-data <- as_data_frame(data)
-data <- data[43:548,] %>% unique()
-data <- data[-c(2, 22, 128, 139,200:209),] %>% rbind("過兒")
-write_csv(data, "sdxl_wordlist.csv")
+data <- as_data_frame(data[21:206]) %>% 
+    rbind("過兒", "靖哥哥") # 手動額外輸入
+
+head(data, 4) %>% kable("markdown", "c")
 ```
+
+最後，將`data`存成`.csv`檔，方便未來使用：
+```{r}
+readr::write_csv(data, "sdxl_wordlist.csv")
+```
+
+## jiebaR 斷詞
+
+jiebaR 斷詞可以選擇外來檔案或將檔案讀入後在進行斷詞，這邊將檔案讀入再斷詞：
+```{r}
+library(stringr)
+raw_text <- readr::read_file("032.txt")
+
+raw_text %>% str_trunc(80)
+```
+
+### 無自訂詞庫
+
+首先，我們可以看看沒有自訂詞庫的斷詞效果：
+```{r}
+library(jiebaR)
+stop_words <- readr::read_table2("stop-zh-tw-withpunc",
+                                 col_names = F) %>%
+                     rbind("\n", "\r") %>%
+                     set_names("word")
+
+seg <- worker(bylines = F, symbol = T)
+
+segment(raw_text, seg) %>%
+    as_data_frame() %>% 
+    anti_join(stop_words, by=c("value"="word")) %>%
+    count(value) %>%
+    arrange(desc(n)) %>%
+    head() %>% kable("markdown", align="c")
+```
+可以看到有些斷詞是正確的，如「公孫止」。但某些似乎常常斷錯，例如，「黃蓉」、「楊過」(某些似乎斷錯，導致有許多單獨的「楊」)。
+
+### 使用自訂詞庫
+
+在`jiebaR::worker()`中設定自訂詞庫的位置：`user="sdxl_wordlist.csv"`，即可在斷詞系統中新增字典：
+```{r}
+seg <- worker(bylines = F, symbol = T,
+              user="sdxl_wordlist.csv")
+
+segment(raw_text, seg) %>%
+    as_data_frame() %>% 
+    anti_join(stop_words, by=c("value"="word")) %>%
+    count(value) %>%
+    arrange(desc(n)) %>%
+    head() %>% kable("markdown", align="c")
+```
+
+可以看到使用自訂詞庫後，斷詞變得有意義多了。

### 2018-07-31 post_source/jieba-dict/jieba-dict.rmd
up

@@
 highlight: true
-title: "jieba：使用自訂詞庫斷詞"
+title: "jieba 自訂詞庫斷詞"
 description: "提供自訂詞庫製作方式以及 jiebaR 自訂詞庫斷詞示範"
@@
 
-在進行中文 Text Mining 前處理時，必須先經過斷詞處理。社群當中存在相當好的斷詞處理工具，如 [jieba](https://github.com/fxsjy/jieba)。但斷詞時常遇到一個問題：**文本中重要的詞彙因為不常見於其它地方而被斷開，像是人物角色名稱**。要處理這個問題，需將自訂詞庫提供給斷詞套件，其才不會將重要詞彙斷開。
+在進行中文 Text Mining 前處理時，必須先經過斷詞處理。社群當中存在相當好的斷詞處理工具，如 [jieba](https://github.com/fxsjy/jieba)。但斷詞時常遇到一個問題：**文本中重要的詞彙因為不常見於其它地方而被斷開，像是人物角色名稱**。要處理這個問題，需將自訂詞庫提供給斷詞套件，才不會將重要詞彙斷開。
 <!--more-->
 
-這邊將使用 [jiebaR](https://github.com/qinwf/jiebaR)，介紹使用自訂詞庫的斷詞方式。同時也提供一種自訂詞庫的製作方式。
+這邊將使用 [jiebaR](https://github.com/qinwf/jiebaR)，介紹使用自訂詞庫的斷詞方式，並提供自訂詞庫的製作方式。
 
@@
 
-在此因為著作權問題[^right]，語料的原始檔(`032.txt`)將不會出現在本文的 [GitHub repo](https://github.com/liao961120/local_depend/tree/master/post_source/jieba-dict) 中。
+因為著作權問題[^right]，語料的原始檔(`032.txt`)將不會出現在本文的 [GitHub repo](https://github.com/liao961120/local_depend/tree/master/post_source/jieba-dict) 中。
 
-[^right]: 本文目的僅在促進教育與學術，並無營利導向。且本文僅顯示極少的小說內容，應在合理使用的範圍內。若有侵犯著作權的疑慮，麻煩透過 [Email](mailto:liaomovie2@gmail.com) 與我聯絡。
+[^right]: 本文目的僅在促進教育與學術，並無營利企圖。且本文僅顯示極少的小說內容，應屬合理使用。若有侵犯著作權的疑慮，麻煩透過 [Email](mailto:liaomovie2@gmail.com) 與我聯絡。
 
@@
 ```
-觀察頁面後，可發現多數與小說相關的詞彙都位在 unordered list 下的連結內文(<a> tag)，因此透過 3 個`html_nodes()`取得連結，並用`html_text()`擷取連結內文。
+
+觀察頁面後，可發現多數與小說相關的詞彙都位在 unordered list 下的連結內文(\<a> tag)，因此透過 3 個`html_nodes()`取得連結，並用`html_text()`擷取連結內文。
 
@@
     - 對應至頁面最下方，與小說有關但並非小說主要內容的連結，如，射鵰英雄。另外，也包含維基百科頁面的固定連結，如「編輯」、「討論」、「下載為PDF」等。
+
 ```{r}
@@
 
-head(data, 4) %>% kable("markdown", "c")
+head(data, 4) %>% kable("markdown", align="c")
 ```
@@
 
-jiebaR 斷詞可以選擇外來檔案或將檔案讀入後在進行斷詞，這邊將檔案讀入再斷詞：
+準備好自訂詞庫後，要開始對文本進行斷詞。
+
+jiebaR 斷詞可以選擇外來檔案或將檔案讀入後在進行斷詞，這邊將文本檔案讀入再斷詞：
 ```{r}
@@
 
-在`jiebaR::worker()`中設定自訂詞庫的位置：`user="sdxl_wordlist.csv"`，即可在斷詞系統中新增字典：
+在`jiebaR::worker()`中設定自訂詞庫的位置：`user = "sdxl_wordlist.csv"`，即可在斷詞系統中新增字典：
 ```{r}
 seg <- worker(bylines = F, symbol = T,
-              user="sdxl_wordlist.csv")
+              user = "sdxl_wordlist.csv")
 

### 2018-08-02 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 
-```yaml
+```{yaml}
 ---
-title: "Rmarkdown Features"
+title: "R Markdown Features"
 subtitle: "A Compact Reference"
@@
 bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa-no-doi-no-issue.csl # APA style sheet
+csl: ./citation/apa.csl # APA style sheet
 link-citations: yes

### 2018-08-02 Ubuntu_16.04_setup/mybashrc_man.sh

@@ -30,4 +30,4 @@ alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybash
 
 
 
-#### Backup Time	Tue Jul 24 23:55:46 CST 2018 ####
+#### Backup Time	Thu Aug  2 12:22:37 CST 2018 ####

### 2018-08-02 post_source/quanteda-chinese/quanteda-tutorial.R

@@ -1,296 +1,0 @@
-### Source Code pulled from "quanteda-tutorial.Rmd" by  ###
-### purl("quanteda-tutorial.Rmd", documentation = 2L)   ###
-
-## ----setup, include=FALSE------------------------------------------------
-knitr::opts_chunk$set(
-	echo = TRUE,
-	fig.dim = c(7, 4),
-	message = FALSE,
-	warning = FALSE,
-	comment = "",
-	out.width = "100%"
-)
-library(knitr)
-
-## ----echo=FALSE----------------------------------------------------------
-library(htmltools)
-HTML('
-<div class="mermaid">
-graph LR
-html("HTML")
-html -.->|"rvest"| df0
-subgraph 前處理
-df1("斷詞 data_frame")
-df0("data_frame")
-df0 -.->|"<br>     jiebaR <br>   (保留標點)<br>"| df1
-df1 -.->|"ropencc <br> 簡轉繁"| df1
-end
-corp("Corpus")
-token("Tokens")
-subgraph quanteda
-df1 -.->|"quanteda <br> corpus()"| corp
-corp -.->|"quanteda <br> tokenize()"| token
-end
-html -.- bls(" ")
-style bls fill:none,stroke:none
-style html fill:#ccbdb9
-style df1 fill:#92ff7f
-linkStyle 5 stroke-width:0px,fill:none;
-</div>
-')
-
-## ------------------------------------------------------------------------
-library(dplyr)
-library(rvest)
-
-list_of_posts <- read_html("https://yihui.name/cn/") %>% 
-    html_nodes(".archive") %>% # 列表在 div.archive 之下
-    html_nodes("p") %>% # 文章標題在 <div> 下之 <p>
-    html_nodes("a") %>% html_attr("href") # 文章連結在 <p> 下之 <a> 
-
-readr::write_lines(list_of_posts, "yihui/list_of_post.txt")
-
-## ------------------------------------------------------------------------
-head(list_of_posts, 2)
-tail(list_of_posts, 2)
-length(list_of_posts)
-
-## ------------------------------------------------------------------------
-library(stringr)
-set.seed(2018) # 設隨機種子 固定隨機函數的結果
-
-idx <- str_detect(list_of_posts, "2018|2015|2010")
-sub_list <- list_of_posts[idx]
-sub_list <- sub_list[sample(seq_along(sub_list), 20)]  %>% # 抽出 20 篇
[…]

### 2018-08-02 post_source/quanteda-chinese/rvest.R

@@ -1,13 +1,0 @@
-library(rvest)
-
-post_list <- read_html("https://yihui.name/cn/") %>% 
-    html_nodes(".archive") %>% 
-    html_nodes("p") %>% 
-    html_nodes("a") %>% html_attr("href")
-
-
-all <- read_html("index.html") %>% html_nodes("article") 
-title <- all %>% html_nodes("h1")
-text <- all %>% html_nodes("p")
-links <- all %>% html_nodes("a") %>% html_attr("href")
-

### 2018-08-12 Ubuntu_16.04_setup/mybashrc.sh
up

@@ -1,28 +1,0 @@
-alias app_link='xdg-open /usr/share/applications/'
-alias dict='goldendict'
-alias r='Rscript -e' #Note capital 'R' is for running R in bash
-alias render_rmdbk='~/bin/render_rmarkdown_book'
-alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
-alias new_rmd='~/bin/append_head_rmd'
-alias R='R --no-save -q'
-
-export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
-PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
-export PS1
-export PATH=~/bin:"$PATH"  #Add ~/bin to PATH so custom shell programs can be found
-
-# Define variables for SSH remote pc.
-### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
-
-rm_MAC="44:87:fc:a1:0b:cc" #MAC address of remote pc
-rm_ip="`head -1 ~/local_depend/hostname/hostname.txt`" #Now floating IP, needs to change to static
-rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
-ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
-
-
-# Backup ~/bin (Custom shell programs)
-cp -r ~/bin/* ~/local_depend/Ubuntu_16.04_setup/sh_program_bak/
-
-# Backup self-defined cmd in git repo (prt lines after 'line 120')
-tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
-alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'

### 2018-08-12 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
   bookdown::html_document2:
-    highlight: haddock
     css: /home/liao/local_depend/style_sheets/style.css
@@
 ```
+
+RegEx
+========
+
+**MetaCharacters**
+
+- `.`: Any character.
+
+- `+`: **1 or more**, e.g. `s+aa` matches 1 or more `s` followed by `aa`.
+
+- `*`: **0 or more**, e.g. `s*aa` matches 0 or more `s` followed by `aa`.
+
+- `{#}`: **Exact #**, e.g. `s{2}` matches strings with exactly 2 `s`(equivalent to `ss`).
+	- `{#_1, #_2}`: **Between #_1 & #_2**.
+
+- `(<some.char>)`: Use `(` & `)` to **group**
+	- `(na){2}`: matches ba**nana**.
 

### 2018-08-12 Ubuntu_16.04_setup/mybashrc.sh

@@ -1,0 +1,28 @@
+alias app_link='xdg-open /usr/share/applications/'
+alias dict='goldendict'
+alias r='Rscript -e' #Note capital 'R' is for running R in bash
+alias render_rmdbk='~/bin/render_rmarkdown_book'
+alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
+alias new_rmd='~/bin/append_head_rmd'
+alias R='R --no-save -q'
+
+export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
+PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
+export PS1
+export PATH=~/bin:"$PATH"  #Add ~/bin to PATH so custom shell programs can be found
+
+# Define variables for SSH remote pc.
+### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###
+
+rm_MAC="44:87:fc:a1:0b:cc" #MAC address of remote pc
+rm_ip="`head -1 ~/local_depend/hostname/hostname.txt`" #Now floating IP, needs to change to static
+rm_ip_b=`bash ~/ip2ipb.sh $rm_ip` #see 'ip2ipb.sh for detail'
+ssh_pc="liao961120@$rm_ip"  #used as 'ssh $ssh_pc'
+
+
+# Backup ~/bin (Custom shell programs)
+cp -r ~/bin/* ~/local_depend/Ubuntu_16.04_setup/sh_program_bak/
+
+# Backup self-defined cmd in git repo (prt lines after 'line 120')
+tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
+alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'

### 2018-08-24 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
 author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %d, %Y')`"
+date: "`r format(Sys.Date(), '%B %e, %Y')`"
 bibliography: /home/liao/local_depend/citation/neanderthals.bib
@@
 )
-str_date <- "`r format(Sys.Date(), '%B %d, %Y')`"
+str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
 ```
@@
 author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r str_date`"
+date: "`r format(Sys.Date(), '%B %e, %Y')`" 
 bibliography: /home/liao/local_depend/citation/neanderthals.bib

### 2018-10-10 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
   bookdown::html_document2:
-    code_folding: show
     css: /home/liao/local_depend/style_sheets/style.css
@@
 options(digits = 2) # auto round to 2 decimals when printed
+```
+
+# Child Documents
+
+It is possible to write R Markdown in separated files and combine them together before knitting to the output file. See [knitr documentation](https://yihui.name/knitr/) for more info.
+
+## Usage
+
+`main.Rmd`:
+
+    ---
+    title: "This is Title"
+    author: "Yongfu Liao"
+    output: html_document
+    ---
+
+    `r ''````{r setup}
+    options(knitr.duplicate.label = 'allow')
+    ```
+
+    `r ''````{r child="part1.Rmd"}
+    ```
+
+    `r ''````{r child="part2.Rmd"}
+    ```
+
+The skeleton file that combines several R Markdown files. Only this file is rendered, other R Markdown files will automatically be inserted in the knitting process.
+
+To avoid code chunks having the same labels, set the option below in `setup` code chunk of `main.Rmd`.
+
+```r
+options(knitr.duplicate.label = 'allow')
+```
+
+# Conditional Compilation
+
+```{r eval=FALSE}
+if (knitr::is_html_output()) {
+  ...
+}
+
+if (knitr::opts_knit$get('rmarkdown.pandoc.to') == "latex")
+  ...
+}
 ```
@@
 
+# Xaringan (remark.js Slide)
+
+Xaringan is a HTML presentation output format of R Markdown.
+Xaringan doesn't support Pandoc markdown, but is very flexible and easy to use if having basic CSS knowledge.
+It also prints well on PDF (using Chrome or [decktape](https://github.com/astefanutti/decktape)).
+Read the [Chapter 7](https://bookdown.org/yihui/rmarkdown/xaringan.html) of *R Markdown Guide* for more details.
+
+<iframe src="https://liao961120.github.io/slides/xaringan/index.html", width=400, height=301>
+</iframe>  
+[Slide Link](https://liao961120.github.io/slides/xaringan/index.html)
+
 # Beamer Slide

### 2018-10-11 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 fi
+```
+
+#### pipe
+
+```bash
+[ -f <file-name> ] && <command>
+[ -d <dir-name> ] || <command>
 ```
@@
 	- `(na){2}`: matches ba**nana**.
+
+String Manipulation
+========
+
+## cut
+
+`list.txt`:
+```
+10/04 2018,xaringan
+09/28 2018,pttR-intro
+```
+
+Read one line of `list.txt` in each loop,
+cut the line into 2 fields, seperated by `,`.
+```bash
+while read p; do
+  date=$(echo "$p" | cut -d ',' -f 1)
+  file=$(echo "$p" | cut -d ',' -f 2)
+done < list.txt
+```
+
+## printf
+
+More consistent then `echo`, 
+can use special characters like `\\n`.
+```bash
+printf "$date &nbsp;&nbsp; [$file](${file}/index.html)\n\n"
+```
+
+## cat
+
+`cat` the text between the two `_EOF_`.
+```bash
+cat << _EOF_
+---
+title: Slides
+---
+
+# List of Slides
+<br><br>
+_EOF_
+```
+
+`cat` the text between the two `_EOF_`, then **redirect the text to `index.md`**.
+```bash
+cat >> index.md  << _EOF_
+---
+title: Slides
+---
+
+# List of Slides
+<br><br>
+_EOF_
+```
 

### 2018-10-11 Ubuntu_16.04_setup/Program_Sci/PsychoPy_1.90.sh

@@ -1,0 +1,7 @@
+## PsychoPy Installation (Ubuntu 18.04)
+
+# sudo apt-get install libgtk-3-dev
+
+pip3 install -U -f https://extras.wxpython.org/wxPython4/extras/linux/gtk3/ubuntu-18.04 wxPython
+
+pip3 install PsychoPy

### 2018-10-11 Ubuntu_16.04_setup/Program_Sci/R_setup_ubuntu_16.04.sh

@@ -1,0 +1,42 @@
+######### Install R + RStudio on Ubuntu 16.04 ###############
+
+#sudo apt-key adv --keyserver keyserver.ubuntu.com --recv-keys E084DAB9
+
+# Ubuntu 12.04: precise
+# Ubuntu 14.04: trusty
+# Ubuntu 16.04: xenial
+
+# /etc/apt/sources.list
+# Basic format of next line deb https://<my.favorite.cran.mirror>/bin/linux/ubuntu <enter your ubuntu version>/
+# Use Rstudio mirror
+
+sudo add-apt-repository 'deb https://cloud.r-project.org/bin/linux/ubuntu xenial/'
+
+
+### On Ubuntu 18.04, skip steps above (5/20 2018)
+sudo apt-get update
+sudo apt-get install r-base
+sudo apt-get install r-base-dev
+
+
+### Install Rstudio with GUI method
+
+# Download and Install RStudio from
+# https://download1.rstudio.org/rstudio-xenial-1.1.447-amd64.deb
+#sudo apt-get install gdebi-core
+#wget https://download1.rstudio.org/rstudio-xenial-1.1.447-amd64.deb
+#sudo gdebi rstudio-xenial-1.1.447-amd64.deb
+#rm rstudio-xenial-1.1.447-amd64.deb
+
+
+######### Install pdflatex (for knitting PDF_documents) ###########
+
+sudo apt-get install texlive-latex-base
+
+## additional packages
+sudo apt-get install texlive-fonts-recommended
+#sudo apt-get install texlive-fonts-extra
+#sudo apt-get install texlive-latex-extra
+
+sudo apt-get install texlive-xetex # xelatex engine
+sudo apt-get install texlive-lang-chinese # for chinese

### 2018-10-11 Ubuntu_16.04_setup/Program_Sci/pulse_secure.sh

@@ -1,0 +1,16 @@
+#https://gist.github.com/tafarij/e92755c7b5d853241c3f0790e2786c65
+
+#wget http://ccnet.ntu.edu.tw/vpn/Download/ps-pulse-linux-5.3r4.2-b639-ubuntu-debian-64-bit-installer.deb
+
+#sudo dpkg –i ps-pulse-linux-5.3r4.2-b639-ubuntu-debian-64-bit-installer.deb
+
+#/usr/local/pulse/PulseClient_x86_64.sh install_dependency_packages
+
+## 32 bit
+wget https://secure.nis.vt.edu/resources/downloads/pulse-8.2R5.i386.deb
+sudo dpkg -i pulse-8.2R5.i386.deb
+/usr/local/pulse/PulseClient.sh install_dependency_packages
+#sudo apt-get install libwebkitgtk-1.0-0
+
+#sudo apt-get update
+

### 2018-10-11 Ubuntu_16.04_setup/R_setup_ubuntu_16.04.sh

@@ -1,42 +1,0 @@
-######### Install R + RStudio on Ubuntu 16.04 ###############
-
-#sudo apt-key adv --keyserver keyserver.ubuntu.com --recv-keys E084DAB9
-
-# Ubuntu 12.04: precise
-# Ubuntu 14.04: trusty
-# Ubuntu 16.04: xenial
-
-# /etc/apt/sources.list
-# Basic format of next line deb https://<my.favorite.cran.mirror>/bin/linux/ubuntu <enter your ubuntu version>/
-# Use Rstudio mirror
-
-sudo add-apt-repository 'deb https://cloud.r-project.org/bin/linux/ubuntu xenial/'
-
-
-### On Ubuntu 18.04, skip steps above (5/20 2018)
-sudo apt-get update
-sudo apt-get install r-base
-sudo apt-get install r-base-dev
-
-
-### Install Rstudio with GUI method
-
-# Download and Install RStudio from
-# https://download1.rstudio.org/rstudio-xenial-1.1.447-amd64.deb
-#sudo apt-get install gdebi-core
-#wget https://download1.rstudio.org/rstudio-xenial-1.1.447-amd64.deb
-#sudo gdebi rstudio-xenial-1.1.447-amd64.deb
-#rm rstudio-xenial-1.1.447-amd64.deb
-
-
-######### Install pdflatex (for knitting PDF_documents) ###########
-
-sudo apt-get install texlive-latex-base
-
-## additional packages
-sudo apt-get install texlive-fonts-recommended
-#sudo apt-get install texlive-fonts-extra
-#sudo apt-get install texlive-latex-extra
-
-sudo apt-get install texlive-xetex # xelatex engine
-sudo apt-get install texlive-lang-chinese # for chinese

### 2018-10-11 Ubuntu_16.04_setup/Writing/ghostwriter.sh

@@ -1,0 +1,3 @@
+sudo add-apt-repository ppa:wereturtle/ppa
+sudo apt-get update
+sudo apt-get install ghostwriter

### 2018-10-11 Ubuntu_16.04_setup/Zotero.sh

@@ -1,5 +1,0 @@
-# https://github.com/smathot/zotero_installer
-
-sudo add-apt-repository ppa:smathot/cogscinl
-sudo apt-get update
-sudo apt-get install zotero-standalone

### 2018-10-11 Ubuntu_16.04_setup/ghostwriter.sh

@@ -1,3 +1,0 @@
-sudo add-apt-repository ppa:wereturtle/ppa
-sudo apt-get update
-sudo apt-get install ghostwriter

### 2018-10-11 Ubuntu_16.04_setup/mybashrc.sh

@@ -2,7 +2,7 @@ alias app_link='xdg-open /usr/share/applications/'
 alias dict='goldendict'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
 alias render_rmdbk='~/bin/render_rmarkdown_book'
-alias rmdbk='vim ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
+alias rmdbk='code ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
 alias new_rmd='~/bin/append_head_rmd'
 alias R='R --no-save -q'
 

### 2018-10-11 Ubuntu_16.04_setup/pulse_secure.sh

@@ -1,16 +1,0 @@
-#https://gist.github.com/tafarij/e92755c7b5d853241c3f0790e2786c65
-
-#wget http://ccnet.ntu.edu.tw/vpn/Download/ps-pulse-linux-5.3r4.2-b639-ubuntu-debian-64-bit-installer.deb
-
-#sudo dpkg –i ps-pulse-linux-5.3r4.2-b639-ubuntu-debian-64-bit-installer.deb
-
-#/usr/local/pulse/PulseClient_x86_64.sh install_dependency_packages
-
-## 32 bit
-wget https://secure.nis.vt.edu/resources/downloads/pulse-8.2R5.i386.deb
-sudo dpkg -i pulse-8.2R5.i386.deb
-/usr/local/pulse/PulseClient.sh install_dependency_packages
-#sudo apt-get install libwebkitgtk-1.0-0
-
-#sudo apt-get update
-

### 2018-10-11 Ubuntu_16.04_setup/sh_program_bak/web-search-nav/background.js

@@ -1,0 +1,10 @@
+const browser = this.chrome && chrome.runtime ? chrome : this.browser;
+
+browser.runtime.onMessage.addListener((request, sender, sendResponse) => {
+  if (request.type === 'tabsCreate') {
+    browser.tabs.create({
+      url: request.options.url,
+      active: request.options.active
+    });
+  }
+});

### 2018-10-11 Ubuntu_16.04_setup/sh_program_bak/web-search-nav/extension.js

@@ -1,0 +1,76 @@
+// noinspection JSUnusedGlobalSymbols
+const browser = this.chrome && chrome.runtime ? chrome : this.browser;
+
+const extension = {
+  options: {
+    sync: new OptionSection(browser.storage.sync, {
+      wrapNavigation: false,
+      autoSelectFirst: true,
+      nextKey: 'down, j',
+      previousKey: 'up, k',
+      navigatePreviousResultPage: 'left, h',
+      navigateNextResultPage: 'right, l',
+      navigateKey: 'return, space',
+      navigateNewTabBackgroundKey: 'ctrl+return, command+return, ctrl+space',
+      navigateNewTabKey:
+        'ctrl+shift+return, command+shift+return, ctrl+shift+space',
+      navigateSearchTab: 'a, s',
+      navigateImagesTab: 'i',
+      navigateVideosTab: 'v',
+      navigateMapsTab: 'm',
+      navigateNewsTab: 'n',
+      navigateShoppingTab: 'alt+s',
+      navigateBooksTab: 'b',
+      navigateFlightsTab: 'alt+l',
+      navigateFinancialTab: 'f',
+      focusSearchInput: '/, escape',
+      navigateShowAll: 'ctrl+shift+a',
+      navigateShowHour: 'ctrl+shift+h',
+      navigateShowDay: 'ctrl+shift+d',
+      navigateShowWeek: 'ctrl+shift+w',
+      navigateShowMonth: 'ctrl+shift+m',
+      navigateShowYear: 'ctrl+shift+y',
+      toggleSort: 'ctrl+shift+s'
+    }),
+
+    local: new OptionSection(browser.storage.local, {
+      lastQueryUrl: null,
+      lastFocusedIndex: 0
+    }),
+
+    load() {
+      return Promise.all([this.local.load(), this.sync.load()]);
+    }
+  }
+};
+
+/**
+ * @param {StorageArea} storage The storage area to which this section will write.
+ * @param {Object} defaultValues The default options.
+ * @constructor
+ */
+function OptionSection(storage, defaultValues) {
+  this.storage = storage;
+  this.values = defaultValues;
+  this.load = function() {
+    return new Promise(resolve => {
+      this.storage.get(this.values, values => {
+        if (!browser.runtime.lastError) {
+          this.values = values;
+        }
+        resolve();
+      });
+    });
+  };
+  this.save = function() {
+    return new Promise((resolve, reject) => {
+      this.storage.set(this.values, () => {
[…]

### 2018-10-11 Ubuntu_16.04_setup/sh_program_bak/web-search-nav/keymaster.js

@@ -1,0 +1,77 @@
+//     keymaster.js
+//     (c) 2011-2013 Thomas Fuchs
+//     keymaster.js may be freely distributed under the MIT license.
+!function(n){var f,c={},u={16:!1,18:!1,17:!1,91:!1},t="all",
+// modifier keys
+a={"⇧":16,shift:16,"⌥":18,alt:18,option:18,"⌃":17,ctrl:17,control:17,"⌘":91,command:91},
+// special keys
+o={backspace:8,tab:9,clear:12,enter:13,return:13,esc:27,escape:27,space:32,left:37,up:38,right:39,down:40,del:46,delete:46,home:36,end:35,pageup:33,pagedown:34,",":188,".":190,"/":191,"`":192,"-":189,"=":187,";":186,"'":222,"[":219,"]":221,"\\":220},s=function(e){return o[e]||e.toUpperCase().charCodeAt(0)},d=[];for(f=1;f<20;f++)o["f"+f]=111+f;
+// IE doesn't support Array#indexOf, so have a simple replacement
+function p(e,n){for(var t=e.length;t--;)if(e[t]===n)return t;return-1}
+// for comparing mods before unassignment
+function h(e,n){if(e.length!=n.length)return!1;for(var t=0;t<e.length;t++)if(e[t]!==n[t])return!1;return!0}var g={16:"shiftKey",18:"altKey",17:"ctrlKey",91:"metaKey"};
+// handle keydown event
+function r(e){var n,t,o,r,i,l;// right command on webkit, command on Gecko
+if(n=e.keyCode,-1==p(d,n)&&d.push(n),
+// if a modifier key, set the key.<modifierkeyname> property to true and return
+93!=n&&224!=n||(n=91),n in u)
+// 'assignKey' from inside this closure is exported to window.key
+for(o in u[n]=!0,a)a[o]==n&&(v[o]=!0);else
+// see if we need to ignore the keypress (filter() can can be overridden)
+// by default ignore key presses if a select, textarea, or input is focused
+if(function(e){for(f in u)u[f]=e[g[f]]}(e),v.filter.call(this,e)&&n in c)
+// for each potential shortcut
+for(l=y(),r=0;r<c[n].length;r++)
+// see if it's in the current scope
+if((t=c[n][r]).scope==l||"all"==t.scope){for(o in
+// check if modifiers match if any
+i=0<t.mods.length,u)(!u[o]&&-1<p(t.mods,+o)||u[o]&&-1==p(t.mods,+o))&&(i=!1);
[…]

### 2018-10-11 Ubuntu_16.04_setup/sh_program_bak/web-search-nav/main.js

@@ -1,0 +1,272 @@
+Object.assign(extension, {
+  init() {
+    if (!/^(www|encrypted)\.google\./.test(window.location.hostname)) {
+      return;
+    }
+    const loadOptions = this.options.load();
+    // Don't initialize results navigation on image search, since it doesn't work
+    // there.
+    if (!/[?&]tbm=isch(&|$)/.test(location.search)) {
+      // This file is loaded only after the DOM is ready, so no need to wait for
+      // DOMContentLoaded.
+      loadOptions.then(() => this.initResultsNavigation());
+    }
+    loadOptions.then(() => this.initCommonGoogleSearchNavigation());
+  },
+
+  changeTools(period) {
+    // Save current period and sort.
+    const res = /&(tbs=qdr:.)(,sbd:.)?/.exec(location.href);
+    const currPeriod = (res && res[1]) || '';
+    const currSort = (res && res[2]) || '';
+    // Remove old period and sort.
+    const strippedHref = location.href.replace(/&tbs=qdr:.(,sbd:.)?/, '');
+    if (period) {
+      location.href =
+        strippedHref + (period === 'a' ? '' : '&tbs=qdr:' + period + currSort);
+    } else if (currPeriod) {
+      // Can't apply sort when not using period.
+      location.href =
+        strippedHref + '&' + currPeriod + (currSort ? '' : ',sbd:1');
+    }
+  },
+
+  initResultsNavigation() {
+    const options = this.options.sync.values;
+    const lastNavigation = this.options.local.values;
+    const results = getGoogleSearchLinks();
+    let isFirstNavigation = true;
+    if (options.autoSelectFirst) {
+      // Highlight the first result when the page is loaded, but don't scroll to
+      // it because there may be KP cards such as stock graphs.
+      results.focus(0, false);
+    }
+    if (location.href === lastNavigation.lastQueryUrl) {
+      isFirstNavigation = false;
+      results.focus(lastNavigation.lastFocusedIndex);
+    }
+    this.register(options.nextKey, () => {
+      if (!options.autoSelectFirst && isFirstNavigation) {
+        results.focus(0);
+        isFirstNavigation = false;
+      } else {
+        results.focusNext(options.wrapNavigation);
+      }
+    });
+    this.register(options.previousKey, () => {
+      if (!options.autoSelectFirst && isFirstNavigation) {
+        results.focus(0);
+        isFirstNavigation = false;
+      } else {
[…]

### 2018-10-11 Ubuntu_16.04_setup/sh_program_bak/web-search-nav/options.js

@@ -1,0 +1,111 @@
+// Based on https://developer.chrome.com/extensions/optionsV2
+
+const flashMessage = message => {
+  // Update status to let user know.
+  const status = document.getElementById('status');
+  status.textContent = message;
+  setTimeout(function() {
+    status.textContent = '';
+  }, 3000);
+};
+
+// Saves options to chrome.storage.sync.
+const saveOptions = () => {
+  const values = {
+    wrapNavigation: document.getElementById('wrap-navigation').checked,
+    autoSelectFirst: document.getElementById('auto-select-first').checked,
+    nextKey: document.getElementById('next-key').value,
+    previousKey: document.getElementById('previous-key').value,
+    navigatePreviousResultPage: document.getElementById(
+      'navigate-previous-result-page'
+    ).value,
+    navigateNextResultPage: document.getElementById('navigate-next-result-page')
+      .value,
+    navigateKey: document.getElementById('navigate-key').value,
+    navigateNewTabKey: document.getElementById('navigate-new-tab-key').value,
+    navigateNewTabBackgroundKey: document.getElementById(
+      'navigate-new-tab-background-key'
+    ).value,
+    navigateSearchTab: document.getElementById('navigate-search-tab').value,
+    navigateImagesTab: document.getElementById('navigate-images-tab').value,
+    navigateVideosTab: document.getElementById('navigate-videos-tab').value,
+    navigateMapsTab: document.getElementById('navigate-maps-tab').value,
+    navigateNewsTab: document.getElementById('navigate-news-tab').value,
+    navigateShoppingTab: document.getElementById('navigate-shopping-tab').value,
+    navigateBooksTab: document.getElementById('navigate-books-tab').value,
+    navigateFlightsTab: document.getElementById('navigate-flights-tab').value,
+    navigateFinancialTab: document.getElementById('navigate-financial-tab')
+      .value,
+    focusSearchInput: document.getElementById('focus-search-input').value,
+    navigateShowAll: document.getElementById('navigate-show-all').value,
+    navigateShowHour: document.getElementById('navigate-show-hour').value,
+    navigateShowDay: document.getElementById('navigate-show-day').value,
+    navigateShowWeek: document.getElementById('navigate-show-week').value,
+    navigateShowMonth: document.getElementById('navigate-show-month').value,
+    navigateShowYear: document.getElementById('navigate-show-year').value,
+    toggleSort: document.getElementById('toggle-sort').value
+  };
+  for (let key in values) {
[…]

### 2018-10-15 GitHubPage/my_R_book/Rmarkdown_features/00-yaml.rmd
restructure rmdbk

--- 2018-08-24 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
@@
   bookdown::html_document2:
-    code_folding: show
-    css: /home/liao/local_depend/style_sheets/style.css
+    css: style.css
     df_print: kable
@@
 
-## yaml of this Doc {-}
+## yaml {-}
 
@@
 
-## HTML Output {-}
+## HTML {-}
 
@@
 
-## PDF Output {-}
+## PDF {-}
 
@@
 urlcolor: "blue"
+linestretch: 1.5
 fontsize: 12pt 
@@
 
-## PDF Output2 {-}
+## PDF 2 {-}
 This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
@@
 always_allow_html: yes
+linestretch: 1.5
 ---
@@
 
-```{tex}
-%加這個就可以設定字體
-\usepackage{fontspec}
-%使用xeCJK，其他的還有CJK或是xCJK
-\usepackage{xeCJK}
+```tex
+`r paste(readLines("~/local_depend/style_sheets/header.tex"), collapse = '\n')`
+```
 
-\usepackage[fontsize=13pt]{scrextend}
+## PDF: template {- #pdf-template}
 
-%設定英文字型，不設的話就會使用預設的字型
-\setmainfont{Calibri}
+```markdown
+output:
+  pdf_document:
+    template: two-col.latex
+    includes:
+      in_header: header.tex
+```
 
-%設定中英文的字型
-%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
-% AR PL KaitiM Big5 標楷體
-% .PingFang TC
-% Noto Sans CJK TC
-\setCJKmainfont{AR PL KaitiM Big5}
+It is possible to define [custom latex template](https://rmarkdown.rstudio.com/pdf_document_format#custom_templates).
+For example, [`two-col.latex`](https://github.com/liao961120/local_depend/blob/master/style_sheets/two-col.latex) is created by putting the variable `body` (which is the rendered content of the Rmd file) inside `multicols` latex extension:
 
-%中文自動換行
-\XeTeXlinebreaklocale "zh"
-
-%文字的彈性間距
-\XeTeXlinebreakskip = 0pt plus 1pt
-
-%設定段落之間的距離
-\setlength{\parskip}{0.15cm}
-
-%設定行距
-\linespread{1.2}
-
-%suppress page number
-%\pagenumbering{gobble}
+```tex
+\begin{multicols}{2}
+$body$
+\end{multicols}
 ```
@@
 For citation syntax, read the section [Bibliography & Citations](#cite).
-
-# knitr Parameters
-
-## Root
-```r
-knitr::opts_knit$set(root.dir='..')
-```
-The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default.
-In the case above, I changed it to  the **directory that is parent to the default directory**.
-This is useful if you build websites with [R Markdown Websites](https://rmarkdown.rstudio.com/rmarkdown_websites.htm), since **R Markdown Websites** doesn't allow hierarchical website structure.
-By changing the root directory, you can more easly organize your project directory structure without violating the requirement of **R Markdown Websites**.
-This is especially true when you source a lot of Rscripts in the `.Rmd` files.
-
-## Code Chunk & Figure Options
-```r
-library(svglite) 
-knitr::opts_chunk$set(
-	echo = FALSE, # No display code chunks
-	message = FALSE,
-	warning = FALSE,
-	dev='svg', # or 'svglite' for multibite characters
-	comment="",
-	fig.dim = c(3.5, 3.5)  # (width, height)
-)
-options(digits = 2) # auto round to 2 decimals when printed
-```
-
-# Dynamic Variables
-
-Include **R Code Chunk Variables** in the body of text. This can be a really useful feature for writing thesis or research paper:
-
-- No need to copy & paste the outcomes, such as the statistics. This greatly reduce the risk of error, and it also largely boosts efficiency.
-
-- Automatically updates the results in the paper when the data are updated.
-This also boosts efficiency and, more importantly, increases the **reproducibility** of the research: you can be confident that the results come directly from the data (unless there are errors in the *code*, which can be 'seen', whereas **errors from copy-&-paste's are invisible**).
-
-Below is a simple demonstration of this feature.
-
-```{r}
-tr1 <- rnorm(n=25, mean=1.1) #data of treatment1
-tr2 <- rnorm(n=25, mean=0.9) #data of treatment2
-ttest <- t.test(tr1, tr2, paired = T)
-diff <- ttest[["estimate"]][["mean of the differences"]]
-p_val <- ttest[["p.value"]]
-```
-
-1. The mean difference between the two groups is `r round(diff, 3)`.
-    ```{latex}
-    The mean difference between the two treatments is `r round(diff, 3)`.
-    ```
-
-2. The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```{latex}
-        The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```
-
-# Some $\LaTeX$ for PDF output
-
-- `\pagenumbering{gobble}`
-This LaTeX code suppress the page number.
-
-- `\pagenumbering{arabic}`
-'Turn on' page number closed by `\pagenumbering{gobble}`.
-
-- `\newpage`: Start a new page
-
-The 3 type of code can be useful in the situation below:
-
-```tex
----
-title: "A Title"
-author: "Someone"
-date: "`r str_date`"
----
-
-... Some content in the first page (title page) ...
-
-\pagenumbering{gobble} % Suppress page number on the title page
-\newpage               % Start a new page
-
-... Some content in the second page ...
-
-\pagenumbering{arabic} % Revert suppression of page number
-                       % Now, the page num starts with '2'
-```
-
-# $\LaTeX$ Math {.tabset}
-
-## Passing Matrix Object {-}
-
-### Setup {-}
-
-Add `results='asis'` to r code chunk option.
-
-````r
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-````
-
-```{r echo=FALSE, results='asis'}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-
-### Include Matrix in Text {-}
-
-````r
-This is the variable `mt`,
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-````
-
-renders as:
-
-<div class="success">
-This is the variable `mt`,
-```{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-</div>
-
-Check [here](http://markheckmann.github.io/mat2tex/){target=_blank""} for more information.
-
-## kable {-}
-```{r}
-library(knitr)
-library(dplyr)
-iris_data <- head(iris) %>%
-    select(Sepal.Length, Sepal.Width)
-
-colnames(iris_data) <- c("$\\alpha$", "$\\frac{a}{b}$")
-kable(iris_data, format = "markdown", align = "c")
-```
-
-## Plotting Expression {-}
-```{r fig.height=3}
-library(latex2exp)
-library(ggplot2)
-iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
-    select(Sepal.Length, Sepal.Width, Species)
-
-iris_data2 %>% ggplot() +
-    geom_point(aes(x = Sepal.Length, 
-                   y = Sepal.Width, 
-                   color = Species)) +
-    labs(x = TeX("Length($\\frac{kg}{cm^2}$)"),
-         y = TeX("\\frac{a}{b}"))
-```
-
-# Display Code Chunk with Code Chunk
-
-```{r include=F}
-code <- htmltools::HTML("<code>`r ''`</code>")
-```
-
-Wrap the code chunk you want to display (without running the code inside) inside **four ticks**:
-
-`````rmd
-````Rmd
-`r code````{r}
-Some R Code
-```
-````
-`````
-
-The code `r code` is for suppressing the execution of the r code chunk after it.
-
-# Bibliographies & Citations{#cite}
-
-You can read the full documentation of [Bibliographies & Citations](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"} at Rstudio.
-
-## Citation syntax
-
-### Classical Citation: **Author**, **year**, and **brackets** {-}
-- `Some text [@citekey].`
-    - Some text [@RN9].
-
-### In-text Citation: **Author (year)** {-}
-- `@citekey Some text`
-    - @RN15 Some text
-
-- `@citekey [p. 20] Some text.`
-    - @RN9 [p. 20] Some text.
-
-### Year only: Suppress Author {-}
-- `Some text [-@citekey].`
-    - Some text [-@RN9]
-
-### Two Citations {-}
-- `Some text [@citekey1; @citekey2].`
-    -  Some text [@RN9; @RN15].
-
-- Prefix & Suffix
-    - `Text [see @citekey1 pp.45; also, @citekey2 ch. 2].`
-    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].
-
-## Include `.bib` file in Reference {.tabset}
-
-Rmarkdown requires specific formats of bibliographies.
-One of the most common one is `.bib`.
-A lot of people (including me) use Endnote to manage bibliographies.
-Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` files from EndNote.
-
-However, you can't control the format of the **citation key** generated by Endnote.
-Having a well-structured format of citation key greatly enhance efficiency, which can be done by using **[Zotero](https://www.zotero.org/)** and its extension **[Better BibTeX](https://retorque.re/zotero-better-bibtex/)**.
-I strongly recommend using this approach, since the learning curve isn't steep and it only hurts once.
-The payoff is a long-term efficiency boost.
-
-Below are some syntax in Rmarkdown to control the display of reference in the document.
-
-### Reference heading {-}
-
-The body of cited reference in the `.bib` file will be shown under the header named Reference (it doesn't matter which **level** of heading you use).
-
-```markdown
-## Reference
-```
-
-### Specific Refs {-}
-Include specific references that were **not cited** in the body of text.
-```{pandoc}
----
-nocite: |
-  @item1, @item2
-...
-```
-
-### All Refs {-}
-Include **All references** in the body of text.
-```{pandoc}
----
-nocite: |
-  @*
-...
-```
-
-# Emphasis {.tabset}
-
-## An Example {-}
-
-````markdown
-`r ''````{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-````
-
-```{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-
-## Colored divs {-}
-
-### Bootstrap Alert {-}
-
-You can use bootstrap's default alert divs in Rmarkdown, defined with four classes:
-
-1. alert alert-success
-2. alert alert-warning
-3. alert alert-info
-4. alert alert-danger
-
-````markdown
-`r ''````{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-````
-
-```{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-
-### Customized divs {-}
-
-Alternative, you can define your own styled divs, as in my stylesheet[^css]:
-
-There are 4 choices of classes,
-
-1. success
-2. warning
-3. info
-4. error
-
-````markdown
-`r ''````{block, type="info"}
-some text in the colored region
-```
-````
-
-```{block, type="info"}
-some text in the colored region
-```
-
-## Bootstrap Callouts {-}
-
-Althougt it's "Bootstrap" callouts, it's not contained in default bootstrap theme. I defined it in my stylesheet.
-
-There are 4 choices of classes,
-
-1. bs-callout bs-callout-success
-2. bs-callout bs-callout-warning
-3. bs-callout bs-callout-info
-4. bs-callout bs-callout-error
-
-````markdown
-`r ''````{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-````
-
-```{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-
-## New Line {-}
-```{markdown}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-```{block2, type="alert alert-success"}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-## Attach Attributes {-}
-By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.
-
-### `class` {-}
-
-Rmarkdown syntax allows attaching attributes (such as class, id, etc.) to certain elements by wrapping attributes into `{ ... }`.
-
-Elements allowed attributes to be attach (by markdown syntax directly):
-
-1. Section: Attributes are added next to **any level of heading**.
-2. Link: `[Text](LINK){attributes}`
-3. `span`: Text wrapped in `[`, `]`. e.g `[Text with class "red"]{.red}`.
-
-```{markdown}
-[**Red Bold text**]{.red}
-```
-
-```{block2, type="alert alert-success"}
-[**Red Bold text**]{.red}
-```
-
-Note[^red].
-
-### Other Attributes {-}
-```{markdown}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-```{block2, type="alert alert-success"}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-# Footnotes with Paragraphs
-
-Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
-
-```{markdown}
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-```
-- Read the output by clicking the superscript[^longnote].
-
-# Shaped Images (HTML) {.tabset}
-
-## Rounded Edge {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-```
-![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-```
-![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-
-## Circle Image {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-```
-![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-```
-![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-
-## Thumbnail {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-```
-![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-
-<!-- footnotes ---------------------------- -->
-[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.
-
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-
-[^red]: `.red` is also a self-defined class in my stylesheet.
-<!-- footnotes -------------------------- -->
-
-<!-- syntax for Reference section -->
-
-# Figures
-
-## Captions
-
-Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
-````r
-`r ''````{r fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris) +
-    geom_point(aes(x = Sepal.Length,
-                   y = Sepal.Width,
-                   color = Species)
-               )
-```
-````
-
-```{r echo=FALSE, fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris)+
-    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
-```
-
-# Beamer Slide
-
-<embed src="beamer.pdf" type="application/pdf" width="90%" height="420px">
-
-Note: You can use (left & right) arrow keys to navigate through the slides page-by-page.
-
-[Download This Slide](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
-
-# References

### 2018-10-15 GitHubPage/my_R_book/Rmarkdown_features/01-knitr.rmd
restructure rmdbk

--- 2018-10-10 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
@@
   bookdown::html_document2:
-    css: /home/liao/local_depend/style_sheets/style.css
+    css: style.css
     df_print: kable
@@
 ```
-
-# yaml Setup {.tabset}
-
-yaml metadata determines the output file format, looking, and any other additional customizing features of Rmarkdown files.
-
-## yaml of this Doc {-}
-
-This is the complete yaml header of this document.
-
-```{yaml}
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`" 
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    code_folding: show
-    css: /home/liao/local_depend/style_sheets/style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-```
-
-## HTML Output {-}
-
-```{yaml}
-output:
-  html_document:
-    includes:
-        before_body: mathjax_bm.tex
-    css: ../style_sheets/style.css
-    df_print: kable
-    code_folding: hide
-    fig_width: 7
-    fig_height: 6
-    toc: true
-    toc_depth: 4
-    toc_float: true
-```
-
-## PDF Output {-}
-
-You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  pdf_document:
-    latex_engine: xelatex    
-    includes:
-        in_header: header.tex
-documentclass: article
-urlcolor: "blue"
-fontsize: 12pt 
-geometry: a5paper, headheight=0pt, margin=0.4in
----
-```
-
-Note that Latex only accepts fontsize of 10pt, 11pt, or 12pt. See [this](https://github.com/rstudio/rmarkdown/issues/878) for more detail.
-
-## PDF Output2 {-}
-This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  bookdown::pdf_document2:
-    number_sections: FALSE
-    toc: False
-    includes:
-      in_header: header.tex
-    latex_engine: xelatex
-  bookdown::html_document2:
-    number_sections: FALSE
-    includes:
-      before_body: mathjax_bm.tex
-urlcolor: blue
-always_allow_html: yes
----
-```
-
-## PDF: header.tex{- #pdf-header}
-
-The code below is for generating PDF documents written in (Traditional) Chinese.
-
-```{tex}
-%加這個就可以設定字體
-\usepackage{fontspec}
-%使用xeCJK，其他的還有CJK或是xCJK
-\usepackage{xeCJK}
-
-\usepackage[fontsize=13pt]{scrextend}
-
-%設定英文字型，不設的話就會使用預設的字型
-\setmainfont{Calibri}
-
-%設定中英文的字型
-%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
-% AR PL KaitiM Big5 標楷體
-% .PingFang TC
-% Noto Sans CJK TC
-\setCJKmainfont{AR PL KaitiM Big5}
-
-%中文自動換行
-\XeTeXlinebreaklocale "zh"
-
-%文字的彈性間距
-\XeTeXlinebreakskip = 0pt plus 1pt
-
-%設定段落之間的距離
-\setlength{\parskip}{0.15cm}
-
-%設定行距
-\linespread{1.2}
-
-%suppress page number
-%\pagenumbering{gobble}
-```
-
-## Bibliography {-}
-
-```{yaml}
-bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa.csl # APA style sheet
-link-citations: yes
-```
-
-For citation syntax, read the section [Bibliography & Citations](#cite).
 
@@
         The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```
-
-# Some $\LaTeX$ for PDF output
-
-- `\pagenumbering{gobble}`
-This LaTeX code suppress the page number.
-
-- `\pagenumbering{arabic}`
-'Turn on' page number closed by `\pagenumbering{gobble}`.
-
-- `\newpage`: Start a new page
-
-The 3 type of code can be useful in the situation below:
-
-```tex
----
-title: "A Title"
-author: "Someone"
-date: "`r str_date`"
----
-
-... Some content in the first page (title page) ...
-
-\pagenumbering{gobble} % Suppress page number on the title page
-\newpage               % Start a new page
-
-... Some content in the second page ...
-
-\pagenumbering{arabic} % Revert suppression of page number
-                       % Now, the page num starts with '2'
-```
-
-# $\LaTeX$ Math {.tabset}
-
-## Passing Matrix Object {-}
-
-### Setup {-}
-
-Add `results='asis'` to r code chunk option.
-
-````r
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-````
-
-```{r echo=FALSE, results='asis'}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-
-### Include Matrix in Text {-}
-
-````r
-This is the variable `mt`,
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-````
-
-renders as:
-
-<div class="success">
-This is the variable `mt`,
-```{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-</div>
-
-Check [here](http://markheckmann.github.io/mat2tex/){target=_blank""} for more information.
-
-## kable {-}
-```{r}
-library(knitr)
-library(dplyr)
-iris_data <- head(iris) %>%
-    select(Sepal.Length, Sepal.Width)
-
-colnames(iris_data) <- c("$\\alpha$", "$\\frac{a}{b}$")
-kable(iris_data, format = "markdown", align = "c")
-```
-
-## Plotting Expression {-}
-```{r fig.height=3}
-library(latex2exp)
-library(ggplot2)
-iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
-    select(Sepal.Length, Sepal.Width, Species)
-
-iris_data2 %>% ggplot() +
-    geom_point(aes(x = Sepal.Length, 
-                   y = Sepal.Width, 
-                   color = Species)) +
-    labs(x = TeX("Length($\\frac{kg}{cm^2}$)"),
-         y = TeX("\\frac{a}{b}"))
     ```
@@
 ```
-
-# Xaringan (remark.js Slide)
-
-Xaringan is a HTML presentation output format of R Markdown.
-Xaringan doesn't support Pandoc markdown, but is very flexible and easy to use if having basic CSS knowledge.
-It also prints well on PDF (using Chrome or [decktape](https://github.com/astefanutti/decktape)).
-Read the [Chapter 7](https://bookdown.org/yihui/rmarkdown/xaringan.html) of *R Markdown Guide* for more details.
-
-<iframe src="https://liao961120.github.io/slides/xaringan/index.html", width=400, height=301>
-</iframe>  
-[Slide Link](https://liao961120.github.io/slides/xaringan/index.html)
-
-# Beamer Slide
-
-<embed src="beamer.pdf" type="application/pdf" width="90%" height="420px">
-
-Note: You can use (left & right) arrow keys to navigate through the slides page-by-page.
-
-[Download This Slide](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
-
-# References

### 2018-10-15 GitHubPage/my_R_book/Rmarkdown_features/02-latex.rmd
restructure rmdbk

--- 2018-08-24 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
@@
 str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
-```
-
-# yaml Setup {.tabset}
-
-yaml metadata determines the output file format, looking, and any other additional customizing features of Rmarkdown files.
-
-## yaml of this Doc {-}
-
-This is the complete yaml header of this document.
-
-```{yaml}
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`" 
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    code_folding: show
-    css: /home/liao/local_depend/style_sheets/style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-```
-
-## HTML Output {-}
-
-```{yaml}
-output:
-  html_document:
-    includes:
-        before_body: mathjax_bm.tex
-    css: ../style_sheets/style.css
-    df_print: kable
-    code_folding: hide
-    fig_width: 7
-    fig_height: 6
-    toc: true
-    toc_depth: 4
-    toc_float: true
-```
-
-## PDF Output {-}
-
-You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  pdf_document:
-    latex_engine: xelatex    
-    includes:
-        in_header: header.tex
-documentclass: article
-urlcolor: "blue"
-fontsize: 12pt 
-geometry: a5paper, headheight=0pt, margin=0.4in
----
-```
-
-Note that Latex only accepts fontsize of 10pt, 11pt, or 12pt. See [this](https://github.com/rstudio/rmarkdown/issues/878) for more detail.
-
-## PDF Output2 {-}
-This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  bookdown::pdf_document2:
-    number_sections: FALSE
-    toc: False
-    includes:
-      in_header: header.tex
-    latex_engine: xelatex
-  bookdown::html_document2:
-    number_sections: FALSE
-    includes:
-      before_body: mathjax_bm.tex
-urlcolor: blue
-always_allow_html: yes
----
-```
-
-## PDF: header.tex{- #pdf-header}
-
-The code below is for generating PDF documents written in (Traditional) Chinese.
-
-```{tex}
-%加這個就可以設定字體
-\usepackage{fontspec}
-%使用xeCJK，其他的還有CJK或是xCJK
-\usepackage{xeCJK}
-
-\usepackage[fontsize=13pt]{scrextend}
-
-%設定英文字型，不設的話就會使用預設的字型
-\setmainfont{Calibri}
-
-%設定中英文的字型
-%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
-% AR PL KaitiM Big5 標楷體
-% .PingFang TC
-% Noto Sans CJK TC
-\setCJKmainfont{AR PL KaitiM Big5}
-
-%中文自動換行
-\XeTeXlinebreaklocale "zh"
-
-%文字的彈性間距
-\XeTeXlinebreakskip = 0pt plus 1pt
-
-%設定段落之間的距離
-\setlength{\parskip}{0.15cm}
-
-%設定行距
-\linespread{1.2}
-
-%suppress page number
-%\pagenumbering{gobble}
-```
-
-## Bibliography {-}
-
-```{yaml}
-bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa.csl # APA style sheet
-link-citations: yes
-```
-
-For citation syntax, read the section [Bibliography & Citations](#cite).
-
-# knitr Parameters
-
-## Root
-```r
-knitr::opts_knit$set(root.dir='..')
-```
-The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default.
-In the case above, I changed it to  the **directory that is parent to the default directory**.
-This is useful if you build websites with [R Markdown Websites](https://rmarkdown.rstudio.com/rmarkdown_websites.htm), since **R Markdown Websites** doesn't allow hierarchical website structure.
-By changing the root directory, you can more easly organize your project directory structure without violating the requirement of **R Markdown Websites**.
-This is especially true when you source a lot of Rscripts in the `.Rmd` files.
-
-## Code Chunk & Figure Options
-```r
-library(svglite) 
-knitr::opts_chunk$set(
-	echo = FALSE, # No display code chunks
-	message = FALSE,
-	warning = FALSE,
-	dev='svg', # or 'svglite' for multibite characters
-	comment="",
-	fig.dim = c(3.5, 3.5)  # (width, height)
-)
-options(digits = 2) # auto round to 2 decimals when printed
-```
-
-# Dynamic Variables
-
-Include **R Code Chunk Variables** in the body of text. This can be a really useful feature for writing thesis or research paper:
-
-- No need to copy & paste the outcomes, such as the statistics. This greatly reduce the risk of error, and it also largely boosts efficiency.
-
-- Automatically updates the results in the paper when the data are updated.
-This also boosts efficiency and, more importantly, increases the **reproducibility** of the research: you can be confident that the results come directly from the data (unless there are errors in the *code*, which can be 'seen', whereas **errors from copy-&-paste's are invisible**).
-
-Below is a simple demonstration of this feature.
-
-```{r}
-tr1 <- rnorm(n=25, mean=1.1) #data of treatment1
-tr2 <- rnorm(n=25, mean=0.9) #data of treatment2
-ttest <- t.test(tr1, tr2, paired = T)
-diff <- ttest[["estimate"]][["mean of the differences"]]
-p_val <- ttest[["p.value"]]
-```
-
-1. The mean difference between the two groups is `r round(diff, 3)`.
-    ```{latex}
-    The mean difference between the two treatments is `r round(diff, 3)`.
-    ```
-
-2. The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```{latex}
-        The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
 ```
@@
 ```
-
-# Display Code Chunk with Code Chunk
-
-```{r include=F}
-code <- htmltools::HTML("<code>`r ''`</code>")
-```
-
-Wrap the code chunk you want to display (without running the code inside) inside **four ticks**:
-
-`````rmd
-````Rmd
-`r code````{r}
-Some R Code
-```
-````
-`````
-
-The code `r code` is for suppressing the execution of the r code chunk after it.
-
-# Bibliographies & Citations{#cite}
-
-You can read the full documentation of [Bibliographies & Citations](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"} at Rstudio.
-
-## Citation syntax
-
-### Classical Citation: **Author**, **year**, and **brackets** {-}
-- `Some text [@citekey].`
-    - Some text [@RN9].
-
-### In-text Citation: **Author (year)** {-}
-- `@citekey Some text`
-    - @RN15 Some text
-
-- `@citekey [p. 20] Some text.`
-    - @RN9 [p. 20] Some text.
-
-### Year only: Suppress Author {-}
-- `Some text [-@citekey].`
-    - Some text [-@RN9]
-
-### Two Citations {-}
-- `Some text [@citekey1; @citekey2].`
-    -  Some text [@RN9; @RN15].
-
-- Prefix & Suffix
-    - `Text [see @citekey1 pp.45; also, @citekey2 ch. 2].`
-    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].
-
-## Include `.bib` file in Reference {.tabset}
-
-Rmarkdown requires specific formats of bibliographies.
-One of the most common one is `.bib`.
-A lot of people (including me) use Endnote to manage bibliographies.
-Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` files from EndNote.
-
-However, you can't control the format of the **citation key** generated by Endnote.
-Having a well-structured format of citation key greatly enhance efficiency, which can be done by using **[Zotero](https://www.zotero.org/)** and its extension **[Better BibTeX](https://retorque.re/zotero-better-bibtex/)**.
-I strongly recommend using this approach, since the learning curve isn't steep and it only hurts once.
-The payoff is a long-term efficiency boost.
-
-Below are some syntax in Rmarkdown to control the display of reference in the document.
-
-### Reference heading {-}
-
-The body of cited reference in the `.bib` file will be shown under the header named Reference (it doesn't matter which **level** of heading you use).
-
-```markdown
-## Reference
-```
-
-### Specific Refs {-}
-Include specific references that were **not cited** in the body of text.
-```{pandoc}
----
-nocite: |
-  @item1, @item2
-...
-```
-
-### All Refs {-}
-Include **All references** in the body of text.
-```{pandoc}
----
-nocite: |
-  @*
-...
-```
-
-# Emphasis {.tabset}
-
-## An Example {-}
-
-````markdown
-`r ''````{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-````
-
-```{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-
-## Colored divs {-}
-
-### Bootstrap Alert {-}
-
-You can use bootstrap's default alert divs in Rmarkdown, defined with four classes:
-
-1. alert alert-success
-2. alert alert-warning
-3. alert alert-info
-4. alert alert-danger
-
-````markdown
-`r ''````{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-````
-
-```{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-
-### Customized divs {-}
-
-Alternative, you can define your own styled divs, as in my stylesheet[^css]:
-
-There are 4 choices of classes,
-
-1. success
-2. warning
-3. info
-4. error
-
-````markdown
-`r ''````{block, type="info"}
-some text in the colored region
-```
-````
-
-```{block, type="info"}
-some text in the colored region
-```
-
-## Bootstrap Callouts {-}
-
-Althougt it's "Bootstrap" callouts, it's not contained in default bootstrap theme. I defined it in my stylesheet.
-
-There are 4 choices of classes,
-
-1. bs-callout bs-callout-success
-2. bs-callout bs-callout-warning
-3. bs-callout bs-callout-info
-4. bs-callout bs-callout-error
-
-````markdown
-`r ''````{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-````
-
-```{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-
-## New Line {-}
-```{markdown}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-```{block2, type="alert alert-success"}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-## Attach Attributes {-}
-By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.
-
-### `class` {-}
-
-Rmarkdown syntax allows attaching attributes (such as class, id, etc.) to certain elements by wrapping attributes into `{ ... }`.
-
-Elements allowed attributes to be attach (by markdown syntax directly):
-
-1. Section: Attributes are added next to **any level of heading**.
-2. Link: `[Text](LINK){attributes}`
-3. `span`: Text wrapped in `[`, `]`. e.g `[Text with class "red"]{.red}`.
-
-```{markdown}
-[**Red Bold text**]{.red}
-```
-
-```{block2, type="alert alert-success"}
-[**Red Bold text**]{.red}
-```
-
-Note[^red].
-
-### Other Attributes {-}
-```{markdown}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-```{block2, type="alert alert-success"}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-# Footnotes with Paragraphs
-
-Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
-
-```{markdown}
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-```
-- Read the output by clicking the superscript[^longnote].
-
-# Shaped Images (HTML) {.tabset}
-
-## Rounded Edge {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-```
-![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-```
-![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-
-## Circle Image {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-```
-![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-```
-![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-
-## Thumbnail {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-```
-![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-
-<!-- footnotes ---------------------------- -->
-[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.
-
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-
-[^red]: `.red` is also a self-defined class in my stylesheet.
-<!-- footnotes -------------------------- -->
-
-<!-- syntax for Reference section -->
-
-# Figures
-
-## Captions
-
-Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
-````r
-`r ''````{r fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris) +
-    geom_point(aes(x = Sepal.Length,
-                   y = Sepal.Width,
-                   color = Species)
-               )
-```
-````
-
-```{r echo=FALSE, fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris)+
-    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
-```
-
-# Beamer Slide
-
-<embed src="beamer.pdf" type="application/pdf" width="90%" height="420px">
-
-Note: You can use (left & right) arrow keys to navigate through the slides page-by-page.
-
-[Download This Slide](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
-
-# References

### 2018-10-15 GitHubPage/my_R_book/Rmarkdown_features/03-slide.rmd
restructure rmdbk

--- 2018-08-24 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
@@
 
-# yaml Setup {.tabset}
+# Xaringan (remark.js Slide)
 
-yaml metadata determines the output file format, looking, and any other additional customizing features of Rmarkdown files.
+Xaringan is a HTML presentation output format of R Markdown.
+Xaringan doesn't support Pandoc markdown, but is very flexible and easy to use if having basic CSS knowledge.
+It also prints well on PDF (using Chrome or [decktape](https://github.com/astefanutti/decktape)).
+Read [Chapter 7](https://bookdown.org/yihui/rmarkdown/xaringan.html) of *R Markdown Guide* for more details.
 
-## yaml of this Doc {-}
-
-This is the complete yaml header of this document.
-
-```{yaml}
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`" 
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    code_folding: show
-    css: /home/liao/local_depend/style_sheets/style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-```
-
-## HTML Output {-}
-
-```{yaml}
-output:
-  html_document:
-    includes:
-        before_body: mathjax_bm.tex
-    css: ../style_sheets/style.css
-    df_print: kable
-    code_folding: hide
-    fig_width: 7
-    fig_height: 6
-    toc: true
-    toc_depth: 4
-    toc_float: true
-```
-
-## PDF Output {-}
-
-You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  pdf_document:
-    latex_engine: xelatex    
-    includes:
-        in_header: header.tex
-documentclass: article
-urlcolor: "blue"
-fontsize: 12pt 
-geometry: a5paper, headheight=0pt, margin=0.4in
----
-```
-
-Note that Latex only accepts fontsize of 10pt, 11pt, or 12pt. See [this](https://github.com/rstudio/rmarkdown/issues/878) for more detail.
-
-## PDF Output2 {-}
-This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  bookdown::pdf_document2:
-    number_sections: FALSE
-    toc: False
-    includes:
-      in_header: header.tex
-    latex_engine: xelatex
-  bookdown::html_document2:
-    number_sections: FALSE
-    includes:
-      before_body: mathjax_bm.tex
-urlcolor: blue
-always_allow_html: yes
----
-```
-
-## PDF: header.tex{- #pdf-header}
-
-The code below is for generating PDF documents written in (Traditional) Chinese.
-
-```{tex}
-%加這個就可以設定字體
-\usepackage{fontspec}
-%使用xeCJK，其他的還有CJK或是xCJK
-\usepackage{xeCJK}
-
-\usepackage[fontsize=13pt]{scrextend}
-
-%設定英文字型，不設的話就會使用預設的字型
-\setmainfont{Calibri}
-
-%設定中英文的字型
-%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
-% AR PL KaitiM Big5 標楷體
-% .PingFang TC
-% Noto Sans CJK TC
-\setCJKmainfont{AR PL KaitiM Big5}
-
-%中文自動換行
-\XeTeXlinebreaklocale "zh"
-
-%文字的彈性間距
-\XeTeXlinebreakskip = 0pt plus 1pt
-
-%設定段落之間的距離
-\setlength{\parskip}{0.15cm}
-
-%設定行距
-\linespread{1.2}
-
-%suppress page number
-%\pagenumbering{gobble}
-```
-
-## Bibliography {-}
-
-```{yaml}
-bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa.csl # APA style sheet
-link-citations: yes
-```
-
-For citation syntax, read the section [Bibliography & Citations](#cite).
-
-# knitr Parameters
-
-## Root
-```r
-knitr::opts_knit$set(root.dir='..')
-```
-The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default.
-In the case above, I changed it to  the **directory that is parent to the default directory**.
-This is useful if you build websites with [R Markdown Websites](https://rmarkdown.rstudio.com/rmarkdown_websites.htm), since **R Markdown Websites** doesn't allow hierarchical website structure.
-By changing the root directory, you can more easly organize your project directory structure without violating the requirement of **R Markdown Websites**.
-This is especially true when you source a lot of Rscripts in the `.Rmd` files.
-
-## Code Chunk & Figure Options
-```r
-library(svglite) 
-knitr::opts_chunk$set(
-	echo = FALSE, # No display code chunks
-	message = FALSE,
-	warning = FALSE,
-	dev='svg', # or 'svglite' for multibite characters
-	comment="",
-	fig.dim = c(3.5, 3.5)  # (width, height)
-)
-options(digits = 2) # auto round to 2 decimals when printed
-```
-
-# Dynamic Variables
-
-Include **R Code Chunk Variables** in the body of text. This can be a really useful feature for writing thesis or research paper:
-
-- No need to copy & paste the outcomes, such as the statistics. This greatly reduce the risk of error, and it also largely boosts efficiency.
-
-- Automatically updates the results in the paper when the data are updated.
-This also boosts efficiency and, more importantly, increases the **reproducibility** of the research: you can be confident that the results come directly from the data (unless there are errors in the *code*, which can be 'seen', whereas **errors from copy-&-paste's are invisible**).
-
-Below is a simple demonstration of this feature.
-
-```{r}
-tr1 <- rnorm(n=25, mean=1.1) #data of treatment1
-tr2 <- rnorm(n=25, mean=0.9) #data of treatment2
-ttest <- t.test(tr1, tr2, paired = T)
-diff <- ttest[["estimate"]][["mean of the differences"]]
-p_val <- ttest[["p.value"]]
-```
-
-1. The mean difference between the two groups is `r round(diff, 3)`.
-    ```{latex}
-    The mean difference between the two treatments is `r round(diff, 3)`.
-    ```
-
-2. The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```{latex}
-        The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```
-
-# Some $\LaTeX$ for PDF output
-
-- `\pagenumbering{gobble}`
-This LaTeX code suppress the page number.
-
-- `\pagenumbering{arabic}`
-'Turn on' page number closed by `\pagenumbering{gobble}`.
-
-- `\newpage`: Start a new page
-
-The 3 type of code can be useful in the situation below:
-
-```tex
----
-title: "A Title"
-author: "Someone"
-date: "`r str_date`"
----
-
-... Some content in the first page (title page) ...
-
-\pagenumbering{gobble} % Suppress page number on the title page
-\newpage               % Start a new page
-
-... Some content in the second page ...
-
-\pagenumbering{arabic} % Revert suppression of page number
-                       % Now, the page num starts with '2'
-```
-
-# $\LaTeX$ Math {.tabset}
-
-## Passing Matrix Object {-}
-
-### Setup {-}
-
-Add `results='asis'` to r code chunk option.
-
-````r
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-````
-
-```{r echo=FALSE, results='asis'}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-
-### Include Matrix in Text {-}
-
-````r
-This is the variable `mt`,
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-````
-
-renders as:
-
-<div class="success">
-This is the variable `mt`,
-```{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-</div>
-
-Check [here](http://markheckmann.github.io/mat2tex/){target=_blank""} for more information.
-
-## kable {-}
-```{r}
-library(knitr)
-library(dplyr)
-iris_data <- head(iris) %>%
-    select(Sepal.Length, Sepal.Width)
-
-colnames(iris_data) <- c("$\\alpha$", "$\\frac{a}{b}$")
-kable(iris_data, format = "markdown", align = "c")
-```
-
-## Plotting Expression {-}
-```{r fig.height=3}
-library(latex2exp)
-library(ggplot2)
-iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
-    select(Sepal.Length, Sepal.Width, Species)
-
-iris_data2 %>% ggplot() +
-    geom_point(aes(x = Sepal.Length, 
-                   y = Sepal.Width, 
-                   color = Species)) +
-    labs(x = TeX("Length($\\frac{kg}{cm^2}$)"),
-         y = TeX("\\frac{a}{b}"))
-```
-
-# Display Code Chunk with Code Chunk
-
-```{r include=F}
-code <- htmltools::HTML("<code>`r ''`</code>")
-```
-
-Wrap the code chunk you want to display (without running the code inside) inside **four ticks**:
-
-`````rmd
-````Rmd
-`r code````{r}
-Some R Code
-```
-````
-`````
-
-The code `r code` is for suppressing the execution of the r code chunk after it.
-
-# Bibliographies & Citations{#cite}
-
-You can read the full documentation of [Bibliographies & Citations](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"} at Rstudio.
-
-## Citation syntax
-
-### Classical Citation: **Author**, **year**, and **brackets** {-}
-- `Some text [@citekey].`
-    - Some text [@RN9].
-
-### In-text Citation: **Author (year)** {-}
-- `@citekey Some text`
-    - @RN15 Some text
-
-- `@citekey [p. 20] Some text.`
-    - @RN9 [p. 20] Some text.
-
-### Year only: Suppress Author {-}
-- `Some text [-@citekey].`
-    - Some text [-@RN9]
-
-### Two Citations {-}
-- `Some text [@citekey1; @citekey2].`
-    -  Some text [@RN9; @RN15].
-
-- Prefix & Suffix
-    - `Text [see @citekey1 pp.45; also, @citekey2 ch. 2].`
-    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].
-
-## Include `.bib` file in Reference {.tabset}
-
-Rmarkdown requires specific formats of bibliographies.
-One of the most common one is `.bib`.
-A lot of people (including me) use Endnote to manage bibliographies.
-Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` files from EndNote.
-
-However, you can't control the format of the **citation key** generated by Endnote.
-Having a well-structured format of citation key greatly enhance efficiency, which can be done by using **[Zotero](https://www.zotero.org/)** and its extension **[Better BibTeX](https://retorque.re/zotero-better-bibtex/)**.
-I strongly recommend using this approach, since the learning curve isn't steep and it only hurts once.
-The payoff is a long-term efficiency boost.
-
-Below are some syntax in Rmarkdown to control the display of reference in the document.
-
-### Reference heading {-}
-
-The body of cited reference in the `.bib` file will be shown under the header named Reference (it doesn't matter which **level** of heading you use).
-
-```markdown
-## Reference
-```
-
-### Specific Refs {-}
-Include specific references that were **not cited** in the body of text.
-```{pandoc}
----
-nocite: |
-  @item1, @item2
-...
-```
-
-### All Refs {-}
-Include **All references** in the body of text.
-```{pandoc}
----
-nocite: |
-  @*
-...
-```
-
-# Emphasis {.tabset}
-
-## An Example {-}
-
-````markdown
-`r ''````{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-````
-
-```{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-
-## Colored divs {-}
-
-### Bootstrap Alert {-}
-
-You can use bootstrap's default alert divs in Rmarkdown, defined with four classes:
-
-1. alert alert-success
-2. alert alert-warning
-3. alert alert-info
-4. alert alert-danger
-
-````markdown
-`r ''````{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-````
-
-```{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-
-### Customized divs {-}
-
-Alternative, you can define your own styled divs, as in my stylesheet[^css]:
-
-There are 4 choices of classes,
-
-1. success
-2. warning
-3. info
-4. error
-
-````markdown
-`r ''````{block, type="info"}
-some text in the colored region
-```
-````
-
-```{block, type="info"}
-some text in the colored region
-```
-
-## Bootstrap Callouts {-}
-
-Althougt it's "Bootstrap" callouts, it's not contained in default bootstrap theme. I defined it in my stylesheet.
-
-There are 4 choices of classes,
-
-1. bs-callout bs-callout-success
-2. bs-callout bs-callout-warning
-3. bs-callout bs-callout-info
-4. bs-callout bs-callout-error
-
-````markdown
-`r ''````{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-````
-
-```{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-
-## New Line {-}
-```{markdown}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-```{block2, type="alert alert-success"}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-## Attach Attributes {-}
-By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.
-
-### `class` {-}
-
-Rmarkdown syntax allows attaching attributes (such as class, id, etc.) to certain elements by wrapping attributes into `{ ... }`.
-
-Elements allowed attributes to be attach (by markdown syntax directly):
-
-1. Section: Attributes are added next to **any level of heading**.
-2. Link: `[Text](LINK){attributes}`
-3. `span`: Text wrapped in `[`, `]`. e.g `[Text with class "red"]{.red}`.
-
-```{markdown}
-[**Red Bold text**]{.red}
-```
-
-```{block2, type="alert alert-success"}
-[**Red Bold text**]{.red}
-```
-
-Note[^red].
-
-### Other Attributes {-}
-```{markdown}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-```{block2, type="alert alert-success"}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-# Footnotes with Paragraphs
-
-Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
-
-```{markdown}
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-```
-- Read the output by clicking the superscript[^longnote].
-
-# Shaped Images (HTML) {.tabset}
-
-## Rounded Edge {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-```
-![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-```
-![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-
-## Circle Image {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-```
-![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-```
-![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-
-## Thumbnail {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-```
-![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-
-<!-- footnotes ---------------------------- -->
-[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.
-
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-
-[^red]: `.red` is also a self-defined class in my stylesheet.
-<!-- footnotes -------------------------- -->
-
-<!-- syntax for Reference section -->
-
-# Figures
-
-## Captions
-
-Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
-````r
-`r ''````{r fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris) +
-    geom_point(aes(x = Sepal.Length,
-                   y = Sepal.Width,
-                   color = Species)
-               )
-```
-````
-
-```{r echo=FALSE, fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris)+
-    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
-```
+<iframe src="https://liao961120.github.io/slides/xaringan/index.html", width=400, height=301>
+</iframe>  
+[Slide Link](https://liao961120.github.io/slides/xaringan/index.html)
 
 # Beamer Slide
+
+Beamer slide is popular among proficient LaTeX users.
+However, I think Xaringan is a better option since it's able to print to PDF properly and at the same time having the ability to use interactive HTML features[^xaringan].
 
@@
 
-[Download This Slide](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
-
-# References
+[^xaringan]: An automatic process can be set to render Xaringan slides, print them to PDF, and host HTML and PDF slides on GitHub Pages.
+See the [output webpage](/slides) and this [.travis.yml](https://github.com/liao961120/slides/blob/master/.travis.yml) if you want to implement it.

### 2018-10-15 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up
restructure rmdbk

--- 2018-08-02 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
@@
 ```{r setup, include=FALSE}
+options(knitr.duplicate.label = 'allow')
 knitr::opts_chunk$set(
@@
 	dev='svg',
-	fig.dim = c(5.5, 3.5)  # (width, height)
+	fig.dim = c(5.5, 3.5)   # width height
 	)
-str_date <- "`r format(Sys.Date(), '%B %d, %Y')`"
+str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
 ```
 
-# yaml Setup {.tabset}
-
-yaml metadata determines the output file format, looking, and any other additional customizing features of Rmarkdown files.
-
-## yaml of this Doc {-}
-
-This is the complete yaml header of this document.
-
-```{yaml}
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r str_date`"
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    code_folding: show
-    css: /home/liao/local_depend/style_sheets/style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
+# (PART) yaml {-}
+```{r child='00-yaml.rmd'}
 ```
 
-## HTML Output {-}
-
-```{yaml}
-output:
-  html_document:
-    includes:
-        before_body: mathjax_bm.tex
-    css: ../style_sheets/style.css
-    df_print: kable
-    code_folding: hide
-    fig_width: 7
-    fig_height: 6
-    toc: true
-    toc_depth: 4
-    toc_float: true
+# (PART) knitr {-}
+```{r child='01-knitr.rmd'}
 ```
 
-## PDF Output {-}
-
-You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  pdf_document:
-    latex_engine: xelatex    
-    includes:
-        in_header: header.tex
-documentclass: article
-urlcolor: "blue"
-fontsize: 12pt 
-geometry: a5paper, headheight=0pt, margin=0.4in
----
+# (PART) LaTeX {-}
+```{r child='02-latex.rmd'}
 ```
 
-Note that Latex only accepts fontsize of 10pt, 11pt, or 12pt. See [this](https://github.com/rstudio/rmarkdown/issues/878) for more detail.
-
-## PDF Output2 {-}
-This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
-```{yaml}
----
-author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
-output:
-  bookdown::pdf_document2:
-    number_sections: FALSE
-    toc: False
-    includes:
-      in_header: header.tex
-    latex_engine: xelatex
-  bookdown::html_document2:
-    number_sections: FALSE
-    includes:
-      before_body: mathjax_bm.tex
-urlcolor: blue
-always_allow_html: yes
----
+# (PART) Presentation {-}
+```{r child='03-slide.rmd'}
 ```
 
-## PDF: header.tex{- #pdf-header}
-
-The code below is for generating PDF documents written in (Traditional) Chinese.
-
-```{tex}
-%加這個就可以設定字體
-\usepackage{fontspec}
-%使用xeCJK，其他的還有CJK或是xCJK
-\usepackage{xeCJK}
-
-\usepackage[fontsize=13pt]{scrextend}
-
-%設定英文字型，不設的話就會使用預設的字型
-\setmainfont{Calibri}
-
-%設定中英文的字型
-%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
-% AR PL KaitiM Big5 標楷體
-% .PingFang TC
-% Noto Sans CJK TC
-\setCJKmainfont{AR PL KaitiM Big5}
-
-%中文自動換行
-\XeTeXlinebreaklocale "zh"
-
-%文字的彈性間距
-\XeTeXlinebreakskip = 0pt plus 1pt
-
-%設定段落之間的距離
-\setlength{\parskip}{0.15cm}
-
-%設定行距
-\linespread{1.2}
-
-%suppress page number
-%\pagenumbering{gobble}
-```
-
-## Bibliography {-}
-
-```{yaml}
-bibliography: ./citation/neanderthals.bib
-csl: ./citation/apa.csl # APA style sheet
-link-citations: yes
-```
-
-For citation syntax, read the section [Bibliography & Citations](#cite).
-
-# knitr Parameters
-
-## Root
-```r
-knitr::opts_knit$set(root.dir='..')
-```
-The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default.
-In the case above, I changed it to  the **directory that is parent to the default directory**.
-This is useful if you build websites with [R Markdown Websites](https://rmarkdown.rstudio.com/rmarkdown_websites.htm), since **R Markdown Websites** doesn't allow hierarchical website structure.
-By changing the root directory, you can more easly organize your project directory structure without violating the requirement of **R Markdown Websites**.
-This is especially true when you source a lot of Rscripts in the `.Rmd` files.
-
-## Code Chunk & Figure Options
-```r
-library(svglite) 
-knitr::opts_chunk$set(
-	echo = FALSE, # No display code chunks
-	message = FALSE,
-	warning = FALSE,
-	dev='svg', # or 'svglite' for multibite characters
-	comment="",
-	fig.dim = c(3.5, 3.5)  # (width, height)
-)
-options(digits = 2) # auto round to 2 decimals when printed
-```
-
-# Dynamic Variables
-
-Include **R Code Chunk Variables** in the body of text. This can be a really useful feature for writing thesis or research paper:
-
-- No need to copy & paste the outcomes, such as the statistics. This greatly reduce the risk of error, and it also largely boosts efficiency.
-
-- Automatically updates the results in the paper when the data are updated.
-This also boosts efficiency and, more importantly, increases the **reproducibility** of the research: you can be confident that the results come directly from the data (unless there are errors in the *code*, which can be 'seen', whereas **errors from copy-&-paste's are invisible**).
-
-Below is a simple demonstration of this feature.
-
-```{r}
-tr1 <- rnorm(n=25, mean=1.1) #data of treatment1
-tr2 <- rnorm(n=25, mean=0.9) #data of treatment2
-ttest <- t.test(tr1, tr2, paired = T)
-diff <- ttest[["estimate"]][["mean of the differences"]]
-p_val <- ttest[["p.value"]]
-```
-
-1. The mean difference between the two groups is `r round(diff, 3)`.
-    ```{latex}
-    The mean difference between the two treatments is `r round(diff, 3)`.
-    ```
-
-2. The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```{latex}
-        The *p*-value of the paired t-test is `r round(p_val, 4)`, which is `r ifelse(p_val<=0.05, "", "not")` significant.
-    ```
-
-# Some $\LaTeX$ for PDF output
-
-- `\pagenumbering{gobble}`
-This LaTeX code suppress the page number.
-
-- `\pagenumbering{arabic}`
-'Turn on' page number closed by `\pagenumbering{gobble}`.
-
-- `\newpage`: Start a new page
-
-The 3 type of code can be useful in the situation below:
-
-```tex
----
-title: "A Title"
-author: "Someone"
-date: "`r str_date`"
----
-
-... Some content in the first page (title page) ...
-
-\pagenumbering{gobble} % Suppress page number on the title page
-\newpage               % Start a new page
-
-... Some content in the second page ...
-
-\pagenumbering{arabic} % Revert suppression of page number
-                       % Now, the page num starts with '2'
-```
-
-# $\LaTeX$ Math {.tabset}
-
-## Passing Matrix Object {-}
-
-### Setup {-}
-
-Add `results='asis'` to r code chunk option.
-
-````r
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-````
-
-```{r echo=FALSE, results='asis'}
-library(mat2tex)
-mt <- c(1,2)
-"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
-```
-
-### Include Matrix in Text {-}
-
-````r
-This is the variable `mt`,
-`r ''````{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-````
-
-renders as:
-
-<div class="success">
-This is the variable `mt`,
-```{r results='asis', echo=FALSE}
-library(mat2tex)
-mt <- matrix(1:4, 2,2)
-"$A =" %_% xm(mt,0) %_%"^{-1}$"
-```
-, which is a matrix.
-</div>
-
-Check [here](http://markheckmann.github.io/mat2tex/){target=_blank""} for more information.
-
-## kable {-}
-```{r}
-library(knitr)
-library(dplyr)
-iris_data <- head(iris) %>%
-    select(Sepal.Length, Sepal.Width)
-
-colnames(iris_data) <- c("$\\alpha$", "$\\frac{a}{b}$")
-kable(iris_data, format = "markdown", align = "c")
-```
-
-## Plotting Expression {-}
-```{r fig.height=3}
-library(latex2exp)
-library(ggplot2)
-iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
-    select(Sepal.Length, Sepal.Width, Species)
-
-iris_data2 %>% ggplot() +
-    geom_point(aes(x = Sepal.Length, 
-                   y = Sepal.Width, 
-                   color = Species)) +
-    labs(x = TeX("Length($\\frac{kg}{cm^2}$)"),
-         y = TeX("\\frac{a}{b}"))
-```
-
-# Display Code Chunk with Code Chunk
-
-```{r include=F}
-code <- htmltools::HTML("<code>`r ''`</code>")
-```
-
-Wrap the code chunk you want to display (without running the code inside) inside **four ticks**:
-
-`````rmd
-````Rmd
-`r code````{r}
-Some R Code
-```
-````
-`````
-
-The code `r code` is for suppressing the execution of the r code chunk after it.
-
-# Bibliographies & Citations{#cite}
-
-You can read the full documentation of [Bibliographies & Citations](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"} at Rstudio.
-
-## Citation syntax
-
-### Classical Citation: **Author**, **year**, and **brackets** {-}
-- `Some text [@citekey].`
-    - Some text [@RN9].
-
-### In-text Citation: **Author (year)** {-}
-- `@citekey Some text`
-    - @RN15 Some text
-
-- `@citekey [p. 20] Some text.`
-    - @RN9 [p. 20] Some text.
-
-### Year only: Suppress Author {-}
-- `Some text [-@citekey].`
-    - Some text [-@RN9]
-
-### Two Citations {-}
-- `Some text [@citekey1; @citekey2].`
-    -  Some text [@RN9; @RN15].
-
-- Prefix & Suffix
-    - `Text [see @citekey1 pp.45; also, @citekey2 ch. 2].`
-    -  Text [see @RN9 pp. 45; also, @RN15 ch. 2].
-
-## Include `.bib` file in Reference {.tabset}
-
-Rmarkdown requires specific formats of bibliographies.
-One of the most common one is `.bib`.
-A lot of people (including me) use Endnote to manage bibliographies.
-Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` files from EndNote.
-
-However, you can't control the format of the **citation key** generated by Endnote.
-Having a well-structured format of citation key greatly enhance efficiency, which can be done by using **[Zotero](https://www.zotero.org/)** and its extension **[Better BibTeX](https://retorque.re/zotero-better-bibtex/)**.
-I strongly recommend using this approach, since the learning curve isn't steep and it only hurts once.
-The payoff is a long-term efficiency boost.
-
-Below are some syntax in Rmarkdown to control the display of reference in the document.
-
-### Reference heading {-}
-
-The body of cited reference in the `.bib` file will be shown under the header named Reference (it doesn't matter which **level** of heading you use).
-
-```markdown
-## Reference
-```
-
-### Specific Refs {-}
-Include specific references that were **not cited** in the body of text.
-```{pandoc}
----
-nocite: |
-  @item1, @item2
-...
-```
-
-### All Refs {-}
-Include **All references** in the body of text.
-```{pandoc}
----
-nocite: |
-  @*
-...
-```
-
-# Emphasis {.tabset}
-
-## An Example {-}
-
-````markdown
-`r ''````{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-````
-
-```{block2, type="success"}
-| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
-| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.
-
-Paragraph two starts here.
-```
-
-## Colored divs {-}
-
-### Bootstrap Alert {-}
-
-You can use bootstrap's default alert divs in Rmarkdown, defined with four classes:
-
-1. alert alert-success
-2. alert alert-warning
-3. alert alert-info
-4. alert alert-danger
-
-````markdown
-`r ''````{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-````
-
-```{block, type="alert alert-success"}
-Bootstrap-defined colored region
-```
-
-### Customized divs {-}
-
-Alternative, you can define your own styled divs, as in my stylesheet[^css]:
-
-There are 4 choices of classes,
-
-1. success
-2. warning
-3. info
-4. error
-
-````markdown
-`r ''````{block, type="info"}
-some text in the colored region
-```
-````
-
-```{block, type="info"}
-some text in the colored region
-```
-
-## Bootstrap Callouts {-}
-
-Althougt it's "Bootstrap" callouts, it's not contained in default bootstrap theme. I defined it in my stylesheet.
-
-There are 4 choices of classes,
-
-1. bs-callout bs-callout-success
-2. bs-callout bs-callout-warning
-3. bs-callout bs-callout-info
-4. bs-callout bs-callout-error
-
-````markdown
-`r ''````{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-````
-
-```{block2, type="bs-callout bs-callout-warning"}
-### Heading in Callout
-**Calleout Text** texttexttexttexttexttext
-```
-
-## New Line {-}
-```{markdown}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-```{block2, type="alert alert-success"}
-| Text of line 1
-| Text of line 2
-
-New paragraph
-```
-
-## Attach Attributes {-}
-By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.
-
-### `class` {-}
-
-Rmarkdown syntax allows attaching attributes (such as class, id, etc.) to certain elements by wrapping attributes into `{ ... }`.
-
-Elements allowed attributes to be attach (by markdown syntax directly):
-
-1. Section: Attributes are added next to **any level of heading**.
-2. Link: `[Text](LINK){attributes}`
-3. `span`: Text wrapped in `[`, `]`. e.g `[Text with class "red"]{.red}`.
-
-```{markdown}
-[**Red Bold text**]{.red}
-```
-
-```{block2, type="alert alert-success"}
-[**Red Bold text**]{.red}
-```
-
-Note[^red].
-
-### Other Attributes {-}
-```{markdown}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-```{block2, type="alert alert-success"}
-Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
-```
-
-# Footnotes with Paragraphs
-
-Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.
-
-```{markdown}
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-```
-- Read the output by clicking the superscript[^longnote].
-
-# Shaped Images (HTML) {.tabset}
-
-## Rounded Edge {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-```
-![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-```
-![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
-
-## Circle Image {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-```
-![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
-
-### Boostrap {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-```
-![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
-
-## Thumbnail {-}
-```{markdown}
-![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-```
-![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
-
-<!-- footnotes ---------------------------- -->
-[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.
-
-[^longnote]: Here's one with multiple blocks.
-
-    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
-
-    In this way, multi-paragraph footnotes work like multi-paragraph list items.
-
-[^red]: `.red` is also a self-defined class in my stylesheet.
-<!-- footnotes -------------------------- -->
-
-<!-- syntax for Reference section -->
-
-# Figures
-
-## Captions
-
-Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
-````r
-`r ''````{r fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris) +
-    geom_point(aes(x = Sepal.Length,
-                   y = Sepal.Width,
-                   color = Species)
-               )
-```
-````
-
-```{r echo=FALSE, fig.cap='An Caption of the Plot'}
-library(ggplot2)
-ggplot(iris)+
-    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
-```
-
-# Beamer Slide
-
-<embed src="beamer.pdf" type="application/pdf" width="90%" height="420px">
-
-Note: You can use (left & right) arrow keys to navigate through the slides page-by-page.
-
-[Download This Slide](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/GitHubPage/my_R_book/Rmarkdown_features/beamer/beamer.pdf)
-
-# References
+# References {-}

### 2018-10-23 GitHubPage/my_R_book/Rmarkdown_features/00-yaml.rmd
up

@@
 geometry: a5paper, headheight=0pt, margin=0.4in
+linestretch: 1.5
+links-as-notes: true
 ---
@@
 linestretch: 1.5
+geometry: a4paper #, headheight=0pt, margin=0.4in, landscape
+links-as-notes: true
 ---

### 2018-10-23 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@
     toc: true
-    toc_depth: 2
+    toc_depth: 1
     toc_float:
@@
 
-# (PART) yaml {-}
+# (PART) **yaml** {-}
+<br>
+
 ```{r child='00-yaml.rmd'}
@@
 
-# (PART) knitr {-}
+# (PART) **knitr** {-}
+<br>
+
 ```{r child='01-knitr.rmd'}
@@
 
-# (PART) LaTeX {-}
+# (PART) **LaTeX** {-}
+<br>
+
 ```{r child='02-latex.rmd'}
@@
 
-# (PART) Presentation {-}
+# (PART) **Presentation** {-}
+<br>
+
 ```{r child='03-slide.rmd'}

### 2018-11-07 Ubuntu_16.04_setup/mybashrc.sh
up

@@ -5,11 +5,15 @@ alias render_rmdbk='~/bin/render_rmarkdown_book'
 alias rmdbk='code ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
 alias new_rmd='~/bin/append_head_rmd'
 alias R='R --no-save -q'
+alias pyvir='source bin/activate'
+alias xampp='sudo /opt/lampp/manager-linux-x64.run'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
 export PS1
 export PATH=~/bin:"$PATH"  #Add ~/bin to PATH so custom shell programs can be found
+export GEM_HOME=$HOME/gems
+export PATH=$HOME/gems/bin:$PATH
 
 # Define variables for SSH remote pc.
 ### Reads IP from git repo ~/local_depend/hostname/hostname.txt ###

### 2018-12-01 Ubuntu_16.04_setup/mylinux.Rmd
up

@@
 ---
-title: "My Linux Notes"
+title: "My Bash Notes"
 subtitle: "A Quick Reference"
@@
 
-## Branching
-
-### case
+## case
 ```bash
@@
 
-### if
+## if
 ```bash
@@
 
-#### pipe
+### Logical Operators
 
 ```bash
-[ -f <file-name> ] && <command>
-[ -d <dir-name> ] || <command>
+-eq # equal
+-ne # not equal
+-lt # less than
+-le # less than or equal
+-gt # greater than
+-ge # greater than or equal
+```
+
+```bash
+[[ $num1 -eq $num2 ]] && echo "true"
+```
+
+## Conditionals (Square brackets)
+
+```bash
+[ -f file.txt ] && echo "File exist" 
+[ -s FB_title.txt ] && echo "File size > 0"
+[ -d dir/ ] && echo "Dir exist"
+[ -z "$var" ]      # Whether $var is empty
 ```
@@
 
+## grep
+
+Search files in working dir that contain certain string:
+```bash
+grep -r ".img" *
+```
+
+Search file names in working dir that contain certain string:
+```bash
+ls | grep ".txt"
+```
+
+## Compare Files
+
+```bash
+ls dir1 > file1.txt
+ls dir2 > file2.txt
+diff file1.txt file2.txt
+```
+
 Navigation
@@
 
+Reading Files
+========
+
+## Loop Over Every Line of a File
+```bash
+while read p; do
+  date=$(echo "$p" | cut -d ',' -f 1)
+  file=$(echo "$p" | cut -d ',' -f 2)
+done < list.txt
+```
+
+## Loop Over Several Files
+```bash
+while IFS=$'\t' read -r title tags link
+do
+  printf "${title}/n"
+  printf "${tags}/n"
+  printf "${link}/n/n"
+done < <(paste FB_title.txt FB_tags.txt FB_link.txt)
+```
+
+Function Flows
+========
+
+```bash
+[ -f file.txt ] && exit 0
+```
+
+```bash
+sleep 10 # seconds
+```
+
 Network
 ========
+
+## Curl
+
+```bash
+curl --silent --show-error --fail https://raw.githubusercontent.com/Rbloggers/web/posts/FB_title.txt > FB_title.txt
+```
+
+- `--silent`: Don't print process to std. output
+- `--show-error`: Print error message to std. output
+- `--fail`: Return empty file if 404
 
@@
 
-1. Fix floating IP
-(Alternative: auto push IP address when turned on
-https://superuser.com/questions/471253/ubuntu-how-to-run-a-terminal-command-on-boot)
-2. Enable WakeOnLane(WOL) at BIOS: 
+Enable WakeOnLane(WOL) at BIOS:
+
 1. `Power Management Setup` > `WOL: enabled`[^wol]
@@
 ```
+
+Other Resources
+===========
+
+- [Bash scripting cheatsheet](https://devhints.io/bash)

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/00-yaml.rmd
restructure rmd features

@@
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`"
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    css: style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = TRUE,
-	message = FALSE,
-	warning = FALSE,
-	dev='svg',
-	fig.dim = c(5.5, 3.5)  # (width, height)
-)
-str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
-```
+# (PART) **yaml** {-}
 

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/01-knitr.rmd
restructure rmd features

@@
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`"
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    css: style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = TRUE,
-	message = FALSE,
-	warning = FALSE,
-	dev='svg',
-	fig.dim = c(5.5, 3.5)  # (width, height)
-)
-str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
-```
+# (PART) **knitr** {-}
 

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/02-latex.rmd
restructure rmd features

@@
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`"
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    css: style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = TRUE,
-	message = FALSE,
-	warning = FALSE,
-	dev='svg',
-	fig.dim = c(5.5, 3.5)  # (width, height)
-)
-str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
-```
+# (PART) **LaTeX** {-}
 

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/03-slide.rmd
restructure rmd features

@@
----
-title: "R Markdown Features"
-subtitle: "A Compact Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
-date: "`r format(Sys.Date(), '%B %e, %Y')`"
-bibliography: /home/liao/local_depend/citation/neanderthals.bib
-csl: /home/liao/local_depend/style_sheets/apa.csl
-link-citations: yes
-output:
-  bookdown::html_document2:
-    css: style.css
-    df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = TRUE,
-	message = FALSE,
-	warning = FALSE,
-	dev='svg',
-	fig.dim = c(5.5, 3.5)  # (width, height)
-)
-str_date <- "`r format(Sys.Date(), '%B %e, %Y')`"
-```
+# (PART) **Presentation** {-}
 

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/04-bookdown.rmd
restructure rmd features

# (PART) **Advanced** {-}

# Printing Bookdown to PDF

Although bookdown nicely provides options to render the book to PDF formats, setting up things related to LaTeX can still be demanding, especially for people not familiar with LaTeX. To make bookdown nicely render elements properly to both HTML and PDF also takes some additional efforts. You have to make sure not to use pure HTML or LaTeX commands in Rmd files.

One possible solution is to forget about LaTeX and use HTML compatible syntax entirely. The PDF can then be generated by using the web browser to print the web page. Currently, I found Firefox working better than Chrome in printing nicer appearance of the PDF (e.g., page break before H1 titles).

To achieve this, one has to make all chapters output to one single HTML file and specify some additional css styles to tweak the appearance of PDF. You can do this by putting the code below in `_output.yml`:

```yaml
bookdown::gitbook:
  split_by: none
  css: style.css
```

and tweak the appearance of PDF by specifying `@media print` in `style.css`:

```css
@media print {
  div.level1 { 
    page-break-before: always;}
  img {
    display: block;
  }
  img, table, ul, ol, .code-snippet, blockquote, pre {
      page-break-inside: avoid;
  }
}
```

Note that `page-break-before: always` doesn't seem to work in Chrome, and `img { page-break-inside: avoid; }` doesn't work on Firefox (so some images get cut into parts), at least on my computer.

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/index.rmd
restructure rmd features

--- 2018-10-15 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
@@
 output:
-  bookdown::html_document2:
-    css: style.css
+  bookdown::gitbook:
+    split_by: rmd
     df_print: kable
-    toc: true
-    toc_depth: 2
-    toc_float:
-        collapsed: false
+    toc_depth: 1
+    #self_contained: true
+    output_dir: _book
 ---
@@
 
-# (PART) yaml {-}
-```{r child='00-yaml.rmd'}
+```{r klippy, echo=FALSE, include=TRUE}
+klippy::klippy(position = c('top', 'right'), all_precode = T)
 ```
-
-# (PART) knitr {-}
-```{r child='01-knitr.rmd'}
-```
-
-# (PART) LaTeX {-}
-```{r child='02-latex.rmd'}
-```
-
-# (PART) Presentation {-}
-```{r child='03-slide.rmd'}
-```
-
-# References {-}

### 2018-12-11 Ubuntu_16.04_setup/mybashrc.sh

@@ -3,10 +3,12 @@ alias dict='goldendict'
 alias r='Rscript -e' #Note capital 'R' is for running R in bash
 alias render_rmdbk='~/bin/render_rmarkdown_book'
 alias rmdbk='code ~/local_depend/GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd'
+alias mypython='code ~/private_repo/python/python_notes.Rmd'
 alias new_rmd='~/bin/append_head_rmd'
 alias R='R --no-save -q'
 alias pyvir='source bin/activate'
 alias xampp='sudo /opt/lampp/manager-linux-x64.run'
+alias serve='chromium-browser "http://127.0.0.1:4000"; bundle exec jekyll serve --drafts'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "

### 2018-12-11 GitHubPage/my_R_book/Rmarkdown_features/index.rmd
up

@@
 link-citations: yes
-output:
-  bookdown::gitbook:
-    split_by: rmd
-    df_print: kable
-    toc_depth: 1
-    #self_contained: true
-    output_dir: _book
 ---

### 2019-01-15 107-1/socpsy_plot/gghighlight-issue.R
up

@@ -2,7 +2,9 @@ library(ggplot2)
 library(gghighlight)
 library(dplyr)
 
-poplev_helping <- readr::read_csv("poplev-helping2.csv") %>% 
+fp <- url('https://raw.githubusercontent.com/liao961120/local_depend/master/107-1/socpsy_plot/poplev-helping2.csv')
+
+poplev_helping <- readr::read_csv(fp) %>% 
   tidyr::gather("types", "y", -pop_level)
 
 poplev_helping[seq(from=1, to=15, by=3),]

### 2019-01-15 Ubuntu_16.04_setup/mybashrc.sh

@@ -51,3 +51,6 @@ cp -r ~/bin/* ~/local_depend/Ubuntu_16.04_setup/sh_program_bak/
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
 tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
 alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
+
+# added by travis gem
+[ -f /home/liao/.travis/travis.sh ] && source /home/liao/.travis/travis.sh

### 2019-07-22 Ubuntu_setup/mylinux.Rmd
update

--- 2018-12-01 Ubuntu_16.04_setup/mylinux.Rmd
@@
 subtitle: "A Quick Reference"
-author: "[Yongfu Liao](https://liao961120.github.io/)"
+author: "Yongfu Liao"
 date: "`r format(Sys.Date(), '%B %d, %Y')`"
@@
 output:
+  rmdformats::readthedown:
+    use_bookdown: true
   bookdown::html_document2:
@@
 ```{bash, preprocess-dir, include=FALSE}
+[[ -d ~/bash_pract ]] || mkdir ~/bash_pract
 cd ~/bash_pract && rm -r dir

### 2019-07-22 Ubuntu_setup/mybashrc.sh

@@ -7,14 +7,21 @@ alias mypython='code ~/private_repo/python/python_notes.Rmd'
 alias new_rmd='~/bin/append_head_rmd'
 alias R='R --no-save -q'
 alias r="radian"
-alias pyvir='source bin/activate'
+#alias pyvir='cd ~/jupyter; source bin/activate; cd -'
 alias xampp='sudo /opt/lampp/manager-linux-x64.run'
-alias serve='chromium-browser "http://127.0.0.1:4000"; bundle exec jekyll serve --drafts'
+alias serve_j='chromium-browser "http://127.0.0.1:4000"; bundle exec jekyll serve --drafts'
+alias ipython='ipython --no-autoindent'
+alias serve='chromium-browser "http://0.0.0.0:8000/"; python3 -m http.server'
 alias micro='~/micro'
 alias bitly='chromium-browser --incognito https://bitly.com &'
 alias pdf_resize='java -jar Desktop/briss-0.9/briss-0.9.jar'
 alias gephi='~/Desktop/SNA/gephi-0.9.2/bin/gephi'
-
+alias lopessh='ssh yongfu@140.112.147.125'
+alias pandoc='/usr/lib/rstudio/bin/pandoc/pandoc'
+alias loderunner='bash ~/Desktop/LODERUNN/LODERUNN'
+alias slp='systemctl suspend'
+alias psudow='python3 ~/Desktop/psudoword_gen.py'
+alias open='xdg-open'
 
 export RSTUDIO_PANDOC=/usr/lib/rstudio/bin/pandoc
 PS1="\[\033[1;32m\]\u@nb:\[\033[1;34m\]\w\[\033[00m\]$ "
@@ -22,6 +29,8 @@ export PS1
 export PATH=~/bin:"$PATH"  #Add ~/bin to PATH so custom shell programs can be found
 export GEM_HOME=$HOME/gems
 export PATH=$HOME/gems/bin:$PATH
+export FLASK_APP=application.py
+export FLASK_DEBUG=1
 
 
 
@@ -50,6 +59,27 @@ function timer(){
     echo -ne "$(date -u --date @$((`date +%s` - $date1)) +%H:%M:%S)\r"; 
     sleep 0.1
    done
+}
+:
+
+# pyvir
+function pyvir(){
+  if [[ $1 == '3.6' ]]; then
+    dir='/home/liao/jupyter'
+  else
[…]

### 2019-07-22 Ubuntu_setup/mybashrc.sh
update .bashrc

@@ -84,11 +84,11 @@ function briss(){
 
 
 # Backup ~/bin (Custom shell programs)
-cp -r ~/bin/* ~/local_depend/Ubuntu_16.04_setup/sh_program_bak/
+cp -r ~/bin/* ~/local_depend/Ubuntu_setup/sh_program_bak/
 
 # Backup self-defined cmd in git repo (prt lines after 'line 120')
-tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc.sh
-alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_16.04_setup/mybashrc_man.sh'
+tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_setup/mybashrc.sh
+alias bak_rc='tail -n +120  ~/.bashrc > ~/local_depend/Ubuntu_setup/mybashrc_man.sh; echo -e "\n\n\n#### Backup Time\t$(date) ####" >> ~/local_depend/Ubuntu_setup/mybashrc_man.sh'
 
 # added by travis gem
 [ -f /home/liao/.travis/travis.sh ] && source /home/liao/.travis/travis.sh
